### 2014-05-20 code/fig/quick_summary.tex
Initial push of the BIZ code. Taking all of the code from the icse cluster, almost all of which is currently checked into the svn repository (what isn't checked in, I will check in soon). Not checking in the top-level doc/ and fig/ directories from the svn repository, as these were specific to the BIZ paper.

\documentclass[12pt]{article}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{graphicx}

\newcommand{\PstarB}{\mathcal{P}^*_B}
\newcommand{\E}{E}
\newcommand{\sigmacom}{\sigma}
\newcommand{\cmax}{1-(P^*)^{\frac1{k-1}}}
\newcommand{\PZ}{\mbox{PZ}}
\begin{document}

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{QUICK-SC-Nk} 
    \includegraphics[width=2.9in]{QUICK-SC-PCS}
    \caption{PCS and $\E[N]/k$ as a function of the number of alternatives $k$ under the slippage configuration (SC),
    $\mu=[\delta,0,\ldots,0]$, with $P^*=0.9$, $\sigmacom=10$,
    $\delta=1$.
    BIZ uses $c=\cmax$ (eliminate aggressively).  
    BKS is the $\PstarB$ procedure.
    \label{fig:SC}}
  \end{figure}

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{QUICK-MDM-Nk} 
    \includegraphics[width=2.9in]{QUICK-MDM-PCS}
    \caption{PCS and $\E[N]/k$ as a function of the number of alternatives $k$ under the monotone
    decreasing means (MDM) configuration, $\mu=[-\delta,-2\delta,\ldots,-k\delta]$,
    with $P^*=0.9$, $\sigmacom=10$, $\delta=1$.  
    \label{fig:MDM}}
  \end{figure}

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{QUICK-RPI-Nk}
    \includegraphics[width=2.9in]{QUICK-RPI-PCSk}
    \caption{Random Problem Instances:
    $P^* = 0.8$, $\sigma^2=100$, $\delta=0.5$.  Each set of sampling means $\mu$ was generated randomly from an independent normal prior and then 
    adjusted to lie in $\PZ(\delta)$.
    \label{fig:RPI}}
  \end{figure}

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{QUICK-SCINC-Nk} 
    \includegraphics[width=2.9in]{QUICK-SCINC-PCS}
    \caption{SC Increasing.  
    PCS and $\E[N]/k$ as a function of the number of alternatives $k$ under the slippage configuration (SC),
    $\mu=[\delta,0,\ldots,0]$, with $P^*=0.9$, $\sigmacom=10$,
    $\delta=1$.
    BIZ uses $c=\cmax$ (eliminate aggressively).  
    \label{fig:SCINC}}
  \end{figure}

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{QUICK-SCDEC-Nk} 
    \includegraphics[width=2.9in]{QUICK-SCDEC-PCS}
    \caption{SC Decreasing.  
    PCS and $\E[N]/k$ as a function of the number of alternatives $k$ under the slippage configuration (SC),
    $\mu=[\delta,0,\ldots,0]$, with $P^*=0.9$, $\sigmacom=10$,
    $\delta=1$.
    BIZ uses $c=\cmax$ (eliminate aggressively).  
    \label{fig:SCDEC}}
  \end{figure}

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{QUICK-MDMINC-Nk} 
    \includegraphics[width=2.9in]{QUICK-MDMINC-PCS}
    \caption{MDM Increasing.  
    PCS and $\E[N]/k$ as a function of the number of alternatives $k$ under the slippage configuration (MDM),
    $\mu=[\delta,0,\ldots,0]$, with $P^*=0.9$, $\sigmacom=10$,
    $\delta=1$.
    BIZ uses $c=\cmax$ (eliminate aggressively).  
    \label{fig:MDMINC}}
  \end{figure}

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{QUICK-MDMDEC-Nk} 
    \includegraphics[width=2.9in]{QUICK-MDMDEC-PCS}
    \caption{MDM Decreasing.  
    PCS and $\E[N]/k$ as a function of the number of alternatives $k$ under the slippage configuration (MDM),
    $\mu=[\delta,0,\ldots,0]$, with $P^*=0.9$, $\sigmacom=10$,
    $\delta=1$.
    BIZ uses $c=\cmax$ (eliminate aggressively).  
    \label{fig:MDMDEC}}
  \end{figure}

  \begin{figure}[tb]
    \center
    \includegraphics[width=4in]{QUICK-ImprovementFactor}
    \caption{The multiplicative improvement of BIZ over Paulson's procedure, expressed as the expected number of samples
    taken under Paulson's procedure, divided by
    the expected number of samples taken under BIZ.  This improvement is plotted for the slippage configuration (SC),
    the monotone decreasing means configurations (MDM), and random problem instances (RPI), all as a function of the number of alternatives $k$.
    % For the largest problems, BIZ requires between 10 and 15 times fewer samples than Paulson's procedure.
    \label{fig:improvement}}
  \end{figure}

\end{document}

### 2014-05-20 code/cpp/BIZ.cpp

@@ -1,0 +1,247 @@
+#include "BIZ.h"
+#include <strings.h>
+
+/*
+ * We can define the following C preprocessor labels in the Makefile, or hardcoded here:
+ * DEBUG, OUTPUT_FOR_ANIMATION, OPTIMIZE:
+ * 	DEBUG turns on debugging output.
+ * 	OPTIMIZE is optional, and does something tricky to make the computation of BIZ faster.
+ * 	OUTPUT_FOR_ANIMATION is used to create output for a single run of BIZ
+ * 		that can be used to create an animation.  Don't simulataneously turn on
+ * 		OUTPUT_FOR_ANIMATION and OPTIMIZE  
+ */
+
+SampleOnceRet_t SampleOnceBIZ(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma, double logElimThresh);
+
+SampleOnceRet_t BIZ(StochasticLib2 &sto, problem_t problem, algArgs_t args) {
+  for(int x=1; x<problem.k; x++) {
+    if (problem.sigma[x] != problem.sigma[0]) {
+      fprintf(stderr, "SampleOnceBIZ requires the sampling variance to be the same across alternatives\n.");
+      exit(-1);
+    }
+  }
+  double logElimThresh = log1p(-pow(problem.pstar,1.0/(problem.k-1)));
+  return SampleOnceBIZ(sto, problem.k, problem.pstar, problem.delta, problem.theta, problem.sigma[0], logElimThresh);
+}
+
+SampleOnceRet_t SampleOnceBIZ(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma, double logElimThresh) {
+  int x; // generic counter
+
+  assert(delta>0);
+  assert(k>0);
+  assert(sigma>=0);
+  assert(k==1 || 1-exp(logElimThresh) >= pow(pstar,1.0/(k-1)));
+
+  // If this condition is not met, then the randomized policy that does no
+  // measurement is acceptable.  We do not treat this case because it isn't
+  // particularly interesting.
+  assert(pstar > (double)1/k);
+
+  // Create a vector of log-likelihoods. If a log-likelihood is -INF, then this indicates that the alternative has been
+  // eliminated.
+  double logq[k];
+  for (x=0; x<k; logq[x++]=0);
+#ifdef OUTPUT_FOR_ANIMATION
+  double Y[k];
[…]

### 2014-05-20 code/cpp/BIZ.h

@@ -1,0 +1,24 @@
+/* BIZ with maximum elimination, with common known variance. */
+
+#ifndef _BIZ_H_
+#define _BIZ_H_
+
+#include "common.h"
+#include <string.h>
+
+// void name_BIZ();
+// void name_BIZHET();
+// void name_BIZUNK();
+
+SampleOnceRet_t BIZ(StochasticLib2 &sto, problem_t problem, algArgs_t args); // common known variance
+// Algorithm accepts no arguments
+
+SampleOnceRet_t BIZHET(StochasticLib2 &sto, problem_t problem, algArgs_t args); // known and possibly heterogeneous variance
+// Algorithm accepts no arguments
+
+SampleOnceRet_t BIZUNK(StochasticLib2 &sto, problem_t problem, algArgs_t args); // unknown and possibly heterogeneous variance
+int BIZUNK_ParseArgs(algArgs_t *args, int num_args, char *args_str[]);
+void BIZUNK_FreeArgs(void *args);
+void BIZUNK_PrintArgs(void *args);
+
+#endif /* _BIZ_H_ */

### 2014-05-20 code/cpp/BIZHET.cpp

@@ -1,0 +1,217 @@
+/*
+ * The BIZ policy with known, heterogeneous sampling variances.
+ */
+
+#include "BIZ.h"
+#include <strings.h>
+
+// #define DEBUG
+
+/*
+ * Structure for storing statistics of a logq vector.
+ */
+typedef struct logqstats {
+  double sumq;
+  double best_logq;
+  int best_x;
+  double worst_logq;
+  int worst_x;
+} logqstats_t;
+
+logqstats_t UpdateLogQ_Known(int k, double delta, unsigned int *n, double *mean, double *var, double *logq);
+
+SampleOnceRet_t SampleOnceBIZHET(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma[], double logElimThresh, int n0, int batchsize);
+
+SampleOnceRet_t BIZHET(StochasticLib2 &sto, problem_t problem, algArgs_t args) {
+  double logElimThresh = log1p(-pow(problem.pstar,1.0/(problem.k-1)));
+  double n0 = 0;
+  int batchsize = 1;
+  return SampleOnceBIZHET(sto, problem.k, problem.pstar, problem.delta, problem.theta, problem.sigma, logElimThresh, n0, batchsize);
+}
+
+SampleOnceRet_t SampleOnceBIZHET(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma[], double logElimThresh, int n0, int batchsize) {
+  int x; // generic counter
+  logqstats_t logqstats;
+
+  assert(delta>0);
+  assert(k>0);
+  for (x=0; x<k; x++)
+    assert(sigma[x]>=0);
+  assert(k==1 || 1-exp(logElimThresh) >= pow(pstar,1.0/(k-1)));
+  assert(batchsize>=1);
+
+  SampleOnceRet_t ret;
+  ret.nSamplesPerAlt = 0;
+  ret.nSamples = 0;
+  ret.nStages = 0;
+
+  // If this condition is not met, then the randomized policy that does no
+  // measurement is acceptable.  We do not treat this case because it isn't
+  // particularly interesting.
+  assert(pstar > (double)1/k);
+
+  double logpstar = log(pstar); // Precompute the log of pstar.
+
+  // Create three vectors.  
+  // n[x] contains the number of samples taken from alternative x.  
+  // mean[x] contains the mean of all the observations from alternative x.  
+  // logq[x] is the log of q_{tx}(A).  
+  // var[x] contains the sampling variances, and does not change.  
[…]

### 2014-05-20 code/cpp/BIZUNK.cpp

@@ -1,0 +1,858 @@
+/*
+ * The BIZ policy with unknown and possibly heterogeneous sampling variances.
+ */
+
+#include "BIZ.h"
+#include <strings.h>
+
+// #define DEBUG
+
+/*
+ * Structure for storing statistics of a logq vector.
+ */
+typedef struct logqstats {
+  double sumq;
+  double best_logq;
+  int best_x;
+  double worst_logq;
+  int worst_x;
+} logqstats_t;
+
+logqstats_t UpdateLogQ_Unknown(int k, double delta, unsigned int *n, double *mean, double *M2, double *logq);
+
+SampleOnceRet_t SampleOnceBIZUNK1(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma[], double logElimThresh, int n0, int batchsize);
+SampleOnceRet_t SampleOnceBIZUNK2(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma[], double logElimThresh, int n0, int batchsize);
+SampleOnceRet_t SampleOnceBIZUNK3(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma[], double logElimThresh, int n0, int batchsize);
+SampleOnceRet_t SampleOnceBIZUNK4(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma[], double logElimThresh, int n0, int batchsize);
+
+/* This is the interface to this code called by outside code, as implemented in BIZ.h. */
+SampleOnceRet_t BIZUNK(StochasticLib2 &sto, problem_t problem, algArgs_t args) {
+  double logElimThresh = log1p(-pow(problem.pstar,1.0/(problem.k-1)));
+  int n0 = *(int *)(args.args);
+  int batchsize = 1;
+  return SampleOnceBIZUNK4(sto, problem.k, problem.pstar, problem.delta, problem.theta, problem.sigma, logElimThresh, n0, batchsize);
+}
+
+
+
+/* 
+ * The version of BIZUNK that I implemented first.  
+ */
+SampleOnceRet_t SampleOnceBIZUNK1(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma[], double logElimThresh, int n0, int batchsize) {
+  int x; // generic counter
+
+  assert(delta>0);
+  assert(k>0);
+  for (x=0; x<k; x++)
[…]

### 2014-05-20 code/cpp/BKS.cpp

@@ -1,0 +1,94 @@
+#include "BKS.h"
+
+/*
+ * Assumes that the maximal element is unique, and has index 0.  Note that we
+ * pass the StochasticLib by reference, rather than by value.  This allows the
+ * seed to get updated by the random numbers we generate.
+ */ 
+
+SampleOnceRet_t SampleOnceBKS(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma);
+SampleOnceRet_t BKS(StochasticLib2 &sto, problem_t problem, algArgs_t args) {
+  for(int x=1; x<problem.k; x++) {
+    if (problem.sigma[x] != problem.sigma[0]) {
+      fprintf(stderr, "SampleOnceBKS requires the sampling variance to be the same across alternatives\n.");
+      exit(-1);
+    }
+  }
+  return SampleOnceBKS(sto, problem.k, problem.pstar, problem.delta, problem.theta, problem.sigma[0]);
+}
+
+
+SampleOnceRet_t SampleOnceBKS(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma) {
+  int x; // generic counter
+
+  assert(delta>0);
+  assert(k>0);
+  assert(sigma>=0);
+
+  // Check that element 0 is the unique argmax, and that it is delta better than the others.
+  for (x=1; x<k; x++)
+    assert(theta[0]-delta >= theta[x]);
+
+  // If this condition is not met, then the randomized policy that does no
+  // measurement is acceptible.  We do not treat this case because it isn't
+  // particularly interesting.
+  assert(pstar > (double)1/k);
+
+  // Create a vector of log-likelihoods.
+  double logq[k];
+  for (x=0; x<k; logq[x++]=0);
+
+  // precompute the coefficient that multiplies the observation z when
+  // calculating logq.  Also precompute the log of pstar.
+  double c = delta / (sigma*sigma); 
+  double logpstar = log(pstar);
+
+
+  SampleOnceRet_t ret;
+  ret.nSamplesPerAlt = 0;
+  ret.nStages = 0;
+  while(1) {
+    // Generate the next samples and add them to logq
+    ret.nSamplesPerAlt++;
+    ret.nStages++;
+    for (x=0; x<k; x++) {
+      double z = theta[x] + sto.Normal(0,sigma);
+      logq[x] += c*z;
+    }
+
+    // Renormalize logq probabilities so that exp(logq) sums to 1.  Also figure
[…]

### 2014-05-20 code/cpp/BKS.h

@@ -1,0 +1,10 @@
+/* Bechhofer-Kiefer-Sobel P-star-B policy */
+
+#ifndef _BKS_H_
+#define _BKS_H_
+
+#include "common.h"
+
+SampleOnceRet_t BKS(StochasticLib2 &sto, problem_t problem, algArgs_t args);
+
+#endif /* _BKS_H_ */

### 2014-05-20 code/cpp/KN.cpp

@@ -1,0 +1,158 @@
+#include "KN.h"
+
+SampleOnceRet_t SampleOnceKN(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma);
+SampleOnceRet_t KN(StochasticLib2 &sto, problem_t problem, algArgs_t args) {
+  for(int x=1; x<problem.k; x++) {
+    if (problem.sigma[x] != problem.sigma[0]) {
+      fprintf(stderr, "SampleOnceKN requires the sampling variance to be the same across alternatives\n.");
+      exit(-1);
+    }
+  }
+  return SampleOnceKN(sto, problem.k, problem.pstar, problem.delta, problem.theta, problem.sigma[0]);
+}
+
+
+/*
+ * Sample according to the KN policy.  Assumes common known variance.
+ */ 
+SampleOnceRet_t SampleOnceKN(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma) {
+  int x; // generic counter
+
+  assert(delta>0);
+  assert(k>0);
+  assert(sigma>=0);
+
+  // If this condition is not met, then the randomized policy that does no
+  // measurement is acceptible.  We do not treat this case because it isn't
+  // particularly interesting.
+  assert(pstar > (double)1/k);
+
+  SampleOnceRet_t ret;
+
+  int r = 0; // number of rounds
+  ret.nSamples = 0; // total number of samples.
+  ret.nStages = 0;
+  double sum[k];
+  for (int x=0;x<k;sum[x++]=0);
+
+  // Constants
+  int n0 = 1;
+  //double eta = -1 * log(2.0 - 2.0*pow(1-pstar,1.0/(k-1)));
+  double alpha = 1-pstar;
+  double eta = log((k-1)/(2.0*alpha));
+  double h2 = 2*eta;
+  double sigma2 = sigma*sigma; // supposed to be sample variance
+  double c1 = h2/(delta*delta);
+
+  // printf("n0=%d eta=%f h2=%f sigma2=%f c1=%f\n", n0,eta,h2,sigma2,c1);
+  
+  // Run a first stage
+  for(r=0;r<n0;r++) {
+    ret.nStages++;
+    for (x=0; x<k; x++) {
+      double z = theta[x] + sto.Normal(0,sigma);
+      sum[x] += z;
+      ret.nSamples++;
+    }
+  }
+  
+  // Sequential Screening
+  bool in[k]; // flags that are set when we are still simulating
+  for (int x=0;x<k;in[x++]=true);
[…]

### 2014-05-20 code/cpp/KN.h

@@ -1,0 +1,15 @@
+#ifndef _KN_H_
+#define _KN_H_
+
+#include "common.h"
+
+SampleOnceRet_t KN(StochasticLib2 &sto, problem_t problem, algArgs_t args); // known, common variance
+SampleOnceRet_t KNHET(StochasticLib2 &sto, problem_t problem, algArgs_t args); // known, heterogeneous variance
+SampleOnceRet_t KNUNK(StochasticLib2 &sto, problem_t problem, algArgs_t args); // unknown and possibly heterogeneous variance
+
+SampleOnceRet_t SampleOnceKNHelper(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma[], bool varknown, int n0);
+
+int KNUNK_ParseArgs(algArgs_t *args, int num_args, char *args_str[]);
+void KNUNK_FreeArgs(void *args);
+void KNUNK_PrintArgs(void *args);
+#endif /* _KN_H_ */

### 2014-05-20 code/cpp/KNHET.cpp

@@ -1,0 +1,150 @@
+#include "KN.h"
+
+SampleOnceRet_t KNHET(StochasticLib2 &sto, problem_t problem, algArgs_t args) {
+  int n0 = 2;
+  bool varknown = 1;
+  return SampleOnceKNHelper(sto, problem.k, problem.pstar, problem.delta, problem.theta, problem.sigma, varknown, n0);
+}
+
+
+/*
+ * Sample according to the KN policy, with heterogeneous sampling variance.
+ * Set varknown to TRUE for known sampling variance, and FALSE for unknown.
+ */ 
+SampleOnceRet_t SampleOnceKNHelper(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma[], bool varknown, int n0) {
+  int x; // generic counter
+
+  assert(delta>0);
+  assert(k>0);
+
+  // If this condition is not met, then the randomized policy that does no
+  // measurement is acceptible.  We do not treat this case because it isn't
+  // particularly interesting.
+  assert(pstar > (double)1/k);
+
+  SampleOnceRet_t ret;
+
+  int r = 0; // number of rounds
+  ret.nSamples = 0; // total number of samples.
+  ret.nStages = 0;
+  double sum[k], varhat[k];
+  for (int x=0;x<k;sum[x++]=0);
+
+  // Constants
+  double eta, h2;
+  double alpha = 1-pstar;
+  if (varknown) { // Known variance
+    eta = log((k-1)/(2.0*alpha));
+    h2 = 2*eta;
+  } else { // Unknown variance
+    eta = (pow(2.0*alpha/(k-1),-2.0/(n0-1))-1)/2.0;
+    h2 = 2*eta*(n0-1);
+  }
+  double c1 = h2/(delta*delta);
+
+  // printf("n0=%d eta=%f h2=%f c1=%f\n", n0,eta,h2,c1);
+  
+  // Run a first stage
+  ret.nStages += n0;
+  for (x=0; x<k; x++) {
+    // mean and M2 are for calculating the sample variance.
+    // The algorithm for updating the mean and M2 came from Wikipedia,
+    // http://en.wikipedia.org/wiki/Algorithms_for_calculating_variance 
+    // who cites Knuth, and Knuth in turn apparently cites Welford.
+    // The sample variance is given by M2 / (ret.nSamples - 1);
+    double mean = 0; // current sample mean.
+    double M2 = 0; // sum of the square differences from the current sample mean.
+    for(r=0;r<n0;r++) {
[…]

### 2014-05-20 code/cpp/KNUNK.cpp

@@ -1,0 +1,47 @@
+#include "KN.h"
+
+SampleOnceRet_t KNUNK(StochasticLib2 &sto, problem_t problem, algArgs_t args) {
+  int n0 = *(int *)(args.args);
+  return SampleOnceKNHelper(sto, problem.k, problem.pstar, problem.delta, problem.theta, problem.sigma, 0, n0);
+}
+
+void KNUNK_FreeArgs(void *args) { free(args); }
+void KNUNK_PrintArgs(void *args) { 
+  int n0 = *(int *)(args);
+  printf("# KNUNK n0 = %d\n", n0);
+}
+
+
+int KNUNK_ParseArgs(algArgs_t *args, int num_args, char *args_str[]) {
+  int n0;
+
+
+  if (num_args > 1) {
+    fprintf(stderr, "KNUNK requires at most 1 argument.\n");
+    return -1;
+  }
+
+  // Default value for n0 is 30
+  if (num_args == 0) 
+    n0 = 30;
+
+  if (num_args == 1) {
+    int ret = sscanf(args_str[0],"n0=%d", &n0);
+    if (ret != 1) {
+      fprintf(stderr, "Argument to KNUNK must be of the form \"n0=integer\".\n");
+      return -1;
+    }
+  }
+
+  args->args = malloc(sizeof(int));
+  if (args->args == NULL) {
+    perror("Out of memory");
+    return -1;
+  }
+  *(int *)(args->args) = n0;
+
+  args->print_args = &KNUNK_PrintArgs;
+  args->free_args = &KNUNK_FreeArgs;
+
+    return 0;
+}

### 2014-05-20 code/cpp/Paulson.cpp

@@ -1,0 +1,140 @@
+#include "Paulson.h"
+
+SampleOnceRet_t SampleOncePaulson(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma);
+SampleOnceRet_t Paulson(StochasticLib2 &sto, problem_t problem, algArgs_t args) {
+  for(int x=1; x<problem.k; x++) {
+    if (problem.sigma[x] != problem.sigma[0]) {
+      fprintf(stderr, "SampleOncePaulson requires the sampling variance to be the same across alternatives\n.");
+      exit(-1);
+    }
+  }
+  return SampleOncePaulson(sto, problem.k, problem.pstar, problem.delta, problem.theta, problem.sigma[0]);
+}
+
+
+/*
+ * Sample according to Paulson's procedure, as described in Paulson (1964).
+ *
+ * Paulson, E. (1964). A Sequential Procedure for Selecting the Population with the Largest Mean from k Normal
+ * Populations. The Annals of Mathematical Statistics, 35(1), 174-180.
+ *
+ * The procedure is also described in Kim & Nelson's chapter in the Simulation Handbook from 2006.
+ */ 
+SampleOnceRet_t SampleOncePaulson(StochasticLib2 &sto, int k, double pstar, double delta, double theta[], double sigma) {
+  int x; // generic counter
+
+  assert(delta>0);
+  assert(k>0);
+  assert(sigma>=0);
+
+  // If this condition is not met, then the randomized policy that does no
+  // measurement is acceptible.  We do not treat this case because it isn't
+  // particularly interesting.
+  assert(pstar > (double)1/k);
+
+  SampleOnceRet_t ret;
+
+  int r = 0; // number of rounds
+  ret.nSamples = 0;
+  ret.nStages = 0;
+  double sum[k];
+  for (int x=0;x<k;sum[x++]=0);
+
+  // Constants
+  double sigma2 = sigma*sigma;
+  double lambda = delta / 2; // use this, as recommended by Kim & Nelson 2001.  Paulson 1964 recommends delta/4.
+  double PICS = 1-pstar; 
+  double a = log((k-1)/PICS) * sigma2 / (delta - lambda);
+
+
+  //printf("a=%f lambda=%f delta=%f sigma2=%f\n", a,lambda,delta,sigma2);
+  
+  // Run a first stage of 1 measurement.
+  ret.nStages++;
+  for (x=0; x<k; x++) {
[…]

### 2014-05-20 code/cpp/Paulson.h

@@ -1,0 +1,9 @@
+#ifndef _PAULSON_H_
+#define _PAULSON_H_
+
+#include "common.h"
+
+SampleOnceRet_t Paulson(StochasticLib2 &sto, problem_t problem, algArgs_t args);
+
+
+#endif /* _PAULSON_H_ */

### 2014-05-20 code/cpp/Sep14.sh

@@ -1,0 +1,2 @@
+jsub -c "./experiments BIZUNK problems/RPI_PGS.dat 10000 > data/BIZUNK_RPI_PGS_final.txt" -q long
+jsub -c "./experiments KNUNK problems/RPI_PGS.dat 10000 > data/KNUNK_RPI_PGS_final.txt" -q long

### 2014-05-20 code/cpp/Sep6.sh

@@ -1,0 +1,26 @@
+# jsub -c "./experiments BIZUNK problems/SC.dat 10000 > data/BIZUNK_SC_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/MDM.dat 10000 > data/BIZUNK_MDM_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/RPI.dat 10000 > data/BIZUNK_RPI_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/SC_INC.dat 10000 > data/BIZUNK_SC_INC_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/SC_DEC.dat 10000 > data/BIZUNK_SC_DEC_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/MDM_INC.dat 10000 > data/BIZUNK_MDM_INC_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/MDM_DEC.dat 10000 > data/BIZUNK_MDM_DEC_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/RPI_hetero.dat 10000 > data/BIZUNK_RPI_hetero_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/SC_INCA.dat 10000 > data/BIZUNK_SC_INCA_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/SC_DECA.dat 10000 > data/BIZUNK_SC_DECA_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/MDM_INCA.dat 10000 > data/BIZUNK_MDM_INCA_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/MDM_DECA.dat 10000 > data/BIZUNK_MDM_DECA_final.txt" -q long
+jsub -c "./experiments BIZUNK problems/RPI_heteroA.dat 10000 > data/BIZUNK_RPI_heteroA_final.txt" -q long
+jsub -c "./experiments KNUNK problems/SC.dat 10000 > data/KNUNK_SC_final.txt" -q long
+jsub -c "./experiments KNUNK problems/MDM.dat 10000 > data/KNUNK_MDM_final.txt" -q long
+jsub -c "./experiments KNUNK problems/RPI.dat 10000 > data/KNUNK_RPI_final.txt" -q long
[…]

### 2014-05-20 code/cpp/common.h

@@ -1,0 +1,49 @@
+#ifndef _COMMON_H_
+#define _COMMON_H_
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <assert.h>
+#include <time.h>
+#include <math.h>
+#include "../stocc/stocc.h"
+
+// A ranking and selection problem.
+typedef struct problem {
+  int k;
+  double pstar;
+  double delta;
+  double *theta;
+  double *sigma;
+} problem_t;
+
+// Return types for information from a simulation.
+typedef struct SampleOnceRet {
+  int correctSelection; 
+  double nSamplesPerAlt; // This is N / k, where N is the number of samples.
+  double nSamples; // This is N, the number of samples.
+  int nStages;
+} SampleOnceRet_t;
+
+/* Arguments to an algorithm. */
+typedef void(*free_algArgs_t)(void *); // function type for freeing the void * stored in an algArgs_t.
+typedef void(*print_algArgs_t)(void *); // function type for printing the contents of the algArgs_t.
+typedef struct algArgs {
+  void *args; 			// flexible representation of arguments.  Created by the algorithm's parser.
+  print_algArgs_t print_args;	// prints the contents of this algArgs.
+  free_algArgs_t free_args; 	// function for freeing the space allocated to the 
+  				// void *args.  Set to NULL if there is no space allocated to args.
+} algArgs_t;
+
+/*
+ * Parser for algArgs_t for algorithms that take no arguments. 
+ */
+int NoArgs(algArgs_t *args, int num_args, char *args_str[]);
+
+/* Definition of an algorithm. */
+typedef SampleOnceRet_t(*algorithm_t)(StochasticLib2 &sto, problem_t problem, algArgs_t args);
+
+/* Returns a 1 if the passed selection x is correct.  Any alternative within delta of the best is considered correct. */  
+int CorrectSelection(int x, int k, double theta[], double delta);
+
+#endif /* _COMMON_H_ */

### 2014-05-20 code/cpp/experiments.cpp

@@ -1,0 +1,223 @@
+/*
+ * This code runs a procedure against all of the problems in a data file.
+ */
+
+#include "common.h"
+#include "BKS.h"
+#include "BIZ.h"
+#include "KN.h"
+#include "Paulson.h"
+#include <strings.h>
+#include <stdio.h>
+#include <fcntl.h>
+#include <time.h>
+
+// define this to use the same seed every time
+#define USE_FIXED_SEED
+
+
+typedef struct SampleManyRet {
+  int nRuns;
+  int nCorrect; // numer of correct selections in the run.
+  double avgNk; // average of the number of samples per alternative, N/k
+  double avgNksq; // the average of (N/k)^2
+  double avgStages; // average of the number of stages.
+  double avgStagesSq; // average of the number of stages squared.
+  // composite estimates produced from raw stats above.
+  double estPCS; // estimate of PCS
+  double stdPCS; // stderr of estimate of PCS
+  double stdNk; // stderr of estimate of N/k.  The estimate of N/k is avgNk.
+  double stdStages; // stderr of estimate of number of stages.  The estimate is avgStages;
+} SampleManyRet_t;
+
+void RunProblemsFromFile(algorithm_t algorithm, char *filename, int nreps, algArgs_t args);
+void RunProblem(algorithm_t algorithm, problem_t problem, int nreps, algArgs_t args);
+void usage();
+
+void usage() {
+  fprintf(stderr, "usage: experiments {BIZ|BIZHET|BIZUNK|KN|KNHET|KNUNK|BKS|Paulson} datafile num_reps [n0=value]\n");
+  fprintf(stderr, "       The optional n0 argument is accepted only by BIZUNK and KNUNK.\n");
+
+  // This is a more general method for accepting arguments, which is a special case of the one described above.
+  /* 
+  fprintf(stderr, "usage: experiments {BIZ|BIZHET|BIZUNK|KN|KNHET|KNUNK|BKS|Paulson} datafile num_reps "
+  "[key1=value [key2=value [...]]]\n");
+  fprintf(stderr, 
+  "The optional key,value pairs are passed to the individual algorithms,\n"
+  "which deal with them in an algorithm specific way.  Currently the only one\n"
[…]

### 2014-05-20 code/cpp/make_experiments.pl

@@ -1,0 +1,188 @@
+#!/usr/bin/perl -w
+
+# Creates the file experiments.mk, which contains targets for making all of the data output files. 
+
+
+@nRuns = ("500", "10000" );
+@HomoAlgorithms = ( "BIZ", "KN", "BKS", "Paulson");
+@HeteroAlgorithms = ( "BIZHET", "KNHET");
+@UnkAlgorithms = ( "BIZUNK", "KNUNK");
+@HomoProblems = ("SC", "MDM", "RPI");
+@HeteroProblems = ("SC_INC", "SC_DEC", "MDM_INC", "MDM_DEC", "RPI_hetero", "SC_INCA", "SC_DECA", "MDM_INCA", "MDM_DECA", "RPI_heteroA");
+@UnkProblems = (@HomoProblems, @HeteroProblems);
+
+@PgsAlgorithms = ("BIZ");
+@PgsProblems = ("PGS3", "PGS10", "PGS100", "PGS32", "RPI_PGS");
+
+
+# Common variance experiments:
+# BIZ, KN, BKS, Paulson against SC, MDM, RPI.
+# In quick, final, and proof versions.
+# 4*3*2=24 experiments
+#
+foreach $alg (@HomoAlgorithms) {
+  foreach $prob (@HomoProblems) {
+    foreach $run (@nRuns) {
+      $filename = sprintf("%s_%s_%s.txt", $alg, $prob, $run == 500 ? "quick" : "final");
+      print("data/$filename: experiments $alg.cpp problems/$prob.dat\n");
+      print("\t./experiments $alg problems/$prob.dat $run > data/$filename\n");
+      print("\n");
+    }
+  }
+}
+
+#
+# Heterogeneous known variance experiments:
+# BIZHET, KNHET against 
+# SC_INC, SC_DEC, MDM_INC, MDM_DEC, RPI_hetero,
+# SC_INCA, SC_DECA, MDM_INCA, MDM_DECA, RPI_heteroA.
+# In both quick and final versions.
+# 2*5*2=20 experiments
+#
+foreach $alg (@HeteroAlgorithms) {
+  foreach $prob (@HeteroProblems) {
+    foreach $run (@nRuns) {
+      $filename = sprintf("%s_%s_%s.txt", $alg, $prob, $run == 500 ? "quick" : "final");
+      print("data/$filename: experiments $alg.cpp problems/$prob.dat\n");
+      print("\t./experiments $alg problems/$prob.dat $run > data/$filename\n");
+      print("\n");
+    }
+  }
[…]

### 2014-05-20 code/cpp/paper_experiments.sh

@@ -1,0 +1,69 @@
+make really_clean
+make
+# store the current state of the svn repository into the directory
+svn info > paper_data/svn_info.txt
+svn status > paper_data/svn_status.txt
+jsub -c "./experiments BIZ problems/SC.dat 10000 > paper_data/BIZ_SC_final.txt" -q long
+jsub -c "./experiments BIZ problems/MDM.dat 10000 > paper_data/BIZ_MDM_final.txt" -q long
+jsub -c "./experiments BIZ problems/RPI.dat 10000 > paper_data/BIZ_RPI_final.txt" -q long
+jsub -c "./experiments KN problems/SC.dat 10000 > paper_data/KN_SC_final.txt" -q long
+jsub -c "./experiments KN problems/MDM.dat 10000 > paper_data/KN_MDM_final.txt" -q long
+jsub -c "./experiments KN problems/RPI.dat 10000 > paper_data/KN_RPI_final.txt" -q long
+jsub -c "./experiments BKS problems/SC.dat 10000 > paper_data/BKS_SC_final.txt" -q long
+jsub -c "./experiments BKS problems/MDM.dat 10000 > paper_data/BKS_MDM_final.txt" -q long
+jsub -c "./experiments BKS problems/RPI.dat 10000 > paper_data/BKS_RPI_final.txt" -q long
+jsub -c "./experiments Paulson problems/SC.dat 10000 > paper_data/Paulson_SC_final.txt" -q long
+jsub -c "./experiments Paulson problems/MDM.dat 10000 > paper_data/Paulson_MDM_final.txt" -q long
+jsub -c "./experiments Paulson problems/RPI.dat 10000 > paper_data/Paulson_RPI_final.txt" -q long
+jsub -c "./experiments BIZHET problems/SC_INC.dat 10000 > paper_data/BIZHET_SC_INC_final.txt" -q long
+jsub -c "./experiments BIZHET problems/SC_DEC.dat 10000 > paper_data/BIZHET_SC_DEC_final.txt" -q long
+jsub -c "./experiments BIZHET problems/MDM_INC.dat 10000 > paper_data/BIZHET_MDM_INC_final.txt" -q long
+jsub -c "./experiments BIZHET problems/MDM_DEC.dat 10000 > paper_data/BIZHET_MDM_DEC_final.txt" -q long
[…]

### 2014-05-20 code/cpp/read_problems.cpp

@@ -1,0 +1,80 @@
+/*
+ * This code reads in a data file containing sets of problems and prints them
+ * in human readable form.
+ */
+
+#include "common.h"
+#include <strings.h>
+#include <stdio.h>
+#include <fcntl.h>
+
+void usage();
+
+void usage() {
+  fprintf(stderr,"usage: read_problems filename\n");
+  exit(-1);
+}
+
+int read_problems(char *filename);
+
+int main(int argc, char *argv[]) {
+  if (argc != 2)
+    usage();
+  read_problems(argv[1]);
+}
+
+int read_problems(char *filename) {
+  int nProblems;
+
+   FILE *file = fopen(filename,"r");
+   if (file == NULL) { fprintf(stderr,"could not open %s", filename); exit(-1); }
+
+   // The first entry in the file is the number of problems.
+   if (fread(&nProblems,sizeof(int),1,file) < 1) { fprintf(stderr,"Error reading from %s", filename); exit(-1); }
+   if (nProblems > 10000) { fprintf(stderr,"Likely data corruption.  The number of problems is > 10000. Exiting."); exit(-1); }
+
+   printf("# %d problems\n", nProblems);
+
+   for (int n=0; n<nProblems; n++) {
+     printf("Problem %d\n", n+1);
+
+     // Read in each problem.  The first entry is the number of alternatives,
+     // the second entry is pstar, and the third entry is delta.
+     int k;
+     double delta, pstar;
+     if (fread(&k,sizeof(int),1,file) < 1) { fprintf(stderr,"Error reading from %s", filename); exit(-1); }
+     if (k > 10000000) {
+       fprintf(stderr,"Likely data corruption.  The number of problems is > 10000000. Exiting.");
+       exit(-1);
+     }
+     if (fread(&pstar,sizeof(pstar),1,file) < 1) { fprintf(stderr, "Error reading from %s", filename); exit(-1); }
+     if (pstar <= 0 or pstar >= 1) {
+       fprintf(stderr,"Likely data corruption.  pstar is not in the interval (0,1). Exiting.");
+       exit(-1);
+     }
+     if (fread(&delta,sizeof(delta),1,file) < 1) { fprintf(stderr,"Error reading from %s", filename); exit(-1); }
+     if (delta <= 0) {
+       fprintf(stderr,"Likely data corruption.  delta is <= 0. Exiting.");
+       exit(-1);
+     }
+
+     printf("delta=%f pstar=%f\n", delta, pstar);
[…]

### 2014-05-20 code/cpp/util.cpp

@@ -1,0 +1,38 @@
+#include "common.h"
+
+/* Returns a 1 if the passed selection x is correct.  Any alternative within delta of the best is considered correct. */  
+int CorrectSelection(int x, int k, double theta[], double delta) {
+  double max = theta[0];
+  //printf("theta[%d]=%.1f ", 0, theta[0]);
+  for (int i=1; i<k; i++) {
+    //printf("theta[%d]=%.1f ", i, theta[i]);
+    if (theta[i] > max)
+      max = theta[i];
+  }
+  //printf("x=%d\n", x);
+  if (theta[x] > max - delta)
+    return 1;
+  else
+    return 0;
+}
+
+/* Parser for the algorithm arguments if the algorithm takes no arguments. */
+int NoArgs(algArgs_t *args, int num_args, char *args_str[]) {
+  if (num_args > 0) {
+    fprintf(stderr, "This algorithm expects no arguments.\n");
+    return -1;
+  }
+  if (num_args < 0) {
+    fprintf(stderr, "Internal Error: args->n is less than 0\n");
+    return -1;
+  }
+
+  args->args = NULL;
+  args->free_args = NULL;
+  args->print_args = NULL;
+  return 0;
+}
+
+
+
+

### 2014-05-20 code/cpp/write_problems.cpp

@@ -1,0 +1,392 @@
+/*
+ * This code creates data files containing sets of problems.
+ */
+
+#include "common.h"
+#include <strings.h>
+#include <stdio.h>
+#include <fcntl.h>
+
+// define this to use the same seed every time
+#define USE_FIXED_SEED
+
+#define FILE_DIR "problems/"
+
+int write_SC(const char *filename, int maxk, double pstar, double delta, double sigma1, double sigma2); 
+int write_MDM(const char *filename, int maxk, double pstar, double delta, double sigma1, double sigma2);
+//int write_RPI(const char *filename, int maxk, double pstar, double delta, double sigma, double RPIsigma, int nProblems, int moveToPreferenceZone);
+int write_RPI(const char *filename, int maxk, double pstar, double delta, double lower_sigma, double upper_sigma, double RPIsigma, int nProblems, int moveToPreferenceZone);
+int write_SCvP(const char *filename, int k, double delta, double sigma1, double sigma2); 
+int write_PGS(const char *filename, int k, int m, double pstar, double delta, double sigma);
+int write_animation(const char *filename, int k, double pstar, double delta, double sigma);
+
+int main(int argc, char *argv[]) {
+
+  // Common-variance and heterogeneous-variance versions of SC and MDM.
+  // The heterogeneous variance versions have the standard deviation range
+  // between 10/2 and 10*2 (variance between 100/4 and 100*4).
+  int maxk = 16384;
+  double pstar = 0.9;
+  double delta = 1;
+  double sigma = 10;
+  write_SC(FILE_DIR "SC.dat", maxk, pstar, delta, sigma, sigma);
+  write_MDM(FILE_DIR "MDM.dat", maxk, pstar, delta, sigma, sigma);
+
+  write_SC(FILE_DIR "SC_INC.dat", maxk, pstar, delta, sigma/2, sigma*2);
+  write_SC(FILE_DIR "SC_DEC.dat", maxk, pstar, delta, sigma*2, sigma/2);
+  write_MDM(FILE_DIR "MDM_INC.dat", maxk, pstar, delta, sigma/2, sigma*2);
+  write_MDM(FILE_DIR "MDM_DEC.dat", maxk, pstar, delta, sigma*2, sigma/2);
+
[…]

### 2014-05-20 code/fig/combine.pl

@@ -1,0 +1,27 @@
+#!/usr/bin/perl -w
+use strict;
+
+# This perl script takes as input two files, both of which have the same number
+# of lines N, and outputs to stdout N lines, where each line n is created by
+# concatenating row n from file 1 with row n of file 2. 
+
+my $num_args = $#ARGV + 1;
+if ($num_args 	!= 2) {
+  die "usage: ./combine.pl file1 file2";
+}
+
+open FILE_A, $ARGV[0] or die $!;
+open FILE_B, $ARGV[1] or die $!;
+
+while (1) {
+  my $lineA = <FILE_A>;
+  my $lineB = <FILE_B>;
+
+  if (!$lineA && !$lineB) { last; }
+  if (!$lineA || !$lineB) { die "Files have different numbers of data rows."; }
+
+  chomp($lineA);
+  chomp($lineB);
+
+  print $lineA . " " . $lineB . "\n";
+}

### 2014-05-20 code/fig/custom_figures/AFOSR2013/animation/animation.R

@@ -1,0 +1,76 @@
+data <- read.csv("animation.txt",header=TRUE,skip=2)
+Y <- data[,4:7]
+q <- data[,8:11]
+lower <- data[,2]
+upper <- data[,3]
+
+# The code doesn't output the correct value for q[1,], i.e., the value of q at the initial time.
+q[1,] = q[1,] / sum(q[1,])
+
+Tmax = nrow(Y)
+Ymin = 1.1*min(Y[!is.na(Y)])
+Ymax = 1.1*max(Y[!is.na(Y)])
+
+my_col = c("red","blue","dark green","purple")
+
+
+
+# This makes a plot with the Y values on top and the q values on the bottom
+for (t in 1:Tmax) {
+
+  # For each alternative, count the number of observations up to the current time
+  # t, which will be less than t if Y has been eliminated.
+  n = rep(NA,4)
+  for (i in 1:4) {
+    tmp = Y[1:t,i]
+    tmp = tmp[!is.na(tmp)]
+    n[i] = length(tmp)
+  }
+
+  winner = which.max(n)
+
+  pdf(sprintf("pdf1/animation_%04d.pdf",t))
+  par(mfrow=c(2,1))
+
+  # Plot the Y values
+  plot(1:t, Y[1:t,winner], t="l", xlim=c(1,Tmax), ylim=c(Ymin,Ymax), xlab="t", ylab="Y(t,x)", cex.lab=1.5,cex.axis=1.5,lwd=3, col=my_col[winner],yaxt="n")
+  axis(2,at=c(0,500),cex.axis=1.5)
+  for (i in 1:4) {
+    lines(1:n[i], Y[1:n[i],i], col=my_col[i], lwd=3)
+  }
+
+  # Plot the q values
+  plot(1:t, q[1:t,winner], t="l", xlim=c(1,Tmax), ylim=c(0,1), xlab="t", ylab="q(t,x)", cex.lab=1.5, cex.axis=1.5, lwd=3, col=my_col[winner],yaxt="n")
+  axis(2,at=c(0,1),cex.axis=1.5)
+  for (i in 1:4) {
+    lines(1:n[i], q[1:n[i],i], col=my_col[i], lwd=3)
+  }
+  lines(1:t,upper[1:t], lwd=3)
+  lines(1:t,lower[1:t], lwd=3)
+  dev.off()
+}
+
+
+# This makes a plot with the Y values on top and the q values on the bottom
[…]

### 2014-05-20 code/fig/improvement.pl

@@ -1,0 +1,75 @@
+#!/usr/bin/perl -w
+use strict;
+
+# This perl script takes as input two files, such as KN_SC_final.txt and BIZ_SC_final.txt, each of which is assumed
+# to have the performance of a single policy on a fixed sequence of problems.  So row n in each file corresponds to the
+# same problem.  It outputs a file in which the record at line n corresponds to this same problem, and has the ratio of
+# the performance of the two 
+# 
+# Warning: this perl script is not very robust, and relies heavily on the particular file format used to create these
+# input text files.
+# example use: ./improvement.pl ../biz/data/Paulson_SC_final.txt ../biz/data/BIZ_SC_final.txt > post_processed_data/improvement_Paulson_BIZ_SC.txt
+
+my $num_args = $#ARGV + 1;
+if ($num_args 	!= 2) {
+  die "usage: ./improvement.pl file1 file2";
+}
+
+# If the files aren't present, print that they aren't there, and produce no
+# output, but don't report an error status because this makes it difficult to
+# use these within a Makefile --- we want to skip those files that aren't there.
+
+if (! -e $ARGV[0]) {
+  print STDERR "WARNING from improvement.pl: $ARGV[0] doesn't exist --- producing no output.\n";
+  exit;
+}
+if (! -e $ARGV[1]) {
+  print STDERR "WARNING from improvement.pl: $ARGV[1] doesn't exist --- producing no output.\n";
+  exit;
+}
+
+
+
+open FILE_A, $ARGV[0] or die $!;
+open FILE_B, $ARGV[1] or die $!;
+
+while (1) {
+  my $lineA = <FILE_A>;
+  my $lineB = <FILE_B>;
+
+  if (!$lineA && !$lineB) { last; }
+  if (!$lineA || !$lineB) { die "Files have different numbers of data rows."; }
+
+  while($lineA =~ /^#/) { $lineA = <FILE_A>; }
+  while($lineB =~ /^#/) { $lineB = <FILE_B>; }
+
+  if (!$lineA && !$lineB) { last; }
[…]

### 2014-05-20 code/fig/improvement_mk.pl

@@ -1,0 +1,40 @@
+#!/usr/bin/perl -w
+
+# Creates the file improvement.mk, which contains targets for making all of the data output files. 
+
+@nRuns = ("500", "10000" );
+@HomoProblems = ("SC", "MDM", "RPI");
+@HeteroProblems = ("SC_INC", "SC_DEC", "MDM_INC", "MDM_DEC", "RPI_hetero", "SC_INCA", "SC_DECA", "MDM_INCA", "MDM_DECA", "RPI_heteroA");
+@UnkProblems = (@HomoProblems, @HeteroProblems);
+
+# This directory contains all of the raw data
+$data = "../biz/data"; 
+
+
+
+#
+# improvement files.
+#
+foreach $run (@nRuns) {
+printf("improvement_%s:\n", $run == 500 ? "quick" : "final"); # These are the targets, one for quick, and one for final.
+foreach $prob (@HomoProblems) {
+    $KN = sprintf("KN_%s_%s.txt", $prob, $run == 500 ? "quick" : "final");
+    $BIZ = sprintf("BIZ_%s_%s.txt", $prob, $run == 500 ? "quick" : "final");
+    $out = sprintf("improvement_KN_BIZ_%s_%s.txt", $prob, $run == 500 ? "quick" : "final");
+    print("\t ./improvement.pl $data/$KN $data/$BIZ > post_processed_data/$out\n");
+}
+foreach $prob (@HeteroProblems) {
+    $KN = sprintf("KNHET_%s_%s.txt", $prob, $run == 500 ? "quick" : "final");
+    $BIZ = sprintf("BIZHET_%s_%s.txt", $prob, $run == 500 ? "quick" : "final");
+    $out = sprintf("improvement_KNHET_BIZHET_%s_%s.txt", $prob, $run == 500 ? "quick" : "final");
+    print("\t ./improvement.pl $data/$KN $data/$BIZ > post_processed_data/$out\n");
+}
+foreach $prob (@UnkProblems) {
+    $KN = sprintf("KNUNK_%s_%s.txt", $prob, $run == 500 ? "quick" : "final");
+    $BIZ = sprintf("BIZUNK_%s_%s.txt", $prob, $run == 500 ? "quick" : "final");
+    $out = sprintf("improvement_KNUNK_BIZUNK_%s_%s.txt", $prob, $run == 500 ? "quick" : "final");
+    print("\t ./improvement.pl $data/$KN $data/$BIZ > post_processed_data/$out\n");
+}
+}
+print("\n");
+

### 2014-05-20 code/matlab/BIZUNK.m

@@ -1,0 +1,151 @@
+% BIZUNK: run the BIZ algorithm for unknown and heterogeneous sampling variances on a problem instance.
+%
+% Inputs:
+% fn, fn_runlength, fn_other -- function handle to the function to be optimized, along with its
+% 	runlength, and any other special state, in the format specified by simopt.org
+% alts -- a matrix, where each row contains an alternative (specified as a vector).
+% Pstar, delta -- indifference-zone parameters to use
+% seed_start, seed_skip -- tells which random number streams to use.  The ones
+% 	used are seed_start, seed_start + seek_skip, seed_start + seed_skip*2, etc.
+% Outputs:
+% xstar -- the alternative selected
+% nsamples -- the number of samples taken overall
+% nstages -- the number of stages of sampling
+function [xstar, nsamples, nstages] = BIZUNK(fn, fn_runlength, fn_other, alts, Pstar, delta, seed_start, seed_skip, n0)
+
+if (nargin < 9)
+  n0 = 30;
+end
+batchsize = 1;
+
+% k is the number of alternatives. d is the dimension of vectors specifying an alternative.
+[k,d] = size(alts); 
+
+if (delta<=0)
+  error('delta must be strictly positive');
+end
+if (Pstar <= 1/k || Pstar >= 1)
+  error('Pstar must be strictly between 1/k and 1');
+end
+logElimThresh = log1p(-Pstar^(1/(k-1)));
+  %double logElimThresh = log1p(-pow(problem.pstar,1.0/(problem.k-1)));
+logpstar = log(Pstar); % cache the log of Pstar
+
+nsamples = 0; % number of samples taken
+nstages = 0; % number of stages of sampling
+
+% Create four vectors.  
+% n[x] contains the number of samples taken from alternative x.  
+% avg[x] contains the mean of all the observations from alternative x.  
+% M2[x] contains the sum of the square differences from the current sample mean.
+% M2[x] = \sum_{i=1}^n (y_i - \ybar_n)^2, where y_i are the samples from alternative x.
+% The algorithm for updating the mean and M2 came from Wikipedia,
+% http://en.wikipedia.org/wiki/Algorithms_for_calculating_variance 
[…]

### 2014-05-20 code/matlab/BIZUNK_UpdateLogQ.m

@@ -1,0 +1,34 @@
+% Computes logq, which is the logarithm of the numerator of qhat_{tx}(A) in
+% equation 11 of the paper on June 25,2012.  The inputs are:
+%
+% k		number of alternatives.  All vectors are of length k.
+% delta	IZ parameter
+% n		vector of number of samples taken from each alternative.
+% avg		vector of sampling means
+% M2		vector of sums of the square of the differences from
+% 		the current sample mean.  M2[x]/n[x] gives the sample variance.
+% logq		vector of length k.  If logq[x] == -INFINITY, this
+% 		means that alternative has already been eliminated.  Otherwise,
+% 		the logq[x] is ignored.
+%
+% Puts results into the vector logq, and returns statistics computed from this vector.
+function [logq sumq worst_logq worst_x] = BIZUNK_UpdateLogQ(delta, n, avg, M2, logq)
+    % Sum up number of samples and sample variances.
+    in_contention = logq > -Inf; % indices of alternatives that haven't been eliminated.
+    N = sum(n(in_contention));
+    sumvar = sum(M2(in_contention) ./ n(in_contention)); % sum of the sample variances.
+
+    % Calculate new logq values and statistics based on them.
+    logq(in_contention) = delta * avg(in_contention) * N / sumvar;
+
+    % This normalizes everything, so that the logqs don't grow too large,
+    % causing numerical overflow when we take exp.  It is not in the C++ code,
+    % at least as of 9/2013, because the problems we were running there didn't
+    % need it, but it would be good to add there just in case.
+    logq = logq - max(logq);
+
+    sumq = sum(exp(logq(in_contention))); % sum of the q values, for those in contention
+    tmp = logq;
+    tmp(logq == -Inf) = Inf; % make it so that the ones out of contention can't be minimum.
+    [worst_logq worst_x] = min(tmp); % worst of the in-contention logq values
+end

### 2014-05-20 code/matlab/DetermineGoodEnough.m

@@ -1,0 +1,21 @@
+% DetermineGoodEnough:  Figure out the set of good-enough alternatives using exhaustive simulation
+% Inputs:
+% 	est_mean, stderr: a vector of estimated means, together with their standard errors, for the alternatives
+% 	delta -- the indifference-zone parameter
+% Outputs:
+% 	good is a vector giving, for each alternative, whether it is estimated to be in the "good enough" set or not.
+% 	z_scores is a vector giving an approximate z-score for the comparison
+% 		of each alternative with the best minus delta.  Take enough samples
+% 		to make stderr small enough to make these all big.
+function [good, z_scores] = DetermineGoodEnough(est_mean, stderr, delta)
+
+% Figure out, if the estimates are correct, which alternatives would consitute good selection.
+[best_val, best_alt] = max(est_mean);
+threshold = best_val - delta;
+good = est_mean > threshold;
+
+% Calculate approximate z-scores.
+% This method is really simple, and ignores the multiple testing aspect, and the selection aspect.
+stderr_for_comparison = sqrt(stderr(best_alt)^2 + stderr.^2);
+stderr_for_comparison(best_alt) = NaN;
+z_scores = abs(est_mean - threshold) ./ stderr_for_comparison; 

### 2014-05-20 code/matlab/KNUNK.m

@@ -1,0 +1,150 @@
+% KNUNK: run the KN algorithm on a problem instance.
+%
+% Inputs:
+% fn, fn_runlength, fn_other -- function handle to the function to be optimized, along with its
+% 	runlength, and any other special state, in the format specified by simopt.org
+% alts -- a matrix, where each row contains an alternative (specified as a vector).
+% Pstar, delta -- indifference-zone parameters to use
+% seed_start, seed_skip -- tells which random number streams to use.  The ones
+% 	used are seed_start, seed_start + seek_skip, seed_start + seed_skip*2, etc.
+% Outputs:
+% xstar -- the alternative selected
+% nsamples -- the number of samples taken overall
+% nstages -- the number of stages of sampling
+
+
+function [xstar, nsamples, nstages] = KNUNK(fn, fn_runlength, fn_other, alts, Pstar, delta, seed_start, seed_skip, n0)
+
+if (nargin < 9)
+  n0 = 30;
+end
+
+% k is the number of alternatives. d is the dimension of vectors specifying an alternative.
+[k,d] = size(alts); 
+
+if (delta<=0)
+  error('delta must be strictly positive');
+end
+
+% If Pstar < 1/k, then the randomized policy that does no measurement is
+% acceptible.  We do not treat this case because it isn't particularly
+% interesting.
+if (Pstar <= 1/k || Pstar >= 1)
+  error('Pstar must be strictly between 1/k and 1');
+end
+
+nSamples = 0; % total number of samples.
+nStages = 0; % number of rounds
+
+sum = zeros(1,k);
+varhat = zeros(1,k);
+
+% Constants
+alpha = 1-Pstar;
+% To handle known variance, change eta and h2 to:
+% eta = log((k-1)/(2.0*alpha));
+% h2 = 2*eta;
+tmp=(2*alpha/(k-1))^(-2/(n0-1));
+eta = (tmp-1)/2;
+h2 = 2*eta*(n0-1);
+c1 = h2/(delta^2);
+
+disp(sprintf('n0=%d eta=%f h2=%f c1=%f', n0,eta,h2,c1));
+
+nsamples = 0; % number of samples taken
+nstages = 0; % number of stages of sampling
+ 
+% Run a first stage
+nstages = nstages + n0;
+  for x=1:k
+    % mean and M2 are for calculating the sample variance.
+    % The algorithm for updating the mean and M2 came from Wikipedia,
+    % http://en.wikipedia.org/wiki/Algorithms_for_calculating_variance 
[…]

### 2014-05-20 code/matlab/Normal.m

@@ -1,0 +1,10 @@
+% This is a function that samples a normal random variable, in the format of simopt.
+% alt(1) is the mean, and alt(2) is the standard deviation.
+function y = normal(alt, runlength, seed, other)
+    m = alt(1); % mean
+    sdev = alt(2); % standard deviation
+    Stream = RandStream.create('mrg32k3a', 'NumStreams', 1);
+    Stream.Substream = seed;
+    OldStream = RandStream.setGlobalStream(Stream);
+    y = normrnd(m, sdev);
+    RandStream.setGlobalStream(OldStream); % Restore previous stream

### 2014-05-20 code/matlab/Oct13_Collect.m

@@ -1,0 +1,40 @@
+% Collect and collate results from running either BIZ or KN on a problem, for a specified value of k.
+% [est_Nk, stderr_Nk, est_PGS, stderr_PGS] = Oct13_Collect(alg, problem, k, max_seed)
+% 
+% for example, Oct13_Collect('BIZ', 'SC', 8, 100) would check the results of
+% BIZ on the SC problem, for k=8, assuming that seeds from 1 to 100 had been
+% run.
+%
+% Inputs:
+%	alg --- either 'KN' or 'BIZ'
+%	problem --- the problem to solve.  Should be a string such that there is a file called problem.mat containing the problem.
+% 	k --- number of alternatives.  Take only the first k alternatives from the alts variable in the loaded file.
+% 	max_seed -- Data will be taken for seeds 1 through max_seed, skipping over files that don't exist.
+
+function [est_Nk, stderr_Nk, est_PGS, stderr_PGS] = Oct13_Collect(alg, problem, k, max_seed)
+problem_file = sprintf('%s.mat',problem);
+load(problem_file); % loads est_mean, stderr, Pstar, delta and some other stuff we don't use.
+seed_skip = 1000;
+[good, z_scores] = DetermineGoodEnough(est_mean(1:k),stderr(1:k),delta); % only take the first k
+disp(sprintf('Min z score is %g', min(z_scores)));
+nsamples = zeros(1,max_seed);
+ngood = 0; % number of good selections
+nruns = 0; % overall number of files that we have
+for seed=1:max_seed
+	infile = sprintf('Oct13/%s_%s_%d_%d.mat', alg, problem, k, seed);
+	if exist(infile, 'file') == 2 
+		nruns = nruns + 1;
+		% loads xstar, nsamples, nstages, seed_start, seed_skip, Pstar, delta, k
+		s=load(infile); 
+		nsamples(nruns) = s.nsamples;
+		ngood = ngood + good(s.xstar);
+	else 
+		disp(sprintf('Missing %s %s k=%d seed=%d', alg, problem, k, seed));
+	end
+end
+nsamples = nsamples(1:nruns);
+est_Nk = mean(nsamples)/k;
+stderr_Nk = sqrt(var(nsamples)/nruns)/k;
+est_PGS = ngood / nruns;
+stderr_PGS = sqrt(est_PGS * (1-est_PGS) / nruns);
[…]

### 2014-05-20 code/matlab/Oct13_CollectAll.m

@@ -1,0 +1,36 @@
+% Runs through all of the data collected by Oct13_RunBIZ.sh and Oct13_RunKN.sh
+% on the sSCont problem for a variety of different values of k, and writes it
+% out to Oct13_BIZ.csv and Oct13_KN.csv.  The format of these two files is as
+% follows:
+% Col 1 is k, col 2 is estimated E[N/k], col 3 is the stderr of this estimate, 
+% col 4 is the estimated PGS, col 5 is the stderr of the estimate of PGS.
+
+kvec = [2, 5, 10, 25, 50, 100, 250, 500, 1000, 2500, 5000, 10000]; % These are the different values of k for which we ran sSCont
+max_seed_BIZ = 300; % This is the number of independent replications we ran
+max_seed_KN = 300;
+% These two matrices, BIZ and KN, store the results from our simulations.  
+BIZ = zeros(length(kvec),5); 
+KN  = zeros(length(kvec),5);
+improvement  = zeros(length(kvec),3);
+for i=1:length(kvec)
+	k = kvec(i);
+	BIZ(i,1)=k;
+	KN(i,1)=k;
+	[BIZ(i,2), BIZ(i,3), BIZ(i,4), BIZ(i,5)] = Oct13_Collect('BIZ','sSCont',k,max_seed_BIZ);
+	if (k>= 2500)
+		max_seed_KN=100;
+	end
+	[KN(i,2), KN(i,3), KN(i,4), KN(i,5)] = Oct13_Collect('KN','sSCont',k,max_seed_KN);
+end
+
+% Compute the improvement (ratio of KN samples to BIZ samples).
+x =  KN(:,2);
+sx = KN(:,3);
+y =  BIZ(:,2)
+sy = BIZ(:,3)
+improvement(:,1) = kvec;
+improvement(:,2) = x ./ y;
+improvement(:,3) = sqrt(sx.^2 + sy.^2 .* improvement(:,1)) ./ y;
+csvwrite('Oct13_BIZ.csv',BIZ);
+csvwrite('Oct13_KN.csv',KN);
+csvwrite('Oct13_improvement.csv',improvement);

### 2014-05-20 code/matlab/Oct13_CountGoodEnough.m

@@ -1,0 +1,7 @@
+kvec = [2, 5, 10, 25, 50, 100, 250, 500, 1000, 2500, 5000, 10000]; % These are the different values of k for which we ran sSCont
+load('sSCont.mat');
+for k=kvec
+	[good, z_scores] = DetermineGoodEnough(est_mean(1:k),stderr(1:k),delta); % only take the first k
+	m = sort(-est_mean(1:k));
+	disp(sprintf('k=%d ngood=%d best-second_best=%g', k, sum(good), m(2)-m(1)));
+end

### 2014-05-20 code/matlab/Oct13_RunBIZ.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+# Run Oct13_RunBIZ.nbs, which runs BIZ at the specified number of alternatives
+# and starting seed, for all starting seeds in a specified range, and a fixed
+# value of k.
+for n in {101..300}
+do
+	# Add a job, which is to run Oct13_RunBIZ.nbs, to the long NBS queue.
+	# The flags at the end tell it to only send email if there is a failure.
+	# The first argument is the problem, e.g., sSCont or SC
+	# The second argument is k.  The third argument is the seed.
+	#jsub "Oct13_RunBIZ.nbs sSCont 2 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunBIZ.nbs sSCont 5 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunBIZ.nbs sSCont 10 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunBIZ.nbs sSCont 25 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunBIZ.nbs sSCont 50 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunBIZ.nbs sSCont 100 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunBIZ.nbs sSCont 250 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunBIZ.nbs sSCont 500 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunBIZ.nbs sSCont 1000 $n" -mail nostart end -mfail
+	jsub "Oct13_RunBIZ.nbs sSCont 2500 $n" -mail nostart end -mfail
+	jsub "Oct13_RunBIZ.nbs sSCont 5000 $n" -mail nostart end -mfail
+	jsub "Oct13_RunBIZ.nbs sSCont 10000 $n" -mail nostart end -mfail
+done

### 2014-05-20 code/matlab/Oct13_RunBIZOnce.m

@@ -1,0 +1,18 @@
+% Run BIZUNK on a problem, and save the result to a file.
+
+% Inputs:
+%	problem --- the problem to solve.  Should be a string such that there is a file called problem.mat containing the problem.
+% 	k --- number of alternatives.  Take only the first k alternatives from the alts variable in the loaded file.
+% 	seed_start -- controls the index of the random number stream to start with.  The
+% 		streams used will be seed_start, seed_start+seed_skip, seed_start+2*seed_skip, etc.
+% Outputs:
+%	xstar, nsamples, nstages --- the selection decision, number of samples
+%		taken, and number of stages of sampling.  These are also saved to file.
+
+function [xstar, nsamples, nstages] = Oct13_RunBIZOnce(problem, k, seed_start)
+problem_file = sprintf('%s.mat',problem);
+load(problem_file); % loads fn, fn_runlength, fn_other, alts, Pstar, delta, and some other stuff we don't use.
+seed_skip = 1000;
+[xstar, nsamples, nstages] = BIZUNK(fn, fn_runlength, fn_other, alts(1:k,:), Pstar, delta, seed_start, seed_skip);
+outfile = sprintf('Oct13/BIZ_%s_%d_%d.mat', problem, k, seed_start);
+save(outfile, 'xstar', 'nsamples', 'nstages', 'seed_start', 'seed_skip', 'Pstar', 'delta', 'k');

### 2014-05-20 code/matlab/Oct13_RunKN.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+# Run Oct13_RunKN.nbs, which runs KN at the specified number of alternatives
+# and starting seed, for all starting seeds in a specified range, and a fixed
+# value of k.
+for n in {101..300}
+do
+	# Add a job, which is to run Oct13_RunKN.nbs, to the long NBS queue.
+	# The flags at the end tell it to only send email if there is a failure.
+	# The first argument is the problem, e.g., sSCont, or SC.
+	# The second argument is k.  The third argument is the seed.
+	#jsub "Oct13_RunKN.nbs sSCont 2 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunKN.nbs sSCont 5 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunKN.nbs sSCont 10 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunKN.nbs sSCont 25 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunKN.nbs sSCont 50 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunKN.nbs sSCont 100 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunKN.nbs sSCont 250 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunKN.nbs sSCont 500 $n" -mail nostart end -mfail
+	#jsub "Oct13_RunKN.nbs sSCont 1000 $n" -mail nostart end -mfail
+	jsub "Oct13_RunKN.nbs sSCont 2500 $n" -mail nostart end -mfail
+	jsub "Oct13_RunKN.nbs sSCont 5000 $n" -mail nostart end -mfail
+	jsub "Oct13_RunKN.nbs sSCont 10000 $n" -mail nostart end -mfail
+done

### 2014-05-20 code/matlab/Oct13_RunKNOnce.m

@@ -1,0 +1,18 @@
+% Run KNUNK on a problem, and save the result to a file.
+%
+% Inputs:
+%	problem --- the problem to solve.  Should be a string such that there is a file called problem.mat containing the problem.
+% 	k --- number of alternatives.  Take only the first k alternatives from the alts variable in the loaded file.
+% 	seed_start -- controls the index of the random number stream to start with.  The
+% 		streams used will be seed_start, seed_start+seed_skip, seed_start+2*seed_skip, etc.
+% Outputs:
+%	xstar, nsamples, nstages --- the selection decision, number of samples
+%		taken, and number of stages of sampling.  These are also saved to file.
+
+function [xstar, nsamples, nstages] = Oct13_RunKNOnce(problem, k, seed_start)
+problem_file = sprintf('%s.mat',problem);
+load(problem_file); % loads fn, fn_runlength, fn_other, alts, Pstar, delta and some other stuff we don't use.
+seed_skip = 1000;
+[xstar, nsamples, nstages] = KNUNK(fn, fn_runlength, fn_other, alts(1:k,:), Pstar, delta, seed_start, seed_skip);
+outfile = sprintf('Oct13/KN_%s_%d_%d.mat', problem, k, seed_start);
+save(outfile, 'xstar', 'nsamples', 'nstages', 'seed_start', 'seed_skip', 'Pstar', 'delta', 'k');

### 2014-05-20 code/matlab/Oct18_Collect.m

@@ -1,0 +1,42 @@
+% Collect and collate results from running either BIZ or KN on a problem, for a specified value of k.
+% [est_Nk, stderr_Nk, est_PGS, stderr_PGS] = Oct18_Collect(alg, problem, k, max_seed)
+% 
+% for example, Oct18_Collect('BIZ', 'SC', 8, 100) would check the results of
+% BIZ on the SC problem, for k=8, assuming that seeds from 1 to 100 had been
+% run.
+%
+% Inputs:
+%	alg --- either 'KN' or 'BIZ'
+%	problem --- the problem to solve.  Should be a string such that there is a file called problem.mat containing the problem.
+% 	k --- number of alternatives.  Take only the first k alternatives from the alts variable in the loaded file.
+% 	max_seed -- Data will be taken for seeds 1 through max_seed, skipping over files that don't exist.
+
+function [est_Nk, stderr_Nk, est_PGS, stderr_PGS] = Oct18_Collect(alg, problem, k, max_seed)
+problem_file = sprintf('%s.mat',problem);
+load(problem_file); % loads est_mean, stderr, Pstar, delta and some other stuff we don't use.
+seed_skip = 1000;
+%delta = 1; % alter delta
+Pstar = 0.9; % alter Pstar
+[good, z_scores] = DetermineGoodEnough(est_mean(1:k),stderr(1:k),delta); % only take the first k
+disp(sprintf('Min z score is %g', min(z_scores)));
+nsamples = zeros(1,max_seed);
+ngood = 0; % number of good selections
+nruns = 0; % overall number of files that we have
+for seed=1:max_seed
+	infile = sprintf('Oct18/%s_%s_%d_%d.mat', alg, problem, k, seed);
+	if exist(infile, 'file') == 2 
+		nruns = nruns + 1;
+		% loads xstar, nsamples, nstages, seed_start, seed_skip, Pstar, delta, k
+		s=load(infile); 
+		nsamples(nruns) = s.nsamples;
+		ngood = ngood + good(s.xstar);
+	else 
+		disp(sprintf('Missing %s %s k=%d seed=%d', alg, problem, k, seed));
+	end
+end
+nsamples = nsamples(1:nruns);
+est_Nk = mean(nsamples)/k;
+stderr_Nk = sqrt(var(nsamples)/nruns)/k;
+est_PGS = ngood / nruns;
[…]

### 2014-05-20 code/matlab/Oct18_CollectAll.m

@@ -1,0 +1,22 @@
+% Runs through all of the data collected by Oct18_RunBIZ.sh and Oct18_RunKN.sh
+% on the sSCont problem for a variety of different values of k, and writes it
+% out to Oct18_BIZ.csv and Oct18_KN.csv.  The format of these two files is as
+% follows:
+% Col 1 is k, col 2 is estimated E[N/k], col 3 is the stderr of this estimate, 
+% col 4 is the estimated PGS, col 5 is the stderr of the estimate of PGS.
+
+kvec = [2, 5, 10, 25, 50, 100, 250, 500, 1000]; % These are the different values of k for which we ran sSCont
+max_seed_BIZ = 100; % This is the number of independent replications we rane 
+max_seed_KN = 100;
+% These two matrices, BIZ and KN, store the results from our simulations.  
+BIZ = zeros(length(kvec),5); 
+KN  = zeros(length(kvec),5);
+for i=1:length(kvec)
+	k = kvec(i);
+	BIZ(i,1)=k;
+	KN(i,1)=k;
+	[BIZ(i,2), BIZ(i,3), BIZ(i,4), BIZ(i,5)] = Oct18_Collect('BIZ','sSCont',k,max_seed_BIZ);
+	[KN(i,2), KN(i,3), KN(i,4), KN(i,5)] = Oct18_Collect('KN','sSCont',k,max_seed_KN);
+end
+csvwrite('Oct18_BIZ.csv',BIZ);
+csvwrite('Oct18_KN.csv',KN);

### 2014-05-20 code/matlab/Oct18_RunBIZ.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+# Run Oct18_RunBIZ.nbs, which runs BIZ at the specified number of alternatives
+# and starting seed, for all starting seeds in a specified range, and a fixed
+# value of k.
+for n in {1..100}
+do
+	# Add a job, which is to run Oct18_RunBIZ.nbs, to the long NBS queue.
+	# The flags at the end tell it to only send email if there is a failure.
+	# The first argument is the problem, e.g., sSCont or SC
+	# The second argument is k.  The third argument is the seed.
+	jsub "Oct18_RunBIZ.nbs sSCont 2 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 5 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 10 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 25 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 50 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 100 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 250 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 500 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 1000 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 2500 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 5000 $n" -mail nostart end -mfail
+	jsub "Oct18_RunBIZ.nbs sSCont 10000 $n" -mail nostart end -mfail
+done

### 2014-05-20 code/matlab/Oct18_RunBIZOnce.m

@@ -1,0 +1,20 @@
+% Run BIZUNK on a problem, and save the result to a file.
+
+% Inputs:
+%	problem --- the problem to solve.  Should be a string such that there is a file called problem.mat containing the problem.
+% 	k --- number of alternatives.  Take only the first k alternatives from the alts variable in the loaded file.
+% 	seed_start -- controls the index of the random number stream to start with.  The
+% 		streams used will be seed_start, seed_start+seed_skip, seed_start+2*seed_skip, etc.
+% Outputs:
+%	xstar, nsamples, nstages --- the selection decision, number of samples
+%		taken, and number of stages of sampling.  These are also saved to file.
+
+function [xstar, nsamples, nstages] = Oct18_RunBIZOnce(problem, k, seed_start)
+problem_file = sprintf('%s.mat',problem);
+load(problem_file); % loads fn, fn_runlength, fn_other, alts, Pstar, delta, and some other stuff we don't use.
+seed_skip = 1000;
+Pstar = 0.90; % alter Pstar and delta
+delta = 1;
+[xstar, nsamples, nstages] = BIZUNK(fn, fn_runlength, fn_other, alts(1:k,:), Pstar, delta, seed_start, seed_skip);
+outfile = sprintf('Oct18/BIZ_%s_%d_%d.mat', problem, k, seed_start);
+save(outfile, 'xstar', 'nsamples', 'nstages', 'seed_start', 'seed_skip', 'Pstar', 'delta', 'k');

### 2014-05-20 code/matlab/Oct18_RunKN.sh

@@ -1,0 +1,23 @@
+#!/bin/sh
+# Run Oct18_RunKN.nbs, which runs KN at the specified number of alternatives
+# and starting seed, for all starting seeds in a specified range, and a fixed
+# value of k.
+for n in {1..100}
+do
+	# Add a job, which is to run Oct18_RunKN.nbs, to the long NBS queue.
+	# The flags at the end tell it to only send email if there is a failure.
+	# The first argument is the problem, e.g., sSCont, or SC.
+	# The second argument is k.  The third argument is the seed.
+	jsub "Oct18_RunKN.nbs sSCont 2 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 5 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 10 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 25 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 50 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 100 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 250 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 500 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 1000 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 2500 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 5000 $n" -mail nostart end -mfail
+	jsub "Oct18_RunKN.nbs sSCont 10000 $n" -mail nostart end -mfail
+done

### 2014-05-20 code/matlab/Oct18_RunKNOnce.m

@@ -1,0 +1,20 @@
+% Run KNUNK on a problem, and save the result to a file.
+%
+% Inputs:
+%	problem --- the problem to solve.  Should be a string such that there is a file called problem.mat containing the problem.
+% 	k --- number of alternatives.  Take only the first k alternatives from the alts variable in the loaded file.
+% 	seed_start -- controls the index of the random number stream to start with.  The
+% 		streams used will be seed_start, seed_start+seed_skip, seed_start+2*seed_skip, etc.
+% Outputs:
+%	xstar, nsamples, nstages --- the selection decision, number of samples
+%		taken, and number of stages of sampling.  These are also saved to file.
+
+function [xstar, nsamples, nstages] = Oct18_RunKNOnce(problem, k, seed_start)
+problem_file = sprintf('%s.mat',problem);
+load(problem_file); % loads fn, fn_runlength, fn_other, alts, Pstar, delta and some other stuff we don't use.
+seed_skip = 1000;
+Pstar = 0.9;
+delta = 1;
+[xstar, nsamples, nstages] = KNUNK(fn, fn_runlength, fn_other, alts(1:k,:), Pstar, delta, seed_start, seed_skip);
+outfile = sprintf('Oct18/KN_%s_%d_%d.mat', problem, k, seed_start);
+save(outfile, 'xstar', 'nsamples', 'nstages', 'seed_start', 'seed_skip', 'Pstar', 'delta', 'k');

### 2014-05-20 code/matlab/SC_SetUpProblem.m

@@ -1,0 +1,23 @@
+k=1000; % number of alternatives
+delta=1; % IZ parameter, and parameter of slippage configuration
+Pstar = 0.9;
+sigma = 10; % sampling sdev.
+
+% alts is a matrix, where each row corresponds to an alternative.  
+% the first column is the alternative's mean, and the second column is its standard deviation.
+alts = zeros(k,2); 
+alts(1,1) = delta; % the first alternative has mean delta, and the rest have mean 0. 
+alts(:,2) = sigma; % homogeneous sampling variance
+
+% this is what you would get out of exhaustive simulation, if you took infinitely many samples
+est_mean = alts(:,1)';
+est_var = (alts(:,2).^2)';
+nruns = ones(1,k)*Inf;
+stderr = zeros(1,k);
+
+% For normal sampling
+fn = @Normal;
+fn_runlength = 1;
+fn_other = [];
+
+save 'SC.mat' alts est_mean est_var nruns stderr fn fn_runlength fn_other delta Pstar

### 2014-05-20 code/matlab/old/DetermineGoodEnough.m

@@ -1,0 +1,30 @@
+% DetermineGoodEnough:  Figure out the set of good-enough alternatives using exhaustive simulation
+% Inputs:
+% 	fn, fn_runlength, fn_other -- function handle to the function to be optimized, along with its
+% 		runlength, and any other special state, in the format specified by simopt.org
+% 	alts -- a matrix, where each row contains an alternative (specified as a vector).
+% 	starting_seed -- the index of the random number stream to start with.  The
+% 		streams used will be starting_seed, starting_seed+1, starting_seed+2, etc.
+% 	exhaustive_n0 -- the number of samples to take from each alternative
+% 	delta -- the indifference-zone parameter
+% Outputs:
+% 	good is a vector giving, for each alternative, whether it is estimated to be in the "good enough" set or not.
+% 	z_scores is a vector giving an approximate z-score for the comparison
+% 		of each alternative with the best minus delta.  Set exhaustive_n0 big
+% 		enough to make these all big.
+% 	nsamples is the number of samples taken overall (which is the number of random number streams used).
+function [good, z_scores, nsamples] = DetermineGoodEnough(fn, fn_runlength, fn_other, alts, starting_seed, exhaustive_n0, delta)
+
+% perform exhaustive simulation
+[est_mean,est_var,stderr,nsamples] = Exhaustive(fn, runlength, other, StartingSol, starting_seed, exhaustive_n0);
+
+% Figure out, if the estimates are correct, which alternatives would consitute good selection.
+[best_val, best_alt] = max(est_mean);
+threshold = best_val - delta;
+good = est_mean >= threshold;
+
+% Calculate approximate z-scores.
+% This method is really simple, and ignores the multiple testing aspect, and the selection aspect.
+stderr_for_comparison = sqrt(stderr(best_alt)^2 + stderr.^2);
+stderr_for_comparison(best_alt) = NaN;
+z_scores = abs(est_mean - threshold) ./ stderr_for_comparison; 

### 2014-05-20 code/matlab/old/Exhaustive.m

@@ -1,0 +1,32 @@
+% Exhaustive --- performs exhaustive simulation to estimate the mean and variance of each alternative.
+%
+% Inputs:
+% fn, fn_runlength, fn_other -- function handle to the function to be optimized, along with its
+% 	runlength, and any other special state, in the format specified by simopt.org
+% alts -- a matrix, where each row contains an alternative (specified as a vector).
+% starting_seed -- the index of the random number stream to start with.  The
+% 	streams used will be starting_seed, starting_seed+1, starting_seed+2, etc.
+% n0 -- the number of samples to take from each alternative
+% Outputs:
+% est_mean is a vector giving, for each alternative, an estimate of the true sampling mean.
+% est_var is a vector giving, for each alternative, an estimate of the true sampling variance.
+% stderr is sqrt(est_var/n0), the standard error of our estimate of the mean.
+% nsamples is the number of samples taken overall (which is the number of random number streams used).
+function [est_mean, est_var, stderr, nsamples] = Exhaustive(fn, fn_runlength, fn_other, alts, starting_seed, n0)
+
+% k is the number of alternatives. d is the dimension of vectors specifying an alternative.
+[k,d] = size(alts); 
+nsamples = 0;
+est_mean = zeros(1,k); 
+est_var = zeros(1,k);
+
+for x=1:k
+  y = zeros(1,n0);
+  for n=1:n0
+	y(n) = fn(alts(x,:),fn_runlength,starting_seed + nsamples,fn_other);
+	nsamples = nsamples+1;
+  end
+  est_mean(x) = mean(y);
+  est_var(x) = var(y);
+end
+stderr = sqrt(est_var/n0);

### 2014-05-20 code/matlab/old/RunAlg.m

@@ -1,0 +1,36 @@
+% Run an algorithm (BIZUNK or KNUNK) on a problem instance, and collect the
+% probability of good selection, expected sample size, and expected number of
+% stages.
+
+% Inputs:
+% alg -- function handle to either BIZUNK or KNUNK
+% fn, fn_runlength, fn_other -- function handle to the function to be optimized, along with its
+% 	runlength, and any other special state, in the format specified by simopt.org
+% alts -- a matrix, where each row contains an alternative (specified as a vector).
+% Pstar, delta -- indifference-zone parameters to use
+% starting_seed -- the index of the random number stream to start with.  The
+% 	streams used will be starting_seed, starting_seed+1, starting_seed+2, etc.
+% good -- binary vector containing, for each alternative, whether we should consider
+% 	it a good selection or not, i.e., whether or not its true mean is within
+% 	delta of the best.
+% nruns -- number of independent replications of the algorithm to do
+% Outputs:
+% 	est_PGS, std_PGS  -- Estimate and corresponding standard error of the probability of good selection
+% 	est_N, std_N  -- Estimate and corresponding standard error of the probability of good selection
+
+function [est_PGS, std_PGS, est_N, std_N] = RunAlg(alg, fn, fn_runlength, fn_other, alts, Pstar, delta, starting_seed, good, nruns)
+ngood = 0;
+seed = starting_seed;
+N_vec = zeros(1,nruns);
+for n=1:nruns
+	[xstar, nsamples, nstages] = alg(fn, fn_runlength, fn_other, alts, Pstar, delta, seed);
+	N_vec(n) = nsamples;
+	seed = seed + nsamples;
+	ngood = ngood + good(xstar);
+	disp(sprintf('Run %d good=%d N=%d\n', n, good(xstar), nsamples));
+end
+% disp(sprintf('%d out of %d were good selections\n', ngood, nruns))
+est_PGS = ngood / nruns;
+std_PGS = sqrt(est_PGS * (1-est_PGS) / nruns);
+est_N = mean(N_vec);
+std_N = sqrt(var(N_vec)/nruns);

### 2014-05-20 code/matlab/old/RunAlgOnce.m

@@ -1,0 +1,25 @@
+% Run an algorithm (BIZUNK or KNUNK) on a problem instance, and save the result
+% to a file.
+
+% Inputs:
+% alg -- function handle to either BIZUNK or KNUNK
+% problem_file --- filename of the problem to run, such as sSCont.mat.
+% 		Contains fn, fn_runlength, fn_other, and alts.
+% k --- number of alternatives.  Take only the first k alternatives from the alts variable.
+% seed_start, seed_skip -- controls the index of the random number stream to start with.  The
+% 	streams used will be seed_start, seed_start+seed_skip, seed_start+2*seed_skip, etc.
+% Outputs:
+%	xstar, nsamples, nstages --- the selection decision, number of samples
+%		taken, and number of stages of sampling.  These are also saved to outfile.
+
+function [xstar, nsamples, nstages] = RunAlgOnce(alg, problem_file, k, seed_start, seed_skip)
+
+% loads fn, fn_runlength, fn_other, alts, est_mean, stderr, Pstar, delta, and some other stuff we don't use.
+load(problem_file); 
+
+% Runs the algorithm, and collects the selection decision, number of samples, and number of stages
+[xstar, nsamples, nstages] = alg(fn, fn_runlength, fn_other, alts(1:k,:), Pstar, delta, seed_start, seek_skip);
+
+outfile = sprintf('run_tmp/%s_%s_%d_%g_%g_%d_%d', problem_file, alg, k, Pstar, delta, seed_start);
+
+save(outfile, 'xstar', 'nsamples', 'nstages', 'seed_start', 'Pstar', 'delta');

### 2014-05-20 code/matlab/old/SetUpProblem.m

@@ -1,0 +1,21 @@
+% This script creates a random problem instance of size k, and then saves the
+% various expensive-to-compute problem parameters to a file.  A runlength of
+% 100 is fixed.
+%
+function SetUpProblem(k, exhaustive_n0)
+
+structure = @sSContStructure;
+fn = @sSCont;
+runlength = 100;
+other = []; % this is not used by this simopt problem
+
+% Get some starting solutions from the simopt structure function.  All other
+% return variables are returned.
+[minmax d m VarNature VarBds FnGradAvail NumConstraintGradAvail alts budget ObjBd OptimalSol] = structure(k,1);
+
+% perform exhaustive simulation, which is needed to figure out which alternatives are good enough for a given delta.
+starting_seed = 1;
+[est_mean,est_var,stderr,nsamples] = Exhaustive(fn, runlength, other, alts, starting_seed, exhaustive_n0);
+
+filename = sprintf('Problem_k%04d_n%04d.mat',k,exhaustive_n0);
+save(filename, 'est_mean','est_var','stderr','nsamples','alts')

### 2014-05-20 code/matlab/sSCont.m

@@ -1,0 +1,134 @@
+%   ***************************************
+%   *** Code written by German Gutierrez***
+%   ***         gg92@cornell.edu        ***
+%   ***************************************
+
+%RETURNS:  Avg. and C.I. half width for per period cost and the stockout
+%rate. Currently set to 1 repetitions of 1,000 days each (50 day warmup).
+% PF: modifications:
+%	modified # of repetitions from 20 to 1.
+%	modified it to return negative cost
+
+function [fn, FnVar, FnGrad, FnGradCov, constraint, ConstraintCov, ConstraintGrad, ConstraintGradCov] = sSCont(x, runlength, seed, other);
+% function [fn, FnVar, FnGrad, FnGradCov, constraint, ConstraintCov, ConstraintGrad, ConstraintGradCov] = sSCont(x, runlength, seed, other);
+% x is the (s, S) vector
+% runlength is the number of days of demand to simulate
+% seed is the index of the substreams to use (integer >= 1)
+% other is not used
+
+constraint = NaN;
+ConstraintCov = NaN;
+ConstraintGrad = NaN;
+ConstraintGradCov = NaN;
+
+if (sum(x < 0)> 0 )|| (runlength <= 0) || (runlength ~= round(runlength)) || (seed <= 0) || (round(seed) ~= seed),
+    fprintf('x should be >= 0, runlength should be positive integer, seed must be a positive integer\n');
+    fn = NaN;
+    FnVar = NaN;
+    FnGrad = NaN;
+    FnGradCov = NaN;
+else
+%%%%%%%%%%%%%%%%PARAMETERS%%%%%%%%%%%%%%%%%%
+nDays = runlength;          %Length of simulation: 10050
+nRepetitions = 1;           %Repetitions
+meanDemand = 100;           %Mean demand
+meanLT = 6;                 %Mean lead time
+fixed = 36;                 %Fixed order cost
+var = 2;                    %Variable, per unit, cost
+holding = 1;                % Holding cost
+warmup = 50;                %length of warm up period
+
+%%%%%%%%Decision Variables%%%%%%%%%
+s=x(1);
+S=x(2); %[1000 2000] starting Sol
+
+    % Generate new streams for 
+    [DemandStream, LeadTimeStream] = RandStream.create('mrg32k3a', 'NumStreams', 2);
+
+    % Set the substream to the "seed"
+    DemandStream.Substream = seed;
+    LeadTimeStream.Substream = seed;
+
[…]

### 2014-05-20 code/matlab/sSContStructure.m

@@ -1,0 +1,72 @@
+function [minmax d m VarNature VarBds FnGradAvail NumConstraintGradAvail StartingSol budget ObjBd OptimalSol] = sSContStructure(NumStartingSol, seed)
+%function [minmax d m VarNature VarBds FnGradAvail NumConstraintGradAvail StartingSol budget ObjBd OptimalSol] = sSContStructure(NumStartingSol, seed);
+% Inputs:
+%	a) NumStartingSol: Number of starting solutions required. Integer, >= 0
+%	b) seed: Seed for generating random starting solutions. Integer, >= 1
+% Return structural information on optimization problem
+%     a) minmax: -1 to minimize objective , +1 to maximize objective
+%     b) d: positive integer giving the dimension d of the domain
+%     c) m: nonnegative integer giving the number of constraints. All
+%        constraints must be inequality constraints of the form LHS >= 0.
+%        If problem is unconstrained (beyond variable bounds) then should be 0.
+%     d) VarNature: a d-dimensional column vector indicating the nature of
+%        each variable - real (0), integer (1), or categorical (2).
+%     e) VarBds: A d-by-2 matrix, the ith row of which gives lower and
+%        upper bounds on the ith variable, which can be -inf, +inf or any
+%        real number for real or integer variables. Categorical variables
+%        are assumed to take integer values including the lower and upper
+%        bound endpoints. Thus, for 3 categories, the lower and upper
+%        bounds could be 1,3 or 2, 4, etc.
+%     f) FnGradAvail: Equals 1 if gradient of function values are
+%        available, and 0 otherwise.
+%     g) NumConstraintGradAvail: Gives the number of constraints for which
+%        gradients of the LHS values are available. If positive, then those
+%        constraints come first in the vector of constraints.
+%     h) StartingSol: One starting solution in each row, or NaN if NumStartingSol=0.
+%        Solutions generated as per problem writeup
+%     i) budget: Column vector of suggested budgets, or NaN if none suggested
+%     j) ObjBd is a bound (upper bounds for maximization problems, lower
+%        bound for minimization problems) on the optimal solution value, or
+%        NaN if no such bound is known.
+%     k) OptimalSol is a d dimensional column vector giving an optimal
+%        solution if known, and it equals NaN if no optimal solution is
+%        known.
+
[…]

### 2014-05-20 code/matlab/sSCont_SetUpProblem1.m

@@ -1,0 +1,12 @@
+% This script creates a random problem instance of size 10000, and saves the
+% alternatives to a file.
+k=10000;
+alts_seed=1;
+
+structure = @sSContStructure;
+fn = @sSCont;
+
+% Get some starting solutions from the simopt structure function.  All other
+% return variables are returned.
+[minmax d m VarNature VarBds FnGradAvail NumConstraintGradAvail alts budget ObjBd OptimalSol] = structure(k,alts_seed);
+save 'sSCont.mat' alts alts_seed

### 2014-05-20 code/matlab/sSCont_SetUpProblem2.m

@@ -1,0 +1,33 @@
+% This script takes the alternatives created by sSCont_SetUpProblem1, stored in
+% sSCont.mat, and runs exhaustive simulation on alternatives from start_x to end_x (inclusive),
+% storing each result in a separate file, sSCont_SetUpProblem/x.mat
+% If only one argument is passed, simulations for just that passed x will be run.
+function sSCont_SetUpProblem2(start_x, end_x)
+if (nargin==1) 
+	end_x = start_x;
+end
+structure = @sSContStructure;
+fn = @sSCont;
+fn_runlength = 1050; % length to run the sSCont simulation
+fn_other = []; % this is not used by this simopt problem
+nruns = 10^4; % number of samples to use for exhaustive simulation
+starting_seed = 1; % seed at which to start the exhaustive simulation
+
+disp(sprintf('sSCont_SetUpProblem2(start_x=%d, end_x=%d)\n',start_x,end_x))
+
+load 'sSCont.mat' % loads a variable called alts, which contains the alternatives.
+
+% k is the number of alternatives. d is the dimension of vectors specifying an alternative.
+[k,d] = size(alts); 
+
+for x=start_x:end_x
+  y = zeros(1,nruns);
+  for n=1:nruns
+    y(n) = fn(alts(x,:),fn_runlength,starting_seed + n - 1,fn_other);
+  end
+  est_mean = mean(y);
+  est_var = var(y);
+
+  filename = sprintf('/fs/home/pf98/svn/biz/code/matlab/sSCont_SetUpProblem/%d.mat',x);
+  save(filename, 'est_mean','est_var','nruns','starting_seed','fn_runlength')
+end

### 2014-05-20 code/matlab/sSCont_SetUpProblem2.sh

@@ -1,0 +1,9 @@
+#!/bin/sh
+# Start many worker threads, each of which will save output to a separate file
+# in a directory specified within sSCont_SetUpProblem2.m
+for n in {1001..10000}
+do
+	# Add a job, which is to run sSCont_SetUpProblem2.nbs, to the long NBS queue.
+	# The flags at the end tell it to only send email if there is a failure.
+	jsub "sSCont_SetUpProblem2.nbs $n" -mail nostart end -mfail
+done

### 2014-05-20 code/matlab/sSCont_SetUpProblem3.m

@@ -1,0 +1,34 @@
+% This script reads in all of the files created by SetUpProblem2.sh in
+% sSCont_SetUpProblem/, and processes them into a single file.
+
+k = 10000; % number of alternatives
+Pstar = 0.8;
+delta = 1;
+structure = @sSContStructure;
+fn = @sSCont;
+fn_runlength = 1050;
+fn_other = []; % this is not used by this simopt problem
+load('sSCont.mat'); % should have alts, and alts_seed 
+
+est_mean = zeros(1,k);
+est_var = zeros(1,k);
+nruns = zeros(1,k);
+exhaustive_seed = zeros(1,k);
+for x=1:k
+  filename = sprintf('/fs/home/pf98/svn/biz/code/matlab/sSCont_SetUpProblem/%d.mat',x);
+  disp(filename);
+  % loads est_mean, est_var, nruns, starting_seed, fn_runlength for this run.
+  % the nruns, starting_seed, fn_runlength should all be the same.  We save nruns to be careful, 
+  % the est_mean and est_var are the estimated mean and variance of the simulation output for this alternative.
+  s = load(filename);  
+  est_mean(x) = s.est_mean;
+  est_var(x) = s.est_var;
+  nruns(x) = s.nruns(1);
+  exhaustive_seed(x) = s.starting_seed;
+  if (fn_runlength ~= s.fn_runlength)
+	warning(sprintf('fn_runlength in %s was %d rather than %d\n', filename, s.fn_runlength, fn_runlenth)); 
+  end
+end
+stderr = sqrt(est_var ./ nruns);
+
+save 'sSCont.mat' alts alts_seed est_mean est_var nruns exhaustive_seed stderr fn fn_runlength fn_other Pstar delta

### 2014-05-20 code/matlab/sSInt.m

@@ -1,0 +1,130 @@
+function [fn, FnVar, FnGrad, FnGradCov, constraint, ConstraintCov, ConstraintGrad, ConstraintGradCov] = sSInt(x, runlength, seed, other);
+% function [fn, FnVar, FnGrad, FnGradCov, constraint, ConstraintCov, ConstraintGrad, ConstraintGradCov] = sSInt(x, runlength, seed, other);
+% x is a vector containing 2 components: (s,S)
+% runlength is the number of hours of simulated time to simulate
+% seed is the index of the substreams to use (integer >= 1)
+% other is not used
+% Returns Mean cost, no var or gradient estimates.
+%   ****************************************
+%   *** Code written by German Gutierrez ***
+%   ***         gg92@cornell.edu         ***
+%   ***                                  ***
+%   *** Updated by Shane Henderson to    ***
+%   *** use standard calling and random  ***
+%   *** number streams                   ***
+%   ****************************************
+% Last updated August 24, 2011
+
+FnGrad = NaN;
+FnGradCov = NaN;
+constraint = NaN;
+ConstraintCov = NaN;
+ConstraintGrad = NaN;
+ConstraintGradCov = NaN;
+
+if (sum(x < 0) > 0) || (sum(x>2500)>0) || (runlength <= 0) || (seed <= 0) || (round(seed) ~= seed),
+    fprintf('x (row vector with %d components)\nx components should be between 0 and 1\nrunlength should be positive and real,\nseed should be a positive integer\n', nAmbulances*2);
+    fn = NaN;
+    FnVar = NaN;
+else % main simulation
+
+%%%%%%%%%%%%%%%%PARAMETERS%%%%%%%%%%%%%%%%%%
+nDays = runlength;               %Length of simulation
+nRepetitions = 20;          %Repetitions
+fixed = 36;                 %Fixed order cost
+var = 2;                    %Variable, per unit, cost
+holding = 1;                % Holding cost
+warmup = 50;                %length of warm up period
+
+%%%%%%%%Decision Variables%%%%%%%%%
+s= x(1); % 1000;
+S= x(2); % 2000;
+
+Output = zeros(2,nRepetitions);
+Inv = zeros(nRepetitions, nDays);
+
+% Generate new streams for demand and lead-time 
+[DemandStream, LTStream] = RandStream.create('mrg32k3a', 'NumStreams', 2);
+
+% Set the substream to the "seed"
+DemandStream.Substream = seed;
[…]

### 2014-05-20 code/matlab/sSIntStructure.m

@@ -1,0 +1,68 @@
+function [minmax d m VarNature VarBds FnGradAvail NumConstraintGradAvail, StartingSol, budget, ObjBd, OptimalSol] = sSIntStructure(NumStartingSol, seed)
+%function [minmax d m VarNature VarBds FnGradAvail NumConstraintGradAvail, StartingSol] = sSIntStructure(NumStartingSol, seed);
+% Inputs:
+%	a) NumStartingSol: Number of starting solutions required. Integer, >= 0
+%	b) seed: Seed for generating random starting solutions. Integer, >= 1
+% Return structural information on optimization problem
+%     a) minmax: -1 to minimize objective , +1 to maximize objective
+%     b) d: positive integer giving the dimension d of the domain
+%     c) m: nonnegative integer giving the number of constraints. All
+%        constraints must be inequality constraints of the form LHS >= 0.
+%        If problem is unconstrained (beyond variable bounds) then should be 0.
+%     d) VarNature: a d-dimensional column vector indicating the nature of
+%        each variable - real (0), integer (1), or categorical (2).
+%     e) VarBds: A d-by-2 matrix, the ith row of which gives lower and
+%        upper bounds on the ith variable, which can be -inf, +inf or any
+%        real number for real or integer variables. Categorical variables
+%        are assumed to take integer values including the lower and upper
+%        bound endpoints. Thus, for 3 categories, the lower and upper
+%        bounds could be 1,3 or 2, 4, etc.
+%     f) FnGradAvail: Equals 1 if gradient of function values are
+%        available, and 0 otherwise.
+%     g) NumConstraintGradAvail: Gives the number of constraints for which
+%        gradients of the LHS values are available. If positive, then those
+%        constraints come first in the vector of constraints.
+%     h) StartingSol: One starting solution in each row, or NaN if NumStartingSol=0.
+%        Solutions generated as per problem writeup
+%     i) budget: Column vector of suggested budgets, or NaN if none suggested
+%     j) ObjBd is a bound (upper bound for maximization problems, lower
+%        bound for minimization problems) on the optimal solution value, or
+%        NaN if no such bound is known.
+%     k) OptimalSol is a d dimensional column vector giving an optimal
+%        solution if known, and it equals NaN if no optimal solution is known.
+
+%   ***************************************
[…]

### 2014-05-20 code/matlab/test1.m

@@ -1,0 +1,23 @@
+% This script runs BIZUNK on a problem from the simopt library
+k = 3;
+Pstar = 0.8;
+delta = 1;
+
+structure = @sSContStructure;
+fn = @sSCont;
+fn_runlength = 1050;
+fn_other = []; % this is not used by this simopt problem
+
+% Get some starting solutions from the simopt structure function.  All other
+% return variables are returned.
+[minmax d m VarNature VarBds FnGradAvail NumConstraintGradAvail alts budget ObjBd OptimalSol] = structure(k,1);
+
+starting_seed = 1;
+
+% Use exhaustive simulation to figure out which alternatives are in the good-selection set.
+% exhaustive_n0 = 100;
+% [good, z_scores, nsamples] = DetermineGoodEnough(fn, runlength, other, StartingSol, starting_seed, exhaustive_n0, delta);
+good = [0 1 0];
+
+% Run BIZUNK
+BIZUNK(fn, fn_runlength, fn_other, alts, Pstar, delta, 1, 10);

### 2014-05-20 code/matlab/test2.m

@@ -1,0 +1,23 @@
+% This script runs KNUNK on a problem from the simopt library
+k = 3;
+Pstar = 0.8;
+delta = 1;
+
+structure = @sSContStructure;
+fn = @sSCont;
+fn_runlength = 1050;
+fn_other = []; % this is not used by this simopt problem
+
+% Get some starting solutions from the simopt structure function.  All other
+% return variables are returned.
+[minmax d m VarNature VarBds FnGradAvail NumConstraintGradAvail alts budget ObjBd OptimalSol] = structure(k,1);
+
+starting_seed = 1;
+
+% Use exhaustive simulation to figure out which alternatives are in the good-selection set.
+% exhaustive_n0 = 100;
+% [good, z_scores, nsamples] = DetermineGoodEnough(fn, runlength, other, StartingSol, starting_seed, exhaustive_n0, delta);
+good = [0 1 0];
+
+% Run KNUNK
+KNUNK(fn, fn_runlength, fn_other, alts, Pstar, delta, 1, 10);

### 2014-05-20 code/matlab/test3.m

@@ -1,0 +1,16 @@
+k=8;
+max_seed = 100;
+[est_N, stderr_N, est_PGS, stderr_PGS] = Oct13_Collect('BIZ','SC',k,max_seed);
+est_Nk = est_N / k;
+stderr_Nk = stderr_N / k;
+% this shouuld match the C++ results for SC under BIZUNK,
+% k=8 PCS=0.893+/-0.003 E[N]/k=362.183+/-1.513 E[stages]=160.864+/-1.302
+PGS_correct = 0.893;
+Nk_correct = 362;
+PGS_z = abs((est_PGS - PGS_correct)/stderr_PGS);
+Nk_z = abs((est_Nk - Nk_correct)/stderr_Nk);
+if (PGS_z > 3 || Nk_z > 3)
+  disp('test failed');
+else
+  disp('test OK');
+end

### 2014-05-20 code/matlab/test4.m

@@ -1,0 +1,18 @@
+k=8;
+max_seed = 1000;
+[est_N, stderr_N, est_PGS, stderr_PGS] = Oct13_Collect('KN','SC',k,max_seed);
+est_Nk = est_N / k;
+stderr_Nk = stderr_N / k;
+% this shouuld match the C++ results for SC under KNUNK,
+% k=8 PCS=0.942+/-0.002 E[N]/k=544.573+/-1.476 E[stages]=778.235+/-2.523
+PGS_correct = 0.942;
+Nk_correct = 544.573;
+PGS_z = abs((est_PGS - PGS_correct)/stderr_PGS);
+Nk_z = abs((est_Nk - Nk_correct)/stderr_Nk);
+if (PGS_z > 3 || Nk_z > 3)
+  disp('test failed');
+else
+  disp('test OK');
+end
+
+

### 2014-05-20 code/cpp/write_problems.cpp
Adding a function called write_trial() to write_problems.cpp, which outputs a new problem file, which has different variances. It currently has a bug, because the first problem has infinite variance.
Also, we re-ran write_problems, and this overwrote the previous values
for various other problem files, like RPI.dat

@@ -19,6 +19,7 @@ int write_RPI(const char *filename, int maxk, double pstar, double delta, double
 int write_SCvP(const char *filename, int k, double delta, double sigma1, double sigma2); 
 int write_PGS(const char *filename, int k, int m, double pstar, double delta, double sigma);
 int write_animation(const char *filename, int k, double pstar, double delta, double sigma);
+int write_trial(const char *filename);
 
 int main(int argc, char *argv[]) {
 
@@ -91,6 +92,10 @@ int main(int argc, char *argv[]) {
   sigma = 10;
   delta = 1;
   write_animation(FILE_DIR "ANIMATION.dat", k, pstar, delta, sigma);
+
+
+  // Write problem configurations for testing performance in certain limiting cases.
+  write_trial(FILE_DIR "TRIAL.dat");
 }
 
 /*
@@ -388,5 +393,47 @@ int write_animation(const char *filename, int k, double pstar, double delta, dou
    if (fwrite(theta,sizeof(*theta),k,file)<k) { fprintf(stderr, "error writing %s", filename); exit(-1); }
    if (fwrite(sigma_vec,sizeof(*sigma_vec),k,file)<k) { fprintf(stderr, "error writing %s", filename); exit(-1); }
 
+   fclose(file);
+}
+
+
+/*
+ * This function writes a problem that has different variances.
+ */
+int write_trial(const char *filename)
+{
+#ifdef USE_FIXED_SEED
+   int seed = 0;
+#else
+   int seed = (int)time(0);
+#endif
+   StochasticLib2 sto(seed);
+
+   FILE *file = fopen(filename,"w");
+   if (file == NULL) { fprintf(stderr,"could not open ", filename); exit(-1); }
+
+   int nProblems = 10;
+   if (fwrite(&nProblems,sizeof(nProblems),1,file)<1) { fprintf(stderr,"error writing %s", filename); exit(-1); }
+
+   int k = 10;
+   double pstar = 0.9;
+   double delta = 1;
+   double sigma = 1;
+   for(int i=0;i<=nProblems;i++) {
+     // least favorable configuration
+     double theta[k];
+     double sigma_vec[k];
+     for (int x=0; x<k; x++) {
+       theta[x]=-delta*x;
+       sigma_vec[x]= sigma/i; // set the variance to decrease with i.
+     }
+
+     // Write to file, in a binary format.
[…]

### 2014-06-03 code/cpp/write_problems.cpp
Adding incomplete proof

@@ -423,9 +423,9 @@ int write_trial(const char *filename)
    int k = 10;
    double pstar = 0.95;
 	double delta2=1.0;
-	double delta=1.0;
+	double delta=1.2;
    double sigma = 50.0;
-	double a=1.0;
+	double a=delta;
 	double b=0.6;
    for(int i=1;i<=nProblems;i++) {
      // least favorable configuration
@@ -435,7 +435,7 @@ int write_trial(const char *filename)
      double theta[k];
      double sigma_vec[k];
      for (int x=0; x<k; x++) {
-       theta[x]=(delta2)*x;
+       theta[x]=(delta)*x;
        sigma_vec[x]= sigma/(x+1); // set the variance to decrease with i.
      }
 

### 2014-06-04 paper/paper.tex
adding paper.pdf and .tex

%% LyX 2.0.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{esint}
\doublespacing

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}

\makeatother

\usepackage{babel}
\begin{document}
Without loss of generality, suppose that the true means of the systems
are indexed so that $\mu_{k}\geq\mu_{k-1}\geq\cdots\geq\mu_{1}$.
Assume $c>0$.

\paragraph*{Assumption 1 }

There exist finite constants $\mu_{i}$ and $v_{i}^{2}$ such that
the probability of distribution of $C_{i}\left(t,r\right)\equiv\frac{\sum_{j=1}^{floor(rt)}X_{ij}-rt\mu_{i}}{v_{i}\sqrt{r}}$
over $D\left[0,1\right]$ converges to that of a standard Brownian
motion process, $W(t)$, for $t$ on the unit interval, as $r$ increases;
i.e.
\[
C_{i}\left(,r\right)\Longrightarrow W\left(\right)
\]
as $r\rightarrow\infty$.

Note: $D\left[0,1\right]$ is the Skorohod space, i.e. it's the space
of real-valued functions on $\left[0,1\right]$ that are right-continuous
and have left-hand limits.

Under Assumption 1, $\mu_{i}$ is the mean, and $v_{i}^{2}=\lim_{r\rightarrow\infty}r\mbox{Var}\left(\bar{X}_{i}\left(r\right)\right)$
where $\bar{X}_{i}\left(r\right)$ is the sample mean of the first
$r$ observations from system $i$.

\paragraph*{Lemma 1.}

For $i\neq l$, if $\mathbf{X}_{i}$ and $\mathbf{X}_{l}$ satisfy
Assumption 1 and are independent, then there exists a constant $v_{il}^{2}$
such that 
\[
\frac{t_{l}\left(Y_{\mbox{floor}\left(rt_{i}\right),i}-rt_{i}\mu_{i}\right)-t_{i}\left(Y_{\mbox{floor}\left(rt_{l}\right),l}-rt_{l}\mu_{l}\right)}{v_{il}\sqrt{r}}\Longrightarrow t_{l}W_{1}\left(t_{i}\right)-t_{i}W_{2}\left(t_{l}\right)
\]
as $r\rightarrow\infty$.

\paragraph*{Proof.}

First, note that
\[
v_{il}^{2}:=\lim_{r,s\rightarrow\infty}\mbox{Var}\left(\sqrt{r}\bar{X}_{i}\left(r\right)+\sqrt{s}\bar{X}_{l}\left(s\right)\right)=v_{i}^{2}+v_{l}^{2}
\]
because of the independence of $\mathbf{X}_{i}$ and $\mathbf{X}_{l}$.
Now,
\begin{eqnarray*}
\frac{t_{l}\left(Y_{\mbox{floor}\left(rt_{i}\right),i}-rt_{i}\mu_{i}\right)-t_{i}\left(Y_{\mbox{floor}\left(rt_{l}\right),l}-rt_{l}\mu_{l}\right)}{v_{il}\sqrt{r}} & =\\
t_{l}\frac{\sum_{j=1}^{\mbox{floor}\left(rt_{i}\right)}X_{ij}-rt_{i}\mu_{i}}{v_{il}\sqrt{r}}-t_{i}\frac{\sum_{j=1}^{\mbox{floor}\left(rt\right)}X_{lj}-rt_{l}\mu_{l}}{v_{il}\sqrt{r}} & =\\
t_{l}\left(\frac{v_{i}}{v_{il}}\right)C_{i}\left(t,r\right)-t_{i}\left(\frac{v_{l}}{v_{il}}\right)C_{l}\left(t,r\right).
\end{eqnarray*}
Because we assume that $\mathbf{X}_{i}$ and $\mathbf{X}_{l}$ are
independent, so are $C_{i}\left(t,r\right)$ and $C_{l}\left(t,r\right)$.
Assumption 1 implies $C_{i}\left(,r\right)\Rightarrow W_{i}\left(\right)$
and $C_{l}\left(,r\right)\Rightarrow W_{l}\left(\right)$ where $W_{i}$
and $W_{l}$ are independent standard Brownian motion processes. By
Theorem 3.2 of Billingsley, $\left(C_{i}\left(,r\right),C_{l}\left(,r\right)\right)\Rightarrow\left(W_{i}\left(\right),W_{l}\left(\right)\right)$.
By the Continuous Mapping Theorem,$ $
\[
t_{l}\left(\frac{v_{i}}{v_{il}}\right)C_{i}\left(t,r\right)-t_{i}\left(\frac{v_{l}}{v_{il}}\right)C_{l}\left(t,s\right)\Rightarrow t_{l}\left(\frac{v_{i}}{v_{il}}\right)W_{i}\left(t\right)-t_{i}\left(\frac{v_{l}}{v_{il}}\right)W_{l}\left(t\right).
\]

\paragraph*{Lemma 2 (Fabian 1974). }

Let $W(t,\Delta)$ be a Brownian motion process on $[0,\infty)$,
with $E\left[W(t,\Delta)\right]=\Delta t$ and $Var\left[W\left(t,\Delta\right)\right]=t,$
where $\Delta>0$. Let 
\begin{eqnarray*}
L & = & -B\\
U & = & B
\end{eqnarray*}
for some $B>0$. Let $R=\left(L,U\right)$ and let $T^{*}$ be the
first time that $W\left(t,\Delta\right)\notin R$. Finally, let $\mathsf{A}$
be the event that $W\left(T^{*},\Delta\right)\leq-B$. Then,
\[
\mathbb{P}\left\{ \mathsf{A}\right\} =\frac{e^{-2B\Delta}}{1+e^{-2B\Delta}}.
\]

\[
\]

\paragraph*{Theorem.}

If samples from system $x\in\left\{ 1\ldots,k\right\} $ are normally
distributed and independent, over time and across alternatives, then
$\mbox{lim}_{\delta\rightarrow0}Pr\left\{ \mbox{BIZ selects }k\right\} \geq P*$
provided $\mu_{k}\geq\mu_{k-1}+\delta$. We also suppose that the
algorithm ends in at most $R\left(\delta\right)\in\mathbb{N}$ iterations,
and $R(\delta)\rightarrow\infty$ as $\delta\rightarrow0$ with probability
$1$. Furthermore, $\sqrt{R}\delta\rightarrow\Delta$ with probability
$1$ where $\infty>\Delta>0$ with probability $1$. Suppose $B_{1}=\cdots=B_{k}=1$.

\paragraph*{Proof.}

Suppose the variances are known. We begin by considering the case
of only two systems, denoted $k$ and $i$, with $\mu_{k}\geq\mu_{i}+\delta*$.
Let $A=\{k,i\}$. Let 
\[
T\left(\delta\right)=\mbox{min}\left\{ t\leq R,t\in\mathbb{N}:\mbox{min}_{x\in A}\hat{q}_{tx}\left(A\right)\leq c\mbox{ or }\mbox{max}_{x\in A}\hat{q}_{tx}\left(A\right)\geq P*\right\} .
\]
Thus $T\left(\delta\right)$ is the stage at which the procedure terminates.

Now, let $a_{t},b_{t}\in A$ such that $\exp\left(\delta\beta_{t}\frac{W_{ta_{t}}}{n_{ta_{t}}}\right)\geq\exp\left(\delta\beta_{t}\frac{W_{tb_{t}}}{n_{tb_{t}}}\right)$,
so 
\begin{eqnarray*}
\mbox{min}_{x\in A}\hat{q}_{tx}\left(A\right) & \leq & c\\
\Leftrightarrow\mbox{min}_{x\in A}\exp\left(\delta\beta_{t}\frac{W_{tx}}{n_{tx}}\right) & \leq & c\sum_{x'\in A}\exp\left(\delta\beta_{t}\frac{W_{tx'}}{n_{tx'}}\right)\\
\Leftrightarrow\exp\left(\delta\beta_{t}\frac{W_{tb_{t}}}{n_{tb_{t}}}\right)\left(1-c\right) & \leq & c\exp\left(\delta\beta_{t}\frac{W_{ta_{t}}}{n_{ta_{t}}}\right)\\
\Leftrightarrow\exp\left(\delta\beta_{t}\left(\frac{W_{tb_{t}}}{n_{tb_{t}}}-\frac{W_{ta_{t}}}{n_{ta_{t}}}\right)\right) & \leq & \frac{c}{1-c}
\end{eqnarray*}
\[
\]
an
\begin{eqnarray*}
\mbox{max}_{x\in A}\hat{q}_{tx}\left(A\right) & \geq & P*\\
\Leftrightarrow\mbox{max}_{x\in A}\exp\left(\delta\beta_{t}\frac{W_{tx}}{n_{tx}}\right) & \geq & P*\sum_{x'\in A}\exp\left(\delta\beta_{t}\frac{W_{tx'}}{n_{tx'}}\right)\\
\Leftrightarrow\exp\left(\delta\beta_{t}\frac{W_{ta_{t}}}{n_{ta_{t}}}\right)\left(1-P^{*}\right) & \geq & P^{*}\exp\left(\delta\beta_{t}\frac{W_{tb_{t}}}{n_{tb_{t}}}\right)\\
\Leftrightarrow\exp\left(\delta\beta_{t}\left(\frac{W_{ta_{t}}}{n_{ta_{t}}}-\frac{W_{tb_{t}}}{n_{tb_{t}}}\right)\right) & \geq & \frac{P^{*}}{1-P^{*}},
\end{eqnarray*}
thus
\begin{eqnarray*}
T\left(\delta\right) & = & \mbox{min}\left\{ t\leq R,t\in\mathbb{N}:\exp\left(\delta\beta_{t}\left|\frac{W_{tk}}{n_{tk}}-\frac{W_{ti}}{n_{ti}}\right|\right)\geq\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right\} \\
 & = & \mbox{min}\left\{ t\leq R,t\in\mathbb{N}:\left|\frac{W_{tk}}{n_{tk}}-\frac{W_{ti}}{n_{ti}}\right|\geq\frac{\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{\delta\beta_{t}}\right\} 
\end{eqnarray*}

Now, let's prove that $n_{ti}\rightarrow\infty,n_{tk}\rightarrow\infty$
as $t\rightarrow\text{\ensuremath{\infty}}$. For each $t$, $n_{t+1,x}=n_{tx}+B_{x}$
for some $x\in A$. If $n_{t+1,i}=n_{ti}+B_{i}$ for a finite number
of $t's$, then $n_{tk}\rightarrow\infty$ as $t\rightarrow\infty$.
So, there exists $l_{0}$ such that $n_{li}/\hat{\lambda}_{li}^{2}>n_{lk}/\hat{\lambda}_{lk}^{2}$
if $l>l_{0}$. Since $\hat{\lambda}_{ti}^{2}\rightarrow\sigma_{i}^{2}$
and $\hat{\lambda}_{tk}^{2}\rightarrow\sigma_{k}^{2}$ as $t\rightarrow\infty$,
then $n_{ti}\rightarrow\infty$ as $t\rightarrow\infty$. Similarly,
we get the same result in the other cases. Thus, $n_{ti}\rightarrow\infty,n_{tk}\rightarrow\infty$
as $t\rightarrow\text{\ensuremath{\infty}}$.

Let $\lambda_{r}^{2}=\mbox{min}\left\{ \lambda_{i}^{2},\lambda_{k}^{2}\right\} $
and $\lambda_{s}^{2}=\mbox{max}\left\{ \lambda_{i}^{2},\lambda_{k}^{2}\right\} $.
Then $n_{1,s}=n_{0}+1$, $n_{1r}=\mbox{max}\left\{ n_{0},ceil\left(\frac{\lambda_{r}^{2}}{\lambda_{s}^{2}}\left(n_{0}+1\right)\right)\right\} $.
Note that $\frac{n_{ts}}{\lambda_{s}^{2}}\leq\frac{n_{tr}}{\lambda_{r}^{2}}$
for all $t$, because by induction
\[
\frac{n_{t+1,r}}{\lambda_{r}^{2}}\geq\frac{\frac{\lambda_{r}^{2}}{\lambda_{s}^{2}}\left(n_{ts}+1\right)}{\lambda_{r}^{2}}=\frac{n_{ts}+1}{\lambda_{s}^{2}}.
\]

So, $n_{tr}=\mbox{max}\left\{ n_{t-1,r},ceil\left(\frac{\lambda_{r}^{2}}{\lambda_{s}^{2}}\left(n_{t-1,s}+1\right)\right)\right\} =\mbox{max}\left\{ n_{t-1,r},ceil\left(\frac{\lambda_{r}^{2}}{\lambda_{s}^{2}}\left(n_{0}+t\right)\right)\right\} $.
Thus there exists $t_{0}$ such that $n_{t_{0},r}=ceil\left(\frac{\lambda_{r}^{2}}{\lambda_{s}^{2}}\left(n_{0}+t_{0}\right)\right)$
and $n_{tr}=n_{0}$ if $t<t_{0}.$ Observe that if $t>t_{0}$, $n_{tr}=ceil\left(\frac{\lambda_{r}^{2}}{\lambda_{s}^{2}}\left(n_{0}+t\right)\right)$.
Furthermore, $n_{ts}=n_{0}+t$.

Suppose $i=s$ or $i=r$ and $t_{0}=1$. If $0\leq t\leq1$, let
\begin{eqnarray*}
D_{i}\left(t,R\right) & = & \frac{\sum_{j=1}^{n_{floor\left(tR\right),i}}X_{ij}-\left(n_{0}+\left(tR\right)\right)\mu_{i}}{v_{i}\sqrt{R}}\\
 & = & \frac{\sum_{j=1}^{n_{0}+floor\left(tR\right)}X_{ij}-\left(n_{0}+\left(tR\right)\right)\mu_{i}}{v_{i}\sqrt{R}}\\
 & = & \frac{\sum_{j=1}^{n_{0}}X_{ij}-n_{0}\mu_{i}}{v_{i}\sqrt{R}}+\frac{\sum_{j=1}^{floor\left(tR\right)}X_{i,n_{0}+j}-\left(tR\right)\mu_{i}}{v_{i}\sqrt{R}}\\
 & \Rightarrow & W_{i}\left(\right).
\end{eqnarray*}

Suppose $\lambda_{i}^{2}\leq\lambda_{k}^{2}$. Assume $t_{0}=1$.
Let
\begin{eqnarray*}
D_{ik}\left(t,R\right) & = & \frac{n_{tR,i}\left(\sum_{j=1}^{n_{floor(tR),k}}X_{kj}-\left(n_{0}+\left(tR\right)\right)\mu_{k}\right)}{v_{ik}R\sqrt{R}}\\
 &  & -\frac{n_{tR,k}\left(\sum_{j=1}^{n_{floor(tR),i}}X_{kj}-ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+\left(tR\right)\right)\right)\mu_{i}\right)}{v_{ik}R\sqrt{R}}\\
 & = & \frac{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(\sum_{j=1}^{(n_{0}+floor(tR))}X_{kj}-\left(n_{0}+\left(tR\right)\right)\mu_{k}\right)}{v_{ik}R\sqrt{R}}\\
 &  & -\frac{\left(n_{0}+tR\right)\left(\sum_{j=1}^{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+floor(tR)\right)\right)}X_{kj}-ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+\left(tR\right)\right)\mu_{i}\right)\right)}{v_{ik}R\sqrt{R}}\\
 & \Rightarrow & \frac{v_{k}}{v_{ik}}\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}tW_{k}\left(t\right)-\frac{v_{i}}{v_{ik}}tW_{i}\left(t\right)=tW\left(\right).
\end{eqnarray*}

Now, let $N=\mbox{max}\left\{ n_{Rk},n_{Ri}\right\} $, then 
\begin{eqnarray*}
\frac{W_{T\left(\delta\right)k}}{n_{T\left(\delta\right)k}} & < & \frac{W_{T\left(\delta\right)i}}{n_{T\left(\delta\right)i}}\\
\Leftrightarrow\frac{\mu_{k}-\mu_{i}}{R^{3/2}v_{ik}}\left(n_{T\left(\delta\right)k}n_{T\left(\delta\right)i}\right) & + & \frac{n_{T\left(\delta\right)i}\left(\sum_{j=1}^{n_{T\left(\delta\right)k}}X_{kj}-n_{T\left(\delta\right)k}\mu_{k}\right)-n_{T\left(\delta\right)k}\left(\sum_{j=1}^{n_{T\left(\delta\right)i}}X_{ij}-n_{T\left(\delta\right)i}\mu_{i}\right)}{R^{3/2}v_{ik}}<0.
\end{eqnarray*}

Then$ $
\begin{eqnarray*}
\mathbb{P}\left\{ \frac{W_{T\left(\delta\right)k}}{n_{T\left(\delta\right)k}}<\frac{W_{T\left(\delta\right)i}}{n_{T\left(\delta\right)i}}\right\}  & \leq & \mathbb{P}\left\{ \frac{n_{T\left(\delta\right)i}\left(\sum_{j=1}^{n_{T\left(\delta\right)k}}X_{kj}-n_{T\left(\delta\right)k}\mu_{k}\right)-n_{T\left(\delta\right)k}\left(\sum_{j=1}^{n_{T\left(\delta\right)i}}X_{ij}-n_{T\left(\delta\right)i}\mu_{i}\right)}{R^{3/2}v_{ik}}\right.\\
 &  & \left.+\frac{\delta}{R^{3/2}v_{ik}}\left(n_{T\left(\delta\right)k}n_{T\left(\delta\right)i}\right)<0\right\} \\
 & = & E\left[\mathbb{P}\left\{ \frac{n_{T\left(\delta\right)i}\left(\sum_{j=1}^{n_{T\left(\delta\right)k}}X_{kj}-n_{T\left(\delta\right)k}\mu_{k}\right)-n_{T\left(\delta\right)k}\left(\sum_{j=1}^{n_{T\left(\delta\right)i}}X_{ij}-n_{T\left(\delta\right)i}\mu_{i}\right)}{R^{3/2}v_{ik}}\right.\right.\\
 &  & \left.\left.+\frac{\delta}{R^{3/2}v_{ik}}\left(n_{T\left(\delta\right)k}n_{T\left(\delta\right)i}\right)<0\right\} \mid\Delta\right]
\end{eqnarray*}
Define
\begin{eqnarray*}
\hat{T}\left(\delta\right) & = & \mbox{min }\left\{ t\in\left\{ \frac{1}{R},\ldots,1\right\} :\left|D_{ik}\left(t,\delta\right)+\frac{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(n_{0}+tR\right)\delta}{R^{3/2}v_{ik}}\right|\right.\\
 &  & \left.\geq\frac{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(n_{0}+tR\right)\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{R^{3/2}v_{ik}\beta_{floor(tR)}\delta}\right\} 
\end{eqnarray*}
where $\beta_{tR}=\frac{n_{0}+tR+ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)}{\lambda_{i}^{2}+\lambda_{k}^{2}}$.

Clearly, $\hat{T}\left(\delta\right)=T\left(\delta\right)/R$. Also,
define the stopping time of the corresponding continuous-time process
as

\begin{eqnarray*}
\tilde{T}\left(\delta\right) & = & \mbox{min }\left\{ 1\geq t\geq\frac{1}{R}:\left|D_{ik}\left(t,\delta\right)+\frac{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(n_{0}+tR\right)\delta}{R^{3/2}v_{ik}}\right|\right.\\
 &  & \left.\geq\frac{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(n_{0}+tR\right)\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{R^{3/2}v_{ik}\beta_{floor(tR)}\delta}\right\} 
\end{eqnarray*}
Note that for fixed $\delta$, $D_{ik}\left(\hat{T}\left(\delta\right),\delta\right)$
corresponds to the right-hand limit of a point of discontinuity of
$D_{ik}\left(,\delta\right)$. We can show that $ $$\hat{T}\left(\delta\right)\rightarrow\tilde{T}\left(\delta\right)$
with probability $1$ as $\delta\rightarrow0$, making use of the
fact that $1/R\rightarrow0$ with probability $1$. Thus, in the limit,
we can focus on $D_{ik}\left(\tilde{T}\left(\delta\right),\delta\right)$.

Now, condition on $\Delta$. By Assumption 1, Lemma 1, and the CMT
we have that
\begin{eqnarray*}
D_{ik}\left(t,\delta\right)+\frac{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(n_{0}+tR\right)\delta}{R^{3/2}v_{ik}} & \Rightarrow & tW\left(t\right)+t^{2}\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\Delta.\\
 & = & t\left(W\left(t\right)+t\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\Delta\right)
\end{eqnarray*}
Let 
\begin{eqnarray*}
A\left(\delta\right) & = & \frac{n_{0}ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{R^{3/2}v_{ik}\beta_{tR}\delta}\\
 & = & \frac{\left(\lambda_{i}^{2}+\lambda_{k}^{2}\right)n_{0}ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{\left(n_{0}+tR+ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\right)R^{3/2}v_{ik}\delta}\overset{\delta\rightarrow0}{\longrightarrow}0
\end{eqnarray*}
and
\begin{eqnarray*}
tB\left(\delta\right) & = & \frac{\left(\lambda_{i}^{2}+\lambda_{k}^{2}\right)ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(tR\right)\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{\left(n_{0}+tR+ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\right)R^{3/2}v_{ik}\delta}\\
 & = & \frac{\left(\lambda_{i}^{2}+\lambda_{k}^{2}\right)ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(t\right)\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{\left(n_{0}+tR+ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\right)R^{1/2}v_{ik}\delta}\\
 & \overrightarrow{\delta\rightarrow0} & \frac{\left(\lambda_{i}^{2}+\lambda_{k}^{2}\right)\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(t\right)\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{\left(1+\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\right)v_{ik}\Delta}=Bt.
\end{eqnarray*}
Note that the stopping time $ $$\tilde{T}\left(\delta\right)$ is
the first time $t$ at which the event
\[
\left\{ \left|D_{ik}\left(t,\delta\right)+\frac{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(n_{0}+tR\right)\delta}{R^{3/2}v_{ik}}\right|-A\left(\delta\right)-tB\left(\delta\right)\geq0\right\} 
\]
occurs. Define the mapping $s_{\delta}:D\left[0,1\right]\rightarrow\mathbb{R}$
such that $s_{\delta}\left(Y\right)=Y\left(T_{Y,\delta}\right)$,
where 
\[
T_{Y,\delta}=\mbox{inf}\left\{ t:\left|Y\left(t\right)\right|-A\left(\delta\right)-B\left(\delta\right)t\geq0\right\} 
\]
for every $Y\in D\left[0,1\right]$ and $\delta>0$. Similarly, define
$s\left(Y\right)=Y\left(T_{Y}\right)$, where
\[
T_{Y}=\mbox{inf}\left\{ t>0:\left|Y\left(t\right)\right|-Bt\geq0\right\} 
\]
for every $Y\in D\left[0,1\right]$. Note that 
\begin{eqnarray*}
s_{\delta}\left(D_{ik}\left(t,\delta\right)+\frac{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(n_{0}+tR\right)\delta}{R^{3/2}v_{ik}}\right) & = & D_{ik}\left(\tilde{T}\left(\delta\right),\delta\right)\\
+\frac{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+\tilde{T}\left(\delta\right)R\right)\right)\left(n_{0}+\tilde{T}\left(\delta\right)R\right)\delta}{R^{3/2}v_{ik}},
\end{eqnarray*}
$s\left(tW\left(t,\Delta\right)\right)=T_{\mathfrak{W}\left(\right)}W\left(T_{\mathfrak{W}\left(\right)},\Delta\right)$
where $ $$\mathfrak{W}\left(t\right)=tW\left(t,\Delta\right)$.

We need to show that
\[
s_{\delta}\left(G_{ik}\left(t,\delta\right)\right)\Rightarrow s\left(tW\left(t,\Delta\right)\right)
\]
as $\delta\rightarrow0$, where
\[
G_{ik}\left(t,\delta\right)\equiv D_{ik}\left(t,\delta\right)+\frac{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+tR\right)\right)\left(n_{0}+tR\right)\delta}{R^{3/2}v_{ik}}
\]
for $t\in\left[0,1\right]$ and $\delta>0$. If $\mathbb{P}\left(tW\left(t,\Delta)\text{\ensuremath{\in}D\ensuremath{\left[0,1\right]}-}D_{s}\right)\right)=1$
where $D_{s}\equiv\left\{ x\right.\in D\left[0,1\right]:\mbox{ for some sequence }\left\{ x_{n}\right\} \subset D\left[0,1\right]\mbox{ with }lim_{n}d\left(x_{n},x\right)=0,\mbox{ the sequence }$$\left\{ s_{\delta_{n}}\left(x_{n}\right)\right\} $
$\left.\mbox{ does not converge to }s\left(x\right)\right\} $, and
$d\left(X,Y\right)$ is the infimum of those positive $w$ for which
there exists $\lambda\in\Lambda$ such that $sup_{t\in\left[0,1\right]}\left|X(t)-Y\left(\lambda(t)\right)\right|\leq w$
and $sup_{t\in\left[0,1\right]}\left|\lambda(t)-t\right|\leq w$ ($\Lambda$
is the class of strictly increasing, continuous mappings of $\left[0,1\right]$
onto itself such that for every $\lambda\in\Lambda$, we have $\lambda(0)=0$
and $\lambda(1)=1$), then by Theorem 5.5 of Billingsley 1968 we conclude
that this is true. By Kim et al. (2005), we know that $\mathbb{P}\left(W\left(t,\Delta)\text{\ensuremath{\in}D\ensuremath{\left[0,1\right]}-}D_{s}\right)\right)=1$,
thus it follows this is true (prove).

Now, unconditioning on $\Delta$ gives
\begin{eqnarray*}
\mbox{lim}sup_{\delta\rightarrow0}\mathbb{P}\left(ICS\right) & \leq & E\left[\mathbb{P}\left[\tilde{T}\left(\delta\right)W\left(\tilde{T}\left(\delta\right),\Delta\right)<0\mid\Delta]]\right.\right.\\
 & = & E\left[\frac{e^{-2B\Delta\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}}}{1+e^{-2B\Delta\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}}}\right]\\
 & = & E\left[\frac{e^{-\frac{2\frac{\lambda_{i}^{4}}{\lambda_{k}^{2}}\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{v_{ik}}}}{1+e^{-\frac{2\frac{\lambda_{i}^{4}}{\lambda_{k}^{2}}\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{v_{ik}}}}\right]\\
 & = & E\left[\frac{1}{1+e^{\frac{2\frac{\lambda_{i}^{4}}{\lambda_{k}^{2}}\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{v_{ik}}}}\right]\\
 & = & E\left[\frac{1}{1+\left(\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right)^{2\frac{\lambda_{i}^{4}}{\lambda_{k}^{2}v_{ik}}}}\right]\\
 & \leq & \frac{1}{1+\left(\frac{P^{*}}{1-P^{*}}\right)^{2\frac{\lambda_{i}^{4}}{\lambda_{k}^{2}v_{ik}}}}\leq1-P^{*}
\end{eqnarray*}
the last equality follows because, if $a=2\frac{\lambda_{i}^{4}}{\lambda_{k}^{2}v_{ik}}$,
\begin{eqnarray*}
\frac{1}{1+\left(\frac{P^{*}}{1-P^{*}}\right)^{a}} & \leq & 1-P^{*}\\
\Leftrightarrow\frac{\left(1-P^{*}\right)^{a}}{\left(1-P^{*}\right)^{a}+P^{*a}} & \leq & 1-P^{*}\\
\Leftrightarrow\left(1-P^{*}\right)^{a-1} & \leq & \left(1-P^{*}\right)^{a}+P^{*a}\\
\Leftrightarrow\left(1-P^{*}\right)^{a-1}\left(1-1+P^{*}\right) & \leq & P^{*a}\\
\Leftrightarrow\left(1-P^{*}\right)^{a-1} & \leq & P^{*\left(a-1\right)}\\
\Leftrightarrow1 & \leq & 2P^{*}.
\end{eqnarray*}

\textbf{\large (I haven't erased the following in case I need it later) }{\large \par}

Observe that,$ $
\[
\mu_{k}-\mu_{i}+\frac{v_{k}}{\sqrt{n_{T\left(\delta\right)k}}}C_{k}\left(1,n_{T\left(\delta\right)k}\right)-\frac{v_{i}}{\sqrt{n_{T\left(\delta\right)i}}}C_{i}\left(1,n_{T\left(\delta\right)i}\right)\Rightarrow\mu_{k}-\mu_{i}
\]
when $\delta\rightarrow0$ if $n_{T(\delta)j}$ is independent of
$C_{j}\left(1,n\right)$ for $n$ sufficiently large and $j=k,i$.

\[
\]

Suppose $i=r$ and $t_{0}>1$. Let $s_{0}\leq t\leq1$ where $floor(s_{0}R)\geq t_{0}$
and $floor(sR)<t_{0}$ if $s<s_{0}$. Let
\begin{eqnarray*}
D_{i}\left(t,R\right) & = & \frac{\sum_{j=1}^{n_{floor\left(tR\right),i}}X_{ij}-\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+\left(tR\right)\right)\mu_{i}}{v_{i}\sqrt{R}}\\
 & = & \frac{\sum_{j=1}^{ceil\left(\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\left(n_{0}+floor\left(tR\right)\right)\right)}X_{ij}-\left(n_{0}+\left(tR\right)\right)\mu_{i}}{v_{i}\sqrt{R}}
\end{eqnarray*}

and if $t<s_{0}$
\begin{eqnarray*}
D_{i}\left(t,R\right) & = & \frac{\sum_{j=1}^{n_{floor\left(tR\right),i}}X_{ij}-n_{0}\mu_{i}}{v_{i}\sqrt{R}}\\
 & = & \frac{\sum_{j=1}^{n_{0}}X_{ij}-n_{0}\mu_{i}}{v_{i}\sqrt{R}},
\end{eqnarray*}
Suppose $D_{i}\left(t,R\right)\Rightarrow W\left(\right)$ if $t\geq s_{0}$.

\[
D_{ik}\left(t,R\right)=\frac{\sum_{j=1}^{n}}{v_{ik}\sqrt{R}}
\]

\[
\]

\[
\]

By Assumption 1, Lemma 1, and the CMT we have that
\[
C_{ik}\left(\frac{n_{t,i}}{N},\frac{n_{t,k}}{N},\delta\right)+\frac{n_{t,k}n_{t,i}\delta}{N^{1/2}v_{ik}}\Rightarrow n_{ti}W_{1}\left(n_{ti}\right)-n_{tk}W_{2}\left(n_{tk}\right)+\frac{n_{t,k}n_{t,i}\Delta}{v_{ik}}.
\]
Let 
\[
A\left(\delta\right)=\frac{\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{N^{1/2}v_{ik}\delta}\rightarrow\frac{\log\left[\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right]}{N^{1/2}v_{ik}\delta}
\]

\[
\beta_{t}=\sum
\]

Observe that,$ $
\[
\mu_{k}-\mu_{i}+\frac{v_{k}}{\sqrt{n_{T\left(\delta\right)k}}}C_{k}\left(1,n_{T\left(\delta\right)k}\right)-\frac{v_{i}}{\sqrt{n_{T\left(\delta\right)i}}}C_{i}\left(1,n_{T\left(\delta\right)i}\right)\Rightarrow\mu_{k}-\mu_{i}
\]
when $\delta\rightarrow0$ if $n_{T(\delta)j}$ is independent of
$C_{j}\left(1,n\right)$ for $n$ sufficiently large and $j=k,i$.

\[
\]

Let $ICS$ denote the even that an incorrect selection is made. Then,
\begin{eqnarray*}
\mbox{lim inf}_{\delta\rightarrow0}\mathbb{P}\left\{ ICS\right\}  & = & \mbox{lim inf}_{\delta\rightarrow0}\mathbb{P}\left\{ \frac{W_{T\left(\delta\right)k}}{n_{T\left(\delta\right)k}}<\frac{W_{T\left(\delta\right)i}}{n_{T\left(\delta\right)i}}\right\} \\
 & = & \mathbb{P}\left\{ \mu_{k}<\mu_{i}\right\} =0.
\end{eqnarray*}

However, it's very likely $n_{T(\delta)k}$ is not independent of
$C_{k}\left(1,n\right)$. Thus, let's give other proof. First, we'll
show that $n_{ti}$ is independent of $C_{i}(1,n)$ if $n\geq1$ and
$t\geq0$. Note that 
\begin{eqnarray*}
C_{i}\left(1,n\right) & = & \frac{\sqrt{n}\sum_{j=1}^{n}X_{ij}}{v_{i}n}-\frac{\sqrt{n}}{v_{i}}\mu_{i}\\
 & = & \frac{\sqrt{n}\bar{X}_{i}\left(n\right)}{v_{i}}-\frac{\sqrt{n}}{v_{i}}\mu_{i}.
\end{eqnarray*}
Since $n_{0i}=n_{0}$, then $C_{i}\left(1,n\right)$ is independent
of $n_{0i}$. Note that
\[
n_{1,i}=\mbox{ceil}\left(\hat{\lambda_{0i}^{2}}\left(n_{0}+B_{z}\right)/\hat{\lambda_{0z}^{2}}\right),
\]
if $z=i$, then $n_{1,i}$ is independent of $C_{i}\left(1,n\right)$.
Suppose $z=k$. Note that

\begin{eqnarray*}
\hat{\lambda_{1i}^{2}} & = & \frac{1}{n-1}\sum_{j=1}^{n_{1i}}\left(X_{ij}-\bar{X}_{i}\left(n_{1i}\right)\right)^{2}\\
 & = & \frac{1}{n-1}\left(\left(X_{i1}-\bar{X}_{i}\left(n_{1i}\right)\right)^{2}+\sum_{j=2}^{n_{ti}}\left(X_{ij}-\bar{X}_{i}\left(n_{1i}\right)\right)^{2}\right)\\
 & = & \frac{1}{n-1}\left(\left[\sum_{j=2}^{n_{1i}}\left(X_{ij}-\bar{X}_{i}\left(n_{1i}\right)\right)^{2}\right]+\sum_{j=2}^{n_{1i}}\left(X_{ij}-\bar{X}_{i}\left(n_{1i}\right)\right)^{2}\right).
\end{eqnarray*}

Then $ $$\hat{\lambda}_{1i}^{2}$ can be written as a function only
of $\left(X_{i2}-\bar{X}_{i}\left(n_{0i}\right),\ldots,X_{in_{ti}}-\bar{X}_{i}\left(n_{ti}\right),n_{ti}\right)$.

\[
\]

Suppose $C_{i}\left(1,n\right)$ is independent of $n_{ti}$. Observe
that 
\[
n_{t+1,i}=\mbox{ceil}\left(\hat{\lambda_{ti}^{2}}\left(n_{tz}+B_{z}\right)/\hat{\lambda_{tz}^{2}}\right),
\]
if $z=i$, then $n_{t+1,i}=\mbox{ceil}\left(\left(n_{tz}+B_{z}\right)\right)$
and $C_{i}\left(1,n\right)$ are independent random variables. Now
suppose $z=k$. Note that $ $
\begin{eqnarray*}
\hat{\lambda_{ti}^{2}} & = & \frac{1}{n-1}\sum_{j=1}^{n_{ti}}\left(X_{ij}-\bar{X}_{i}\left(n_{ti}\right)\right)^{2}\\
 & = & \frac{1}{n-1}\left(\left(X_{i1}-\bar{X}_{i}\left(n_{ti}\right)\right)^{2}+\sum_{j=2}^{n_{ti}}\left(X_{ij}-\bar{X}_{i}\left(n_{ti}\right)\right)^{2}\right)\\
 & = & \frac{1}{n-1}\left(\left[\sum_{j=2}^{n_{ti}}\left(X_{ij}-\bar{X}_{i}\left(n_{ti}\right)\right)\right]^{2}+\sum_{j=2}^{n_{ti}}\left(X_{ij}-\bar{X}_{i}\left(n_{ti}\right)\right)^{2}\right).
\end{eqnarray*}
Then $ $$\hat{\lambda_{ti}^{2}}$ can be written as a function only
of $\left(X_{i2}-\bar{X}_{i}\left(n_{ti}\right),\ldots,X_{in_{ti}}-\bar{X}_{i}\left(n_{ti}\right),n_{ti}\right)$.
Suppose $n_{ti}$ is given. The joint pdf of the sample $X_{i1},\ldots,X_{in_{ti}}$
is given by
\[
f\left(x_{1},\ldots,x_{n_{ti}}\right)=\frac{1}{\left(2\pi\right)^{n_{ti}/2}}e^{-\left(1/2\right)\sum_{i=1}^{n_{ti}}x_{i}^{2}}.
\]
Make the transformation $y_{1}=\bar{x}\left(n_{ti}\right),y_{2}=x_{2}-\bar{x}\left(n_{ti}\right),\ldots,y_{n_{ti}}=x_{n_{ti}}-\bar{x}\left(n_{ti}\right)$.
This is a linear transformation with a Jacobian equal to $1/n_{ti}$.
We have
\begin{eqnarray*}
f\left(y_{1},\ldots,y_{n_{ti}}\right) & = & \frac{n_{ti}}{\left(2\pi\right)^{n_{ti}/2}}e^{-\left(1/2\right)\left(y_{1}-\sum_{i=2}^{n_{ti}}y_{i}\right)^{2}}e^{-\left(1/2\right)\sum_{i=2}^{n_{ti}}\left(y_{i}+y_{1}\right)^{2}}\\
 & = & \left[\left(\frac{n_{ti}}{2\pi}\right)^{1/2}e^{\left(-n_{ti}y_{1}^{2}\right)/2}\right]\left[\frac{n_{ti}^{1/2}}{\left(2\pi\right)^{(n_{ti}-1)/2}}e^{-\left(1/2\right)\left[\sum_{i=2}^{n_{ti}}y_{i}^{2}+\left(\sum_{i=2}^{n_{ti}}y_{i}\right)^{2}\right]}\right].
\end{eqnarray*}
Then $y_{1}$ is independent of $\hat{\lambda_{ti}^{2}}$ given $n_{ti}$.
If $n_{ti}\geq n$, then $\bar{X}_{i}\left(n\right)$ is independent
of $\hat{\lambda_{ti}^{2}}$ because $ $$X_{ij}$ is independent
of $X_{ij'}$ for $j'<j$. If $n_{ti}<n$,
\begin{eqnarray*}
\bar{X}_{i}\left(n\right) & = & \frac{\sum_{j=1}^{n_{ti}}X_{ij}}{n_{ti}}\frac{n_{ti}}{n}+\frac{\sum_{j=n_{ti+1}}^{n}X_{ij}}{n}\\
 & = & Y_{1}\frac{n_{ti}}{n}+\frac{\sum_{j=n_{ti+1}}^{n}X_{ij}}{n}
\end{eqnarray*}
and then $\bar{X}_{i}\left(n\right)$ is independent of $\hat{\lambda_{ti}^{2}}$.
Thus, $C_{i}\left(1,n\right)$ is independent of $ $$\hat{\lambda_{ti}^{2}}$
given $n_{ti}$. $ $So, by induction, 
\begin{eqnarray*}
f\left(C_{i}\left(1,n\right),\hat{\lambda_{ti}^{2}}\right) & = & \int f\left(C_{i}\left(1,n\right),\hat{\lambda_{ti}^{2}}\mid n_{ti}\right)f\left(n_{ti}\right)dn_{ti}\\
 & = & f\left(C_{i}\left(1,n\right)\right)f\left(\hat{\lambda_{ti}^{2}}\right),
\end{eqnarray*}
then $C_{i}\left(1,n\right)$ is independent of $ $$\hat{\lambda_{ti}^{2}}$.
Consequently, $C_{i}\left(1,n\right)$ is independent of $n_{t,i+1}$.
Thus
\[
\mu_{k}-\mu_{i}+\frac{v_{k}}{\sqrt{n_{tk}}}C_{k}\left(1,n_{tk}\right)-\frac{v_{i}}{\sqrt{n_{ti}}}C_{i}\left(1,n_{ti}\right)\Rightarrow\mu_{k}-\mu_{i}
\]
as $t\rightarrow\infty$. Let $Y_{t}=C_{k}\left(1,n_{T\left(1/t\right)k}\right)$
and $X_{t}=C_{k}\left(1,n_{tk}\right)$, if $d\left(Y_{t},X_{t}\right)\rightarrow0$
in probability, then $Y_{t}\Rightarrow W\left(\right)$. Thus the
result would be proved. Let's show that $ $$d\left(Y_{t},X_{t}\right)\rightarrow0$.
???Let $\epsilon>0$.

\[
\]

\[
\]

\[
\mu_{k}-\mu_{i}+\frac{v_{k}}{\sqrt{n_{T\left(\delta\right)k}}}C_{k}\left(1,n_{tk}\right)-\frac{v_{i}}{\sqrt{n_{T\left(\delta\right)i}}}C_{i}\left(1,n_{T\left(\delta\right)i}\right)\Rightarrow\mu_{k}-\mu_{i}
\]

\begin{eqnarray*}
\mathbb{P}\left\{ \frac{W_{T\left(\delta\right)k}}{n_{T\left(\delta\right)k}}<\frac{W_{T\left(\delta\right)i}}{n_{T\left(\delta\right)i}}\right\}  & = & \mathbb{P}\left\{ \frac{W_{T\left(\delta\right)k}}{n_{T\left(\delta\right)k}}<\frac{W_{T\left(\delta\right)i}}{n_{T\left(\delta\right)i}}\right\} \\
\end{eqnarray*}

Now consider $k\geq2$ systems and let $CS$ be the event that $k$
is selected and let $ICS_{i}$ be the event that an incorrect selection
is made when systems $k$ and $i$ are considered in isolation.

\paragraph*{Theorem.}

If samples from system $x\in\left\{ 1\ldots,k\right\} $ are normally
distributed and independent, over time and across alternatives, then
$\mbox{lim}_{\mbox{min}_{x}\sigma_{x}^{2}\rightarrow\infty}Pr\left\{ \mbox{BIZ selects }k\right\} \geq P*$
provided $\mu_{k}\geq\mu_{k-1}+\delta*$ for some $\delta*>0$.

\paragraph*{Graphs}

Delta goes to 0

\includegraphics[scale=0.5]{/Users/saultoscano/Documents/graph1}

Delta goes to 0.

\includegraphics[scale=0.5]{graph1_paper}

\includegraphics[scale=0.5]{graph4}

Variances go to infinity.

\includegraphics[scale=0.5]{graph2}

\includegraphics[scale=0.5]{graph3}

\paragraph*{Theorem.}

If samples from system $x\in\left\{ 1\ldots,k\right\} $ are normally
distributed and independent, over time and across alternatives, then
$\mbox{lim}_{\delta\rightarrow0}Pr\left\{ \mbox{BIZ selects }k\right\} \geq P*$
(or =1??) provided $\mu_{k}\geq\mu_{k-1}+\delta^{*}$.

\paragraph*{Prooof.}

We begin by considering the case of only two systems, denoted $k$
and $i$, with $\mu_{k}\geq\mu_{i}+\delta*$. Let $A=\{k,i\}$. For
$\delta\leq\delta*$, let 
\[
T\left(\delta\right)=\mbox{min}\left\{ t\in\mathbb{N}:\mbox{min}_{x\in A}\hat{q}_{tx}\left(A\right)\leq c\mbox{ or }\mbox{max}_{x\in A}\hat{q}_{tx}\left(A\right)\geq P*\right\} .
\]
Thus $T\left(\delta\right)$ is the stage at which the procedure terminates.

Now,
\begin{eqnarray*}
\mbox{min}_{x\in A}\hat{q}_{tx}\left(A\right) & \leq & c\\
\Leftrightarrow\mbox{min}_{x\in A}\exp\left(\delta\beta_{t}\frac{W_{tx}}{n_{tx}}\right) & \leq & c\sum_{x'\in A}\exp\left(\delta\beta_{t}\frac{W_{tx'}}{n_{tx'}}\right)\\
\Leftrightarrow\mbox{min}_{x\in A}\frac{W_{tx}}{n_{tx}} & \leq & \log\left[c\sum_{x'\in A}\exp\left(\delta\beta_{t}\frac{W_{tx'}}{n_{tx'}}\right)\right]/\left(\delta\beta_{t}\right)\\
\Leftrightarrow\left(\frac{W_{tk}}{n_{tk}}+\frac{W_{ti}}{n_{ti}}-\left|\frac{W_{tk}}{n_{tk}}-\frac{W_{ti}}{n_{ti}}\right|\right) & \leq & 2\log\left[c\sum_{x'\in A}\exp\left(\delta\beta_{t}\frac{W_{tx'}}{n_{tx'}}\right)\right]/\left(\delta\beta_{t}\right)
\end{eqnarray*}
\[
\]
and
\begin{eqnarray*}
\mbox{max}_{x\in A}\hat{q}_{tx}\left(A\right) & \geq & P*\\
\Leftrightarrow\mbox{max}_{x\in A}\exp\left(\delta\beta_{t}\frac{W_{tx}}{n_{tx}}\right) & \geq & P*\sum_{x'\in A}\exp\left(\delta\beta_{t}\frac{W_{tx'}}{n_{tx'}}\right)\\
\Leftrightarrow\mbox{max}_{x\in A}\frac{W_{tx}}{n_{tx}} & \geq & \log\left[P*\sum_{x'\in A}\exp\left(\delta\beta_{t}\frac{W_{tx'}}{n_{tx'}}\right)\right]/\left(\delta\beta_{t}\right)\\
\Leftrightarrow\left(\frac{W_{tk}}{n_{tk}}+\frac{W_{ti}}{n_{ti}}+\left|\frac{W_{tk}}{n_{tk}}-\frac{W_{ti}}{n_{ti}}\right|\right) & \geq & 2\log\left[P*\sum_{x'\in A}\exp\left(\delta\beta_{t}\frac{W_{tx'}}{n_{tx'}}\right)\right]/\left(\delta\beta_{t}\right).
\end{eqnarray*}

Let $d\left(\delta\right):=2\log\left(\sum_{x'\in A}\exp\left(\delta\beta_{t}\frac{W_{tx'}}{n_{tx'}}\right)\right)/\left(\delta\beta_{t}\right)$,
then 
\begin{eqnarray*}
T\left(\delta\right) & = & \mbox{min}\left\{ t\in\mathbb{N}:\left(\frac{W_{tk}}{n_{tk}}+\frac{W_{ti}}{n_{ti}}+\left|\frac{W_{tk}}{n_{tk}}-\frac{W_{ti}}{n_{ti}}\right|\right)\geq2\frac{\log\left(P*\right)}{\delta\beta_{t}}+d\left(\delta\right)\mbox{ or}\right.\\
 &  & \left.\mbox{{\color{white}ssssssssss}}\left(\frac{W_{tk}}{n_{tk}}+\frac{W_{ti}}{n_{ti}}-\left|\frac{W_{tk}}{n_{tk}}-\frac{W_{ti}}{n_{ti}}\right|\right)\leq2\frac{\log c}{\delta\beta_{t}}+d\left(\delta\right){\color{white}aaaaaa}\right\} .
\end{eqnarray*}

Now, let's prove that $n_{ti}\rightarrow\infty,n_{tk}\rightarrow\infty$
as $t\rightarrow\text{\ensuremath{\infty}}$. For each $t$, $n_{t+1,x}=n_{tx}+B_{x}$
for some $x\in A$. If $n_{t+1,i}=n_{ti}+B_{i}$ for a finite number
of $t's$, then $n_{tk}\rightarrow\infty$ as $t\rightarrow\infty$.
So, there exists $l_{0}$ such that $n_{li}/\hat{\lambda}_{li}^{2}>n_{lk}/\hat{\lambda}_{lk}^{2}$
if $l>l_{0}$. Since $\hat{\lambda}_{ti}^{2}\rightarrow\sigma_{i}^{2}$
and $\hat{\lambda}_{tk}^{2}\rightarrow\sigma_{k}^{2}$ as $t\rightarrow\infty$,
then $n_{ti}\rightarrow\infty$ as $t\rightarrow\infty$. Similarly,
we get the same result in the other cases. Thus, $n_{ti}\rightarrow\infty,n_{tk}\rightarrow\infty$
as $t\rightarrow\text{\ensuremath{\infty}}$. Furthermore, it's easy
to see that $T\left(\delta\right)\rightarrow\infty$ as $\delta\rightarrow0$.

Now, we'll show that $T\left(\delta\right)$ is finite. Observe that
there exists $t_{0}$ such that if $t>t_{0}$
\[
W_{ti}/n_{ti}<W_{tk}/n_{tk},
\]
otherwise there would exists $t$ such that 
\[
\mu_{k}-\delta/2<W_{tk}/n_{tk}\leq W_{ti}/n_{ti}<\delta/2+\mu_{i}
\]
which is a contradiction. Moreover, there exists $t_{1}>t_{0}$ such
that if $t>t_{1}$ 
\[
\beta_{t}\left(W_{tk}/n_{tk}-W_{ti}/n_{ti}\right)>\log\left(P*/\left(1-P*\right)\right)/\delta
\]
since $\beta_{t}\rightarrow\infty$ as $t\rightarrow\infty$ and $P*>\frac{1}{2}$.
Consequently, if $t>t_{1}$
\begin{eqnarray*}
\exp\left(\delta\beta_{t}\frac{W_{tk}}{n_{tk}}\right)/\exp\left(\delta\beta_{t}\frac{W_{ti}}{n_{ti}}\right) & > & \frac{P*}{1-P*}\\
\Rightarrow\exp\left(\delta\beta_{t}\frac{W_{tk}}{n_{tk}}\right) & > & P*\exp\left(\delta\beta_{t}\frac{W_{ti}}{n_{ti}}\right)\\
 &  & +P*\exp\left(\delta\beta_{t}\frac{W_{tk}}{n_{tk}}\right)
\end{eqnarray*}
and so $T\left(\delta\right)\leq t_{1}\left(\delta\right)<\infty$.

By the strong law of large numbers, almost surely

\[
\frac{W_{T\left(\delta\right)k}}{n_{T\left(\delta\right)k}}-\frac{W_{T\left(\delta\right)i}}{n_{T\left(\delta\right)i}}\rightarrow\mu_{k}-\mu_{i}
\]
as $\delta\rightarrow0$. Thus, 
\[
\frac{W_{T\left(\delta\right)k}}{n_{T\left(\delta\right)k}}-\frac{W_{T\left(\delta\right)i}}{n_{T\left(\delta\right)i}}\Rightarrow\mu_{k}-\mu_{i}
\]
as $\delta\rightarrow0$.

Let $ICS$ denote the even that an incorrect selection is made. Then,
\begin{eqnarray*}
\mbox{lim inf}_{\delta\rightarrow0}\mathbb{P}\left\{ ICS\right\}  & = & \mbox{lim inf}_{\delta\rightarrow0}\mathbb{P}\left\{ \frac{W_{T\left(\delta\right)k}}{n_{T\left(\delta\right)k}}<\frac{W_{T\left(\delta\right)i}}{n_{T\left(\delta\right)i}}\right\} \\
 & = & \mathbb{P}\left\{ \mu_{k}<\mu_{i}\right\} =0.
\end{eqnarray*}

\end{document}

### 2014-06-27 paper/paper.tex
,

@@
 \usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
 \usepackage{color}
@@
 \usepackage{babel}
+\usepackage{xunicode}
 \begin{document}
@@
 \begin{eqnarray*}
-\mbox{lim}sup_{\delta\rightarrow0}\mathbb{P}\left(ICS\right) & \leq & E\left[\mathbb{P}\left[\tilde{T}\left(\delta\right)W\left(\tilde{T}\left(\delta\right),\Delta\right)<0\mid\Delta]]\right.\right.\\
+\mbox{lim}sup_{\delta\rightarrow0}\mathbb{P}\left(ICS\right) & \leq & E\left[\mathbb{P}\left[\tilde{T}\left(\delta\right)W\left(\tilde{T}\left(\delta\right),\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}\Delta\right)<0\mid\Delta]]\right.\right.\\
  & = & E\left[\frac{e^{-2B\Delta\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}}}{1+e^{-2B\Delta\frac{\lambda_{i}^{2}}{\lambda_{k}^{2}}}}\right]\\
@@
  & = & E\left[\frac{1}{1+\left(\mbox{min}\left\{ \frac{P^{*}}{1-P^{*}},\frac{1-c}{c}\right\} \right)^{2\frac{\lambda_{i}^{4}}{\lambda_{k}^{2}v_{ik}}}}\right]\\
- & \leq & \frac{1}{1+\left(\frac{P^{*}}{1-P^{*}}\right)^{2\frac{\lambda_{i}^{4}}{\lambda_{k}^{2}v_{ik}}}}\leq1-P^{*}
+ & \leq & \frac{1}{1+\left(\frac{P^{*}}{1-P^{*}}\right)^{2\frac{\lambda_{i}^{4}}{\lambda_{k}^{2}v_{ik}}}}\leq\left(1-P^{*}\right)\leq\left(1-P^{*}\right)^{1/(k-1)}
 \end{eqnarray*}
@@
 \Leftrightarrow\frac{\left(1-P^{*}\right)^{a}}{\left(1-P^{*}\right)^{a}+P^{*a}} & \leq & 1-P^{*}\\
-\Leftrightarrow\left(1-P^{*}\right)^{a-1} & \leq & \left(1-P^{*}\right)^{a}+P^{*a}\\
-\Leftrightarrow\left(1-P^{*}\right)^{a-1}\left(1-1+P^{*}\right) & \leq & P^{*a}\\
+\Leftrightarrow\left(1-P^{*}\right)^{a} & \leq & \left(1-P^{*}\right)^{a}+P^{*a}\\
+\Leftrightarrow\left(1-P^{*}\right)^{a}\left(1-1+P^{*}\right) & \leq & P^{*a}\\
 \Leftrightarrow\left(1-P^{*}\right)^{a-1} & \leq & P^{*\left(a-1\right)}\\
@@
 \end{eqnarray*}
+
+\paragraph{PROOF OF THE GENERAL CASE.}
+
+First, suppose $c=0$, $\lambda_{k}=max_{i}\left\{ \lambda_{i}\right\} $.
+
+Let
+\begin{eqnarray*}
+C_{x}\left(\delta,t\right) & = & \frac{Y_{floor(t/\delta),x}-t\frac{1}{\delta}\mu_{x}}{\sqrt{1/\delta}\lambda_{x}}\\
+ & = & \frac{\delta Y_{floor(t/\delta),x}-t\mu_{x}}{\sqrt{\delta}\lambda_{x}}\\
+ & \Rightarrow & W_{x}\left(t\right)
+\end{eqnarray*}
+and
+\[
+\mathfrak{C}\left(\delta\right)=\left(C_{x}\left(\delta,t\right):t\in[0,R\left(\delta\right)];x\in A\right),
+\]
+then$ $
+\[
+\mathfrak{C}\left(\delta\right)\Rightarrow\left(W_{x}(t):t\in[0,R\left(\delta\right)];x\in A\right)
+\]
+
+Let 
+\[
+f\left(\mathfrak{C}\left(\delta\right)\right)=\begin{cases}
+1 & \mbox{correct selection}\\
+0 & \mbox{otherwise}
+\end{cases}.
+\]
+We would like to prove that 
+\[
+\mathbb{P}\left(f\left(\mathfrak{C}\left(\delta\right)\right)=1\right)\rightarrow\mathbb{P}\left(f\left(W\right)=1\right)
+\]
+as $\delta$ goes to $0$ and $W$ is a standard Brownian motion process
+in $\mathbb{R}^{k}$.
+
+Define the mapping $s_{\delta}:D\left[0,1\right]\rightarrow\mathbb{R}$
+such that $s_{\delta}\left(Y\right)=Y\left(T_{Y,\delta}\right)$,
+where 
+\[
+T_{Y,\delta}=\mbox{inf}\left\{ t:\left|Y\left(t\right)\right|-A\left(\delta\right)-B\left(\delta\right)t\geq0\right\} 
+\]
+for every $Y\in D\left[0,1\right]$ and $\delta>0$.
+
+Define the mapping $ $$g_{\delta}\left(Y\right))=exp\left(\left(Y\left(t\delta\right)\sqrt{1/\delta}\lambda_{x}^{2}+t\mu_{x}\right)\beta_{t}/n_{tx}\right)/\sum_{x'\in A}exp\left(\left(Y\left(t\delta\right)\sqrt{1/\delta}\lambda_{x'}^{2}+t\mu_{x'}\right)\beta_{t}/n_{tx'}\right)$
+\[
+g_{\delta}\left(C_{x}\left(\delta,t\right)\right)=C_{x}\left(\delta,t\delta\right)
+\]
+\begin{eqnarray*}
+\hat{q}_{tx}\left(A\right) & = & \mbox{exp}\left(\delta\beta_{t}\frac{W_{tx}}{n_{tx}}\right)/\sum_{x'\in A}exp\left(\delta\beta_{t}\frac{W_{tx'}}{n_{tx'}}\right)\\
+ & = & exp\left(\left(C_{x}\left(\delta,t\delta\right)\sqrt{1/\delta}\lambda_{x}^{2}+t\mu_{x}\right)\beta_{t}/n_{tx}\right)/\sum_{x'\in A}exp\left(\left(C_{x'}\left(\delta,t\delta\right)\sqrt{1/\delta}\lambda_{x'}^{2}+t\mu_{x'}\right)\beta_{t}/n_{tx'}\right)\\
+ & = & g_{\delta}\left(C_{x}\left(\delta,t\right)\right)
+\end{eqnarray*}
+
+Let 
+\begin{eqnarray*}
+\hat{T}\left(\delta\right) & = & \mbox{min}\left\{ t\in\left\{ \frac{1}{R},\ldots,1\right\} :max_{x}q_{tR,x}\left(A\right)\geq P\right\} .\\
+ & = & \mbox{min}\left\{ t\in\left\{ \frac{1}{R},\ldots,1\right\} :max_{x}exp\left(\delta\beta_{tR}\frac{W_{tR,x}}{n_{tR,x}}\right)\geq P\sum_{x'\in A}exp\left(\delta\beta_{tR}\frac{W_{tR,x'}}{n_{tR,x'}}\right)\right\} \\
+ & = & \mbox{min}\left\{ t\in\left\{ \frac{1}{R},\ldots,1\right\} :\exists x\mbox{ s.t.
+}\left(\delta\beta_{tR}\frac{Y_{n_{tR,x}}}{n_{tR,x}}\right)\geq log\left(P\sum_{x'\in A}exp\left(\delta\beta_{tR}\frac{W_{n_{tR,x'}}}{n_{tR,x'}}\right)\right)\right\} \\
+ & = & \mbox{min}\left\{ t\in\left\{ \frac{1}{R},\ldots,1\right\} :\exists x\mbox{ s.t. }\right.\left(\frac{Y_{n_{tR,x}-\left(n_{tR,x}\right)\mu_{X}}}{\lambda_{x}\sqrt{R}}\right)\geq\\
+ &  & \frac{n_{tR,x}}{\lambda_{x}\sqrt{R}}\\
+ &  & \left.\left(log\left(P\sum_{x'\in A}exp\left(\left(\frac{\lambda_{x'}\sqrt{R}}{n_{tR,x'}}\left(\delta\beta_{tR}\frac{Y_{n_{tR,x'}-\left(n_{tR,x'}\right)\mu_{X'}}}{\lambda_{x'}\sqrt{R}}\right)+\delta\beta_{tR}\mu_{x'}\right)\right)\right)-\mu_{x}\delta\beta_{tR}\right)/\left(\delta\beta_{tR}\right)\right\}
+\end{eqnarray*}
+and
+\[
+T\left(\delta\right)=\hat{T}\left(\delta\right)R
+\]
+
+Now, we know that
+\[
+\frac{Y_{n_{tR,x}-\left(n_{tR,x}\right)\mu_{X}}}{\lambda_{x}\sqrt{R}}\Rightarrow W_{x}\left(t\right)
+\]
+as $\delta\rightarrow0$.
+
+Now, if $\lambda_{r}^{2}=\mbox{max}_{i\in A-\left\{ k\right\} }\left\{ \lambda_{i}^{2}\right\} $,
+then \textbackslash{}lim inf\_\{\textbackslash{}delta\textbackslash{}rightarrow0\}
+
+\begin{eqnarray*}
+\mathbb{P}\left(f\left(\mathfrak{C}\left(\delta\right)\right)=1\right) & = & \mathbb{P}\left(\frac{W_{Tk}}{n_{Tk}}\geq\frac{W_{Tx}}{n_{Tx}}\mbox{ }\forall x\in A\right)\\
+ & = & E\left[\prod_{i\in A-\left\{ k\right\} }\mathbb{P}\left\{ \frac{\left(\sum_{j=1}^{n_{T\left(\delta\right)k}}X_{kj}-n_{T\left(\delta\right)k}\mu_{k}\right)}{n_{T\left(\delta\right)k}}-\frac{\lambda_{i}^{2}\left(\sum_{j=1}^{n_{T\left(\delta\right)i}}X_{ij}-n_{T\left(\delta\right)i}\mu_{i}\right)}{\lambda_{i}^{2}n_{T\left(\delta\right)i}}\right.\right.\\
+ &  & \left.\left.+\delta>0\right\} \mid\Delta,X_{k1},\ldots,X_{kn_{Tk}},T\}\right]\\
+ & \geq & E\left[\prod_{i\in A-\left\{ k\right\} }\mathbb{P}\left\{ \frac{\left(\sum_{j=1}^{n_{T\left(\delta\right)k}}dX_{kj}-n_{T\left(\delta\right)k}\mu_{k}\right)}{n_{T\left(\delta\right)k}}-\frac{\lambda_{r}^{2}\left(\sum_{j=1}^{n_{T\left(\delta\right)i}}X_{ij}-n_{T\left(\delta\right)i}\mu_{i}\right)}{\lambda_{i}^{2}n_{T\left(\delta\right)i}}\right.\right.\\
+ & = & \left.\left.+\delta>0\right\} \mid\Delta,X_{k1},\ldots,X_{kn_{Tk}},T\}\right]\\
+ & = & E\left[\left(\mathbb{P}\left\{ \frac{\left(\sum_{j=1}^{n_{T\left(\delta\right)k}}X_{kj}-n_{T\left(\delta\right)k}\mu_{k}\right)}{n_{T\left(\delta\right)k}}-\frac{\left(\sum_{j=1}^{n_{T\left(\delta\right)r}}X_{rj}-n_{T\left(\delta\right)r}\mu_{r}\right)}{n_{T\left(\delta\right)r}}\right.\right.\right.\\
+ & = & \left.\left.+\delta>0\right\} \mid\Delta,X_{k1},\ldots,X_{kn_{Tk}}\left.,T\}\right)^{k-1}\right]\\
+ & = & E\left[\left(\mathbb{P}\left\{ \frac{n_{T\left(\delta\right)r}\left(\sum_{j=1}^{n_{T\left(\delta\right)k}}X_{kj}-n_{T\left(\delta\right)k}\mu_{k}\right)-n_{T\left(\delta\right)k}\left(\sum_{j=1}^{n_{T\left(\delta\right)r}}X_{rj}-n_{T\left(\delta\right)r}\mu_{r}\right)}{R^{3/2}v_{rk}}\right.\right.\right.\\
+ &  & \left.\left.+\frac{\delta}{R^{3/2}v_{rk}}\left(n_{T\left(\delta\right)k}n_{T\left(\delta\right)r}\right)>0\right\} \mid\Delta,X_{k1},\left.\ldots,X_{kn_{Tk}},T\right)^{k-1}\right]\\
+ & \geq & E\left[\left(\mathbb{P}\left\{ \frac{n_{T\left(\delta\right)r}\left(\sum_{j=1}^{n_{T\left(\delta\right)k}}X_{kj}-n_{T\left(\delta\right)k}\mu_{k}\right)-n_{T\left(\delta\right)k}\left(\sum_{j=1}^{n_{T\left(\delta\right)r}}X_{rj}-n_{T\left(\delta\right)r}\mu_{r}\right)}{R^{3/2}v_{rk}}\right.\right.\right.\\
+ &  & \left.\left.+\frac{\delta}{R^{3/2}v_{rk}}\left(n_{T\left(\delta\right)k}n_{T\left(\delta\right)r}\right)>0\right\} \mid\Delta,X_{k1},\left.\ldots,X_{kn_{Tk}},T\right)\right]^{k-1}\\
+ & = & E\left[\left(\mathbb{P}\left\{ \frac{n_{T\left(\delta\right)r}\left(\sum_{j=1}^{n_{T\left(\delta\right)k}}X_{kj}-n_{T\left(\delta\right)k}\mu_{k}\right)-n_{T\left(\delta\right)k}\left(\sum_{j=1}^{n_{T\left(\delta\right)r}}X_{rj}-n_{T\left(\delta\right)r}\mu_{r}\right)}{R^{3/2}v_{rk}}\right.\right.\right.\\
+ &  & \left.\left.+\frac{\delta}{R^{3/2}v_{rk}}\left(n_{T\left(\delta\right)k}n_{T\left(\delta\right)r}\right)>0\right\} \mid\Delta\right]^{k-1}\\
+ & \geq
+\end{eqnarray*}
+
+Now,
+
+Suppose $c>0$.
 

### 2014-09-01 paper/paper_version2.tex
s

%% LyX 2.0.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{verbose,tmargin=1.5cm,bmargin=1.5cm,lmargin=1.5cm,rmargin=1.5cm}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\onehalfspacing

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\documentclass[opre,blindrev]{informs3} % current default for manuscript submission

% current default line spacing
%%\OneAndAHalfSpacedXII 
%%\DoubleSpacedXII
%%\DoubleSpacedXI

% If hyperref is used, dvi-to-ps driver of choice must be declared as
%   an additional option to the \documentclass. For example
%\documentclass[dvips,opre]{informs3}      % if dvips is used 
%\documentclass[dvipsone,opre]{informs3}   % if dvipsone is used, etc.

%%% OPRE uses endnotes
\usepackage{endnotes}
\let\footnote=\endnote
\let\enotesize=\normalsize
\def\notesname{Endnotes}%
\def\makeenmark{\hbox to1.275em{\theenmark.\enskip\hss}}
\def\enoteformat{\rightskip0pt\leftskip0pt\parindent=1.275em
  \leavevmode\llap{\makeenmark}}

% Private macros here (check that there is no clash with the style)
\newcommand{\lambdahat}{\widehat{\lambda}}
\newcommand{\xtilde}{\tilde{x}}
\newcommand{\qhat}{\widehat{q}}
\newcommand{\as}{\ a.s.}
\newcommand{\zap}[1]{}
\newcommand{\Ncal}{\mathcal{N}}
\newcommand{\sigmahat}{\hat{\sigma}}
\newcommand{\Nat}{\mathbb{N}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\Pb}[2]{\mathbb{P}_{#1}\left\{#2\right\}}
\newcommand{\Ybar}{\overline{Y}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
% \newcommand{\argmax}{\operatornamewithlimits{arg\,max}}
% \newcommand{\argmin}{\operatornamewithlimits{arg\,min}}
\newcommand{\g}{\,\vert\,}
\newcommand{\ind}[1]{1_{\left\{#1\right\}}}
\newcommand{\Fcal}{\mathcal{F}}
\newcommand{\Gcal}{\mathcal{G}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\xhat}{\hat{x}}
\newcommand{\xwig}{\tilde{x}}
\newcommand{\PZ}{\mbox{PZ}}
\newcommand{\PCS}{\mbox{PCS}}
\newcommand{\PGS}{\mbox{PGS}}
\newcommand{\uLFC}{\underline{u}}
\newcommand{\e}[1]{\left\{ #1 \right\}}
\newcommand{\T}{\mathbb{T}} % Time index set.
\newcommand{\CS}{\mbox{CS}}
\newcommand{\Ft}{\mathcal{F}_t}
\newcommand{\F}[1]{\mathcal{F}_{#1}}
\newcommand{\Ftau}{\mathcal{F}_\tau}
\newcommand{\Rcal}{\mathcal{R}}
\newcommand{\upthresh}{P}
\newcommand{\xstar}{X^*}
\newcommand{\cmax}{1-(P^*)^{\frac1{k-1}}}
\newcommand{\NewN}{M}
\newcommand{\thetavec}{\vec{\theta}}
\newcommand{\uvec}{\vec{u}}
\newcommand{\sigmavec}{\lambda}
\newcommand{\sigmacom}{\sigma}
\newcommand{\sigmascal}{\lambda}
\newcommand{\PstarB}{\mathcal{P}^*_B}
\newcommand{\Ymod}{Y'}
\newcommand{\ceil}{\mathrm{ceil}}
% How to state the common variance assumption at the beginning of lemmas, propositions and theorems
\newcommand{\homog}{Suppose $\lambda^2_x = \sigma^2>0\ \forall x$.  }
\newcommand{\algref}[1]{Alg.~\ref{#1}}

\usepackage{algorithm,algorithmic,enumerate}

%% Setup of theorem styles. Outcomment only one. 
%% Preferred default is the first option.
  % Preferred (Theorem 1, Lemma 1, Theorem 2)
%\TheoremsNumberedByChapter  % (Theorem 1.1, Lema 1.1, Theorem 1.2)

\makeatother

\usepackage{babel}
\usepackage{xunicode}
\begin{document}

\title{On the Asymptotic Validity of a Fully Sequential Elimination Procedure
for Indifference-Zone Ranking and Selection with Tight Bounds on Probability
of Correct Selection}

\maketitle
We prove the validity of the sequential elimination IZ procedure proposed
by Frazier \cite{key-5} when $\delta$ goes to $0$. Specifically,
we analyze Algorithm 2, when $B_{1}=\cdots=B_{k}=1$:

\paragraph{Algorithm 2: Discrete-time implementation of BIZ, for unknown and/or heterogeneous variances.}    
\begin{algorithmic}[1]   
\label{alg:hetero-BIZ}   
\REQUIRE $c \in [0,\cmax]$, $\delta>0$, $P^*\in(1/k,1)$, $n_0\ge0$ an integer, $B_1,\ldots,B_k$ strictly positive integers.  Recommended choices are $c=\cmax$, $B_1=\cdots=B_k=1$ and $n_0$ between $10$ and $30$.     If the sampling variances $\lambda^2_x$ are known, replace the estimators     
$\lambdahat^2_{tx}$ with the true values $\lambda^2_x$, and set $n_0=0$.     
To compute $\qhat_{tx}(A)$, use \begin{equation}   q'_{t,x}(A) =    \exp\left(\gamma \delta Y'_{tx}\right) \bigg/ \sum_{x'\in A} \exp\left(\gamma \delta Y'_{tx'}\right)   = \exp\left(\frac{\delta}{\lambda^2_x} Y_{n_x(t),x}\right) \bigg/ \sum_{x'\in A} \exp\left(\frac{\delta}{\lambda^2_{x'}} Y_{n_x'(t),x'}\right), \end{equation}   
where $Y_{n_x(t),x}$ is the sum of the first $n_x(t)$ samples.

\STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.     
\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$, $t \leftarrow 1$.
\WHILE{$x\in\mbox{max}_{x\in A}\qhat_{tx}(A)<P$}
\WHILE{$\mbox{min}_{x\in A} \qhat_{tx}(A) \le c$}
 \STATE Let $x\in\mbox{arg min}_{x\in A}\qhat_{tx}(A)$.
    \STATE Let $\upthresh \leftarrow \upthresh/(1-\qhat_{tx}(A))$.     
\STATE Remove $x$ from $A$.
\ENDWHILE
  \STATE Let $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.     
\STATE For each $x\in A$, let      $n_{t+1,x} = \ceil\left( \lambdahat^2_{tx} (n_{tz} + B_z) / \lambdahat^2_{tz} \right)$.     \STATE For each $x\in A$, if $n_{t+1,x}>n_{tx}$, take $n_{t+1,x}-n_{tx}$ additional samples from alternative $x$.  Let $W_{t+1,x}$ and $\lambdahat^2_{t+1,x}$ be the sample mean and sample variance respectively of all samples from alternative $x$ thus far.    
\STATE Increment $t$.
 \ENDWHILE
  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} W_{tx} / n_{tx}$ as our estimate of the best.

\end{algorithmic}

\section{Introduction}

This paper is organized as follows: In $\text{§}2$, we present the
proof of the validity of the algorithm when the variances are known.
In $\text{§}3$, we prove the case when the variances are unknown.

To prove the case when the variances are known, we use a Functional
Central Limit Theorem that shows how to standardize the output data
to make them behave like Brownian motion processes in the limit. We
also use an extension of the Continuous Mapping Theorem (Theorem 5.5
of Billingsley 1968) to see that the algorithm behaves like a sequential
elimination IZ procedure with a Brownian motion process instead of
the standardize of the sum of the output data in the limit. Finally,
we use the results of the paper of Frazier \cite{key-5} to prove
the validity of this algorithm in the limit.

\section{Asymptotic Validity when the Variances are Known}

Without loss of generality, suppose that the true means of the systems
are indexed so that $\mu_{k}\geq\mu_{k-1}\geq\cdots\geq\mu_{1}$.
We suppose that samples from system $x\in\left\{ 1\ldots,k\right\} $
are identically distributed and independent, over time and across
alternatives. We also define $\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$.
We suppose that $\mbox{min}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}>0$
and $c\neq1/k$.

Now we are going to see that the standardize of the sum of the output
data converges to a Brownian motion in $D[0,\infty)$, which is the
set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$ that
are right-continuous and have left-hand limits, with the Skorohod
topology. The Skorohod metric $d_{t}$ on $D\left[0,t\right]$ is:
\[
d_{t}\left(X,Y\right)=\mbox{inf}_{\lambda\in\Lambda_{t}}\left\{ \left\Vert \lambda-I\right\Vert \vee\left\Vert X-Y\circ\lambda\right\Vert \right\} 
\]
where $\Lambda_{t}$ is the set of strictly increasing, continuous
mappings of $\left[0,t\right]$ onto itself, and $\left\Vert \cdot\right\Vert $
is the uniform norm, and $I$ is the identity map. Note that uniform
convergence on $\left[0,t\right]$ implies Skorohod convergence.

For $X\in D\left[0,\text{\ensuremath{\infty}}\right)$, let $X^{m}$
be the element of $D[0,\infty)$ defined by
\[
X^{m}\left(t\right)=g_{m}\left(t\right)X\left(t\right)
\]
where 
\[
g_{m}\left(t\right)=\begin{cases}
1 & \mbox{if }t\leq m-1,\\
m-t & \mbox{if }m-1\leq t\leq m,\\
0 & \mbox{if }t\geq m.
\end{cases}
\]
And now take
\[
d_{\infty}\left(X,Y\right)=\sum_{m=1}^{\infty}2^{-m}\left(1\wedge d_{m}\left(X,Y\right)\right)
\]
which is the Skorohod metric on $D\left[0,\infty\right)$.

\paragraph*{Lemma 1.}

If $x\in\left\{ 1\ldots,k\right\} $, then
\[
C_{x}\left(\delta,\cdot\right):=\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\right),x}-\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right)
\]
in the sense of $D[0,\infty)$, where $Y_{n,x}$ is the sum of the
first $n$ samples and $W_{x}$ is a standard Brownian motion.

\paragraph*{Proof.}

By the Theorem 19.1 of Billingsley 1999 and the sandwich theorem,
\[
\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right).
\]

Since $\frac{\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}-ceil\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right)}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\rightarrow0$
uniformly on $[0,r]$ for every $r$, then it also converges to $0$
on $D[0,\infty)$ and so 
\[
\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right).
\]

Observe that for $\epsilon>0$ and $\delta$ sufficiently small
\[
\left|\frac{-Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right),x}+Y_{\mbox{ceil}\left(n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right),x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\right|<\epsilon\left(n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}+2\right)
\]
and then 
\[
C_{x}\left(\delta,\cdot\right)\Rightarrow W_{x}\left(\cdot\right).
\]

$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$

${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$

Now we are going to define new algorithms that are almost the same
than the one proposed by Frazier, but instead of $q_{tx}^{\delta}\left(A\right)$,
these algorithms use new functions $q_{tx}^{Y,\delta}\left(A\right)$
which depend on a function $Y$ that is in $D\left[0,\infty\right)^{k}$.

First we are going to suppose that $\delta>0$ and $\mu_{k}=\delta$,$\mu_{k-1}=\cdots=\mu_{\text{1}}=0$.

Let$ $ $Y\in D\left[0,\infty\right)^{k}$ , we define
\begin{eqnarray*}
q_{tx}^{Y,\delta}\left(A\right): & = & \mbox{exp}\left(\frac{Y_{x}\left(t\right)}{\lambda_{z}}+\delta^{2}\beta_{t\frac{1}{\delta^{2}}}I_{\left\{ x=k\right\} }\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{Y_{x^{'}}\left(t\right)}{\lambda_{z}}+\delta^{2}\beta_{t\frac{1}{\delta^{2}}}I_{\left\{ x^{'}=k\right\} }\right)
\end{eqnarray*}
where $\beta_{t\frac{1}{\delta^{2}}}=\frac{\left(n_{0}+t\frac{1}{\delta^{2}}\right)}{\lambda_{z}^{2}}$.

We define
\begin{eqnarray*}
T_{Y,\delta}^{0} & = & 0\\
A_{0}^{Y,\delta} & = & \left\{ 1,\ldots,k\right\} \\
P_{0}^{Y,\delta} & = & P^{*}\\
T_{Y,\delta}^{n+1}\left(P_{n}^{Y,\delta}\right) & = & \mbox{inf}\left\{ t\geq T_{Y,\delta}^{n}:\mbox{ min}_{x\in A_{n}^{Y,\delta}}q_{tx}^{Y,\delta}\left(A_{n}^{Y,\delta}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}^{Y,\delta}}q_{tx}^{Y,\delta}\left(A_{n}^{Y,\delta}\right)\geq P_{n}^{Y,\delta}\right\} \\
Z_{n+1}^{Y,\delta} & \in & \mbox{arg min}_{x\in A_{n}^{Y,\delta}}q_{T_{Y,\delta}^{n+1},x}^{Y,\delta}\left(A_{n}^{Y,\delta}\right)\\
A_{n+1}^{Y,\delta} & = & A_{n}-\left\{ Z_{n+1}^{Y,\delta}\right\} \\
P_{n+1}^{Y,\delta} & = & P_{n}^{Y,\delta}/\left(1-\mbox{min}_{x\in A_{n}^{Y,\delta}}q_{T_{Y,\delta}^{n+1}x}^{Y,\delta}\left(A_{n}^{Y,\delta}\right)\right).
\end{eqnarray*}
Now, let
\[
M_{Y,\delta}=\mbox{inf}\left\{ n=1,\ldots,k-1:\mbox{max}_{x\in A_{n-1}^{Y,\delta}}q_{T_{Y,\delta}^{n},x}\left(A_{n-1}^{Y,\delta}\right)\geq P_{n-1}^{Y,\delta}\right\} 
\]

and

\begin{eqnarray*}
f\left(Y,\delta\right) & = & \begin{cases}
1 & \mbox{if }k\mbox{ is chosen}\\
0 & \mbox{otherwise}
\end{cases}.
\end{eqnarray*}

Now, we also define$ $
\[
q_{tx}^{Y}\left(A\right):=\mbox{exp}\left(\frac{Y_{x}\left(t\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}tI_{\left\{ x=k\right\} }\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{Y_{x'}\left(t\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}tI_{\left\{ x'=k\right\} }\right)
\]

\begin{eqnarray*}
T_{Y}^{0} & = & 0\\
A_{0}^{Y} & = & \left\{ 1,\ldots,k\right\} \\
P_{0}^{Y} & = & P^{*}\\
T_{Y}^{n+1}\left(P_{n}^{Y}\right) & = & \mbox{inf}\left\{ t\geq T_{Y}^{n}:\mbox{ min}_{x\in A_{n}^{Y}}q_{tx}^{Y}\left(A_{n}^{Y}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}^{Y}}q_{tx}^{Y}\left(A_{n}^{Y}\right)\geq P_{n}^{Y}\right\} \\
Z_{n+1}^{Y} & \in & \mbox{arg min}_{x\in A_{n}^{Y}}q_{T_{Y}^{n+1},x}^{Y}\left(A_{n}^{Y}\right)\\
A_{n+1}^{Y} & = & A_{n}^{Y}-\left\{ Z_{n+1}^{Y}\right\} \\
P_{n+1}^{Y} & = & P_{n}^{Y,\delta}/\left(1-\mbox{min}_{x\in A_{n}^{Y,}}q_{T_{Y}^{n+1}x}^{Y}\left(A_{n}^{Y}\right)\right).
\end{eqnarray*}

Now, let
\[
M_{Y}=\mbox{inf}\left\{ n=1,\ldots,k-1:\mbox{max}_{x\in A_{n-1}^{Y}}q_{T_{Y}^{n},x}\left(A_{n-1}^{Y}\right)\geq P_{n-1}^{Y}\right\} 
\]
and
\[
\]
\begin{eqnarray*}
g\left(Y\right) & = & \begin{cases}
1 & \mbox{if }k\mbox{ is chosen}\mbox{ }\\
0 & \mbox{otherwise}
\end{cases}.
\end{eqnarray*}

We want to prove that 
\[
f\left(C\left(\delta,\cdot\right),\delta\right)\Rightarrow g\left(W\right).
\]

In order to prove this, we will prove the following lemma which will
allow us to use the Theorem 5.5 of Billingsley 1968 that implies the
desired result.

\paragraph*{Lemma 2.}

Let $\left\{ \delta_{n}\right\} \subset\left(0,\infty\right)$ such
that $\delta_{n}\rightarrow0$. If $D_{s}\equiv\{x\in D\left[0,\infty\right)^{k}:\mbox{ for all sequences }\left\{ x_{n}\right\} \subset D\left[0,\infty\right)^{k},\mbox{ such that }$
$lim_{n}d\left(x_{n},x\right)=0$ the sequence $\left\{ f\left(x_{n},\delta_{n}\right)\right\} $
converges to $\left\{ g\left(x\right)\right\} $$\left.\right\} $$ $,
then $ $$\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\right)=1$.

\paragraph*{Proof.}

We will use the following property: if $T$ is a stopping time, then
by the local version of the law of the iterated logarithm for Brownian
motion 
\begin{equation}
\mbox{lim sup}_{u\rightarrow0^{+}}\frac{\left[W_{x}\left(T+u\right)-W_{x}\left(T\right)\right]}{\sqrt{2u\mbox{ln}\left[\mbox{ln}\left(1/u\right)\right]}}=1\label{eq:1.1}
\end{equation}
almost surely for each system $x$. Furthermore, note that $W$ is
almost surely continuous on $\left[0,t\right]^{k}$ if $t>0$ and
so $W$ is also almost surely uniformly continuous on $\left[0,t\right]^{k}$.

Let $\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}$ such
that $Z_{n}\rightarrow W$. Note that $\delta_{n}^{2}\frac{\left(n_{0}+t\frac{1}{\delta_{n}^{2}}\right)}{\lambda_{z}^{2}}\rightarrow\frac{t}{\lambda_{z}^{2}}$
in $D\left[0,\infty\right)$ and $\frac{\delta_{n}\sqrt{\frac{1}{\delta_{n}^{2}}}}{\lambda_{z}}\rightarrow\frac{1}{\lambda_{z}}$
in $D\left[0,\infty\right)$ because uniformly convergence implies
convergence in the Skorohod topology. Consequently, for each $s>0$
there exist functions $\lambda_{s}^{n}$ in $\Lambda$ such that 
\[
\mbox{lim}_{n}Z_{n}\left(\lambda_{s}^{n}t\right)=W\left(t\right)
\]
uniformly in $t$ and
\[
\mbox{lim}_{n}\lambda_{s}^{n}t=t
\]
uniformly in $t$. Then
\[
\mbox{lim}_{n}\frac{\delta_{n}\sqrt{\frac{1}{\delta_{n}^{2}}}}{\lambda_{z}}Z_{n}\left(\lambda_{s}^{n}t\right)+\delta_{n}^{2}\frac{\left(n_{0}+\lambda_{s}^{n}\left(t\right)\frac{1}{\delta_{n}^{2}}\right)}{\lambda_{z}^{2}}=W\left(t\right)\frac{1}{\lambda_{z}}+\frac{t}{\lambda_{z}^{2}}
\]
uniformly in $t$, and so
\[
\mbox{lim}_{n}\mbox{exp}\left(\frac{\delta_{n}\sqrt{\frac{1}{\delta_{n}^{2}}}}{\lambda_{z}}Z_{n}\left(\lambda_{n}t\right)+\delta_{n}^{2}\frac{\left(n_{0}+\lambda_{s}^{n}\left(t\right)\frac{1}{\delta_{n}^{2}}\right)}{\lambda_{z}^{2}}\right)=\mbox{exp}\left(W\left(t\right)\frac{1}{\lambda_{z}}+\frac{t}{\lambda_{z}^{2}}\right)
\]
uniformly in $t$ since $\mbox{exp}$ is uniformly continuous in $\left[0,s\right]$.
Consequently,
\[
q_{\lambda_{s}^{n}\left(t\right)x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{tx}^{W}\left(A\right)
\]
uniformly in $t\in\left[0,s\right]$. Thus, $q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{\cdot x}^{W}\left(A\right)$
in $D\left[0,s\right]$ for any set $A\subset\left\{ 1,\ldots,k\right\} $
and $s\geq0$. Consequently, $q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{\cdot x}^{W}\left(A\right)$
in $D\left[0,\infty\right)$. Then for each $m\geq0$ there exists
$\lambda_{n,A}\in\Lambda_{\infty}$ such that $\mbox{sup}_{t<\infty}\left\Vert \lambda_{n,A}\left(t\right)-t\right\Vert \leq d\left(q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right),q_{\cdot x}^{W}\left(A\right)\right)+\frac{1}{n}$
and $\mbox{sup}_{t\leq m}\left\Vert q_{tx}^{Z_{n},\delta_{n}}\left(A\right)-q_{\lambda_{n,A}\left(t\right)x}^{W}\left(A\right)\right\Vert \leq d\left(q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right),q_{\cdot x}^{W}\left(A\right)\right)+\frac{1}{n}$.
Taking $g_{n}^{A}\equiv\mbox{sup}_{t\leq m}\left\Vert q_{tx}^{W}\left(A\right)-q_{\lambda_{n}\left(t\right)x}^{W}\left(A\right)\right\Vert $,
we see from the uniform continuity of $W$ on $\left[0,m\right]^{k}$
and the definition of $g_{n}^{A}$ that $\mbox{lim}_{n\rightarrow\infty}g_{n}^{A}=0.$
Moreover, if we take $\epsilon_{n}^{A}=3n^{-1}+3\mbox{sup}\left\{ d\left(q_{\cdot x}^{Z_{l},\delta_{l}}\left(A\right),q_{\cdot x}^{W}\left(A\right)\right)+g_{l}^{A}:l=n,n+1,\ldots\right\} $,
then $\left\{ \epsilon_{n}^{A}\right\} $ is a monotonically decreasing
sequence of positive numbers with limit zero.

From the definition of $\epsilon_{n}$ we have $d\left(q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right),q_{\cdot x}^{W}\left(A\right)\right)<\epsilon_{n}/2$
and $g_{n}^{A}<\epsilon_{n}/2$ for $n=1,2,\ldots$ Consequently,
we have 
\begin{eqnarray*}
\left\Vert q_{tx}^{Z_{n},\delta_{n}}\left(A\right)-q_{tx}^{W}\left(A\right)\right\Vert  & \leq & \left\Vert q_{tx}^{Z_{n},\delta_{n}}\left(A\right)-q_{\lambda_{n}\left(t\right)x}^{W}\left(A\right)\right\Vert +\left\Vert q_{\lambda_{n}\left(t\right)x}^{W}\left(A\right)-q_{tx}^{W}\left(A\right)\right\Vert \\
 & < & \epsilon_{n}^{A}
\end{eqnarray*}
for all $t\in\left[0,m\right]$ and $x\in A$.

We will show that $\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\mid M_{W}=i\right)=1$
for $i\in\left\{ 1,\ldots,k-1\right\} $ so that the desired conclusion
follows.

Suppose first that $M_{W}=1$. Let's prove that $T_{Z_{n},\delta_{n}}^{1}\left(P\right)\rightarrow T_{W}^{1}\left(P\right)$
as $n\rightarrow\infty$. Since $M_{W}=1$, then $\mbox{max}_{x\in A}q_{T_{W}^{1}\left(P\right)x}^{W}\left(A\right)=P$
almost surely because $W$ is continuous almost surely. Let $q_{x}^{*}=\mbox{min}_{t\in\left[0,T_{W}^{1}\left(P\right)\right]}q_{tx}^{W}$
(the minimum exists because $q_{tx}^{W}$ is continuous) and let $q^{*}=\mbox{min}_{x}q_{x}^{*}$.
Let $N$ such that if $n>N$ then $\epsilon_{n}^{A}<q^{*}-c$ (note
that in the last equation $m=T_{W}^{1}\left(P\right)$ and $q^{*}-c>0$
because $M_{W}=1$ and $N$ is a random variable). If $n>N$ and $t\leq T_{W}^{1}\left(P\right)$
then
\begin{eqnarray*}
q_{tx}^{W}\left(A\right) & < & q_{tx}^{Z_{n},\delta_{n}}\left(A\right)+q^{*}-c\\
\Rightarrow c & < & q_{tx}^{Z_{n},\delta_{n}}\left(A\right)+q^{*}-q_{tx}^{W}\left(A\right)\leq q_{tx}^{Z_{n},\delta_{n}}\left(A\right).
\end{eqnarray*}

Case 1. $T_{W}^{1}\left(P\right)=0$. Note that $q_{0x}^{W}\left(A\right)=\frac{1}{k}<P$
and so this case is not possible.

Case 2. $0<T_{W}^{1}\left(P\right)$.

Note that $T_{Z_{n},\delta_{n}}^{1}\left(P\right)\leq T_{Z_{n},\delta_{n}}^{1}\left(P+\delta_{n}\right)\leq T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right)$
because if $t<T_{Z_{n},\delta_{n}}^{1}\left(P+\delta_{n}\right)$
(for the sequence $\left\{ \epsilon_{n}\right\} $ we take $m=\mbox{sup}_{n}P+\delta_{n}$)
\[
q_{tx}^{W}\left(A\right)-\epsilon_{n}<q_{tx}^{Z_{n},\delta_{n}}\left(A\right)<P+\delta_{n}.
\]
Furthermore, 
\begin{eqnarray*}
T_{W}^{1}\left(P\right) & \leq & \mbox{lim inf}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right)\\
 & \leq & \mbox{lim sup}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right).
\end{eqnarray*}
 Now, let $x=\mbox{arg max}q_{T_{W}^{1}x}^{W}\left(A\right)$. By
(\ref{eq:1.1}), for any $\varepsilon\in\left(0,1\right)$, there
exists a monotonically decreasing sequence $\left\{ s_{k}:\mbox{ }k=1,2,\ldots\right\} \subset\left(T_{W}^{1}\left(P\right),\infty\right)$
such that $\mbox{lim}_{n}s_{n}=T_{W}^{1}\left(P\right)$; and for
$k=1,2,\ldots$ we have

\begin{eqnarray*}
W_{x}\left(s_{k}\right)-W_{x}\left(T_{W}^{1}\left(P\right)\right) & >v_{k}\equiv & \left(\varepsilon\right)\sqrt{2\left(s_{k}-T_{W}^{1}\left(A\right)\right)\mbox{ln}\mbox{ln}\left(1/\left(s_{k}-T_{W}^{1}\left(P\right)\right)\right)}.
\end{eqnarray*}

Notice that $v_{k}>0$ and $\mbox{lim}_{k}v_{k}=0$. Let $\alpha>0$.
Let $\delta$ such that if $\delta_{3}<\delta$, then $\alpha>-\mbox{log}\left(1-\delta_{3}\right)$.
Pick $\delta_{3}<\delta$. Let $K$ such that if $k>K$, $\frac{\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{1}\left(P\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{1}\left(P\right)I_{\left\{ x^{'}=k\right\} }\right)}{\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)}>1-\delta_{3}$.
Pick $k>K$. Let $N_{4}$ such that if $n>N_{4}$, then $\frac{\epsilon_{n}}{P}<v_{k}\frac{1}{\lambda_{z}}+\alpha$
and $\frac{\delta_{n}}{P}<\left(v_{k}\frac{1}{\lambda_{z}}+\alpha\right)^{2}/2$.
$ $Observe that
\begin{eqnarray*}
q_{s_{k}x}^{W} & = & \mbox{exp}\left(\frac{W_{x}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x=k\right\} }\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)\\
 & > & \frac{\mbox{exp}\left(\frac{W_{x}\left(T_{W}^{1}\left(P\right)\right)+v_{k}}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{1}\left(P\right)I_{\left\{ x=k\right\} }\right)}{\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{1}\left(P\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{1}\left(P\right)I_{\left\{ x^{'}=k\right\} }\right)}\times\frac{\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{1}\left(P\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{1}\left(P\right)I_{\left\{ x^{'}=k\right\} }\right)}{\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)}\\
 & \geq & q_{T_{W}^{1}\left(P\right)x}^{W}\left(A\right)\mbox{exp}\left(v_{k}\frac{1}{\lambda_{z}}\right)\left(1-\delta_{3}\right)\geq q_{T_{W}^{1}\left(P\right)x}^{W}\left(A\right)\mbox{exp}\left(v_{k}\frac{1}{\lambda_{z}}\right)\mbox{exp}\left(\alpha\right)\\
 & \geq & P\left(1+v_{k}\frac{1}{\lambda_{z}}+\alpha+\frac{\left(v_{k}\frac{1}{\lambda_{z}}+\alpha\right)^{2}}{2}\right)>\left(P+\epsilon_{n}+\delta_{n}\right).
\end{eqnarray*}
Consequently, 
\[
s_{k}>T_{W}^{1}\left(P+\epsilon_{n}+\delta_{n}\right)
\]
if $n>N_{4}$, and so 
\[
s_{k}\geq\mbox{lim sup}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right).
\]

Since $s_{k}\rightarrow T_{W}^{1}$, we must have that
\begin{eqnarray*}
T_{W}^{1}\left(P\right) & \geq & \mbox{lim sup}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right)\\
 & \geq & \mbox{lim inf}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right)\\
 & \geq & T_{W}^{1}\left(P\right)
\end{eqnarray*}
Consequently, 
\[
T_{W}^{1}\left(P\right)=\mbox{lim}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right).
\]

Now,
\[
T_{Z_{n},\delta_{n}}^{1}\left(P\right)\geq T_{Z_{n},\delta_{n}}^{1}\left(P-\delta_{n}\right)\geq T_{W}^{1}\left(P-\delta_{n}-\epsilon_{n}\right)
\]

because if $t<T_{W}^{1}\left(P-\delta_{n}-\epsilon_{n}\right)$ 
\[
q_{tx}^{Z_{n},\delta_{n}}\left(A\right)-\epsilon_{n}<q_{tx}^{W}\left(A\right)<P-\delta_{n}-\epsilon_{n}.
\]
Similarly we can prove that 
\[
\mbox{lim}_{n}T_{W}^{1}\left(P-\delta_{n}-\epsilon_{n}\right)=T_{W}^{1}\left(P\right).
\]
Consequently,
\[
T_{W}^{1}\left(P\right)=\mbox{lim}_{n}T_{Z_{n},\delta_{n}}^{1}\left(P\right).
\]

Let $x=\mbox{arg max}_{x}q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)$.
Let $\epsilon>0$. Let $N$ such that if $n>N$, then $2\epsilon_{n}+2\epsilon<-\mbox{max}_{y\in A-\left\{ x\right\} }q_{T_{W\left(P\right)}^{1},y}^{W}\left(A\right)+q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)$
\[
\left|q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)-q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),x}^{Z_{n},\delta_{n}}\left(A\right)\right|<\epsilon+\epsilon_{n}
\]
for all $x\in A$, and so if $z\in A-\left\{ x\right\} $,
\begin{eqnarray*}
q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),z}^{Z_{n},\delta_{n}}\left(A\right) & < & \epsilon+\epsilon_{n}+q_{T_{W}^{1}\left(P\right),z}^{W}\left(A\right)\\
 & < & -\epsilon-\epsilon_{n}+q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)\\
 & < & q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),x}^{Z_{n},\delta_{n}}\left(A\right)
\end{eqnarray*}
and so $x=\mbox{arg max}_{x}q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),x}^{Z_{n},\delta_{n}}\left(A\right)$.
\[
\]

Now, we suppose that $ $$M_{W}=2$. Let's prove that $T_{W}^{1}\left(A\right)=\mbox{lim}_{n}T_{Z_{n},\delta_{n}}^{1}$.

Case 1. $0<T_{W}^{1}\left(P\right)$. Like in the previous proof,
we conclude that 
\[
T_{W}^{1}\left(P\right)=\mbox{lim}_{n}T_{Z_{n},\delta_{n}}^{1}\left(P\right).
\]

Furthermore, if $x=\mbox{arg min}_{x\in A_{1}^{W}}q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)$.
Let $N$ such that if $n>N$, then $2\epsilon_{n}+2\epsilon<\mbox{min}_{y\in A_{1}^{W}-\left\{ x\right\} }q_{T_{W}^{1}\left(P\right),y}^{W}\left(A\right)-q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)$
for some $\epsilon>0$ and
\[
\left|q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right)z}^{Z_{n},\delta_{n}}-q_{T_{W}^{1}\left(P\right),z}^{W}\right|<\epsilon
\]
for all $z\in A-\left\{ x\right\} $.

Then if \textbf{\large $z\in A-\left\{ x\right\} $, 
\begin{eqnarray*}
q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),z}^{Z_{n},\delta_{n}}\left(A\right) & > & -\epsilon_{n}-\epsilon+q_{T_{W}^{1}\left(P\right),z}^{W}\left(A\right)>q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)+\epsilon_{n}+\epsilon\\
 & > & q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),x}^{Z_{n},\delta_{n}}\left(A\right)
\end{eqnarray*}
}{\large \par}

for $n$ sufficiently large and so $x=\mbox{arg min}_{x\in A_{n}^{Y}}q_{T_{Z_{n,\delta_{n}}}^{1}\left(P\right),x}^{Z_{n},\delta_{n}}\left(A\right)$.
Consequently, $A_{1}^{Z_{n},\delta_{n}}=A_{1}^{W}$ for $n$ sufficiently
large.

Case 2. $T_{W}^{1}\left(P\right)=0$, then $ $$\mbox{ min}_{x\in A_{n}^{Y}}q_{0x}^{W}\left(A_{n}^{W}\right)=1/k\leq c$.
Suppose $c>\frac{1}{k}$. Let $N$ such that if $n>N$, then $\epsilon_{n}<c-\frac{1}{k}$.
Thus if $n>N$, 
\[
q_{0x}^{Z_{n},\delta_{n}}<\epsilon_{n}+\frac{1}{k}<c
\]

and so $T_{Z_{n},\delta_{n}}^{1}=0$. We can also see that $A_{1}^{Z_{n},\delta_{n}}=A_{1}^{W}$
for $n$ sufficiently large.

Now, let's prove that $T_{W}^{2}\left(P_{1}^{W}\right)=\mbox{lim}_{n}T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n},\delta_{n}}\right)$.
By the above argument, we know that there exists $N$ such that if
$n>N$, then $A_{1}^{Z_{n},\delta_{n}}=A_{1}^{W}$ and
\[
P_{1}^{Z_{n},\delta_{n}}<P_{1}^{W}.
\]

Case 1. $T_{W}^{2}\left(P_{1}^{W}\right)=0=T_{W}^{1}\left(P\right)$.
This is impossible because $P_{1}^{W}\leq\frac{1}{k}\leq c$ and $ $$P_{1}^{W}\geq P^{*}>\frac{1}{k}$.

Case 2. $0<T_{W}^{2}\left(P_{1}^{W}\right)$.

Note that $T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n}}\right)\leq T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n}}+\delta_{n}\right)\leq T_{W}^{2}\left(P_{1}^{Z_{n}}+\delta_{n}+\epsilon_{n}\right)$
because if $T_{Z_{n},\delta_{n}}^{1}\left(P\right)\leq t<T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n}}+\delta_{n}\right)$
\begin{eqnarray*}
q_{tx}^{W}\left(A_{1}^{W}\right)-\epsilon_{n} & < & q_{tx}^{Z_{n},\delta_{n}}\left(A_{1}^{W}\right)<P_{1}^{Z_{n}}+\delta_{n}
\end{eqnarray*}
Now, let $x=\mbox{arg max}q_{T_{W}^{2}\left(P_{1}^{W}\right)x}^{W}\left(A_{1}^{W}\right)$.
By (\ref{eq:1.1}), for any $\varepsilon\in\left(0,1\right)$, there
exists a monotonically decreasing sequence $\left\{ s_{k}:\mbox{ }k=1,2,\ldots\right\} \subset\left(T_{W}^{2}\left(P_{1}^{W}\right),1\right)$
such that $\mbox{lim}_{n}s_{n}=T_{W}^{2}\left(P_{1}^{W}\right)$;
and for $k=1,2,\ldots$ we have

\begin{eqnarray*}
W_{x}\left(s_{k}\right)-W_{x}\left(T_{W}^{2}\left(P_{1}^{W}\right)\right) & >v_{k}\equiv & \left(\varepsilon\right)\sqrt{2\left(s_{k}-T_{W}^{2}\left(P_{1}^{W}\right)\right)\mbox{ln}\mbox{ln}\left(1/\left(s_{k}-T_{W}^{2}\left(P_{1}^{W}\right)\right)\right)}.
\end{eqnarray*}
 Notice that $v_{k}>0$ and $\mbox{lim}_{k}v_{k}=0$. Let $\alpha>0$.
Let $\delta$ such that if $\delta_{3}<\delta$, then $\alpha>-\mbox{log}\left(1-\delta_{3}\right)$.
Pick $\delta_{3}<\delta$. Let $K$ such that if $k>K$, $\frac{\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{2}\left(P_{1}^{W}\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{2}\left(P_{1}^{W}\right)I_{\left\{ x^{'}=k\right\} }\right)}{\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)}>1-\delta_{3}$.
Pick $k>K$. Let $N_{4}$ such that if $n>N_{4}$, then $\frac{\epsilon_{n}}{P_{1}^{W}}<v_{k}\frac{1}{\lambda_{z}}+\alpha$
and $\frac{\delta_{n}}{P_{1}^{W}}<\left(v_{k}\frac{1}{\lambda_{z}}+\alpha\right)^{2}/2$.
$ $Observe that
\begin{eqnarray*}
q_{s_{k}x}^{W}\left(A_{1}^{W}\right) & = & \mbox{exp}\left(\frac{W_{x}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x=k\right\} }\right)/\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)\\
 & > & \frac{\mbox{exp}\left(\frac{W_{k}\left(T_{W}^{2}\left(P_{1}^{W}\right)\right)+v_{k}}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{2}\left(P_{1}^{W}\right)I_{\left\{ x=k\right\} }\right)}{\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{2}\left(P_{1}^{W}\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{2}\left(P_{1}^{W}\right)I_{\left\{ x^{'}=k\right\} }\right)}\\
 &  & \times\frac{\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{2}\left(P_{1}^{W}\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{2}\left(P_{1}^{W}\right)I_{\left\{ x^{'}=k\right\} }\right)}{\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)}\\
 & \geq & q_{T_{W}^{2}\left(P_{1}^{W}\right)x}^{W}\mbox{exp}\left(v_{k}\frac{1}{\lambda_{z}}\right)\left(1-\delta_{3}\right)\geq q_{T_{W}^{2}\left(P_{1}^{W}\right)x}^{W}\left(A_{1}^{W}\right)\mbox{exp}\left(v_{k}\frac{1}{\lambda_{z}}\right)\mbox{exp}\left(\alpha\right)\\
 &  & \geq P_{1}^{W}\left(1+v_{k}\frac{1}{\lambda_{z}}+\alpha+\frac{\left(v_{k}\frac{1}{\lambda_{z}}+\alpha\right)^{2}}{2}\right)>P_{1}^{W}+\epsilon_{n}+\delta_{n}.
\end{eqnarray*}
Consequently, 
\[
s_{k}>T_{W}^{2}\left(P_{1}^{W}+\epsilon_{n}+\delta_{n}\right)
\]
if $n>N_{4}$, and so 
\[
s_{k}\geq\mbox{lim sup}_{n}T_{W}^{2}\left(P_{1}^{W}+\delta_{n}+\epsilon_{n}\right).
\]
Since $s_{k}\rightarrow T_{W}^{1}$, we must have that
\begin{eqnarray*}
T_{W}^{2}\left(P_{1}^{W}\right) & \geq & \mbox{lim sup}_{n}T_{W}^{2}\left(P_{1}^{W}+\delta_{n}+\epsilon_{n}\right)\\
 & \geq & \mbox{lim inf}_{n}T_{W}^{2}\left(P_{1}^{W}+\delta_{n}+\epsilon_{n}\right)\\
 & \geq & T_{W}^{2}\left(P_{1}^{W}\right)
\end{eqnarray*}
Consequently, 
\[
T_{W}^{2}\left(P_{1}^{W}\right)=\mbox{lim}_{n}T_{W}^{2}\left(P_{1}^{W}+\delta_{n}+\epsilon_{n}\right).
\]

Now,
\[
T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n}}\right)\geq T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n}}-\delta_{n}\right)\geq T_{W}^{2}\left(P_{1}^{Z_{n}}-\delta_{n}-\epsilon_{n}\right)
\]

because if $t<T_{W}^{2}\left(P_{1}^{Z_{n}}-\delta_{n}-\epsilon_{n}\right)$
\[
q_{tx}^{Z_{n},\delta_{n}}\left(A_{1}^{W}\right)-\epsilon_{n}<q_{tx}^{W}\left(A_{1}^{W}\right)<P_{1}^{Z_{n}}-\delta_{n}-\epsilon_{n}.
\]
Similarly we can prove that 
\[
\mbox{lim}_{n}T_{W}^{2}\left(P_{1}^{W}-\delta_{n}-\epsilon_{n}\right)=T_{W}^{2}\left(P_{1}^{W}\right).
\]
Consequently,
\[
T_{W}^{2}\left(P_{1}^{W}\right)=\mbox{lim}_{n}T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{W}\right).
\]

By a similar argument than before, we can see that $\mbox{arg max}_{x}q_{T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{W}\right),x}^{Z_{n},\delta_{n}}\left(A_{1}^{W}\right)=\mbox{arg max}_{x}q_{T_{W}^{2}\left(P_{1}^{W}\right),x}^{W}\left(A_{1}^{W}\right)$
for $n$ sufficiently large.

The cases $M_{W}=i$ for $k-1\geq i\geq3$ can be proved in a similar
way.

Since almost surely $M_{Y}\in\left\{ 1,\ldots,k-1\right\} $ by Frazier
\cite{key-5}, we conclude that

\[
\mathbb{P}\left(W\text{\ensuremath{\in}D\ensuremath{\left[0,1\right]^{k}}-}D_{s}\right)=1.
\]

$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$

\[
\]

By the extension of the CMT (Theorem 5.5 of Billingsley 1968), we
have the following corollary.

\paragraph*{Corollary 1.}

We have that

\[
f\left(C\left(\delta,t\right),\delta\right)\Rightarrow g\left(W\left(t\right)\right)
\]
in distribution as $\delta\rightarrow0$.

\[
\]

\paragraph*{Theorem 1.}

If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
distributed and independent, over time and across alternatives, then
$\mbox{lim}_{\delta\rightarrow0}Pr\left\{ \mbox{BIZ selects }k\right\} \geq P*$
provided $\mu_{k}=\delta,\mu_{k-1}=\cdots=\mu_{1}=0$. We also suppose
$B_{1}=\cdots=B_{k}=1$ and $c\neq\frac{1}{k}$.

\paragraph*{Proof.}

Let 
\[
\hat{T}_{n}\left(\delta\right)=\min\left\{ t\in\left\{ 0,\delta^{2},2\delta^{2},\ldots\right\} :\mbox{ min}_{x\in A_{n}^{Y,\delta}}q_{tx}^{C\left(\delta,\cdot\right),\delta}\left(A_{n}^{C\left(\delta,\cdot\right),\delta}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}^{Y,\delta}}q_{tx}^{C\left(\delta,\cdot\right),\delta}\left(A_{n}^{C\left(\delta,\cdot\right),\delta}\right)\geq P_{n}^{C\left(\delta,\cdot\right),\delta}\right\} 
\]
and $T_{n}\left(\delta\right)$ the usual stopping times of the algorithm.
Then $T_{n}\left(\delta\right)=\hat{T}_{n}\left(\delta\right)/\delta^{2}$.
Now, we can prove that $\hat{T}_{n}\left(\delta\right)-T_{C\left(\delta,\cdot\right),\delta}^{n}\left(P_{n}^{C\left(\delta,\cdot\right),\delta}\right)\rightarrow0$
with probability $1$ as $\delta\rightarrow0$ using that $C\left(\delta,\cdot\right)$
is right-continuous and $\delta^{2}\rightarrow0$. Consequently, we
can use $C\left(\delta,T_{C\left(\delta,\cdot\right),\delta}^{n}\left(P_{n}^{C\left(\delta,\cdot\right),\delta}\right)\right)$
instead of $C\left(\delta,\hat{T}_{n}\left(\delta\right)\right)$.

Let $CS_{\delta}$ be the event of doing a correct selection given
the configuration $\mu_{k}=\delta,\mu_{k-1}=\cdots=\mu_{1}=0$. Then
\begin{eqnarray*}
\underline{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right) & = & \underline{lim}_{\delta\rightarrow0}\mathbb{P}\left(f\left(C\left(\delta,t\right),\delta\right)=1\right)\\
 & = & \mathbb{P}\left(g\left(W\right)=1\right)\\
 & \geq & P^{*}
\end{eqnarray*}
where the last inequality follows from the paper of Frazier \cite{key-5}.

$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}\;\;\;\;}$

\paragraph*{Theorem 2.}

If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
distributed and independent, over time and across alternatives, then
$\mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right)\geq P*$
provided $\mu_{k}-\mu_{k-1}\geq\delta$. We suppose $B_{1}=\cdots=B_{k}=1$
and $c\neq\frac{1}{k}$.

\paragraph*{Proof.}

Suppose $X_{1},\ldots,X_{k}$ are the observations of the systems
$1,\ldots,k$, respectively. Consider, $\hat{X}_{i}=X_{i}-\mu_{i}e$
if $i\neq k$ and $\hat{X}_{k}=X_{k}-\mu_{k}e+\delta e$. Then
\begin{eqnarray*}
\underline{lim}_{\delta\rightarrow0}\mathbb{P}_{\text{\ensuremath{\mu}}}\left(CS_{\delta}\mid\mathbf{X}\right) & = & \underline{lim}_{\delta\rightarrow0}\mathbb{P}_{\left(0,\ldots,0,\delta\right)}\left(CS_{\delta}\mid\hat{\mathbf{X}}\right)\\
 & = & \underline{lim}_{\delta\rightarrow0}\mathbb{P}\left(g\left(W\right)=1\right)\\
 & \geq & P^{*}.
\end{eqnarray*}

$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
\begin{thebibliography}{References}
\bibitem{key-3}Billingsley, P. 1968. \textit{Convergence of Probability
Measures. }John Wiley and Sons. New York.

\bibitem{key-5}Frazier, P. I. A Fully Sequential Elimination Procedure
for Indifference-Zone Ranking and Selection with Tight Bounds on Probability
of Correct Selection. \textit{Operations Research,} to appear.

\end{thebibliography}
\[
\]
\[
\]

\end{document}

### 2015-01-26 code/fig/final_summary.tex
# Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.

\documentclass[12pt]{article}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{graphicx}

\newcommand{\PstarB}{\mathcal{P}^*_B}
\newcommand{\E}{E}
\newcommand{\sigmacom}{\sigma}
\newcommand{\cmax}{1-(P^*)^{\frac1{k-1}}}
\newcommand{\PZ}{\mbox{PZ}}
\begin{document}

  % Common variance (known and unknown).

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{pdf/FINAL-SC-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-SC-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-MDM-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-MDM-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-RPI-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-RPI-PCS}

    \caption{Common known variance.  
    First row: SC;
    Second row: MDM;
    Third row: RPI}

  \end{figure}

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-SC-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-SC-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-MDM-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-MDM-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-RPI-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-RPI-PCS}

    \caption{Common unknown variance.  
    First row: SC;
    Second row: MDM;
    Third row: RPI}
  \end{figure}

  % Heterogeneous known variance

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{pdf/FINAL-SCINCA-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-SCINCA-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-SCDECA-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-SCDECA-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-MDMINCA-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-MDMINCA-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-MDMDECA-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-MDMDECA-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-RPIHETA-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-RPIHETA-PCS}

    \caption{Heterogeneous known variance, factor of 2 between largest and smallest variances. 
    Row 1: SCINCA;
    Row 2: SCDECA;
    Row 3: MDMINCA;
    Row 4: MDMDECA;
    Row 5: RPIHETA.
    }
  \end{figure}

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{pdf/FINAL-SCINC-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-SCINC-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-SCDEC-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-SCDEC-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-MDMINC-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-MDMINC-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-MDMDEC-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-MDMDEC-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-RPIHET-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-RPIHET-PCS}

    \caption{Heterogeneous known variance, factor of 16 between largest and smallest variances. 
    Row 1: SCINC;
    Row 2: SCDEC;
    Row 3: MDMINC;
    Row 4: MDMDEC;
    Row 5: RPIHET.
    }
  \end{figure}

  % Heterogeneous unknown variance

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-SCINCA-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-SCINCA-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-SCDECA-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-SCDECA-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-MDMINCA-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-MDMINCA-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-MDMDECA-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-MDMDECA-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-RPIHETA-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-RPIHETA-PCS}

    \caption{Heterogeneous unknown variance, factor of 2 between largest and smallest variances.
    Row 1: SCINC;
    Row 2: SCDEC;
    Row 3: MDMINC;
    Row 4: MDMDEC;
    Row 5: RPIHET.
    }
  \end{figure}

  \begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-SCINC-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-SCINC-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-SCDEC-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-SCDEC-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-MDMINC-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-MDMINC-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-MDMDEC-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-MDMDEC-PCS}
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-RPIHET-Nk} 
    \includegraphics[width=2.9in]{pdf/FINAL-UNK-RPIHET-PCS}

    \caption{Heterogeneous unknown variance, factor of 16 between largest and smallest variances.
    Row 1: SCINC;
    Row 2: SCDEC;
    Row 3: MDMINC;
    Row 4: MDMDEC;
    Row 5: RPIHET.
    }
  \end{figure}

% Improvement factors
\begin{figure}[tb]
    \center
    \includegraphics[width=2.9in]{pdf/FINAL-Common-Known-ImprovementFactor}
    \includegraphics[width=2.9in]{pdf/FINAL-Common-Unknown-ImprovementFactor}
    \includegraphics[width=2.9in]{pdf/FINAL-HeteroA-Known-ImprovementFactor}
    \includegraphics[width=2.9in]{pdf/FINAL-Hetero-Known-ImprovementFactor}
    \includegraphics[width=2.9in]{pdf/FINAL-HeteroA-Unknown-ImprovementFactor}
    \includegraphics[width=2.9in]{pdf/FINAL-Hetero-Unknown-ImprovementFactor}

    \caption{Improvement factors.  
    (Top left) Common known variance.  
    (Top right) Common unknown variance.  
    (Middle left) Heterogeneous known variance, factor of 2 between largest and smallest variance.
    (Middle right) Heterogeneous known variance, factor of 16 between largest and smallest variance.
    (Bottom left) Heterogeneous unknown variance, factor of 2 between largest and smallest variance.
    (Bottom right) Heterogeneous unknown variance, factor of 16 between largest and smallest variance.
  }
  \end{figure}

% PGS plot
\begin{figure}[tb]
    \center
    \includegraphics[width=4in]{pdf/FINAL-PGS}

    \caption{Probability of Good Selection under BIZ, as a function of the
    distance between the best and the second best alternatives, for different
  numbers of alternatives $k$.}
  \end{figure}

\end{document}

### 2015-01-26 code/cpp/plot.R

@@ -1,0 +1,17 @@
+d=read.table("ex2.txt")
+library("Hmisc")
+
+d = data.frame(
+  x  = d[,2]
+  , y  = d[,3]
+  , sd = d[,4]
+)
+
+
+plot(d$x, d$y, type="n",ylim=c(0.95,0.983),xlab="delta",ylab="PCS",main="k=10; pstar=0.95; n=5000; sigma=50")
+with (
+  data = d
+  , expr = errbar(x, y, y+sd, y-sd, add=T, pch=1, cap=.1)
+)
+abline(h=0.95)
+

### 2015-01-26 code/cpp/read_problems.cpp

@@ -15,7 +15,7 @@ void usage() {
   exit(-1);
 }
 
-int read_problems(char *filename);
+void read_problems(char *filename);
 
 int main(int argc, char *argv[]) {
   if (argc != 2)
@@ -23,7 +23,7 @@ int main(int argc, char *argv[]) {
   read_problems(argv[1]);
 }
 
-int read_problems(char *filename) {
+void read_problems(char *filename) {
   int nProblems;
 
    FILE *file = fopen(filename,"r");
@@ -77,4 +77,5 @@ int read_problems(char *filename) {
      printf("\n");
    }
    fclose(file);
+    
 }

### 2015-01-26 code/cpp/write_problems.cpp

@@ -13,15 +13,15 @@
 
 #define FILE_DIR "problems/"
 
-int write_SC(const char *filename, int maxk, double pstar, double delta, double sigma1, double sigma2); 
-int write_MDM(const char *filename, int maxk, double pstar, double delta, double sigma1, double sigma2);
+void write_SC(const char *filename, int maxk, double pstar, double delta, double sigma1, double sigma2);
+void write_MDM(const char *filename, int maxk, double pstar, double delta, double sigma1, double sigma2);
 //int write_RPI(const char *filename, int maxk, double pstar, double delta, double sigma, double RPIsigma, int nProblems, int moveToPreferenceZone);
-int write_RPI(const char *filename, int maxk, double pstar, double delta, double lower_sigma, double upper_sigma, double RPIsigma, int nProblems, int moveToPreferenceZone);
-int write_SCvP(const char *filename, int k, double delta, double sigma1, double sigma2); 
-int write_PGS(const char *filename, int k, int m, double pstar, double delta, double sigma);
-int write_animation(const char *filename, int k, double pstar, double delta, double sigma);
-int write_trial(const char *filename);
-int write_trial2(const char *filename);
+void write_RPI(const char *filename, int maxk, double pstar, double delta, double lower_sigma, double upper_sigma, double RPIsigma, int nProblems, int moveToPreferenceZone);
+void write_SCvP(const char *filename, int k, double delta, double sigma1, double sigma2);
+void write_PGS(const char *filename, int k, int m, double pstar, double delta, double sigma);
+void write_animation(const char *filename, int k, double pstar, double delta, double sigma);
+void write_trial(const char *filename);
+void write_trial2(const char *filename);
 
 int main(int argc, char *argv[]) {
 
@@ -106,7 +106,7 @@ int main(int argc, char *argv[]) {
 /*
  * Writes random problem instances to a file.
  */
-int write_RPI(const char *filename, int maxk, double pstar, double delta, double lower_sigma, double upper_sigma, double RPIsigma, int nProblems, int moveToPreferenceZone) {
+void write_RPI(const char *filename, int maxk, double pstar, double delta, double lower_sigma, double upper_sigma, double RPIsigma, int nProblems, int moveToPreferenceZone) {
 #ifdef USE_FIXED_SEED
    int seed = 0;
 #else
[…]

### 2015-01-26 code/stocc/erfres.cpp

@@ -25,8 +25,10 @@ ERFRES_L =   48    (length of each table)
 * Copyright 2004-2008 by Agner Fog. 
 * GNU General Public License http://www.gnu.org/licenses/gpl.html
 *****************************************************************************/
-extern "C" {
 
+extern "C" {
+    int ERFRES_N =   13 ;
+    const int ERFRES_L =   48  ;
    //number of standard deviations to integrate
    double NumSDev[ERFRES_N] = {
    4.324919041, 4.621231001, 4.900964208, 5.16657812, 5.419983175, 5.662697617, 5.895951217, 6.120756286, 6.337957755, 6.548269368, 6.752300431, 6.950575948, 7.143552034};

### 2015-01-26 code/stocc/wnchyppr.cpp

@@ -531,7 +531,9 @@ void CWalleniusNCHypergeometric::findpars() {
    // find r to center peak of integrand at 0.5
    double dd, d1, z, zd, rr, lastr, rrc, rt, r2, r21, a, b, dummy;
    double oo[2];
-   double xx[2] = {x, n-x};
+    double aux=x;
+    double aux1=n-x;
+   double xx[2] = {aux, aux1};
    int i, j = 0;
    if (omega > 1.) { // make both omegas <= 1 to avoid overflow
       oo[0] = 1.;  oo[1] = 1./omega;
@@ -617,7 +619,9 @@ int CWalleniusNCHypergeometric::BernouilliH(int32_t x_, double h, double rh, Sto
    double qi1;                     // 1-qi
    double omegai[2] = {omega,1.};  // weights for each color
    double romegi;                  // r*omega[i]
-   double xi[2] = {x_, n-x_};      // number of each color sampled
+    double aux=x_;
+    double aux2=n-x_;
+   double xi[2] = {aux, aux2};      // number of each color sampled
    double k;                       // adjusted width for majorizing function Ypsilon(t)
    double erfk;                    // erf correction
    double rdm1;                    // rd - 1
@@ -782,7 +786,10 @@ double CWalleniusNCHypergeometric::laplace() {
    int degree;                   // max expansion degree
    double accur;                 // stop expansion when terms below this threshold
    double omegai[COLORS] = {omega, 1.}; // weights for each color
-   double xi[COLORS] = {x, n-x}; // number of each color sampled
+    double aux=x;
+    double aux2=n-x;
+    double xi[COLORS] = {aux, aux2};
+   
    double f0;                    // factor outside integral
    double rho[COLORS];           // r*omegai
    double qi;                    // 2^(-rho)

### 2015-01-26 ranking/ranking/main.cpp

@@ -1,0 +1,15 @@
+//
+//  main.cpp
+//  ranking
+//
+//  Created by Saul Toscano Palmerin on 12/18/14.
+//  Copyright (c) 2014 Saul Toscano Palmerin. All rights reserved.
+//
+
+#include <iostream>
+
+int main(int argc, const char * argv[]) {
+    // insert code here...
+    std::cout << "Hello, World!\n";
+    return 0;
+}

### 2015-04-10 paper/paper_version2.tex
4/10/15

@@
-%% LyX 2.0.0 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.1.2.1 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
@@
 \usepackage[T1]{fontenc}
+\usepackage[latin9]{inputenc}
 \usepackage{geometry}
@@
   \leavevmode\llap{\makeenmark}}
+
+\date{}
 
@@
 \usepackage{babel}
-\usepackage{xunicode}
 \begin{document}
 
-\title{On the Asymptotic Validity of a Fully Sequential Elimination Procedure
-for Indifference-Zone Ranking and Selection with Tight Bounds on Probability
+\title{Asymptotic Validity of a Fully Sequential Elimination Procedure for
+Indifference-Zone Ranking and Selection with Tight Bounds on Probability
 of Correct Selection}
 
+\author{Saul Toscano\\
+{\small{}School of Operations Research and Information Engineering,
+Cornell University}\\
+Peter I. Frazier\\
+{\small{}School of Operations Research and Information Engineering,
+Cornell University}}
+
 \maketitle
-We prove the validity of the sequential elimination IZ procedure proposed
-by Frazier \cite{key-5} when $\delta$ goes to $0$. Specifically,
-we analyze Algorithm 2, when $B_{1}=\cdots=B_{k}=1$:
+We consider the indifference-zone (IZ) formulation of the ranking
+and selection problem. Conservatism leads classical IZ procedures
+to take too many samples in problems with many alternatives. The Bayes-inspired
+Indifference Zone (BIZ) procedure, proposed in Frazier (2014), is
+less conservative than previous procedures, but its proof of validity
+requires strong assumptions. In this paper, we present a new proof
+of asymptotic validity that relaxes these assumptions.
+
+\section{Introduction}
+
+One common problem in simulation is that of choosing the best among
+several simulated systems. The problem of deciding how many samples
+to use from each alternative to support our selection as the best
+is the ranking and selection problem. An efficient solution to this
+problem has to balance between the time spent simulating and the quality
+of the selection.
+
+This paper will consider the indifference-zone (IZ) formulation of
+the ranking and selection problem, in which we choose the best system
+with probability larger than a pre-specified threshold, whenever the
+distance between the best system and the others is sufficiently large.
+We say that a sampling procedure having this property satisfies the
+IZ guarantee and the set of system configurations under which the
+best alternative is better than the second best by at least some given
+$\delta>0$ is called the preference zone (PZ). The seminal work dates
+back to Bechhofer (1954), with early work compiled in the monograph
+Bechhofer et al. (1968). The progress in the area has been summarized
+in Bechhofer et al. (1995), Swisher et al. (2003), Kim and Nelson
+(2006, 2007) and Frazier (2014).
+
+The goal of an IZ algorithm is to take as few samples as possible
+while the IZ guarantee is satisfied. The first IZ procedures presented
+in Bechhofer (1954), Paulson (1964), Fabian (1974), Rinott (1978),
+Hartmann (1988, 1991), Paulson (1994) satisfy the IZ guarantee, but
+they usually take too many samples when there are many alternatives,
+in part because their probability of correct selection (PCS) is much
+larger than the probability specified by the user. A reason of this
+is the use of the Bonferroni's inequality which leads to sample more
+than necessary. More recent algorithms in Kim and Nelson (2001), Goldsman
+et al. (2002), Hong (2006) improve the performance but they still
+use the Bonferroni's inequality, and so the methods are inefficient
+when there are several systems. Procedures in Kim and Dieker (2011),
+Dieker and Kim (2012) do not use the Bonferroni's inequality only
+when compare groups of three alternatives.
+
+Since the classic IZ procedures take too many samples with many alternatives,
+these methods are unpopular when there are more than a few hundred
+alternatives. However, Frazier (2014) presented a new sequential elimination
+IZ procedure, called BIZ (Bayes-inspired Indifference Zone), whose
+lower bound on worst-case probability of correct selection in the
+preference zone is tight in continuous time, and almost tight in the
+discrete time. In numerical experiments, the number of samples required
+by BIZ is significantly smaller than that of the most popular IZ procedures,
+especially on problems with many alternatives. Unfortunately, the
+proof that the BIZ procedure satisfies the IZ guarantee for the discrete-time
+case assumes that variances are known and have an integer multiple
+structure which is not very realistic. In practice, variances are
+unknown. However, asymptotically we can use a central limit theorem
+that allows us to prove the asymptotic validity of the BIZ procedure
+for the discrete-time case. Moreover, we only need to assume that
+the systems are independent, identically distributed and have finite
+variance.
+
+Kim et al. (2006) also proves the asymptotical validity of a IZ procedure.
+Our proof is larger because the BIZ procedure is more sophisticated
+and the bound for the PCS is tighter. To prove the case when the variances
+are known, we use a theorem for Ergodic processes that shows how to
+standardize the output data to make them behave like Brownian motion
+processes in the limit. We also use an extension of the Continuous
+Mapping Theorem (Theorem 5.5 of Billingsley 1968) to see that the
+algorithm behaves like a sequential elimination IZ procedure with
+a Brownian motion process instead of the standardized sum of the output
+data in the limit, and then we use the results of the paper of Frazier
+\cite{key-5} to prove the validity of this algorithm in the limit.
+Finally, we use a random change of time argument to prove the case
+when the variances are unknown.
+
+This paper is organized as follows: In $\text{§}2$, we recall the
+indifference-zone ranking and selection problem. In $\text{§}3$,
+we recall the Bayes-inspired IZ (BIZ) procedure. In $\text{§}4$,
+we present the proof of the validity of the algorithm when the variances
+are known. In $\text{§}5$, we prove the case when the variances are
+unknown. In $\text{§}6$, we present some simulations showing the
+effectiveness of the algorithm. In $\text{§}7$, we conclude.
+
+\section{Indifference-Zone Ranking and Selection }
+
+Ranking and Selection is a procedure for selecting the best system
+among a finite set of alternatives, i.e. the system with the largest
+mean. The method selects a system as the best based on the samples
+that are observed sequentially over the time. If the best system is
+selected, we say that the procedure has made the \emph{correct selection}
+(CS). We define the \emph{probability of correct selection} as 
+\[
+\mbox{PCS}\left(\mu,\lambda\right)=\mathbb{P}_{\mu,\lambda}\left(\hat{x}\in\mbox{arg max}_{x}\mu_{x}\right)
+\]
+where $\hat{x}$ is the alternative chosen by the procedure and $\mathbb{P}_{\mu,\lambda}$
+is the probability measure under which samples from system $x$ have
+mean $\mu_{x}$ and finite variance $\lambda_{x}^{2}$.
+
+In the Indifference-Zone Ranking and Selection, the procedure is indifferent
+in the selection of a system whenever the means of the populations
+are nearly the same. Formally, let $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
+be the vector of the true means, the \emph{indifference zone} is defined
+as the set $\left\{ \mu\in\mathbb{R}^{k}:\mu_{\left[k\right]}-\mu_{\left[k-1\right]}<\delta\right\} $.
+The complement of the indifference zone is called the \emph{preference
+zone} (PZ) and $\delta>0$ is called the indifference zone parameter.
+We say that a procedure meets the \emph{indifference-zone (IZ) guarantee
+}at $P^{*}\in\left(1/k,1\right)$ and $\delta>0$ if
+\[
+\mbox{PCS}\left(\mu,\lambda\right)\geq P^{*}\mbox{ for all }\mu\in\mbox{PZ}\left(\delta\right).
+\]
+We assume $P^{*}>1/k$ because IZ guarantees can be meet by choosing
+$\hat{x}$ uniformly at random from among $\left\{ 1,\ldots,k\right\} $.
+
+\section{The Bayes-inspired IZ (BIZ) Procedure}
+
+BIZ is an elimination procedure. This procedure maintains a set of
+alternatives that are in contention, and it takes samples from each
+alternative in this set at each point in time. At beginning, all alternatives
+are in contention, and over the time alternatives are eliminated.
+The procedure ends when there is only one alternative in the contention
+set and this remain alternative is chosen as the best.
+
+Frazier (2014) showed that the BIZ procedure with known common variance
+satisfies the IZ guarantee when the systems follow the normal distribution
+, with tight bounds on worst-case preference-zone in continuous time.
+He also proved that this procedure retains the IZ guarantee when the
+systems follow the normal distribution, and the variances are known
+and are integer multiples of a common value. The continuous time version
+of this procedure also satisfies the IZ guarantee, with a tight worst-case
+preference-zone PCS bound.
+
+The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
+variances is given in Alg. 2. It takes a variable number of samples
+from each alternative, and $n_{tx}$ is this number. This algorithm
+depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
+and $n_{0}$. $n_{0}$ is the number of samples to use in the first
+stage of samples, and $100$ is the recommended value for $n_{0}$.
+$B_{x}$ controls the number of samples taken from system $x$ in
+each stage.
+
+For each $t$, $x\in\left\{ 1,\ldots,k\right\} $, and subset $A\subset\left\{ 1,\ldots,k\right\} $,
+we define a function
+\[
+q_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right),\right.\mbox{ }\beta_{t}=\frac{\sum_{x'\in A}n_{tx'}}{\sum_{x'\in A}\hat{\lambda}_{tx'}^{2}}
+\]
+where $\hat{\lambda}_{tx'}^{2}$ is the sample variance of all samples
+from alternative $x$ thus far and $Z_{tx}=Y_{n_{tx},x}$.
+
+\paragraph{Algorithm: Discrete-time implementation of BIZ, for unknown and/or heterogeneous variances.}    
+\begin{algorithmic}[1]   
+\label{alg:hetero-BIZ}   
+\REQUIRE $c \in [0,\cmax]$, $\delta>0$, $P^*\in(1/k,1)$, $n_0\ge0$ an integer, $B_1,\ldots,B_k$ strictly positive integers.
+Recommended choices are $c=\cmax$, $B_1=\cdots=B_k=1$ and $n_0$ between $10$ and $30$.
+If the sampling variances $\lambda^2_x$ are known, replace the estimators
+$\lambdahat^2_{tx}$ with the true values $\lambda^2_x$, and set $n_0=0$.
+
+\STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
+Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.     
+\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
+\WHILE{$x\in\mbox{max}_{x\in A} q_{tx}\left(A\right)<P$}
+\WHILE{$\mbox{min}_{x\in A} q_{tx}\left(A\right) \le c$}
+ \STATE Let $x\in\mbox{arg min}_{x\in A} q_{tx}\left(A\right)$.
+    \STATE Let $\upthresh \leftarrow \upthresh/(1-q_{tx}\left(A\right))$.     
+\STATE Remove $x$ from $A$.
+\ENDWHILE
+  \STATE Let $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.     
+\STATE For each $x\in A$, let      $n_{t+1,x} = \ceil\left( \lambdahat^2_{tx} (n_{tz} + B_z) / \lambdahat^2_{tz} \right)$.
+\STATE For each $x\in A$, if $n_{t+1,x}>n_{tx}$, take $n_{t+1,x}-n_{tx}$ additional samples from alternative $x$.
+Let $W_{t+1,x}$ and $\lambdahat^2_{t+1,x}$ be the sample mean and sample variance respectively of all samples from alternative $x$ thus far.
+\STATE Increment $t$.
+ \ENDWHILE
+  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} Z_{tx} / n_{tx}$ as our estimate of the best.
+
+\end{algorithmic}
+
+\vspace{10mm}
+This algorithm generalizes the BIZ procedure with known common variance.
+In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$.
+The algorithm 2 can be generalized to the continuous case (See appendix B and Frazier (2014)).
+This procedure is a slightly modification of the original BIZ procedure
+
+\section{Asymptotic Validity when the Variances are Known}
+
+In this section we prove that the BIZ procedure satisfies the IZ guarantee
+when the variances are known and $\delta\rightarrow0$, where the
+vector of the true means $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
+is equal to $\delta a$ for some $a\in\mathbb{R}^{k}$ and $\delta>0$.
+Without loss of generality suppose that the true means satisfy that
+$\mu_{k}>\mu_{k-1}\geq\cdots\geq\mu_{1}$. We suppose that samples
+from system $x\in\left\{ 1\ldots,k\right\} $ are identically distributed
+and independent, over time and across alternatives. We also define
+$\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$
+and we suppose that $\mbox{min}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}>0$
+and $\mbox{max}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}<\infty$.
+
+The BIZ procedure maps $\left(Y_{n_{x}\left(t\right),x}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
+to a selection decision, where $Y_{n_{x}\left(t\right),t}$ is the
+sum of samples observed by time $t$. In more detail, it works by
+transforming $\left(Y_{n_{x}\left(t\right),x}:A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
+to $\left(q'_{tx}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$.
+This $q'$ process is given by time process with jumps at $t\in\mathbb{N}$,
+\[
+q'_{tx}\left(A\right)=q'\left(\left(Z_{tx},t:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\right.
+\]
+where the variances are fixed. The same distribtuion over selection
+decision will result if we apply the same same selection process to
+the following time process with jumps at $t\in\left\{ 0,\delta^{2},2\delta^{2},\ldots\right\} =\delta^{2}\mathbb{N}$,
+\[
+q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
+\]
+Later, we can approximate the previous process by the continuous time
+process
+\begin{eqnarray}
+q_{tx}\left(A\right) & = & q\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)\label{eq:0.001}
+\end{eqnarray}
+where $t\geq0$ . Later we will show the difference in selection decisions
+vanishes as $\delta\rightarrow0$.
+
+After that, we would like to use a kind of central limit theorem for
+$Z_{\frac{t}{\delta^{2}}x}=Y_{n_{x}\left(t/\delta^{2}\right),x}$
+when $\delta$ goes to zero to work with a Brownian motion instead.
+Specifically, we are going to see that the the standardized sum of
+the output data converges to a Brownian motion in the sense of $D_{\infty}:=D[0,\infty)$,
+which is the set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$
+that are right-continuous and have left-hand limits, with the Skorohod
+topology. The definition and the properties of this topology may be
+found in Chapter 3 of Billingsley 1999 and the appendix. We will first
+see this result because it will give us a clue for proving the asymptotic
+validity of the Algorithm 2.
+
+We briefly recall the definition of convergence of random paths in
+the sense of $D_{\infty}$. Suppose that we have a sequence of random
+paths $\left(\mathcal{X}_{n}\right)_{n\geq0}^{\infty}$ such that
+$\mathcal{X}_{n}:\varOmega\rightarrow D_{\infty}$ where $\left(\Omega,\mathcal{F},\mathbb{P}\right)$
+is our probability space. We say that $\mathcal{X}_{n}\Rightarrow\mathcal{X}_{0}$
+in the sense of $D_{\infty}$ if $P_{n}\Rightarrow P_{0}$ where $P_{n}:\mathcal{D}_{\infty}\rightarrow\left[0,1\right]$
+are defined as $P_{n}\left[A\right]=\mathbb{P}\left[\mathcal{X}_{n}^{-1}\left(A\right)\right]$
+for all $n\geq0$ and $\mathcal{D}_{\infty}$ are the Borel subsets
+for the Skorohod topology.
+
+The following lemma shows that the standardized sum of the output
+data with $t$ changed by $t/\delta^{2}$ converges to a Brownian
+motion in the sense of $D_{\infty}$.
+
+\paragraph*{Lemma 1.}
+
+For each $x\in\left\{ 1\ldots,k\right\} $, we define
+\[
+\mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
+\]
+where $Y_{n,x}$ is the sum of the first $n$ samples from alternative
+$x$. Let $x\in\left\{ 1\ldots,k\right\} $, then
+\[
+\mathcal{C}_{x}\left(\delta,\cdot\right)\Rightarrow W_{x}\left(\cdot\right)
+\]
+as $\delta\rightarrow0$ in the sense of $D[0,\infty)$, where $W_{x}$
+is a standard Brownian motion.
+
+\paragraph*{Proof.}
+
+By Theorem 19.1 of Billingsley 1999,
+
+\[
+\frac{Y_{n_{x}\left(t\right),x}-\mbox{floor}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right)
+\]
+in the sense of $D[0,\infty)$.
+
+Fix $w\in\Omega$. Observe that
+\[
+\frac{Y_{\mbox{floor}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{floor}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}-\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\rightarrow0
+\]
+uniformly in $\left[0,s\right]$ for all $s\geq0$ and then by Theorem
+A.2 
+\[
+\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right)
+\]
+in the sense of $D[0,\infty)$.
+
+Since $\frac{\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}-ceil\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right)}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\rightarrow0$
+uniformly on $[0,s]$ for every $s\geq0$, then by Theorem A.2
+
+\[
+\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right).
+\]
+
+Finally, observe that for fixed $\omega\in\Omega$,
+\begin{eqnarray*}
+ &  & \frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}-\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)+n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\right),x}-\mbox{}\left(n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\\
+ & = & \frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)+n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\right),x}+\left(n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\\
+ & \rightarrow & 0
+\end{eqnarray*}
+uniformly in $\left[0,t\right]$ for all $t\geq0$, and so by Theorem
+A.2 the result follows.
+
+$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+Now, we use the product topology in $D^{k}\left[0,\infty\right)$
+for $k\in\mathbb{N}$. This topology may be described as the one under
+which $\left(Z_{n}^{1},\ldots,Z_{n}^{k}\right)\rightarrow\left(Z_{0}^{1},\ldots,Z_{0}^{k}\right)$
+if and only if $Z_{n}^{i}\rightarrow Z_{0}^{i}$ for all $i\in\left\{ 1,\ldots,k\right\} $.
+See the Miscellany of Billingsley 1968. The following corollary follows
+from the previous result and independence.
+
+\paragraph*{Corollary 1.}
+
+We have that
+\[
+\mathcal{C}\left(\delta,\cdot\right):=\left(\mathcal{C}_{x}\left(\delta,\cdot\right)\right)_{x\in A}\Rightarrow W\left(\cdot\right):=\left(W_{x}\left(\cdot\right)\right)_{x\in A}
+\]
+as $\delta\rightarrow0$ in the sense of $D_{\infty}^{k}$.\\
+
+We now gain the insight that we were looking for. We will use $\mathcal{C}_{x}\left(\delta,\cdot\right)$
+instead of $Z_{\frac{t}{\delta^{2}}x}$ in $\left(1\right)$, which
+is the definition of $q_{tx}\left(A\right)$,
+\[
+q_{tx}\left(A\right)=q'\left(\left(C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right),
+\]
+the previous equation is true beucase 
+\[
+Z_{\frac{t}{\delta^{2}}x}=C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right).
+\]
+
+Observe that $\mathcal{C}\left(\delta,\cdot\right)\in D\left[0,\infty\right)^{k}$
+and the convergence of Lemma 1 is in $D\left[0,\infty\right)^{k}$,
+consequently the following natural step is to generalize the continuous-time
+procedure for the heterogeneous variance setting, see Appendix B,
+to the space $D\left[0,\infty\right)^{k}$. Specifically, for each
+$F\in D\left[0,\infty\right)^{k}$, we define $q_{tx}^{F,\delta}\left(A\right)$
+as
+\[
+q_{tx}^{F,\delta}\left(A\right)=q'\left(\left(F_{x}\left(t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
+\]
+
+Note that if we replace $F$ by $\mathcal{C}\left(\delta,t\right)$,
+we get $q{}_{tx}\left(A\right)$ in the previous equation. Using the
+continuous-time procedure for the heterogeneous variance setting with
+the paths $\left(q_{tx}^{F,\delta}\left(A\right):t\geq0\right)$,
+we see that there exists a selection decision for each $F\in D\left[0,\infty\right)^{k}$.
+Since we are interested in the right selection, ( i.e. in choosing
+$k$) for each $F\in D\left[0,\infty\right)^{k}$, we define the following
+function 
+\begin{eqnarray*}
+f\left(F,\delta\right) & = & \begin{cases}
+1 & \mbox{if }k\mbox{ is chosen}\mbox{ }\\
+0 & \mbox{otherwise}
+\end{cases}
+\end{eqnarray*}
+ Observe that $f$ is a function that depends in the path $\left\{ q_{tx}^{F,\delta}\left(A\right):t\geq0\right\} $.
+We are doing all this because we want to see that $f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)$
+looks like the right or wrong selection decision of an algorithm that
+depends on a standard Brownian motion instead of $\mathcal{C}\left(\delta,\cdot\right)$,
+and this will give us the proof because we will be able to use the
+theory developed by Frazier (2014) to prove the theorem. Thus, the
+following step is to find the limit of $q_{tx}^{F,\delta}\left(A\right)$
+when $\delta$ goes to zero, which is called $q_{tx}^{F}\left(A\right)$
+and equal to
+
+\[
+q_{tx}^{F}\left(A\right):=\mbox{exp}\left(\frac{F_{x}\left(t\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}ta_{x}\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{F_{x'}\left(t\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}ta_{x^{'}}\right).
+\]
+ Using the same previous idea, for each $F\in D\left[0,\infty\right)^{k}$,
+we define the new functions
+\[
+\]
+\begin{eqnarray*}
+g\left(F\right) & = & \begin{cases}
+1 & \mbox{if }k\mbox{ is chosen}\mbox{ }\\
+0 & \mbox{otherwise}
+\end{cases}.
+\end{eqnarray*}
+
+So, we want to prove that 
+\[
+f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)\Rightarrow g\left(W\right)
+\]
+as $\delta\rightarrow0$ in distribution.
+
+In order to prove this, we first prove Lemma 2, which will allow us
+to use Theorem 5.5 of Billingsley 1968, which implies the desired
+result.
+
+\paragraph*{Lemma 2.}
+
+Let $\left\{ \delta_{n}\right\} \subset\left(0,\infty\right)$ such
+that $\delta_{n}\rightarrow0$. If $D_{s}\equiv\{Z\in D\left[0,\infty\right)^{k}:\mbox{ if }\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}\mbox{ and }$
+$\mbox{lim}{}_{n}d_{\infty}\left(Z_{n},Z\right)=0$ , then the sequence
+$\left\{ f\left(Z_{n},\delta_{n}\right)\right\} $ converges to $\left\{ g\left(Z\right)\right\} $$\left.\right\} $$ $,
+then $ $$\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\right)=1$.\\
+
+First, we are going to prove the following five results.\\
+
+\paragraph*{Proposition 1.}
+
+Suppose $\left\{ f_{n}\right\} $ and $\left\{ g_{n}\right\} $ are
+two sequences of functions on $D_{\infty}$ such that $f_{n}\rightarrow f$
+and $g_{n}\rightarrow g$ in $D_{\infty}$. If $f$ and $g$ are continuous,
+then
+\[
+\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)
+\]
+in $D_{\infty}$.
+
+\paragraph*{Proof.}
+
+Let $t^{*}>0$. We will prove that $\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)$
+in $D_{t^{*}}$ and the theorem will follow from Theorem 16.2 of Billingsley
+1999.
+
+Since $f$ and $g$ are uniformly continuous in $\left[0,t^{*}\right]$
+and $f_{n}\rightarrow f$ and $g_{n}\rightarrow g$ in $\left[0,t^{*}\right]$,
+then $ $ $f_{n}$ and $g_{n}$ converge uniformly to $f$ and $g$,
+respectively. Consequently, $\left(f_{n},g_{n}\right)\rightarrow\left(f,g\right)$
+uniformly in $\left[0,t^{*}\right]$. Let $a_{f}^{+}=\mbox{max}_{t\in\left[0,t^{*}\right]}\left|f(t)\right|$,
+$a_{f}^{-}=-a_{f}^{+}$, $a_{g}^{+}=\mbox{max}_{t\in\left[0,t^{*}\right]}\left|g(t)\right|$
+and $a_{g}^{-}=-a_{g}^{+}$. Let $N$ such that if $n\geq N$, implies
+$\left|f_{n}\left(t\right)-f\left(t\right)\right|<1$ and $\left|g_{n}\left(t\right)-g\left(t\right)\right|<1$
+for all $t\in\left[0,t^{*}\right]$. Consequently, if $n\geq N$,$ $
+$f_{n}\left(t\right)\in\left[a_{f}^{-}-1,a_{f}^{+}+1\right]$ and
+$g_{n}\left(t\right)\in\left[a_{g}^{-}-1,a_{g}^{+}+1\right]$ for
+all $t$ in $\left[0,t^{*}\right]$. Since $\mbox{min}\left(x,y\right)$
+is continuous, then it is uniformly continuous in $A=\left[a_{f}^{-}-1,a_{f}^{+}+1\right]\times\left[a_{g}^{-}-1,a_{g}^{+}+1\right]$.
+
+Let $\epsilon>0$, then there exists $\delta>0$ such that if $\left\Vert \left(u,v\right)\right\Vert _{2}<\delta$
+and $ $$\left(u:=\left(u_{1},u_{2}\right),v:=\left(v_{1},v_{2}\right)\right)\in A$,
+then 
+\begin{equation}
+\left|\mbox{min}\left(u_{1},u_{2}\right)-\mbox{min}\left(v_{1},v_{2}\right)\right|<\epsilon.\label{eq:1.10}
+\end{equation}
+Let $M>N$ such that if $n>M$, then
+\[
+\left\Vert \left(f_{n}\left(t\right),g_{n}\left(t\right)\right)-\left(f\left(t\right),g\left(t\right)\right)\right\Vert _{2}<\delta
+\]
+for all $t\in\left[0,t^{*}\right]$. Consequently, if $n>M$, by (\ref{eq:1.10}),
+\[
+\left|\mbox{min}\left(f_{n}\left(t\right),g_{n}\left(t\right)\right)-\mbox{min}\left(f\left(t\right),g\left(t\right)\right)\right|<\epsilon
+\]
+for all $t\in\left[0,t^{*}\right]$. Since uniform convergence implies
+Skorohod convergente, then $\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)$
+in $D_{t^{*}}$, and the result follows.
+
+$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+\paragraph*{Proposition 2.}
+
+Suppose $\left\{ f_{n}\right\} $ is a sequence of functions in $D_{\infty}$
+such that $f_{n}\rightarrow f$ in $D_{\infty}$ , $f$ is continuous,
+and $\left\{ T_{n}\right\} \subset\left[0,\infty\right)$ is a sequence
+such that $T_{n}\rightarrow T$. We define $T\left(a\right):=\mbox{inf}\left\{ t\geq T:f\left(t\right)\geq a\right\} $
+for each $a\in\mathbb{R}$. Suppose $T\left(0\right)\in\mathbb{R}$.
+Furthermore, we suppose that there exists $\left\{ \epsilon_{n}\right\} \subset\left(0,\infty\right)$
+such that $\epsilon_{n}\rightarrow0$ , $\epsilon_{n}\geq\epsilon_{n+1}$,
+and$ $
+\begin{equation}
+\left\Vert f_{n}\left(t\right)-f\left(t\right)\right\Vert _{2}<\epsilon_{n}\label{eq:2.11}
+\end{equation}
+for all $t\in\left[0,T\left(0\right)\right]$. We also suppose that
+$\mbox{lim sup}_{n}T\left(\epsilon_{n}\right)\leq T\left(0\right)$.
+Thus we have that
+
+\[
+\mbox{inf}\left\{ t\geq T_{n}:f_{n}\left(t\right)\geq0\right\} \rightarrow\mbox{inf}\left\{ t\geq T:f\left(t\right)\geq0\right\} 
+\]
+if $T\left(0\right)>T$ or $T_{n}=T$.
+
+\paragraph*{Proof.}
+
+We are going to suppose $T\left(0\right)>T$, and the case $T_{n}=T$
+can be proved using almost the same ideas. We introduce the notation
+$T_{n}\left(a\right):\mbox{inf}\left\{ t\geq T_{n}:f_{n}\left(t\right)\geq a\right\} $
+for $a\in\mathbb{R}$. Since $T\left(0\right)>T$, we can take $N$
+such that if $n>N$, then $T_{n}<T+T\left(0\right)-T=T\left(0\right)$
+and $\epsilon>\epsilon_{n}$ where $\epsilon:=sup_{n}\epsilon_{n}$.
+Let $n>N$. Note that $T_{n}\left(0\right)\leq T_{n}\left(\epsilon_{n}\right)$.
+
+We also have that
+\begin{eqnarray}
+T\left(0\right) & \leq & \mbox{lim inf}_{n}T\left(\epsilon_{n}\right)\nonumber \\
+ & \leq & \mbox{lim sup}_{n}T\left(\epsilon_{n}\right)\label{eq:2.3}
+\end{eqnarray}
+Now, since $\mbox{lim sup}_{n}T\left(\epsilon_{n}\right)\leq T\left(0\right)$,
+\begin{eqnarray*}
+T\left(0\right) & \geq & \mbox{lim sup}_{n}T\left(\epsilon_{n}\right)\\
+ & \geq & \mbox{lim inf}_{n}T\left(\epsilon_{n}\right)\\
+ & \geq & T\left(0\right)
+\end{eqnarray*}
+and so 
+\[
+\mbox{lim inf}_{n}T_{n}\left(0\right)\leq\mbox{lim sup}_{n}T_{n}\left(0\right)\leq\mbox{lim sup}_{n}T_{n}\left(\epsilon_{n}\right)=\mbox{lim}_{n}T\left(\epsilon_{n}\right)=T\left(0\right)
+\]
+
+Now, let's prove that $\mbox{lim inf}_{n}T_{n}\left(0\right)\geq T\left(0\right)$.
+Since $T\left(0\right)>T$, there exists $M$ such that $T\left(0\right)-\frac{1}{m}\geq T$
+if $m>M$, and let $t_{m}=T\left(0\right)-\frac{1}{m}$ and $\alpha_{m}=\mbox{max}\left\{ f\left(t\right):t\in\left[T,t_{m}\right]\right\} $.
+Note that $\alpha_{m}<0$ because $t_{m}<T\left(0\right)$. Since
+$\epsilon_{n}\rightarrow0$, there exists $N$ such that if $n>N$,
+then
+\[
+\epsilon_{n}\leq-\alpha_{m}
+\]
+Thus, since $\left\Vert f_{n}\left(t\right)-f\left(t\right)\right\Vert _{2}<\epsilon_{n}$
+if $t\in\left[T,t_{m}\right]$, then
+\begin{equation}
+f_{n}\left(t\right)<f\left(t\right)+\epsilon_{n}\leq f\left(t\right)-\alpha_{m}\leq0\label{eq:20.1}
+\end{equation}
+
+If $T\leq T_{n}\left(0\right)$ for all $n>N$, then $T_{n}\left(0\right)\geq t_{m}$
+by (\ref{eq:20.1}) and so $\mbox{lim inf}_{n}T_{n}\left(0\right)\geq t_{m}$.
+Taking the limit $m\rightarrow\infty$, we conclude that $\mbox{lim inf}_{n}T_{n}\left(0\right)\geq T\left(0\right)$.
+
+So, we only need to prove that $T\leq T_{n}\left(0\right)$ for $n$
+large. We proceed by contradiction. Let $s>0$ be any number. Take
+$N$ such that if $n>N$, then $\epsilon_{n}<s$. Since we are supposing
+that for all $N'$ there exists $n>N'$ such that $T>T_{n}\left(0\right)$,
+and $T_{n}\left(0\right)\geq T_{n}$, $T_{n}\rightarrow T$, then
+we have that for every $\epsilon>0$ there exists $n$ large such
+that $T-\epsilon<T_{n}\left(0\right)<T$ . By (\ref{eq:2.11}), 
+\begin{eqnarray*}
+f\left(T_{n}\left(0\right)\right) & \geq & f_{n}\left(T_{n}\left(0\right)\right)-\epsilon_{n}\\
+ & \geq & -\epsilon_{n}>-s
+\end{eqnarray*}
+Let $a>0$, since $f$ is continuous there exists $\epsilon>0$ such
+that $f\left(x\right)<f\left(T\right)+a$ if $\left|x-T\right|<\epsilon$.
+Thus, there exists $n>N$ such that $T-\epsilon<T_{n}\left(0\right)<T$
+and so 
+\[
+-s<f\left(T_{n}\left(0\right)\right)<f\left(T\right)+a
+\]
+
+Since $s$ and $a$ are arbitrary, 
+\[
+f\left(T\right)\geq0
+\]
+which is a contradiction because $T\left(0\right)>T$. Consequently,
+$T\leq T_{n}\left(0\right)$ and so
+\[
+\mbox{lim}_{n}T_{n}\left(0\right)=T\left(0\right).
+\]
+
+$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+\paragraph*{Proposition 3.}
+
+Let $\mathcal{S}$ be the event such that $W$ is continuous and $\mathbb{P}\left[\mathcal{S}\right]=1$.
+Fix $\omega\in\mathcal{S}$ and let $\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}$
+be a sequence of functions such that $Z_{n}\rightarrow W$ in $D^{k}\left[0,\infty\right)$,
+then 
+\begin{eqnarray*}
+f_{Z_{n}}\left(\cdot\right): & = & \mbox{max}\left\{ c-\mbox{min}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right),\mbox{max}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)-P\right\} \\
+ & \rightarrow & f_{W}\left(\cdot\right):=\mbox{max}\left\{ c-\mbox{min}_{x\in A}q_{\cdot x}^{W}\left(A\right),\mbox{max}_{x\in A}q_{\cdot x}^{W}\left(A\right)-P\right\} 
+\end{eqnarray*}
+
+in $D\left[0,\infty\right)$ for any $P\in\left(0,1\right)$ and $ $$A\subset\left\{ 1,\ldots,k\right\} $.
+Furthermore, if $m\in\mathbb{N}$, there exists a sequence $\left\{ \epsilon_{k}\right\} $
+such that $\epsilon_{k}\downarrow0$ and 
+\[
+\left|f_{Z_{k}}\left(t\right)-f_{W}\left(t\right)\right|<\epsilon_{k}
+\]
+for all $t\in\left[0,m\right]$.
+
+\paragraph*{Proof.}
+
+\paragraph*{\textmd{Since $Z_{n}\rightarrow W$ in $D\left[0,\infty\right)$,
+by Theorem 16.2 of Billingsley 1999, for each $s\geq0$ there exist
+functions $\lambda_{s}^{n}$ in $\Lambda_{s}$ such that 
+\[
+\mbox{lim}_{n}Z_{n}\left(\lambda_{s}^{n}t\right)=W\left(t\right)
+\]
+uniformly in $t$ and
+\[
+\mbox{lim}_{n}\lambda_{s}^{n}t=t
+\]
+uniformly in $t$. Then
+\[
+\mbox{lim}_{n}\frac{\lambda_{x}^{2}\beta_{\delta}\left(\lambda_{s}^{n}t\right)}{\lambda_{z}\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{\lambda_{s}^{n}\left(t\right)}{\delta^{2}}\right)\right)}Z_{n}^{x}\left(\lambda_{s}^{n}t\right)+\delta_{n}^{2}\lambda_{x}^{2}\frac{\left(n_{0}+\lambda_{s}^{n}\left(t\right)\frac{1}{\delta_{n}^{2}}\right)\beta_{\delta}\left(\lambda_{s}^{n}\left(t\right)\right)}{\lambda_{z}^{2}\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{\lambda_{s}^{n}\left(t\right)}{\delta^{2}}\right)\right)}a_{x}=W_{x}\left(t\right)\frac{1}{\lambda_{z}}+\frac{t}{\lambda_{z}^{2}}a_{x}
+\]
+uniformly in $t$, and so
+\[
+\mbox{lim}_{n}\mbox{exp}\left(\frac{\lambda_{x}^{2}\beta_{\delta}\left(\lambda_{s}^{n}t\right)}{\lambda_{z}\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{\lambda_{s}^{n}\left(t\right)}{\delta^{2}}\right)\right)}Z_{n}^{x}\left(\lambda_{s}^{n}t\right)+\delta_{n}^{2}\lambda_{x}^{2}\frac{\left(n_{0}+\lambda_{s}^{n}\left(t\right)\frac{1}{\delta_{n}^{2}}\right)\beta_{\delta}\left(\lambda_{s}^{n}\left(t\right)\right)}{\lambda_{z}^{2}\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{\lambda_{s}^{n}\left(t\right)}{\delta^{2}}\right)\right)}\right)=\mbox{exp}\left(W_{x}\left(t\right)\frac{1}{\lambda_{z}}+\frac{t}{\lambda_{z}^{2}}a_{x}\right)
+\]
+uniformly in $t$ since $\mbox{exp}$ is uniformly continuous in $\left[0,s\right]$.
+Consequently,
+\[
+q_{\lambda_{s}^{n}\left(t\right)x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{tx}^{W}\left(A\right)
+\]
+uniformly in $t\in\left[0,s\right]$. Thus, $q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{\cdot x}^{W}\left(A\right)$
+in $D\left[0,s\right]$ for any set $A\subset\left\{ 1,\ldots,k\right\} $
+and $s\geq0$. Consequently, $q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{\cdot x}^{W}\left(A\right)$
+in $D\left[0,\infty\right)$ by Theorem 16.2 of Billingsley 1999.
+By Proposition 1, $\mbox{min}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow\mbox{min}_{x\in A}q_{\cdot x}^{W}\left(A\right)$
+and $\mbox{max}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow\mbox{max}_{x\in A}q_{\cdot x}^{W}\left(A\right)$
+in $D\left[0,\infty\right)$, and so by Proposition 1,
+\[
+f_{Z_{n}}:=\mbox{max}\left\{ c-\mbox{min}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right),\mbox{max}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)-P\right\} \rightarrow f_{W}:=\mbox{max}\left\{ c-\mbox{min}_{x\in A}q_{\cdot x}^{W}\left(A\right),\mbox{max}_{x\in A}q_{\cdot x}^{W}\left(A\right)-P\right\}
+\]
+in $D\left[0,\infty\right)$ for any $P\in\left(0,1\right)$.}}
+
+Now, let's prove the second part. Fix $m\in\mathbb{N}$. By the definition
+of $d_{m}\left(f_{Z_{n}},f_{W}\right)$, we have that there exists
+$\lambda_{n}\in\Lambda_{\infty}$ such that 
+\begin{eqnarray*}
+\mbox{sup}_{t\leq m}\left\Vert \lambda_{n}\left(t\right)-t\right\Vert _{2} & \leq & d_{m}\left(f_{Z_{n}},f_{W}\right)+\frac{1}{n}\\
+\mbox{sup}_{t\leq m}\left\Vert f_{Z_{n}}\left(t\right)-f_{W}\left(\lambda_{n}t\right)\right\Vert _{2} & \leq & d_{m}\left(f_{Z_{n}},f_{W}\right)+\frac{1}{n}
+\end{eqnarray*}
+for all $n$. Taking $g_{n}\equiv\mbox{sup}_{t\leq m}\left\Vert f_{W}\left(t\right)-f_{W}\left(\lambda_{n}t\right)\right\Vert _{2}$,
+we see from the uniform continuity of $f_{W}$ on $\left[0,m\right]$
+($f_{W}$ is uniformly continuous because it's continuos in a compact
+set) and the definition of $g_{n}$ that $\mbox{lim}_{n\rightarrow\infty}g_{n}=0.$
+Moreover, if we take $\epsilon_{n}=2n^{-1}+2\mbox{sup}\left\{ d_{m}\left(f_{Z_{l}},f_{W}\right)+g_{l}:l=n,n+1,\ldots\right\} $,
+then $\left\{ \epsilon_{n}\right\} $ is a monotonically decreasing
+sequence of positive numbers with limit zero by the previous result.
+
+From the definition of $\epsilon_{n}$ we have that $d_{m}\left(f_{Z_{n}},f_{W}\right)<\epsilon_{n}/2-\frac{1}{n}$
+and $g_{n}<\epsilon_{n}/2$ for $n=1,2,\ldots$ Consequently, we have
+\begin{eqnarray*}
+\left\Vert f_{Z_{n}}\left(t\right)-f_{W}\left(t\right)\right\Vert  & \leq & \left\Vert f_{Z_{n}}\left(t\right)-f_{W}\left(\lambda_{n}t\right)\right\Vert +\left\Vert f_{W}\left(\lambda_{n}t\right)-f_{W}\left(t\right)\right\Vert \\
+ & < & d_{m}\left(f_{Z_{n}},f_{W}\right)+\frac{1}{n}+g_{n}\\
+ & < & \epsilon_{n}
+\end{eqnarray*}
+for all $t\in\left[0,m\right]$.
+
+$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+\paragraph*{Proposition 4.}
+
+Let $W=\left(W_{1},\ldots,W_{k}\right)$ be a $k-$dimensional independent
+standard Brownian motion.
+Let $q_{tx}^{W}\left(A\right):=\mbox{exp}\left(\frac{1}{\lambda_{z}^{2}}\left(\lambda_{z}W_{x}\left(t\right)+ta_{x}\right)\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{1}{\lambda_{z}^{2}}\left(\lambda_{z}W_{x^{'}}\left(t\right)+ta_{x^{'}}\right)\right)$
+for all $x\in A$ and $A\subset\left\{ 1,\ldots,k\right\} $. Fix
+$m\in\left\{ 1,\ldots,k-1\right\} $. We have that for all $N\in\mathbb{N}$,
+there exists $t$ such that $\tau_{m}+\frac{1}{N}\geq t>\tau_{m}$
+and $q_{tx}^{W}\left(A_{m-1}\right)>P_{m-1}$ for some $x\in A_{m-1}$
+almost surely given that $M=m$. (See the definitions in p. 4).
+
+\paragraph*{Proof.}
+
+The proof has the same spirit than the proof of Lemma 4 of Frazier
+\cite{key-5}, there Frazier proved that $\tau_{m}<\infty$ almost
+surely. Furthermore, $M\leq k-1$ almost surely. We should note that
+the Lemma 4 supposes that all systems have the same variance which
+is the case here because $\mbox{Var}\left(\lambda_{z}W_{x}\left(t\right)+ta_{x}\right)=\lambda_{z}^{2}t$.
+We condition on the event $\mathcal{S}$ such that the previous properties
+hold and has probability $1$.
+
+Define $a=\lambda_{z}\mbox{log}\left(\frac{P_{m-1}\left(k-1\right)}{1-P_{m-1}}\right)$.
+If $m=1$, then $P_{m-1}=P^{*}\in\left(0,1\right)$, and so $a$ is
+finite. If $m>1$, then 
+\[
+P^{*}\leq P_{m-1}\leq P^{*}/\left(1-c\right)^{m-1}\leq P^{*}/\left(1-c\right)^{k-2}\leq P^{*}/\left(P^{*}\right)^{k-2/k-1}<1
+\]
+and so $P_{m-1}\in\left(0,1\right)$ and $a$ is finite.
+
+We define $T^{*}=\mbox{inf}\left\{ t\geq\tau_{m}:q_{t,x}^{W}\left(A_{m-1}\right)>P_{m-1}\mbox{ for some }x\in A_{m-1}\right\} $.
+Fix $n\in\mathbb{N}$, $n>2$, and define $\tau=\tau_{m}+\frac{t^{*}}{nN}$
+for a deterministic $t^{*}\in\left\{ 1,\ldots,n-1\right\} $. Let
+$x$ be any $\mathcal{F}_{\tau_{m}}$-measurable random variable that
+is almost surely in $A_{m-1}$ and we define $\Gamma_{t,x}=W_{x}\left(t\right)+t\frac{a_{x}}{\lambda_{z}}$.
+Consider the event $ $$a<\Gamma_{\tau+\frac{1}{nN},x}-\Gamma_{\tau+\frac{1}{nN},y}$
+for each $y\in A_{m-1}-\left\{ x\right\} $.
+On this event, $q_{\tau+\frac{1}{mN},y}^{W}\left(A_{m-1}\right)/q_{\tau+\frac{1}{mN},x}^{W}\left(A_{m-1}\right)=\mbox{exp}\left(\frac{1}{\lambda_{z}}\left(\Gamma_{\tau+\frac{1}{nN},y}-\Gamma_{\tau+\frac{1}{nN},x}\right)\right)<\mbox{exp}\left(-a/\lambda_{z}\right)$
+for $ $ $y\in A_{m-1}-\left\{ x\right\} $ and
+\[
+q_{\tau+\frac{1}{nN},x}\left(A_{m-1}\right)=\left[1+\sum_{y\in A_{m-1}-\left\{ x\right\} }q_{\tau+\frac{1}{nN},y}\left(A_{m-1}\right)/q_{\tau+\frac{1}{nN},x}\left(A_{m-1}\right)\right]^{-1}>\left[1+\left(k-1\right)\mbox{exp}\left(-a/\lambda_{z}\right)\right]^{-1}=P_{m-1}.
+\]
+Thus, on the event considered, $T^{*}\leq\tau+\frac{1}{nN}$.
+
+We now define $\tilde{x}\in\mbox{arg max}_{x\in A_{m-1}}\mbox{ }\Gamma_{\tau,x}$,
+which is $\mathcal{F}_{\tau}$-measurable and is almost surely in
+$A_{m-1}$. Then we have that
+\begin{eqnarray*}
+\mathbb{P}\left\{ T^{*}\leq\tau+\frac{1}{nN}\mid\mathcal{F}_{\tau},T^{*}>\tau\right\}  & \geq & \mathbb{P}\left\{ a<\Gamma_{\tau+\frac{1}{nN},\tilde{x}}-\Gamma_{\tau+\frac{1}{nN},x}\mbox{ \mbox{}}\forall x\in A_{m-1}-\left\{ \tilde{x}\right\} \mid\mathcal{F}_{\tau},T^{*}>\tau\right\} \\
+ & \geq & \mathbb{P}\left\{ \Gamma_{\tau+\frac{1}{nN},\tilde{x}}\geq\Gamma_{\tau,\tilde{x}},\Gamma_{\tau,\tilde{x}}-\Gamma_{\tau+\frac{1}{nN},x}>a\mbox{ \mbox{}}\forall x\in A_{m-1}-\left\{ \tilde{x}\right\} \mid\mathcal{F}_{\tau},T^{*}>\tau\right\} \\
+ & \geq & \mathbb{P}\left\{ \Gamma_{\tau+\frac{1}{nN},\tilde{x}}\geq\Gamma_{\tau,\tilde{x}},\Gamma_{\tau,x}-\Gamma_{\tau+\frac{1}{nN},x}>a\mbox{ \mbox{}}\forall x\in A_{m-1}-\left\{ \tilde{x}\right\} \mid\mathcal{F}_{\tau},T^{*}>\tau\right\} \\
+ & = & \mathbb{P}\left\{ \Gamma_{\tau+\frac{1}{nN},\tilde{x}}\geq\Gamma_{\tau_{m},\tilde{x}}\mid\mathcal{F}_{\tau}\right\} \prod_{x\in A_{m-1}\setminus\left\{ \tilde{x}\right\} }\mathbb{P}\left\{ \Gamma_{\tau,x}-\Gamma_{\tau+\frac{1}{nN},x}>a\mid\mathcal{F}_{\tau}\right\} .
+\end{eqnarray*}
+Note that $\Gamma_{t,x}$ is a Brownian motion, and so $\mathbb{P}\left\{ \Gamma_{\tau+\frac{1}{nN},\tilde{x}}\geq\Gamma_{\tau_{m},\tilde{x}}\mid\mathcal{F}_{\tau_{m}}\right\} $
+is the probability of a conditionally $N\left(\frac{a_{\tilde{x}}}{nN}\frac{1}{\lambda_{z}},1\right)$
+random variable $\Gamma_{\tau+\frac{1}{nN},\tilde{x}}-\Gamma_{\tau,\tilde{x}}$,
+exceeding $0$. This probability is $\Phi\left(\frac{a_{\tilde{x}}}{nN}\frac{1}{\lambda_{z}}\right)$,
+which is bounded below by $ $$\Phi\left(\frac{\mbox{min}_{x}a_{x}}{N}\frac{x_{0}}{\lambda_{z}}\right)$
+where $x_{0}=0$ if $\mbox{min}_{x}a_{x}\geq0$, and $x_{0}=\frac{1}{3}$
+otherwise. Here, $\Phi$ is the normal cumulative distribution function.
+Similarly, the probability $\mathbb{P}\left\{ \Gamma_{\tau,x}-\Gamma_{\tau+\frac{1}{nN},x}>a\mid\mathcal{F}_{\tau_{m}}\right\} $
+is the probability of a conditionally $N\left(-a-\frac{a_{x}}{nN}\frac{1}{\lambda_{z}},1\right)$
+random variable, $\Gamma_{\tau,x}-\Gamma_{\tau+\frac{1}{nN},x}-a$,
+exceeding $0$. This probability is $\Phi\left(-a-\frac{a_{x}}{nN}\frac{1}{\lambda_{z}}\right)$,
+and is bounded below by $\Phi\left(-a-\frac{\mbox{max}_{x}a_{x}}{N}\frac{x_{0}^{+}}{\lambda_{z}}\right)$
+where $x_{0}^{+}=0$ if $\mbox{max}_{x}a_{x}\leq0$ and $x_{0}^{+}=\frac{1}{3}$
+otherwise.
+
+Thus, replacing $\tau$ with $\tau_{m}+\frac{t^{*}}{nN}$,
+\[
+\mathbb{P}\left\{ T^{*}\leq\tau_{m}+\frac{t^{*}}{nN}+\frac{1}{nN}\mid\mathcal{F}_{\tau_{m}+\frac{t^{*}}{nN}},T^{*}>\tau_{m}+\frac{t^{*}}{nN}\right\} \geq\Phi\left(\frac{\mbox{min}_{x}a_{x}}{N}\frac{x_{0}}{\lambda_{z}}\right)\Phi\left(-a-\frac{\mbox{max}_{x}a_{x}}{N}\frac{x_{0}^{+}}{\lambda_{z}}\right)^{k-1}
+\]
+Let $\epsilon$ be the quantity on the righ-hand side of this inequality,
+then $\epsilon<1$ and it does not depend on $t^{*}$ and $n$.
+
+By repeated application of this inequality, we have that $\mathbb{P}\left\{ T^{*}>T_{W}^{1}\left(P\right)+\frac{1}{N}\mid\mathcal{F}_{\tau_{m}}\right\} \leq\left(1-\epsilon\right)^{n}$
+for all $n>2$. This is true because
+\begin{eqnarray*}
+\mathbb{P}\left\{ T^{*}>T_{W}^{1}\left(P\right)+\frac{1}{N}\mid\mathcal{F}_{\tau_{m}+\frac{n-1}{nN}},T^{*}>\tau_{m}+\frac{n-1}{nN}\right\}  & < & \left(1-\epsilon\right)\\
+\Rightarrow\mathbb{P}\left\{ T^{*}>\tau_{m}+\frac{1}{N}\mid\mathcal{F}_{T_{W}^{1}\left(P\right)+\frac{n-2}{nN}},T^{*}>\tau_{m}+\frac{n-2}{nN}\right\}  & < & \left(1-\epsilon\right)\mathbb{P}\left\{ T^{*}>\tau_{m}+\frac{n-1}{nN}\mid\mathcal{F}_{\tau_{m}++\frac{n-2}{nN}},T^{*}>\tau_{m}+\frac{n-2}{nN}\right\} \\
+ & \leq & \left(1-\epsilon\right)^{2}\\
+ & \vdots\\
+\Rightarrow\mathbb{P}\left\{ T^{*}>\tau_{m}+\frac{1}{N}\mid\mathcal{F}_{T_{W}^{1}\left(P\right)}\right\}  & \leq & \left(1-\epsilon\right)^{n}
+\end{eqnarray*}
+and $\left(1-\epsilon\right)^{n}$ vanishes in the limit as $n\rightarrow\infty$.
+Then, $\mathbb{P}\left\{ T^{*}>\tau_{m}+\frac{1}{N}\mid\mathcal{F}_{T_{W}^{1}\left(P\right)}\right\} =0$
+and then 
+\[
+\mathbb{P}\left\{ \tau_{m}\leq T^{*}\leq\tau_{m}+\frac{1}{N}\mid\mathcal{F}_{T_{W}^{1}\left(P\right)}\right\} =1
+\]
+ for all $N$.
+
+$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+The following proposition can be proved using a similar argument.
+
+\paragraph*{Proposition 5.}
+
+Let $W=\left(W_{1},\ldots,W_{k}\right)$ be a $k-$dimensional independent
+standard Brownian motion.
+Let $q_{tx}^{W}\left(A\right):=\mbox{exp}\left(\frac{1}{\lambda_{z}^{2}}\left(\lambda_{z}W_{x}\left(t\right)+ta_{x}\right)\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{1}{\lambda_{z}^{2}}\left(\lambda_{z}W_{x^{'}}\left(t\right)+ta_{x^{'}}\right)\right)$
+for all $x\in A$ and $A\subset\left\{ 1,\ldots,k\right\} $. Fix
+$m\in\left\{ 1,\ldots,k-1\right\} $. We have that for all $N\in\mathbb{N}$,
+there exists $t$ such that $\tau_{m}-\frac{1}{N}\leq t<\tau_{m}$
+and $q_{tx}^{W}\left(A_{m-1}\right)<c$ for some $x\in A_{m-1}$ almost
+surely given that $M=m$. \\
+
+We are now ready to prove the lemma 2.
+
+\paragraph*{Lemma 2.}
+
+Let $\left\{ \delta_{n}\right\} \subset\left(0,\infty\right)$ such
+that $\delta_{n}\rightarrow0$. If $D_{s}\equiv\{Z\in D\left[0,\infty\right)^{k}:\mbox{ if }\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}\mbox{ and }$
+$\mbox{lim}{}_{n}d_{\infty}\left(Z_{n},Z\right)=0$ , then the sequence
+$\left\{ f\left(Z_{n},\delta_{n}\right)\right\} $ converges to $\left\{ g\left(Z\right)\right\} $$\left.\right\} $$ $,
+then $ $$\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\right)=1$.
+
+\paragraph*{Proof of Lemma 2.}
+
+By Lemma 4 and 6 of Frazier, $\tau_{n}<\infty$ for $n=0,1,\ldots,k-1$,
+$M\leq k-1$,$\tau_{n}=\tau_{M}$ for all $n\geq M$, $\hat{x}\in\mbox{arg max}_{x\in A_{m-1}}\left(\lambda_{z}W_{x}\left(\tau_{M}\right)+a_{x}\tau_{M}\right)$
+and $\tau_{M-1}<\tau_{M}$ with probability 1. Then there exists a
+measurable set $\mathcal{L}$ such that $\mathbb{P}\left[\mathcal{L}\right]=1$
+and the previous properties are true, $W$ is continuous and Proposition
+4 and 5 hold. We will show that $\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\mid M_{W}=i,\mathcal{L}\right)=1$
+for $i\in\left\{ 1,\ldots,k-1\right\} $ so that the desired conclusion
+follows. It will be useful to use the same notation than in Proposition
+2: 
+\begin{eqnarray*}
+T_{W}^{m}\left(a\right) & = & \begin{cases}
+\mbox{inf}\left\{ t\geq\tau_{m-1}:\mbox{max}_{x\in A_{m-1}}q_{tx}^{W}\left(A_{m-1}\right)\geq a\right\}  & \mbox{if }m\geq M_{W}\\
+\mbox{inf}\left\{ t\geq\tau_{m-1}:\mbox{min}_{x\in A_{m-1}}q_{tx}^{W}\left(A_{m-1}\right)\leq a\right\}  & \mbox{if }m<M_{W}
+\end{cases}
+\end{eqnarray*}
+ and 
+\[
+T_{n}^{m}\left(a\right):=\mbox{inf}\left\{ t\geq\tau_{m-1}:\mbox{max}_{x\in A_{m-1}}q_{tx}^{Z_{n},\delta_{n}}\left(A_{m-1}\right)\geq a\mbox{ or }\mbox{min}_{x\in A_{m-1}}q_{tx}^{Z_{n},\delta_{n}}\left(A_{m-1}\right)\leq c\right\}
+\]
+ for any $a\in\mathbb{R}$ and $1\leq m\leq k-1$.
+
+\subparagraph*{Case I.}
+
+First, we fix $\omega\in\mathcal{L}\bigcap\left\{ M_{W}=1\right\} $.
+Let $\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}$ such
+that $Z_{n}\rightarrow W$. We want to prove that $f\left(Z_{n},\delta_{n}\right)\rightarrow g\left(W\right)$.
+Let's prove that $\tau_{1}^{Z_{n},\delta_{n}}\rightarrow\tau_{1}^{W}$
+as $n\rightarrow\infty$.
+
+First, we are going to prove that $ $$T_{W}^{1}\left(P_{0}\right)=\mbox{lim}_{n}T_{W}^{1}\left(P_{0}+\epsilon_{n}\right)$.
+Note that $ $ $\mbox{lim}_{n}T_{W}^{1}\left(P_{0}+\epsilon_{n}\right)=\mbox{inf}_{n}T_{W}^{1}\left(P_{0}+\epsilon_{n}\right)$
+and so we have to prove that for all $M>0$ there exists $n$ such
+that $T_{W}^{1}\left(P_{0}+\epsilon_{n}\right)<T_{W}^{1}\left(P_{0}\right)+M.$
+Equivalently, we should prove that for all $N\in\mathbb{N}$ there
+exists $t\in\left(T_{W}^{1}\left(P_{0}\right),T_{W}^{1}\left(P_{0}\right)+\frac{1}{N}\right]$
+such that for some $x\in A_{0}$, $q_{t,x}^{W}\left(A_{0}\right)>P_{0}$.
+However, this is true by proposition 4.
+
+By Proposition 2 and 3,
+\begin{equation}
+T_{W}^{1}\left(P_{0}\right)=\mbox{lim}_{n}T_{n}^{1}\left(P_{0}\right).\label{eq:10.1}
+\end{equation}
+
+By Proposition 3, we have that $f_{Z_{n}}\left(\cdot\right)\rightarrow f_{W}\left(\cdot\right)$
+uniformly in $\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$ and so
+it should be the case that $\mbox{max}_{x\in A_{0}}q_{T_{n}^{1}\left(P_{0}\right)x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\geq P_{0}$
+for $n$ large.
+
+Recall that $\hat{x}\in\gamma:=\mbox{arg max}_{x\in A_{0}}\left(\lambda_{z}W_{x}\left(T_{W}^{1}\left(P_{0}\right)\right)+a_{x}T_{W}^{1}\left(P_{0}\right)\right)$.
+
+Let $\epsilon=\left(q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-\mbox{arg max}_{x\in A_{0}-\gamma}q_{T_{W}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)\right)/4$.
+Since the function $q_{\cdot,x}^{W}\left(A_{0}\right)$ is uniformly
+continuous in $\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$ for
+all $x\in A_{0}$, then there exists $\delta>0$ such that if $\left|t-s\right|<\delta$
+and $t,s\in\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$, then 
+\[
+\left|q_{t,x}^{W}\left(A_{0}\right)-q_{s,x}^{W}\left(A_{0}\right)\right|<\frac{\epsilon}{2}
+\]
+for all $x\in A_{0}$. By the proof of Proposition 3, $q_{\cdot,x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\rightarrow q_{\cdot,x}^{W}\left(A_{0}\right)$
+in $\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$ with the Skorohod
+topology, and then $q_{\cdot,x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\rightarrow q_{\cdot,x}^{W}\left(A_{0}\right)$
+uniformly in $\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$ because
+$q_{\cdot,x}^{W}\left(A_{0}\right)$ is uniformly continuous in $\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$
+for all $x\in A_{0}$. Consequently, there exists $N_{1}$ such that
+if $n>N_{1}$, then $\left|q_{t,x}^{W}\left(A_{0}\right)-q_{t,x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right|<\frac{\epsilon}{2}$
+for all $t\in\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$ and all
+$x\in A_{0}$. By (\ref{eq:10.1}), there exists $N_{2}$ such that
+if $n>N_{2}$, then $\left|T_{W}^{1}\left(P_{0}\right)-T_{n}^{1}\left(P_{0}\right)\right|<\delta$
+and $T_{n}^{1}\left(P_{0}\right)\in\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$.
+So if $n>\mbox{max}\left\{ N_{1},N_{2}\right\} $, we have that
+
+\begin{eqnarray*}
+\left|q_{T_{W}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)-q_{T_{n}^{1}\left(P_{0}\right),x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right| & = & \left|q_{T_{W}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)-q_{T_{n}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)\right|+\left|q_{T_{n}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)-q_{T_{n}^{1}\left(P_{0}\right),x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right|\\
+ & < & \frac{\epsilon}{2}+\frac{\epsilon}{2}=\epsilon
+\end{eqnarray*}
+
+for all $x\in A_{0}$.
+
+By Proposition 3, there exists a sequence $\left\{ \epsilon_{n}\right\} _{n>N^{*}}$
+decreasing to zero for some $N^{*}$ such that if $n>N^{*}$ .
+\[
+\left|q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-\mbox{max}_{x\in A_{0}}q_{T_{n}^{1}\left(P_{0}\right),x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right|<\epsilon_{n}.
+\]
+
+Let $y_{n}\in\mbox{arg max}q_{T_{n}^{1}\left(P_{0}\right),y}^{Z_{n},\delta_{n}}\left(A_{0}\right)$.
+Thus if $n>\mbox{max}\left\{ N^{*},N_{1},N_{2}\right\} $, then
+\begin{eqnarray*}
+\left|q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-q_{T_{W}^{1}\left(P_{0}\right),y_{n}}^{W}\left(A_{0}\right)\right| & \leq & \left|q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-q_{T_{n}^{1}\left(P_{0}\right),y_{n}}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right|+\left|-q_{T_{W}^{1}\left(P_{0}\right),y_{n}}^{W}\left(A_{0}\right)+q_{T_{n}^{1}\left(P_{0}\right),y_{n}}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right|\\
+ & < & \epsilon_{n}+\epsilon
+\end{eqnarray*}
+
+Take $N_{3}$ such that if $n>N_{3}$, then $\epsilon_{n}<\epsilon$.
+Consequently, if $n>\mbox{max}\left\{ N_{3},N_{1},N_{2},N^{*}\right\} $,
+we have that
+\begin{eqnarray*}
+\left|q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-q_{T_{W}^{1}\left(P_{0}\right),y_{n}}^{W}\left(A_{0}\right)\right| & < & \frac{q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-\mbox{arg max}_{x\in A_{0}-\gamma}q_{T_{W}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)}{2}
+\end{eqnarray*}
+if $y_{n}\neq\hat{x}$, then
+\[
+\left|q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-q_{T_{W}^{1}\left(P_{0}\right),y_{n}}^{W}\left(A_{0}\right)\right|<\frac{q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-q_{T_{W}^{1}\left(P_{0}\right),y_{n}}^{W}\left(A_{0}\right)}{2}
+\]
+which is a contradiction. Consequently, $y_{n}=\hat{x}$ for $n$
+large. Consequently, $f\left(Z_{n},\delta_{n}\right)$ converges to
+$g\left(W\right)$.
+
+\subparagraph*{Case II.}
+
+Now, we fix we fix $\omega\in\mathcal{L}\bigcap\left\{ M_{W}=2\right\} $.
+Similarly, we take $\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}$
+such that $Z_{n}\rightarrow W$. Let's prove that $\tau_{1}^{Z_{n},\delta_{n}}\rightarrow\tau_{1}^{W}$.
+First, we are going to prove that $ $$T_{W}^{1}\left(c\right)=\mbox{lim}_{n}T_{W}^{1}\left(c-\epsilon_{n}\right)$.
+Note that $ $ $\mbox{lim}_{n}T_{W}^{1}\left(c-\epsilon_{n}\right)=\mbox{inf}_{n}T_{W}^{1}\left(c-\epsilon_{n}\right)$
+and so we have to prove that for all $M>0$ there exists $n$ such
+that $T_{W}^{1}\left(c-\epsilon_{n}\right)<T_{W}^{1}\left(c\right)+M.$
+Equivalently, we should prove that for all $N\in\mathbb{N}$ there
+exists $t\in\left(T_{W}^{1}\left(c\right),T_{W}^{1}\left(c\right)+\frac{1}{N}\right]$
+such that for some $x\in A_{0}$, $q_{t,x}^{W}\left(A_{0}\right)<c$.
+However, this is true by proposition 5. By Proposition 2 and 3, $T_{W}^{1}\left(c\right)=\mbox{lim}_{n}T_{n}^{1}\left(P_{0}\right).$
+Using similar arguments than the given in Case I, we can conclude
+that $f\left(Z_{n},\delta_{n}\right)$ converges to $g\left(W\right)$.\\
+
+The cases $M_{W}=i$ for $k-1\geq i\geq3$ can be proved in a similar
+way. Then we conclude that $\mathbb{P}\left(W\in D_{s}\right)=1.$
+
+$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+\[
+\]
+
+By the extension of the CMT (Theorem 5.5 of Billingsley 1968), we
+have the following corollary.
+
+\paragraph*{Corollary 2.}
+
+We have that
+
+\[
+f\left(C\left(\delta,t\right),\delta\right)\Rightarrow g\left(W\left(t\right)\right)
+\]
+in distribution as $\delta\rightarrow0$.
+
+\[
+\]
+
+\paragraph*{Theorem 1.}
+
+If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
+distributed and independent, over time and across alternatives, then
+$\mbox{lim}_{\delta\rightarrow0}Pr\left\{ \mbox{BIZ selects }k\right\} \geq P*$
+provided $\mu_{k}=a_{k}\delta,\mu_{k-1}=a_{k-1}\delta,\ldots,\mu_{1}=a_{1}\delta$,
+and $\mu_{k}>\mu_{k-1}>\cdots>\mu_{1}$.
+
+Furthermore,
+\[
+\mbox{inf}_{a\in PZ\left(1\right)}\mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right)=P^{*}
+\]
+where $PZ\left(1\right)=\left\{ a\in\mathbb{R}^{k}:a_{k}-a_{k-1}\geq1\right\} $.
+
+\paragraph*{Proof.}
+
+By the comments given at the beginning of this section, we know that
+we can work with the algorithm defined by
+
+\[
+q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
+\]
+where $t\in\delta^{2}\mathbb{N}$, instead of the algorithm defined
+by
+\[
+q'_{tx}\left(A\right)=q'\left(\left(Z_{tx},t:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
+\]
+where $t\in\mathbb{N}$.
+
+Now, we define
+\begin{eqnarray*}
+\hat{\tau}_{n+1}\left(\delta\right) & = & \mbox{inf}\left\{ t\in\left\{ \tau_{n}\delta^{2},\left(\tau_{n}+1\right)\delta^{2},\ldots\right\} :\mbox{ min}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\geq P_{n}\right\}
+\end{eqnarray*}
+We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
+which are defined as $\tau_{n+1}=\mbox{inf}\left\{ t\geq\tilde{\tau}_{n}:\mbox{ min}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\geq P_{n}\right\} $.
+
+Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
+we can prove that $\hat{\tau}_{n}\left(\delta\right)-\tau_{n}\left(\delta\right)\rightarrow0$
+with probability $1$ as $\delta\rightarrow0$, and so we can use
+$\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
+of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$
+in the limit.
+
+Let $CS_{\delta}$ be the event of doing a correct selection given
+the configuration $\mu_{k}=a_{k}\delta,\mu_{k-1}=a_{k-1}\delta,\ldots,\mu_{1}=a_{1}\delta$
+$ $. Then by the previous argument and the Corollary 2, 
+\begin{eqnarray*}
+\mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right) & = & \mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(f\left(\mathcal{C}\left(\delta,t\right),\delta\right)=1\right)\\
+ & = & \mathbb{P}\left(g\left(W\right)=1\right)\\
+ & \geq & P^{*}
+\end{eqnarray*}
+where the last inequality follows from the Theorem 2 of Frazier \cite{key-5}.
+
+Furthermore, by the same theorem 2,
+\[
+\mbox{inf}_{a\in PZ\left(1\right)}\mathbb{P}\left(g\left(W\right)=1\right)=P^{*}
+\]
+
+where $PZ\left(1\right)=\left\{ a\in\mathbb{R}^{k}:a_{k}-a_{k-1}\geq1\right\} $.
+
+$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}\;\;\;\;}$
+
+\section{Asymptotic Validity when the Variances are Unknown}
+
+We use a random change of time to prove that the new $\hat{\mathcal{C}}_{x}$
+defined using the sample variances also converges to a Brownian motion
+in the sense of $D_{\infty}$.
+
+\paragraph*{Lemma 3.}
+
+We have that
+\[
+\hat{\mathcal{C}}_{x}\left(\delta,\cdot\right):=\frac{Y_{\mbox{ceil}\left(\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\right),x}-\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\mu_{x}}{\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}}\frac{1}{\delta}}\Rightarrow W_{x}\left(\cdot\right)
+\]
+
+in the sense of $D_{\infty}$ for each $x\in A$, where $\hat{\lambda}_{t/\delta^{2},x}^{2}=\frac{1}{n_{t/\delta^{2},x}-1}\sum_{i=1}^{n_{t/\delta^{2},x}}\left(X_{xi}-Y_{n_{t/\delta^{2},x}}\right)^{2}$.
+
+\paragraph*{Proof. }
+
+Fix $x\in A$. Define $\Psi_{\delta}:\left[0,\infty\right)\rightarrow\left[0,\infty\right)$
+by $\Psi_{\delta}\left(t\right)=-n_{0}\delta^{2}+\frac{\lambda_{z}^{2}}{\lambda_{x}^{2}}\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}^{2}}\left(t+\delta^{2}n_{0}\right)$,
+then $\Psi_{\delta}\in D_{\infty}$. Now define $\varphi:D_{\infty}\times D_{\infty}\rightarrow D_{\infty}$
+by
+\[
+\varphi\left(\mathcal{X},\mathcal{Y}\right)=\mathcal{X}\circ\mathcal{Y}
+\]
+
+Using Lemma 1, we have that $\left(\mathcal{C}_{x}\left(\delta,\cdot\right),\Psi_{\delta}\left(\cdot\right)\right)\Rightarrow\left(W_{x}\left(\cdot\right),I\left(\cdot\right)\right)$
+as $\delta\rightarrow0$ in the sense of $D_{\infty}$. We can prove
+that $\varphi$ is measurable, and since $W_{x}$ is continuous almost
+surely, we can use a generalization of the Lemma from the chapter
+Random Change of Time of Billingsley (1999) to conclude that $\varphi\left(\mathcal{C}_{x}\left(\delta,\cdot\right),\Psi_{\delta}\left(\cdot\right)\right)\Rightarrow\varphi\left(W_{x}\left(\cdot\right),I\left(\cdot\right)\right)=W_{x}\left(\cdot\right)$
+in the sense of $D_{\infty}$ as we wanted to prove.
+
+$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}\;\;\;\;}$\\
+
+In the previous proof, we only have to replace $\lambda_{x}^{2}$
+by its estimators and we get the same result. We should note that
+\[
+\mbox{ceil}\left(\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\right)-n_{t/\delta^{2},x}\rightarrow0
+\]
+for any $x$. Consequently, we will have that
+\[
+\frac{Y_{n_{t/\delta^{2},x},x}-n_{t/\delta^{2},x}\mu_{x}}{\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}}\frac{1}{\delta}}\Rightarrow W_{x}\left(\cdot\right)
+\]
+
+So, we have the following theorem.
+
+\paragraph*{Theorem 2.}
+
+If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
+distributed and independent, over time and across alternatives, then
+$\mbox{lim}_{\delta\rightarrow0}Pr\left\{ \mbox{BIZ selects }k\right\} \geq P*$
+provided $\mu_{k}=a_{k}\delta,\mu_{k-1}=a_{k-1}\delta,\ldots,\mu_{1}=a_{1}\delta$,
+and $\mu_{k}>\mu_{k-1}>\cdots>\mu_{1}$.
+
+Furthermore,
+\[
+\mbox{inf}_{a\in PZ\left(1\right)}\mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right)=P^{*}
+\]
+where $PZ\left(1\right)=\left\{ a\in\mathbb{R}^{k}:a_{k}-a_{k-1}\geq1\right\} $.
+
+\section{Probability of Good Selection}
+
+Ideally, we would like that the difference between the chosen system
+and the best system is practically insignificant. We thus define the
+probability of good selection as
+\[
+\mbox{PGS}\left(\mu\right)=\mathbb{P}\left(\mu_{k}-\mu_{\hat{x}}\leq\delta\right).
+\]
+
+We would like to prove the PGS guarantee:
+\[
+\forall\mu,\mbox{ PGS}\left(\mu\right)\geq P^{*}.
+\]
+First, observe that if $\mu_{k}-\mu_{k-1}>\delta$, then $\mbox{PGS}\left(\mu\right)=\mbox{PCS}\left(\mu\right)$
+and so $\mbox{PGS}\left(\mu\right)\geq P^{*}$. Consequently, we only
+need to prove that if $\mu_{k}-\mu_{k-1}\leq\delta$, then we have
+that $\mbox{PGS}\left(\mu\right)\geq P^{*}$.
+
+Inspired on Frazier (2014), we first construct a probability measure
+$Q$ as follows. Let $X^{*}$ be chosen uniformly at random from among
+$1,\ldots,k$ and let $\theta_{X^{*}}=\delta$ and $\theta_{x}=0$
+if $x\neq X^{*}$. We then define a family of probability measures
+$Q_{u}$ that i
+
+\section{Simulations}
+
+\section{Conclusion}
+
+We have proved the asymptotic validity of the Bayes-inspired Zone
+procedure (Frazier 2014) when the variances are known, which is a
+new sequential elemination procedure. This algorithm is relevant because
+it takes fewer samples than other IZ procedures, especially for problems
+with large numbers of alternatives. Even though this proof does not
+guarantee that the algorithm will work for any sample, we know that
+it will work if the alternatives are not very different, which are
+the most difficult cases.
+
+\section*{Appendix A: Skorohod topology}
+
+We are going to define the Skorohod topology on $D[0,\infty)$ by
+defining a metric on the space. The Skorohod metricric $d_{t}$ on
+$D\left[0,t\right]$ for each $t\geq0$ is:
+\[
+d_{t}\left(\mathcal{X},\mathcal{Y}\right)=\mbox{inf}_{\lambda\in\Lambda_{t}}\left\{ \left\Vert \lambda-I\right\Vert \vee\left\Vert \mathcal{X}-\mathcal{Y}\circ\lambda\right\Vert \right\} 
+\]
+where $\Lambda_{t}$ is the set of strictly increasing, continuous
+mappings of $\left[0,t\right]$ onto itself, and $\left\Vert \cdot\right\Vert $
+is the uniform norm, and $I$ is the identity map. Note that uniform
+convergence on $\left[0,t\right]$ implies Skorohod convergence.
+
+We define the Skorohod topology on $D\left[0,\infty\right)$. For
+$\mathcal{X}\in D\left[0,\text{\ensuremath{\infty}}\right)$, let
+$\mathcal{X}^{m}$ be the element of $D_{\infty}:=D[0,\infty)$ defined
+by
+\[
+\mathcal{X}^{m}\left(t\right)=g_{m}\left(t\right)\mathcal{X}\left(t\right)
+\]
+where 
+\[
+g_{m}\left(t\right)=\begin{cases}
+1 & \mbox{if }t\leq m-1,\\
+m-t & \mbox{if }m-1\leq t\leq m,\\
+0 & \mbox{if }t\geq m.
+\end{cases}
+\]
+And now take
+\[
+d_{\infty}\left(\mathcal{X},\mathcal{Y}\right)=\sum_{m=1}^{\infty}2^{-m}\left(1\wedge d_{m}\left(\mathcal{X}^{m},\mathcal{Y}^{m}\right)\right)
+\]
+which is the Skorohod metric on $D\left[0,\infty\right)$. By Theorem
+16.2 of Billingsley1999, there is convergence $d_{\infty}\left(x_{n},x\right)\rightarrow0$
+in $D_{\infty}$ if and only if $d_{t}\left(x_{n},x\right)\rightarrow0$
+for each continuity point $t$ of $x$.
+
+We can also define
+
+\[
+d_{\infty}^{\circ}\left(\mathcal{X},Y\right)=\sum_{m=1}^{\infty}2^{-m}\left(1\wedge d_{m}^{\circ}\left(\mathcal{X}^{m},\mathcal{Y}^{m}\right)\right)
+\]
+where $d_{m}^{\circ}\left(\mathcal{X}^{m},\mathcal{Y}^{m}\right)=\mbox{inf}_{\lambda\in\Lambda_{m}}\left\{ \mbox{sup}_{s<t}\left|\mbox{log}\frac{\lambda t-\lambda s}{t-s}\right|\vee\left\Vert \mathcal{X}-\mathcal{Y}\circ\lambda\right\Vert \right\} $.
+This is also a metric and the proof is in Bilingsley 1999 and these
+two metrics are equivalent.
+
+\subparagraph*{Theorem A.1}
+
+We have that $d_{\infty}\left(\mathcal{X}_{n},\mathcal{Y}_{n}\right)\rightarrow0$
+if and only if $d_{\infty}^{\circ}\left(\mathcal{X}_{n},\mathcal{Y}_{n}\right)\rightarrow0$
+and $d_{t}\left(\mathcal{X}_{n},\mathcal{Y}_{n}\right)\rightarrow0$
+if and only if $d_{t}^{\circ}\left(\mathcal{X}_{n},\mathcal{Y}_{n}\right)\rightarrow0$
+for all $t\geq0$.
+
+\subparagraph*{Theorem A.2}
+
+Suppose we have two sequences of random paths $\left\{ \mathcal{X}_{n}=\left(X_{n}\left(t\right):0\leq t<\infty\right)\right\} _{n\geq0}^{\infty}$,$\left\{ \mathcal{Y}_{n}=\left(Y_{n}\left(t\right):0\leq t<\infty\right)\right\} _{n\geq1}^{\infty}$
+such that $\mathcal{X}_{n},\mathcal{Y}_{n}:\mathcal{F}\rightarrow D_{\infty}$
+for all $n\geq0$ where $\left(\Omega,\mathcal{F},\mathbb{P}\right)$
+is our space of probability. Suppose that $\mathcal{X}_{n}\Rightarrow\mathcal{X}_{0}$
+in the sense of $D\left[0,\infty\right)$ and $\mathcal{X}_{n}-\mathcal{Y}_{n}\rightarrow0$
+uniformly in $\left[0,m\right]$ for all $m\in\mathbb{N}$ with probability
+1, then $\mathcal{Y}_{n}\Rightarrow\mathcal{X}_{0}$.
+
+\subparagraph*{Proof.}
+
+We only need to prove that $d_{\infty}\left(\mathcal{X}_{n},\mathcal{Y}_{n}\right)\rightarrow0$
+almost surely and the result will follow by Theorem 3.1 of Billingsley
+1999. Then we only need to prove that $d_{m}\left(\mathcal{Y}_{n}^{m},\mathcal{X}_{n}^{m}\right)\rightarrow0$
+almost surely for all $m\in\mathbb{N}$. Fix $\omega\in\Omega$ and
+$m\in\mathbb{N}$ such that $\mathcal{X}_{n}-\mathcal{Y}_{n}\rightarrow0$
+uniformly in $\left[0,m\right]$. Observe that 
+\begin{eqnarray*}
+d_{m}\left(\mathcal{Y}_{n}^{m},\mathcal{X}_{n}^{m}\right) & = & \mbox{inf}_{\lambda\in\Lambda_{m}}\left\{ \left\Vert \lambda-I\right\Vert \vee\left\Vert \mathcal{Y}_{n}^{m}-\mathcal{X}_{n}^{m}\circ\lambda\right\Vert \right\} \\
+ & \leq & \left\Vert \mathcal{Y}_{n}^{m}-\mathcal{X}_{n}^{m}\right\Vert \\
+ & = & \left\Vert g_{m}\mathcal{Y}_{n}-g_{m}\mathcal{X}_{n}\right\Vert \\
+ & = & \mbox{sup}_{t\leq m-1}\left\Vert Y_{n}\left(t\right)-X_{n}\left(t\right)\right\Vert \lor\mbox{sup}_{t>m-1}\left\Vert Y_{n}\left(t\right)-X_{n}\left(t\right)\right\Vert \left(m-t\right)\\
+ & \leq & \mbox{sup}_{t\leq m}\left\Vert Y_{n}\left(t\right)-X_{n}\left(t\right)\right\Vert \\
+ & \rightarrow & 0
+\end{eqnarray*}
+as we wanted to prove.
+
+$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+
+\section*{Appendix B: The BIZ Procedure}
+
+\subsection*{B.1 The BIZ Procedure with Known Common Variance}
+
+We first define the Bayes-inspired indifference zone (BIZ) procedure
+for the case of known common variance, when $\lambda_{x}^{2}=\sigma^{2}<\infty$
+for all $x$. Frazier (2014) showed that this procedure satisfies
+the IZ guarantee when the systems follow the normal distribution,
+with tight bounds on worst-case preference-zone in continuous time.
+
+BIZ depends on $P^{*}\in\left(1/k,1\right)$ and $\delta>0$ for which
+we desire an IZ guarantee, and a parameter $c$ such that
+\begin{eqnarray*}
+c & \in & \left[0,1-\left(P^{*}\right)^{\frac{1}{k-1}}\right]\mbox{ if }k>2\\
+c & = & 0\mbox{ if }k=2
+\end{eqnarray*}
+The parameter $c$controls how aggressively the alternatives are eliminated.
+It is recommended to choose $c$ equal to $1-\left(P^{*}\right)^{\frac{1}{k-1}}$.
+
+For each $t$, $x\in\left\{ 1,\ldots,k\right\} $, and subset $A\subset\left\{ 1,\ldots,k\right\} $,
+we define a function
+\[
+\hat{q}_{tx}\left(A\right)=\mbox{exp}\left(\frac{\delta}{\sigma^{2}}Y_{tx}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\frac{\delta}{\sigma^{2}}Y_{tx'}\right)\right.
+\]
+where $Y_{tx}$ is the sum of the samples observed from alternative
+$x$ by time $t$.
+
+Then, the BIZ procedure for known common variance is defined by Alg.
+1.
+
+\paragraph{Algorithm 1: BIZ for known common sampling variance, in discrete time.}    
+\begin{algorithmic}[1]   
+\label{alg:hetero-BIZ}   
+\REQUIRE $c \in [0,\cmax]$, $\delta>0$, $P^*\in(1/k,1)$, common sampling variance $\sigma^2>0$.     
+\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$, $Y_{0x} \leftarrow 0$ for each $x$.
+\WHILE{$\mbox{max}_{x\in A} \hat{q}_{tx}\left(A\right)<P$}
+\WHILE{$\mbox{min}_{x\in A} \hat{q}_{tx}\left(A\right) \le c$}
+ \STATE Let $x\in\mbox{arg min}_{x\in A} \hat{q}_{tx}\left(A\right)$.
+    \STATE Let $\upthresh \leftarrow \upthresh/(1-\hat{q}_{tx}\left(A\right))$.     
+\STATE Remove $x$ from $A$.
+\ENDWHILE
+  \STATE Sample from each $x \in A$ and add this sample to $Y_{tx}$ to obtain $Y_{t+1,x}$. Then increment $t$.        
+ \ENDWHILE
+  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} Y_{tx}$ as our estimate of the best.
+
+\end{algorithmic}
+
+\subsection*{B.2 The BIZ Procedure with Heterogeneous and Unknown Sampling Variances}
+
+Frazier (2014) showed that this procedure retains the IZ guarantee
+when the systems follow the normal distribution, and the variances
+are known and are integer multiples of a common value. The continuous
+time version of this procedure also satisfies the IZ guarantee, with
+a tight worst-case preference-zone PCS bound.
+
+The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
+variances is given in Alg. 2. It takes a variable number of samples
+from each alternative, and $n_{tx}$ is this number. This algorithm
+depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
+and $n_{0}$. $n_{0}$ is the number of samples to use in the first
+stage of samples, and $100$ is the recommended value for $n_{0}$.
+$B_{x}$ controls the number of samples taken from system $x$ in
+each stage.
+
+For each $t$, $x\in\left\{ 1,\ldots,k\right\} $, and subset $A\subset\left\{ 1,\ldots,k\right\} $,
+we define a function
+\[
+q_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right),\right.\mbox{ }\beta_{t}=\frac{\sum_{x'\in A}n_{tx'}}{\sum_{x'\in A}\hat{\lambda}_{tx'}^{2}}
+\]
+where $\hat{\lambda}_{tx'}^{2}$ is the sample variance of all samples
+from alternative $x$ thus far and $Z_{tx}=Y_{n_{tx},x}$.
 
@@
 $\lambdahat^2_{tx}$ with the true values $\lambda^2_x$, and set $n_0=0$.
-To compute $\qhat_{tx}(A)$, use \begin{equation}   q'_{t,x}(A) =    \exp\left(\gamma \delta Y'_{tx}\right) \bigg/ \sum_{x'\in A} \exp\left(\gamma \delta Y'_{tx'}\right)   = \exp\left(\frac{\delta}{\lambda^2_x} Y_{n_x(t),x}\right) \bigg/ \sum_{x'\in A} \exp\left(\frac{\delta}{\lambda^2_{x'}} Y_{n_x'(t),x'}\right), \end{equation}
-where $Y_{n_x(t),x}$ is the sum of the first $n_x(t)$ samples.
 
@@
 Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.     
-\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$, $t \leftarrow 1$.
-\WHILE{$x\in\mbox{max}_{x\in A}\qhat_{tx}(A)<P$}
-\WHILE{$\mbox{min}_{x\in A} \qhat_{tx}(A) \le c$}
- \STATE Let $x\in\mbox{arg min}_{x\in A}\qhat_{tx}(A)$.
-    \STATE Let $\upthresh \leftarrow \upthresh/(1-\qhat_{tx}(A))$.     
+\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
+\WHILE{$x\in\mbox{max}_{x\in A} q_{tx}\left(A\right)<P$}
+\WHILE{$\mbox{min}_{x\in A} q_{tx}\left(A\right) \le c$}
+ \STATE Let $x\in\mbox{arg min}_{x\in A} q_{tx}\left(A\right)$.
+    \STATE Let $\upthresh \leftarrow \upthresh/(1-q_{tx}\left(A\right))$.     
 \STATE Remove $x$ from $A$.
@@
 
-\section{Introduction}
-
-This paper is organized as follows: In $\text{§}2$, we present the
-proof of the validity of the algorithm when the variances are known.
-In $\text{§}3$, we prove the case when the variances are unknown.
-
-To prove the case when the variances are known, we use a Functional
-Central Limit Theorem that shows how to standardize the output data
-to make them behave like Brownian motion processes in the limit. We
-also use an extension of the Continuous Mapping Theorem (Theorem 5.5
-of Billingsley 1968) to see that the algorithm behaves like a sequential
-elimination IZ procedure with a Brownian motion process instead of
-the standardize of the sum of the output data in the limit. Finally,
-we use the results of the paper of Frazier \cite{key-5} to prove
-the validity of this algorithm in the limit.
-
-\section{Asymptotic Validity when the Variances are Known}
-
-Without loss of generality, suppose that the true means of the systems
-are indexed so that $\mu_{k}\geq\mu_{k-1}\geq\cdots\geq\mu_{1}$.
-We suppose that samples from system $x\in\left\{ 1\ldots,k\right\} $
-are identically distributed and independent, over time and across
-alternatives. We also define $\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$.
-We suppose that $\mbox{min}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}>0$
-and $c\neq1/k$.
-
-Now we are going to see that the standardize of the sum of the output
-data converges to a Brownian motion in $D[0,\infty)$, which is the
-set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$ that
-are right-continuous and have left-hand limits, with the Skorohod
-topology. The Skorohod metric $d_{t}$ on $D\left[0,t\right]$ is:
-\[
-d_{t}\left(X,Y\right)=\mbox{inf}_{\lambda\in\Lambda_{t}}\left\{ \left\Vert \lambda-I\right\Vert \vee\left\Vert X-Y\circ\lambda\right\Vert \right\} 
-\]
-where $\Lambda_{t}$ is the set of strictly increasing, continuous
-mappings of $\left[0,t\right]$ onto itself, and $\left\Vert \cdot\right\Vert $
-is the uniform norm, and $I$ is the identity map. Note that uniform
-convergence on $\left[0,t\right]$ implies Skorohod convergence.
-
-For $X\in D\left[0,\text{\ensuremath{\infty}}\right)$, let $X^{m}$
-be the element of $D[0,\infty)$ defined by
-\[
-X^{m}\left(t\right)=g_{m}\left(t\right)X\left(t\right)
-\]
-where 
-\[
-g_{m}\left(t\right)=\begin{cases}
-1 & \mbox{if }t\leq m-1,\\
-m-t & \mbox{if }m-1\leq t\leq m,\\
-0 & \mbox{if }t\geq m.
-\end{cases}
-\]
-And now take
-\[
-d_{\infty}\left(X,Y\right)=\sum_{m=1}^{\infty}2^{-m}\left(1\wedge d_{m}\left(X,Y\right)\right)
-\]
-which is the Skorohod metric on $D\left[0,\infty\right)$.
-
-\paragraph*{Lemma 1.}
-
-If $x\in\left\{ 1\ldots,k\right\} $, then
-\[
-C_{x}\left(\delta,\cdot\right):=\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\right),x}-\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right)
-\]
-in the sense of $D[0,\infty)$, where $Y_{n,x}$ is the sum of the
-first $n$ samples and $W_{x}$ is a standard Brownian motion.
-
-\paragraph*{Proof.}
-
-By the Theorem 19.1 of Billingsley 1999 and the sandwich theorem,
-\[
-\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right).
-\]
-
-Since $\frac{\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}-ceil\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right)}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\rightarrow0$
-uniformly on $[0,r]$ for every $r$, then it also converges to $0$
-on $D[0,\infty)$ and so 
-\[
-\frac{Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right),x}-\mbox{}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(\cdot\frac{1}{\delta^{2}}\right)\right)\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\Rightarrow W_{x}\left(\cdot\right).
-\]
-
-Observe that for $\epsilon>0$ and $\delta$ sufficiently small
-\[
-\left|\frac{-Y_{\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right),x}+Y_{\mbox{ceil}\left(n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}t\frac{1}{\delta^{2}}\right),x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\sqrt{\frac{1}{\delta^{2}}}}\right|<\epsilon\left(n_{0}\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}+2\right)
-\]
-and then 
-\[
-C_{x}\left(\delta,\cdot\right)\Rightarrow W_{x}\left(\cdot\right).
-\]
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-Now we are going to define new algorithms that are almost the same
-than the one proposed by Frazier, but instead of $q_{tx}^{\delta}\left(A\right)$,
-these algorithms use new functions $q_{tx}^{Y,\delta}\left(A\right)$
-which depend on a function $Y$ that is in $D\left[0,\infty\right)^{k}$.
-
-First we are going to suppose that $\delta>0$ and $\mu_{k}=\delta$,$\mu_{k-1}=\cdots=\mu_{\text{1}}=0$.
-
-Let$ $ $Y\in D\left[0,\infty\right)^{k}$ , we define
-\begin{eqnarray*}
-q_{tx}^{Y,\delta}\left(A\right): & = & \mbox{exp}\left(\frac{Y_{x}\left(t\right)}{\lambda_{z}}+\delta^{2}\beta_{t\frac{1}{\delta^{2}}}I_{\left\{ x=k\right\} }\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{Y_{x^{'}}\left(t\right)}{\lambda_{z}}+\delta^{2}\beta_{t\frac{1}{\delta^{2}}}I_{\left\{ x^{'}=k\right\} }\right)
-\end{eqnarray*}
-where $\beta_{t\frac{1}{\delta^{2}}}=\frac{\left(n_{0}+t\frac{1}{\delta^{2}}\right)}{\lambda_{z}^{2}}$.
-
-We define
-\begin{eqnarray*}
-T_{Y,\delta}^{0} & = & 0\\
-A_{0}^{Y,\delta} & = & \left\{ 1,\ldots,k\right\} \\
-P_{0}^{Y,\delta} & = & P^{*}\\
-T_{Y,\delta}^{n+1}\left(P_{n}^{Y,\delta}\right) & = & \mbox{inf}\left\{ t\geq T_{Y,\delta}^{n}:\mbox{ min}_{x\in A_{n}^{Y,\delta}}q_{tx}^{Y,\delta}\left(A_{n}^{Y,\delta}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}^{Y,\delta}}q_{tx}^{Y,\delta}\left(A_{n}^{Y,\delta}\right)\geq P_{n}^{Y,\delta}\right\} \\
-Z_{n+1}^{Y,\delta} & \in & \mbox{arg min}_{x\in A_{n}^{Y,\delta}}q_{T_{Y,\delta}^{n+1},x}^{Y,\delta}\left(A_{n}^{Y,\delta}\right)\\
-A_{n+1}^{Y,\delta} & = & A_{n}-\left\{ Z_{n+1}^{Y,\delta}\right\} \\
-P_{n+1}^{Y,\delta} & = & P_{n}^{Y,\delta}/\left(1-\mbox{min}_{x\in A_{n}^{Y,\delta}}q_{T_{Y,\delta}^{n+1}x}^{Y,\delta}\left(A_{n}^{Y,\delta}\right)\right).
-\end{eqnarray*}
-Now, let
-\[
-M_{Y,\delta}=\mbox{inf}\left\{ n=1,\ldots,k-1:\mbox{max}_{x\in A_{n-1}^{Y,\delta}}q_{T_{Y,\delta}^{n},x}\left(A_{n-1}^{Y,\delta}\right)\geq P_{n-1}^{Y,\delta}\right\} 
-\]
-
-and
-
-\begin{eqnarray*}
-f\left(Y,\delta\right) & = & \begin{cases}
-1 & \mbox{if }k\mbox{ is chosen}\\
-0 & \mbox{otherwise}
-\end{cases}.
-\end{eqnarray*}
-
-Now, we also define$ $
-\[
-q_{tx}^{Y}\left(A\right):=\mbox{exp}\left(\frac{Y_{x}\left(t\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}tI_{\left\{ x=k\right\} }\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{Y_{x'}\left(t\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}tI_{\left\{ x'=k\right\} }\right)
-\]
-
-\begin{eqnarray*}
-T_{Y}^{0} & = & 0\\
-A_{0}^{Y} & = & \left\{ 1,\ldots,k\right\} \\
-P_{0}^{Y} & = & P^{*}\\
-T_{Y}^{n+1}\left(P_{n}^{Y}\right) & = & \mbox{inf}\left\{ t\geq T_{Y}^{n}:\mbox{ min}_{x\in A_{n}^{Y}}q_{tx}^{Y}\left(A_{n}^{Y}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}^{Y}}q_{tx}^{Y}\left(A_{n}^{Y}\right)\geq P_{n}^{Y}\right\} \\
-Z_{n+1}^{Y} & \in & \mbox{arg min}_{x\in A_{n}^{Y}}q_{T_{Y}^{n+1},x}^{Y}\left(A_{n}^{Y}\right)\\
-A_{n+1}^{Y} & = & A_{n}^{Y}-\left\{ Z_{n+1}^{Y}\right\} \\
-P_{n+1}^{Y} & = & P_{n}^{Y,\delta}/\left(1-\mbox{min}_{x\in A_{n}^{Y,}}q_{T_{Y}^{n+1}x}^{Y}\left(A_{n}^{Y}\right)\right).
-\end{eqnarray*}
-
-Now, let
-\[
-M_{Y}=\mbox{inf}\left\{ n=1,\ldots,k-1:\mbox{max}_{x\in A_{n-1}^{Y}}q_{T_{Y}^{n},x}\left(A_{n-1}^{Y}\right)\geq P_{n-1}^{Y}\right\} 
-\]
-and
-\[
-\]
-\begin{eqnarray*}
-g\left(Y\right) & = & \begin{cases}
-1 & \mbox{if }k\mbox{ is chosen}\mbox{ }\\
-0 & \mbox{otherwise}
-\end{cases}.
-\end{eqnarray*}
-
-We want to prove that 
-\[
-f\left(C\left(\delta,\cdot\right),\delta\right)\Rightarrow g\left(W\right).
-\]
-
-In order to prove this, we will prove the following lemma which will
-allow us to use the Theorem 5.5 of Billingsley 1968 that implies the
-desired result.
-
-\paragraph*{Lemma 2.}
-
-Let $\left\{ \delta_{n}\right\} \subset\left(0,\infty\right)$ such
-that $\delta_{n}\rightarrow0$. If $D_{s}\equiv\{x\in D\left[0,\infty\right)^{k}:\mbox{ for all sequences }\left\{ x_{n}\right\} \subset D\left[0,\infty\right)^{k},\mbox{ such that }$
-$lim_{n}d\left(x_{n},x\right)=0$ the sequence $\left\{ f\left(x_{n},\delta_{n}\right)\right\} $
-converges to $\left\{ g\left(x\right)\right\} $$\left.\right\} $$ $,
-then $ $$\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\right)=1$.
-
-\paragraph*{Proof.}
-
-We will use the following property: if $T$ is a stopping time, then
-by the local version of the law of the iterated logarithm for Brownian
-motion 
-\begin{equation}
-\mbox{lim sup}_{u\rightarrow0^{+}}\frac{\left[W_{x}\left(T+u\right)-W_{x}\left(T\right)\right]}{\sqrt{2u\mbox{ln}\left[\mbox{ln}\left(1/u\right)\right]}}=1\label{eq:1.1}
-\end{equation}
-almost surely for each system $x$. Furthermore, note that $W$ is
-almost surely continuous on $\left[0,t\right]^{k}$ if $t>0$ and
-so $W$ is also almost surely uniformly continuous on $\left[0,t\right]^{k}$.
-
-Let $\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}$ such
-that $Z_{n}\rightarrow W$. Note that $\delta_{n}^{2}\frac{\left(n_{0}+t\frac{1}{\delta_{n}^{2}}\right)}{\lambda_{z}^{2}}\rightarrow\frac{t}{\lambda_{z}^{2}}$
-in $D\left[0,\infty\right)$ and $\frac{\delta_{n}\sqrt{\frac{1}{\delta_{n}^{2}}}}{\lambda_{z}}\rightarrow\frac{1}{\lambda_{z}}$
-in $D\left[0,\infty\right)$ because uniformly convergence implies
-convergence in the Skorohod topology. Consequently, for each $s>0$
-there exist functions $\lambda_{s}^{n}$ in $\Lambda$ such that 
-\[
-\mbox{lim}_{n}Z_{n}\left(\lambda_{s}^{n}t\right)=W\left(t\right)
-\]
-uniformly in $t$ and
-\[
-\mbox{lim}_{n}\lambda_{s}^{n}t=t
-\]
-uniformly in $t$. Then
-\[
-\mbox{lim}_{n}\frac{\delta_{n}\sqrt{\frac{1}{\delta_{n}^{2}}}}{\lambda_{z}}Z_{n}\left(\lambda_{s}^{n}t\right)+\delta_{n}^{2}\frac{\left(n_{0}+\lambda_{s}^{n}\left(t\right)\frac{1}{\delta_{n}^{2}}\right)}{\lambda_{z}^{2}}=W\left(t\right)\frac{1}{\lambda_{z}}+\frac{t}{\lambda_{z}^{2}}
-\]
-uniformly in $t$, and so
-\[
-\mbox{lim}_{n}\mbox{exp}\left(\frac{\delta_{n}\sqrt{\frac{1}{\delta_{n}^{2}}}}{\lambda_{z}}Z_{n}\left(\lambda_{n}t\right)+\delta_{n}^{2}\frac{\left(n_{0}+\lambda_{s}^{n}\left(t\right)\frac{1}{\delta_{n}^{2}}\right)}{\lambda_{z}^{2}}\right)=\mbox{exp}\left(W\left(t\right)\frac{1}{\lambda_{z}}+\frac{t}{\lambda_{z}^{2}}\right)
-\]
-uniformly in $t$ since $\mbox{exp}$ is uniformly continuous in $\left[0,s\right]$.
-Consequently,
-\[
-q_{\lambda_{s}^{n}\left(t\right)x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{tx}^{W}\left(A\right)
-\]
-uniformly in $t\in\left[0,s\right]$. Thus, $q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{\cdot x}^{W}\left(A\right)$
-in $D\left[0,s\right]$ for any set $A\subset\left\{ 1,\ldots,k\right\} $
-and $s\geq0$. Consequently, $q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{\cdot x}^{W}\left(A\right)$
-in $D\left[0,\infty\right)$. Then for each $m\geq0$ there exists
-$\lambda_{n,A}\in\Lambda_{\infty}$ such that $\mbox{sup}_{t<\infty}\left\Vert \lambda_{n,A}\left(t\right)-t\right\Vert \leq d\left(q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right),q_{\cdot x}^{W}\left(A\right)\right)+\frac{1}{n}$
-and $\mbox{sup}_{t\leq m}\left\Vert q_{tx}^{Z_{n},\delta_{n}}\left(A\right)-q_{\lambda_{n,A}\left(t\right)x}^{W}\left(A\right)\right\Vert \leq d\left(q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right),q_{\cdot x}^{W}\left(A\right)\right)+\frac{1}{n}$.
-Taking $g_{n}^{A}\equiv\mbox{sup}_{t\leq m}\left\Vert q_{tx}^{W}\left(A\right)-q_{\lambda_{n}\left(t\right)x}^{W}\left(A\right)\right\Vert $,
-we see from the uniform continuity of $W$ on $\left[0,m\right]^{k}$
-and the definition of $g_{n}^{A}$ that $\mbox{lim}_{n\rightarrow\infty}g_{n}^{A}=0.$
-Moreover, if we take $\epsilon_{n}^{A}=3n^{-1}+3\mbox{sup}\left\{ d\left(q_{\cdot x}^{Z_{l},\delta_{l}}\left(A\right),q_{\cdot x}^{W}\left(A\right)\right)+g_{l}^{A}:l=n,n+1,\ldots\right\} $,
-then $\left\{ \epsilon_{n}^{A}\right\} $ is a monotonically decreasing
-sequence of positive numbers with limit zero.
-
-From the definition of $\epsilon_{n}$ we have $d\left(q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right),q_{\cdot x}^{W}\left(A\right)\right)<\epsilon_{n}/2$
-and $g_{n}^{A}<\epsilon_{n}/2$ for $n=1,2,\ldots$ Consequently,
-we have 
-\begin{eqnarray*}
-\left\Vert q_{tx}^{Z_{n},\delta_{n}}\left(A\right)-q_{tx}^{W}\left(A\right)\right\Vert  & \leq & \left\Vert q_{tx}^{Z_{n},\delta_{n}}\left(A\right)-q_{\lambda_{n}\left(t\right)x}^{W}\left(A\right)\right\Vert +\left\Vert q_{\lambda_{n}\left(t\right)x}^{W}\left(A\right)-q_{tx}^{W}\left(A\right)\right\Vert \\
- & < & \epsilon_{n}^{A}
-\end{eqnarray*}
-for all $t\in\left[0,m\right]$ and $x\in A$.
-
-We will show that $\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\mid M_{W}=i\right)=1$
-for $i\in\left\{ 1,\ldots,k-1\right\} $ so that the desired conclusion
-follows.
-
-Suppose first that $M_{W}=1$. Let's prove that $T_{Z_{n},\delta_{n}}^{1}\left(P\right)\rightarrow T_{W}^{1}\left(P\right)$
-as $n\rightarrow\infty$. Since $M_{W}=1$, then $\mbox{max}_{x\in A}q_{T_{W}^{1}\left(P\right)x}^{W}\left(A\right)=P$
-almost surely because $W$ is continuous almost surely. Let $q_{x}^{*}=\mbox{min}_{t\in\left[0,T_{W}^{1}\left(P\right)\right]}q_{tx}^{W}$
-(the minimum exists because $q_{tx}^{W}$ is continuous) and let $q^{*}=\mbox{min}_{x}q_{x}^{*}$.
-Let $N$ such that if $n>N$ then $\epsilon_{n}^{A}<q^{*}-c$ (note
-that in the last equation $m=T_{W}^{1}\left(P\right)$ and $q^{*}-c>0$
-because $M_{W}=1$ and $N$ is a random variable). If $n>N$ and $t\leq T_{W}^{1}\left(P\right)$
-then
-\begin{eqnarray*}
-q_{tx}^{W}\left(A\right) & < & q_{tx}^{Z_{n},\delta_{n}}\left(A\right)+q^{*}-c\\
-\Rightarrow c & < & q_{tx}^{Z_{n},\delta_{n}}\left(A\right)+q^{*}-q_{tx}^{W}\left(A\right)\leq q_{tx}^{Z_{n},\delta_{n}}\left(A\right).
-\end{eqnarray*}
-
-Case 1. $T_{W}^{1}\left(P\right)=0$. Note that $q_{0x}^{W}\left(A\right)=\frac{1}{k}<P$
-and so this case is not possible.
-
-Case 2. $0<T_{W}^{1}\left(P\right)$.
-
-Note that $T_{Z_{n},\delta_{n}}^{1}\left(P\right)\leq T_{Z_{n},\delta_{n}}^{1}\left(P+\delta_{n}\right)\leq T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right)$
-because if $t<T_{Z_{n},\delta_{n}}^{1}\left(P+\delta_{n}\right)$
-(for the sequence $\left\{ \epsilon_{n}\right\} $ we take $m=\mbox{sup}_{n}P+\delta_{n}$)
-\[
-q_{tx}^{W}\left(A\right)-\epsilon_{n}<q_{tx}^{Z_{n},\delta_{n}}\left(A\right)<P+\delta_{n}.
-\]
-Furthermore, 
-\begin{eqnarray*}
-T_{W}^{1}\left(P\right) & \leq & \mbox{lim inf}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right)\\
- & \leq & \mbox{lim sup}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right).
-\end{eqnarray*}
- Now, let $x=\mbox{arg max}q_{T_{W}^{1}x}^{W}\left(A\right)$. By
-(\ref{eq:1.1}), for any $\varepsilon\in\left(0,1\right)$, there
-exists a monotonically decreasing sequence $\left\{ s_{k}:\mbox{ }k=1,2,\ldots\right\} \subset\left(T_{W}^{1}\left(P\right),\infty\right)$
-such that $\mbox{lim}_{n}s_{n}=T_{W}^{1}\left(P\right)$; and for
-$k=1,2,\ldots$ we have
-
-\begin{eqnarray*}
-W_{x}\left(s_{k}\right)-W_{x}\left(T_{W}^{1}\left(P\right)\right) & >v_{k}\equiv & \left(\varepsilon\right)\sqrt{2\left(s_{k}-T_{W}^{1}\left(A\right)\right)\mbox{ln}\mbox{ln}\left(1/\left(s_{k}-T_{W}^{1}\left(P\right)\right)\right)}.
-\end{eqnarray*}
-
-Notice that $v_{k}>0$ and $\mbox{lim}_{k}v_{k}=0$. Let $\alpha>0$.
-Let $\delta$ such that if $\delta_{3}<\delta$, then $\alpha>-\mbox{log}\left(1-\delta_{3}\right)$.
-Pick $\delta_{3}<\delta$.
-Let $K$ such that if $k>K$, $\frac{\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{1}\left(P\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{1}\left(P\right)I_{\left\{ x^{'}=k\right\} }\right)}{\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)}>1-\delta_{3}$.
-Pick $k>K$. Let $N_{4}$ such that if $n>N_{4}$, then $\frac{\epsilon_{n}}{P}<v_{k}\frac{1}{\lambda_{z}}+\alpha$
-and $\frac{\delta_{n}}{P}<\left(v_{k}\frac{1}{\lambda_{z}}+\alpha\right)^{2}/2$.
-$ $Observe that
-\begin{eqnarray*}
-q_{s_{k}x}^{W} & = & \mbox{exp}\left(\frac{W_{x}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x=k\right\} }\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)\\
- & > & \frac{\mbox{exp}\left(\frac{W_{x}\left(T_{W}^{1}\left(P\right)\right)+v_{k}}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{1}\left(P\right)I_{\left\{ x=k\right\} }\right)}{\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{1}\left(P\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{1}\left(P\right)I_{\left\{ x^{'}=k\right\} }\right)}\times\frac{\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{1}\left(P\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{1}\left(P\right)I_{\left\{ x^{'}=k\right\} }\right)}{\sum_{x^{'}\in A}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)}\\
- & \geq & q_{T_{W}^{1}\left(P\right)x}^{W}\left(A\right)\mbox{exp}\left(v_{k}\frac{1}{\lambda_{z}}\right)\left(1-\delta_{3}\right)\geq q_{T_{W}^{1}\left(P\right)x}^{W}\left(A\right)\mbox{exp}\left(v_{k}\frac{1}{\lambda_{z}}\right)\mbox{exp}\left(\alpha\right)\\
- & \geq & P\left(1+v_{k}\frac{1}{\lambda_{z}}+\alpha+\frac{\left(v_{k}\frac{1}{\lambda_{z}}+\alpha\right)^{2}}{2}\right)>\left(P+\epsilon_{n}+\delta_{n}\right).
-\end{eqnarray*}
-Consequently, 
-\[
-s_{k}>T_{W}^{1}\left(P+\epsilon_{n}+\delta_{n}\right)
-\]
-if $n>N_{4}$, and so 
-\[
-s_{k}\geq\mbox{lim sup}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right).
-\]
-
-Since $s_{k}\rightarrow T_{W}^{1}$, we must have that
-\begin{eqnarray*}
-T_{W}^{1}\left(P\right) & \geq & \mbox{lim sup}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right)\\
- & \geq & \mbox{lim inf}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right)\\
- & \geq & T_{W}^{1}\left(P\right)
-\end{eqnarray*}
-Consequently, 
-\[
-T_{W}^{1}\left(P\right)=\mbox{lim}_{n}T_{W}^{1}\left(P+\delta_{n}+\epsilon_{n}\right).
-\]
-
-Now,
-\[
-T_{Z_{n},\delta_{n}}^{1}\left(P\right)\geq T_{Z_{n},\delta_{n}}^{1}\left(P-\delta_{n}\right)\geq T_{W}^{1}\left(P-\delta_{n}-\epsilon_{n}\right)
-\]
-
-because if $t<T_{W}^{1}\left(P-\delta_{n}-\epsilon_{n}\right)$ 
-\[
-q_{tx}^{Z_{n},\delta_{n}}\left(A\right)-\epsilon_{n}<q_{tx}^{W}\left(A\right)<P-\delta_{n}-\epsilon_{n}.
-\]
-Similarly we can prove that 
-\[
-\mbox{lim}_{n}T_{W}^{1}\left(P-\delta_{n}-\epsilon_{n}\right)=T_{W}^{1}\left(P\right).
-\]
-Consequently,
-\[
-T_{W}^{1}\left(P\right)=\mbox{lim}_{n}T_{Z_{n},\delta_{n}}^{1}\left(P\right).
-\]
-
-Let $x=\mbox{arg max}_{x}q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)$.
-Let $\epsilon>0$.
-Let $N$ such that if $n>N$, then $2\epsilon_{n}+2\epsilon<-\mbox{max}_{y\in A-\left\{ x\right\} }q_{T_{W\left(P\right)}^{1},y}^{W}\left(A\right)+q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)$
-\[
-\left|q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)-q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),x}^{Z_{n},\delta_{n}}\left(A\right)\right|<\epsilon+\epsilon_{n}
-\]
-for all $x\in A$, and so if $z\in A-\left\{ x\right\} $,
-\begin{eqnarray*}
-q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),z}^{Z_{n},\delta_{n}}\left(A\right) & < & \epsilon+\epsilon_{n}+q_{T_{W}^{1}\left(P\right),z}^{W}\left(A\right)\\
- & < & -\epsilon-\epsilon_{n}+q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)\\
- & < & q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),x}^{Z_{n},\delta_{n}}\left(A\right)
-\end{eqnarray*}
-and so $x=\mbox{arg max}_{x}q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),x}^{Z_{n},\delta_{n}}\left(A\right)$.
-\[
-\]
-
-Now, we suppose that $ $$M_{W}=2$. Let's prove that $T_{W}^{1}\left(A\right)=\mbox{lim}_{n}T_{Z_{n},\delta_{n}}^{1}$.
-
-Case 1. $0<T_{W}^{1}\left(P\right)$. Like in the previous proof,
-we conclude that 
-\[
-T_{W}^{1}\left(P\right)=\mbox{lim}_{n}T_{Z_{n},\delta_{n}}^{1}\left(P\right).
-\]
-
-Furthermore, if $x=\mbox{arg min}_{x\in A_{1}^{W}}q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)$.
-Let $N$ such that if $n>N$, then $2\epsilon_{n}+2\epsilon<\mbox{min}_{y\in A_{1}^{W}-\left\{ x\right\} }q_{T_{W}^{1}\left(P\right),y}^{W}\left(A\right)-q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)$
-for some $\epsilon>0$ and
-\[
-\left|q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right)z}^{Z_{n},\delta_{n}}-q_{T_{W}^{1}\left(P\right),z}^{W}\right|<\epsilon
-\]
-for all $z\in A-\left\{ x\right\} $.
-
-Then if \textbf{\large $z\in A-\left\{ x\right\} $, 
-\begin{eqnarray*}
-q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),z}^{Z_{n},\delta_{n}}\left(A\right) & > & -\epsilon_{n}-\epsilon+q_{T_{W}^{1}\left(P\right),z}^{W}\left(A\right)>q_{T_{W}^{1}\left(P\right),x}^{W}\left(A\right)+\epsilon_{n}+\epsilon\\
- & > & q_{T_{Z_{n},\delta_{n}}^{1}\left(P\right),x}^{Z_{n},\delta_{n}}\left(A\right)
-\end{eqnarray*}
-}{\large \par}
-
-for $n$ sufficiently large and so $x=\mbox{arg min}_{x\in A_{n}^{Y}}q_{T_{Z_{n,\delta_{n}}}^{1}\left(P\right),x}^{Z_{n},\delta_{n}}\left(A\right)$.
-Consequently, $A_{1}^{Z_{n},\delta_{n}}=A_{1}^{W}$ for $n$ sufficiently
-large.
-
-Case 2. $T_{W}^{1}\left(P\right)=0$, then $ $$\mbox{ min}_{x\in A_{n}^{Y}}q_{0x}^{W}\left(A_{n}^{W}\right)=1/k\leq c$.
-Suppose $c>\frac{1}{k}$. Let $N$ such that if $n>N$, then $\epsilon_{n}<c-\frac{1}{k}$.
-Thus if $n>N$, 
-\[
-q_{0x}^{Z_{n},\delta_{n}}<\epsilon_{n}+\frac{1}{k}<c
-\]
-
-and so $T_{Z_{n},\delta_{n}}^{1}=0$. We can also see that $A_{1}^{Z_{n},\delta_{n}}=A_{1}^{W}$
-for $n$ sufficiently large.
-
-Now, let's prove that $T_{W}^{2}\left(P_{1}^{W}\right)=\mbox{lim}_{n}T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n},\delta_{n}}\right)$.
-By the above argument, we know that there exists $N$ such that if
-$n>N$, then $A_{1}^{Z_{n},\delta_{n}}=A_{1}^{W}$ and
-\[
-P_{1}^{Z_{n},\delta_{n}}<P_{1}^{W}.
-\]
-
-Case 1. $T_{W}^{2}\left(P_{1}^{W}\right)=0=T_{W}^{1}\left(P\right)$.
-This is impossible because $P_{1}^{W}\leq\frac{1}{k}\leq c$ and $ $$P_{1}^{W}\geq P^{*}>\frac{1}{k}$.
-
-Case 2. $0<T_{W}^{2}\left(P_{1}^{W}\right)$.
-
-Note that $T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n}}\right)\leq T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n}}+\delta_{n}\right)\leq T_{W}^{2}\left(P_{1}^{Z_{n}}+\delta_{n}+\epsilon_{n}\right)$
-because if $T_{Z_{n},\delta_{n}}^{1}\left(P\right)\leq t<T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n}}+\delta_{n}\right)$
-\begin{eqnarray*}
-q_{tx}^{W}\left(A_{1}^{W}\right)-\epsilon_{n} & < & q_{tx}^{Z_{n},\delta_{n}}\left(A_{1}^{W}\right)<P_{1}^{Z_{n}}+\delta_{n}
-\end{eqnarray*}
-Now, let $x=\mbox{arg max}q_{T_{W}^{2}\left(P_{1}^{W}\right)x}^{W}\left(A_{1}^{W}\right)$.
-By (\ref{eq:1.1}), for any $\varepsilon\in\left(0,1\right)$, there
-exists a monotonically decreasing sequence $\left\{ s_{k}:\mbox{ }k=1,2,\ldots\right\} \subset\left(T_{W}^{2}\left(P_{1}^{W}\right),1\right)$
-such that $\mbox{lim}_{n}s_{n}=T_{W}^{2}\left(P_{1}^{W}\right)$;
-and for $k=1,2,\ldots$ we have
-
-\begin{eqnarray*}
-W_{x}\left(s_{k}\right)-W_{x}\left(T_{W}^{2}\left(P_{1}^{W}\right)\right) & >v_{k}\equiv & \left(\varepsilon\right)\sqrt{2\left(s_{k}-T_{W}^{2}\left(P_{1}^{W}\right)\right)\mbox{ln}\mbox{ln}\left(1/\left(s_{k}-T_{W}^{2}\left(P_{1}^{W}\right)\right)\right)}.
-\end{eqnarray*}
- Notice that $v_{k}>0$ and $\mbox{lim}_{k}v_{k}=0$. Let $\alpha>0$.
-Let $\delta$ such that if $\delta_{3}<\delta$, then $\alpha>-\mbox{log}\left(1-\delta_{3}\right)$.
-Pick $\delta_{3}<\delta$.
-Let $K$ such that if $k>K$, $\frac{\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{2}\left(P_{1}^{W}\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{2}\left(P_{1}^{W}\right)I_{\left\{ x^{'}=k\right\} }\right)}{\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)}>1-\delta_{3}$.
-Pick $k>K$. Let $N_{4}$ such that if $n>N_{4}$, then $\frac{\epsilon_{n}}{P_{1}^{W}}<v_{k}\frac{1}{\lambda_{z}}+\alpha$
-and $\frac{\delta_{n}}{P_{1}^{W}}<\left(v_{k}\frac{1}{\lambda_{z}}+\alpha\right)^{2}/2$.
-$ $Observe that
-\begin{eqnarray*}
-q_{s_{k}x}^{W}\left(A_{1}^{W}\right) & = & \mbox{exp}\left(\frac{W_{x}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x=k\right\} }\right)/\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)\\
- & > & \frac{\mbox{exp}\left(\frac{W_{k}\left(T_{W}^{2}\left(P_{1}^{W}\right)\right)+v_{k}}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{2}\left(P_{1}^{W}\right)I_{\left\{ x=k\right\} }\right)}{\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{2}\left(P_{1}^{W}\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{2}\left(P_{1}^{W}\right)I_{\left\{ x^{'}=k\right\} }\right)}\\
- &  & \times\frac{\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{^{x'}}\left(T_{W}^{2}\left(P_{1}^{W}\right)\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}T_{W}^{2}\left(P_{1}^{W}\right)I_{\left\{ x^{'}=k\right\} }\right)}{\sum_{x^{'}\in A_{1}^{W}}\mbox{exp}\left(\frac{W_{x'}\left(s_{k}\right)}{\lambda_{z}}+\frac{1}{\lambda_{z}^{2}}s_{k}I_{\left\{ x'=k\right\} }\right)}\\
- & \geq & q_{T_{W}^{2}\left(P_{1}^{W}\right)x}^{W}\mbox{exp}\left(v_{k}\frac{1}{\lambda_{z}}\right)\left(1-\delta_{3}\right)\geq q_{T_{W}^{2}\left(P_{1}^{W}\right)x}^{W}\left(A_{1}^{W}\right)\mbox{exp}\left(v_{k}\frac{1}{\lambda_{z}}\right)\mbox{exp}\left(\alpha\right)\\
- &  & \geq P_{1}^{W}\left(1+v_{k}\frac{1}{\lambda_{z}}+\alpha+\frac{\left(v_{k}\frac{1}{\lambda_{z}}+\alpha\right)^{2}}{2}\right)>P_{1}^{W}+\epsilon_{n}+\delta_{n}.
-\end{eqnarray*}
-Consequently, 
-\[
-s_{k}>T_{W}^{2}\left(P_{1}^{W}+\epsilon_{n}+\delta_{n}\right)
-\]
-if $n>N_{4}$, and so 
-\[
-s_{k}\geq\mbox{lim sup}_{n}T_{W}^{2}\left(P_{1}^{W}+\delta_{n}+\epsilon_{n}\right).
-\]
-Since $s_{k}\rightarrow T_{W}^{1}$, we must have that
-\begin{eqnarray*}
-T_{W}^{2}\left(P_{1}^{W}\right) & \geq & \mbox{lim sup}_{n}T_{W}^{2}\left(P_{1}^{W}+\delta_{n}+\epsilon_{n}\right)\\
- & \geq & \mbox{lim inf}_{n}T_{W}^{2}\left(P_{1}^{W}+\delta_{n}+\epsilon_{n}\right)\\
- & \geq & T_{W}^{2}\left(P_{1}^{W}\right)
-\end{eqnarray*}
-Consequently, 
-\[
-T_{W}^{2}\left(P_{1}^{W}\right)=\mbox{lim}_{n}T_{W}^{2}\left(P_{1}^{W}+\delta_{n}+\epsilon_{n}\right).
-\]
-
-Now,
-\[
-T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n}}\right)\geq T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{Z_{n}}-\delta_{n}\right)\geq T_{W}^{2}\left(P_{1}^{Z_{n}}-\delta_{n}-\epsilon_{n}\right)
-\]
-
-because if $t<T_{W}^{2}\left(P_{1}^{Z_{n}}-\delta_{n}-\epsilon_{n}\right)$
-\[
-q_{tx}^{Z_{n},\delta_{n}}\left(A_{1}^{W}\right)-\epsilon_{n}<q_{tx}^{W}\left(A_{1}^{W}\right)<P_{1}^{Z_{n}}-\delta_{n}-\epsilon_{n}.
-\]
-Similarly we can prove that 
-\[
-\mbox{lim}_{n}T_{W}^{2}\left(P_{1}^{W}-\delta_{n}-\epsilon_{n}\right)=T_{W}^{2}\left(P_{1}^{W}\right).
-\]
-Consequently,
-\[
-T_{W}^{2}\left(P_{1}^{W}\right)=\mbox{lim}_{n}T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{W}\right).
-\]
-
-By a similar argument than before, we can see that $\mbox{arg max}_{x}q_{T_{Z_{n},\delta_{n}}^{2}\left(P_{1}^{W}\right),x}^{Z_{n},\delta_{n}}\left(A_{1}^{W}\right)=\mbox{arg max}_{x}q_{T_{W}^{2}\left(P_{1}^{W}\right),x}^{W}\left(A_{1}^{W}\right)$
-for $n$ sufficiently large.
-
-The cases $M_{W}=i$ for $k-1\geq i\geq3$ can be proved in a similar
-way.
-
-Since almost surely $M_{Y}\in\left\{ 1,\ldots,k-1\right\} $ by Frazier
-\cite{key-5}, we conclude that
-
-\[
-\mathbb{P}\left(W\text{\ensuremath{\in}D\ensuremath{\left[0,1\right]^{k}}-}D_{s}\right)=1.
-\]
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-\[
-\]
-
-By the extension of the CMT (Theorem 5.5 of Billingsley 1968), we
-have the following corollary.
-
-\paragraph*{Corollary 1.}
-
-We have that
-
-\[
-f\left(C\left(\delta,t\right),\delta\right)\Rightarrow g\left(W\left(t\right)\right)
-\]
-in distribution as $\delta\rightarrow0$.
-
-\[
-\]
-
-\paragraph*{Theorem 1.}
-
-If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
-distributed and independent, over time and across alternatives, then
-$\mbox{lim}_{\delta\rightarrow0}Pr\left\{ \mbox{BIZ selects }k\right\} \geq P*$
-provided $\mu_{k}=\delta,\mu_{k-1}=\cdots=\mu_{1}=0$. We also suppose
-$B_{1}=\cdots=B_{k}=1$ and $c\neq\frac{1}{k}$.
-
-\paragraph*{Proof.}
-
-Let 
-\[
-\hat{T}_{n}\left(\delta\right)=\min\left\{ t\in\left\{ 0,\delta^{2},2\delta^{2},\ldots\right\} :\mbox{ min}_{x\in A_{n}^{Y,\delta}}q_{tx}^{C\left(\delta,\cdot\right),\delta}\left(A_{n}^{C\left(\delta,\cdot\right),\delta}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}^{Y,\delta}}q_{tx}^{C\left(\delta,\cdot\right),\delta}\left(A_{n}^{C\left(\delta,\cdot\right),\delta}\right)\geq P_{n}^{C\left(\delta,\cdot\right),\delta}\right\}
-\]
-and $T_{n}\left(\delta\right)$ the usual stopping times of the algorithm.
-Then $T_{n}\left(\delta\right)=\hat{T}_{n}\left(\delta\right)/\delta^{2}$.
-Now, we can prove that $\hat{T}_{n}\left(\delta\right)-T_{C\left(\delta,\cdot\right),\delta}^{n}\left(P_{n}^{C\left(\delta,\cdot\right),\delta}\right)\rightarrow0$
-with probability $1$ as $\delta\rightarrow0$ using that $C\left(\delta,\cdot\right)$
-is right-continuous and $\delta^{2}\rightarrow0$. Consequently, we
-can use $C\left(\delta,T_{C\left(\delta,\cdot\right),\delta}^{n}\left(P_{n}^{C\left(\delta,\cdot\right),\delta}\right)\right)$
-instead of $C\left(\delta,\hat{T}_{n}\left(\delta\right)\right)$.
-
-Let $CS_{\delta}$ be the event of doing a correct selection given
-the configuration $\mu_{k}=\delta,\mu_{k-1}=\cdots=\mu_{1}=0$. Then
-\begin{eqnarray*}
-\underline{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right) & = & \underline{lim}_{\delta\rightarrow0}\mathbb{P}\left(f\left(C\left(\delta,t\right),\delta\right)=1\right)\\
- & = & \mathbb{P}\left(g\left(W\right)=1\right)\\
- & \geq & P^{*}
-\end{eqnarray*}
-where the last inequality follows from the paper of Frazier \cite{key-5}.
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}\;\;\;\;}$
-
-\paragraph*{Theorem 2.}
-
-If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
-distributed and independent, over time and across alternatives, then
-$\mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right)\geq P*$
-provided $\mu_{k}-\mu_{k-1}\geq\delta$. We suppose $B_{1}=\cdots=B_{k}=1$
-and $c\neq\frac{1}{k}$.
-
-\paragraph*{Proof.}
-
-Suppose $X_{1},\ldots,X_{k}$ are the observations of the systems
-$1,\ldots,k$, respectively. Consider, $\hat{X}_{i}=X_{i}-\mu_{i}e$
-if $i\neq k$ and $\hat{X}_{k}=X_{k}-\mu_{k}e+\delta e$. Then
-\begin{eqnarray*}
-\underline{lim}_{\delta\rightarrow0}\mathbb{P}_{\text{\ensuremath{\mu}}}\left(CS_{\delta}\mid\mathbf{X}\right) & = & \underline{lim}_{\delta\rightarrow0}\mathbb{P}_{\left(0,\ldots,0,\delta\right)}\left(CS_{\delta}\mid\hat{\mathbf{X}}\right)\\
- & = & \underline{lim}_{\delta\rightarrow0}\mathbb{P}\left(g\left(W\right)=1\right)\\
- & \geq & P^{*}.
-\end{eqnarray*}
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+\subsection*{B.3 Generalization to Continuous Time}
+
+We let $\left(Y_{tx}:t\in\mathbb{R}_{+}\right)$ be a Brownian motion
+under $\mathbb{P}_{\mu,\lambda}$ starting from $0$, with drift $\mu_{x}$,
+volatility $\lambda_{x}$ and independence across $x$.
+
+\subsubsection*{B.3.1 Generalization to Continuous Time: The BIZ Procedure with Common
+Variance}
+
+In this section, we assume $\lambda_{x}^{2}=\sigma^{2}$ for all $x$,
+with $\sigma^{2}$ known. To define this procedure, we recursively
+define the stopping times $0=\tau_{1}\leq\tau_{2}\leq\cdots\leq\tau_{k-1}\leq\infty$,
+random variables $Z_{1},\ldots,Z_{k-1}$, and $P_{0},\ldots,P_{k-1}$,
+and random sets $A_{0},A_{1},\ldots,A_{k-1}$. We first define $\tau_{0},A_{0}$
+and $P_{0}$ as 
+\[
+\tau_{0}=0,\mbox{ }A_{0}=\left\{ 1,\ldots,k\right\} ,\mbox{ },P_{0}=P^{*}.
+\]
+Then, for each $n=0,1,\ldots,k-2$, we define
+\begin{eqnarray*}
+\tau_{n+1} & = & \mbox{inf }\left\{ t\in\mathbb{R}_{+}\bigcap\left[\tau_{n},\infty\right):\mbox{min}_{x\in A_{n}}\hat{q}_{tx}\left(A_{n}\right)\leq c\mbox{ or}\mbox{max}_{x\in A_{n}}\hat{q}_{tx}\left(A_{n}\right)\geq P\right\} \\
+Z_{n+1} & \in & \mbox{arg min}_{x\in A_{n}}\hat{q}_{\tau_{n+1},x}\left(A_{n}\right)\\
+A_{n+1} & = & A_{n}\left\backslash \left\{ Z_{n+1}\right\} \right.\\
+P_{n+1} & = & P_{n}\left/\left(1-\mbox{min}_{x\in A_{n}}\hat{q}_{\tau_{n+1},x}\left(A_{n}\right)\right)\right.
+\end{eqnarray*}
+Finally, $\hat{x}$ is the single alternative in $A_{k-1}$.
+
+We also define
+\[
+M=\mbox{inf}\left\{ n=1,\ldots,k-1:\mbox{max}_{x\in A_{n-1}}\hat{q}_{\tau_{n},x}\left(A_{n-1}\right)\geq P_{n-1}\right\} .
+\]
+
+Frazier (2014) showed that $\tau_{M}=\tau_{M+1}=\cdots=\tau_{k-1}$,
+and that the one alternative remaining in $A_{k-1}$ is the one whose
+$\hat{q}_{tx}\left(A_{n}\right)$ satisfied $\hat{q}_{tx}\left(A_{n}\right)\geq P_{n}$
+at time $\tau_{M}$. He also showed that $\tau_{M}<\infty$ almost
+surely under any $\mathbb{P}_{\mu,\sigma}$.
+
+\subsubsection*{B.3.2 Generalization to Continuous Time: The BIZ Procedure for the
+Heterogeneous Variance Setting}
+
+This procedure is similar than the one given in 3.4. For each $x$
+let $n_{x}\left(t\right)=\gamma\lambda_{x}^{2}t$. Now, we define
+a stochastic process $\left(Y'_{tx}:t\geq0\right)$ as $Y'_{tx}=Y_{n_{x}\left(t\right),x}/\gamma\lambda_{x}^{2}$.
+We have that $\left(Y'_{tx}:t\geq0\right)$ is a Brownian motion with
+drift $\mu_{x}$ and volatility $1/\gamma$.
+
+The procedure is defined by first defining $\tau_{0},A_{0}$ and $P_{0}$
+as 
+\[
+\tau_{0}=0,\mbox{ }A_{0}=\left\{ 1,\ldots,k\right\} ,\mbox{ },P_{0}=P^{*},
+\]
+then defining recursively, for $n=0,1,\ldots,k-2$,
+
+\begin{eqnarray*}
+\tau_{n+1} & = & \mbox{inf }\left\{ t\in\mathbb{R}_{+}\bigcap\left[\tau_{n},\infty\right):\mbox{min}_{x\in A_{n}}q'_{tx}\left(A_{n}\right)\leq c\mbox{ or}\mbox{max}_{x\in A_{n}}q'_{tx}\left(A_{n}\right)\geq P\right\} \\
+Z_{n+1} & \in & \mbox{arg min}_{x\in A_{n}}q'_{\tau_{n+1},x}\left(A_{n}\right)\\
+A_{n+1} & = & A_{n}\left\backslash \left\{ Z_{n+1}\right\} \right.\\
+P_{n+1} & = & P_{n}\left/\left(1-\mbox{min}_{x\in A_{n}}q'_{\tau_{n+1},x}\left(A_{n}\right)\right)\right.
+\end{eqnarray*}
+where $q'_{tx}\left(A\right)$ is defined by
+\[
+q'_{tx}\left(A\right)=\mbox{exp}\left(\gamma\delta Y'_{tx}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\gamma\delta Y'_{tx'}\right)\right.=\mbox{exp}\left(\frac{\delta}{\lambda_{x}^{2}}Y_{n_{x}\left(t\right),x}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\frac{\delta}{\lambda_{x'}^{2}}Y_{n_{x'}\left(t\right),x'}\right)\right..
+\]
+Frazier (2014) showed that this procedure satisfies the IZ guarantee,
+and and its worst-case preference-zone PCS bound is tight in continuous
+time.
+
+\[
+\]
+
 \begin{thebibliography}{References}
@@
 
+\bibitem{key-8}Billingsley, P. 1999. \textit{Convergence of Probability
+Measures, }second edition. .John Wiley and Sons. New York.
+
 \bibitem{key-5}Frazier, P. I. A Fully Sequential Elimination Procedure
@@
 
+\bibitem{key-9}Karatzas, I., Shreve, S. E. 1991. \textit{Brownian
+Motion and Stochastic Calculus}, second edition. Springer. New York.
+
 \end{thebibliography}

### 2015-04-15 paper/paper_version2.tex
4/15/15

@@
 \STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
-Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.     
+Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.Let $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$.     
 \STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
@@
 \ENDWHILE    
-  \STATE Let $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.     
 \STATE For each $x\in A$, let      $n_{t+1,x} = \ceil\left( \lambdahat^2_{tx} (n_{tz} + B_z) / \lambdahat^2_{tz} \right)$.
@@
 The algorithm 2 can be generalized to the continuous case (See appendix B and Frazier (2014)).
-This procedure is a slightly modification of the original BIZ procedure
+This procedure is a slightly modification of the original BIZ procedure where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.
 
@@
 
-The BIZ procedure maps $\left(Y_{n_{x}\left(t\right),x}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
-to a selection decision, where $Y_{n_{x}\left(t\right),t}$ is the
-sum of samples observed by time $t$. In more detail, it works by
-transforming $\left(Y_{n_{x}\left(t\right),x}:A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
-to $\left(q'_{tx}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$.
-This $q'$ process is given by time process with jumps at $t\in\mathbb{N}$,
-\[
-q'_{tx}\left(A\right)=q'\left(\left(Z_{tx},t:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\right.
-\]
-where the variances are fixed. The same distribtuion over selection
-decision will result if we apply the same same selection process to
-the following time process with jumps at $t\in\left\{ 0,\delta^{2},2\delta^{2},\ldots\right\} =\delta^{2}\mathbb{N}$,
+Any ranking and selection algorithm can be viewed as mapping from
+paths of the $k$-dimensional discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
+onto selection decisions. The BIZ procedure's mapping from paths onto
+selections decisions can be understood as the composition of three
+simpler maps.
+
+The first is the mapping from the raw discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
+onto a time changed version of this random walk, written as $\left(Z_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$,
+where we recall $Z_{tx}=Y_{n_{x}\left(t\right),t}$ is the sum of
+the samples from alternative $x$ observed by stage $t$.
+
+The second maps this time-changed random walk through a non-linear
+mapping for each $t,x$ and subset $A\subset\left\{ 1,\ldots,k\right\} $,
+to obtain $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$,
+where
+
+\[
+q'_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\right.:=q'\left(\left(Z_{tx},t:x\in A\right),\delta,t\right)
+\]
+where we note that $n_{x}\left(t\right)$ and $\beta_{t}$ are deterministic
+in the version of the known-variance BIZ procedure that we consider
+here.
+
+The third maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
+onto selection decisions. Specifically, this mapping finds the first
+time.
+
+The same distribution over selection decision will result if we apply
+the same same selection process to the following time process with
+jumps at $t\in\left\{ 0,\delta^{2},2\delta^{2},\ldots\right\} =\delta^{2}\mathbb{N}$,
 \[
@@
 \end{eqnarray}
-where $t\geq0$ . Later we will show the difference in selection decisions
+where $t\geq0$ . Then we will show the difference in selection decisions
 vanishes as $\delta\rightarrow0$.
@@
 \]
-the previous equation is true beucase 
+the previous equation is true because 
 \[
@@
 for all $t\in\left[0,t^{*}\right]$. Since uniform convergence implies
-Skorohod convergente, then $\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)$
+Skorohod convergence, then $\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)$
 in $D_{t^{*}}$, and the result follows.
@@
 \]
-Let $\epsilon$ be the quantity on the righ-hand side of this inequality,
+Let $\epsilon$ be the quantity on the right-hand side of this inequality,
 then $\epsilon<1$ and it does not depend on $t^{*}$ and $n$.
@@
 procedure (Frazier 2014) when the variances are known, which is a
-new sequential elemination procedure. This algorithm is relevant because
+new sequential elimination procedure. This algorithm is relevant because
 it takes fewer samples than other IZ procedures, especially for problems
@@
 We are going to define the Skorohod topology on $D[0,\infty)$ by
-defining a metric on the space. The Skorohod metricric $d_{t}$ on
-$D\left[0,t\right]$ for each $t\geq0$ is:
+defining a metric on the space. The Skorohod metric $d_{t}$ on $D\left[0,t\right]$
+for each $t\geq0$ is:
 \[

### 2015-04-17 paper/paper_version2.tex
04/17/15

@@
 \[
-q_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right),\right.\mbox{ }\beta_{t}=\frac{\sum_{x'\in A}n_{tx'}}{\sum_{x'\in A}\hat{\lambda}_{tx'}^{2}}
+q'_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right),\right.\mbox{ }\beta_{t}=\frac{\sum_{x'\in A}n_{tx'}}{\sum_{x'\in A}\hat{\lambda}_{tx'}^{2}}
 \]
@@
 \STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
-\WHILE{$x\in\mbox{max}_{x\in A} q_{tx}\left(A\right)<P$}
-\WHILE{$\mbox{min}_{x\in A} q_{tx}\left(A\right) \le c$}
+\WHILE{$x\in\mbox{max}_{x\in A} q'_{tx}\left(A\right)<P$}
+\WHILE{$\mbox{min}_{x\in A} q'_{tx}\left(A\right) \le c$}
  \STATE Let $x\in\mbox{arg min}_{x\in A} q_{tx}\left(A\right)$.
@@
 onto selection decisions. Specifically, this mapping finds the first
-time.
-
-The same distribution over selection decision will result if we apply
-the same same selection process to the following time process with
-jumps at $t\in\left\{ 0,\delta^{2},2\delta^{2},\ldots\right\} =\delta^{2}\mathbb{N}$,
-\[
-q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
-\]
+time that $\mbox{max}_{x\in A}q_{tx}\left(A\right)$ is larger than
+some threshold $P$, and then it chooses the system with the largest
+empirical mean $Z_{tx}/n_{tx}$.
+
 Later, we can approximate the previous process by the continuous time
@@
 \begin{eqnarray}
-q_{tx}\left(A\right) & = & q\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)\label{eq:0.001}
+q_{tx}\left(A\right) & = & q\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)\label{eq:0.001-1}
 \end{eqnarray}
@@
 After that, we would like to use a kind of central limit theorem for
-$Z_{\frac{t}{\delta^{2}}x}=Y_{n_{x}\left(t/\delta^{2}\right),x}$
-when $\delta$ goes to zero to work with a Brownian motion instead.
-Specifically, we are going to see that the the standardized sum of
-the output data converges to a Brownian motion in the sense of $D_{\infty}:=D[0,\infty)$,
+$Z_{\frac{t}{\delta^{2}}x}$ when $\delta$ goes to zero to work with
+a Brownian motion instead. In order to do this, we are going to rewrite
+equation (1) in terms of a centralized version of $Z$:
+
+\[
+\mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
+\]
+and the resulting expresion is
+
+\[
+q_{tx}\left(A\right)=q\left(\left(C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
+\]
+
+Thus, we can see the selection decision resulting from the BIZ algorithm
+as the result of applying some mapping $f\left(\cdot,\delta\right)$
+to the paths $t\mapsto\mathcal{C}_{x}\left(\delta,t\right)$ .
+
+The last part of our proof is to observe that (1) $\mathcal{C}\left(\delta,\cdot\right)$
+converges to a multivariate Brownian motion $W$ as $\delta$ goes
+to 0; (2) the function $f$ has a continuity property that causes
+\[
+f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)\Rightarrow g\left(W\right)
+\]
+where g is the selection decision from applying the BIZ procedure
+in continuous time; and (3) the BIZ procedure satsifies the IZ guarantee
+when applied in continuous time.
+
+First, we are going to see that the the standardized sum of the output
+data converges to a Brownian motion in the sense of $D_{\infty}:=D[0,\infty)$,
 which is the set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$
@@
 topology. The definition and the properties of this topology may be
-found in Chapter 3 of Billingsley 1999 and the appendix. We will first
-see this result because it will give us a clue for proving the asymptotic
-validity of the Algorithm 2.
+found in Chapter 3 of Billingsley 1999 and the appendix.
 
@@
 
-We now gain the insight that we were looking for. We will use $\mathcal{C}_{x}\left(\delta,\cdot\right)$
-instead of $Z_{\frac{t}{\delta^{2}}x}$ in $\left(1\right)$, which
-is the definition of $q_{tx}\left(A\right)$,
-\[
-q_{tx}\left(A\right)=q'\left(\left(C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right),
-\]
-the previous equation is true because 
-\[
-Z_{\frac{t}{\delta^{2}}x}=C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right).
-\]
-
 Observe that $\mathcal{C}\left(\delta,\cdot\right)\in D\left[0,\infty\right)^{k}$
@@
 
-In order to prove this, we first prove Lemma 2, which will allow us
-to use Theorem 5.5 of Billingsley 1968, which implies the desired
-result.
+In order to prove this, we first prove a continuity property in Lemma
+2, which will allow us to use Theorem 5.5 of Billingsley 1968, which
+implies the desired result.
 

### 2015-04-17 paper/wsc15LatexPaper/wsc15poster.tex
04/17/15

%**************************************************************************
%*
%*  Paper: ``INSTRUCTIONS FOR AUTHORS OF LATEX (Poster) ABSTRACTS''
%*
%*  Publication: 2011 Winter Simulation Conference Author Kit
%*
%*  Filename: wsc11poster.tex
%*
%*      DATE: Feb 08, 2011 to become the primary WSC'11 LaTeX file
%*
%*  Word Processing System: TeXnicCenter and MiKTeX
%*
%*
%*  All files need the following
\input{wsc15style.tex}     % download from author kit.  Style files for wsc formatting

\documentclass{wscposterproc}
\usepackage{latexsym}
%\usepackage{caption}
\usepackage{graphicx}
\usepackage{mathptmx}

%
%****************************************************************************
% AUTHOR: You may want to use some of these packages. (Optional)
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm}
%****************************************************************************

%
%****************************************************************************
% AUTHOR: If you do not wish to use hyperlinks, then just comment
% out the hyperref usepackage commands below.

%% This version of the command is used if you use pdflatex. In this case you
%% cannot use ps or eps files for graphics, but pdf, jpeg, png etc are fine.

\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}

%% The next versions of the hyperref command are used if you adopt the
%% traditional latex-dvips-ps2pdf route in generating your pdf file. In
%% this case you can use ps or eps files for graphics, but not pdf, jpeg, png etc.
%% If you are using WinEdt or PCTeX, then use the following. If you are using
%% Y&Y TeX then replace "dvips" with "dvipsone"

%%\usepackage[dvips,colorlinks=true,urlcolor=blue,citecolor=black,%
%% anchorcolor=black,linkcolor=black]{hyperref}
%****************************************************************************

%****************************************************************************
% AUTHOR: You may need to use the following command to adjust the space on the title page
% to properly list all authors.
% Please use: 2.5in for 1 row of authors, 3.75in [default] for 2 rows of authors
%\setlength{\titlevboxsize}{2.5in}  % 2.5in for 1 row of authors, 3.75in for 2 rows of authors
%****************************************************************************

%
%****************************************************************************
%*
%* AUTHOR: YOUR CALL!  Document-specific macros can come here.
%*
%****************************************************************************

%#########################################################
%*
%*  The Document.
%*
\begin{document}

%***************************************************************************
% AUTHOR: AUTHOR NAMES GO HERE
% FORMAT AUTHORS NAMES Like: Author1, Author2 and Author3 (last names)
%
%		You need to change the author listing below!
%               Please list ALL authors using last name only, separate by a comma except
%               for the last author, separate with "and"
%
% These names will be used from the 2nd page on - thus for one page abstracts this can stay as it is.
% DON'T REMOVE THIS LINE!
%
\WSCpagesetup{LastName1, LastName2, and LastNameLastAuthor}

% AUTHOR: Enter the title, all letters in upper case
\title{INSTRUCTIONS FOR AUTHORS OF POSTER ABSTRACTS USING \LaTeX}

% AUTHOR: Enter the author(s) of the poster abstract
\author{Levent Yilmaz \\[12pt]
Computer Science and Software Engineering\\
Auburn University \\
3116 Shelby Center\\
Auburn, AL 36849, USA
}

\maketitle

\section*{ABSTRACT}

This set of instructions for producing an extended abstract for a poster presentation at the 2015 Winter Simulation Conference (WSC) with \LaTeX\ also serves as a sample file that you can edit to produce your submission. Please follow the guidelines herein when preparing your poster abstract. Failure to do so may result in a poster being rejected, returned for appropriate revision, or edited without your knowledge.

%\begin{center}
\section{INTRODUCTION}
%\end{center}
This paper provides instructions for the preparation of an extended abstract for a poster presentation at the 2015 Winter Simulation Conference (WSC) using \LaTeX. There is a companion paper that provides instructions for the preparation of extended abstracts using Microsoft Word.

\textbf{The easiest way to write an abstract using \LaTeX\ that complies with the
requirements is to edit the source file, {\tt wsc15poster.tex,} for this document.}
The style of this document is based on the special paper class file {\tt wscposterproc} which is selected by using {\tt $\backslash$documentclass\{wscposterproc\}}.

An author kit is available online via the  \href{http://www.wintersim.org}%
{conference website} \cite{WSC}.
The author kit includes this \LaTeX\ document and its Microsoft Word companion.

This document was typeset using {\tt pdflatex}, which allows you to use certain
graphics file types that are not allowed using the outdated {\tt latex-dvips-ps2pdf} route.

\section{LENGTH AND CONTENTS OF EXTENDED ABSTRACTS}
%\end{center}
The extended abstract will be strictly limited to a maximum  of 2 pages. The first page of the extended abstract will be formatted the same as a proceedings paper. The title will appear in BOLD UPPERCASE text. The title is followed by the author names and affiliations.

Each extended abstract will have a one paragraph abstract that will be limited to 150 words. This one paragraph abstract will also appear in the final program for the 2015 Winter Simulation Conference. Following the abstract, the content of the extended abstract may be broken down into one or more numbered sections with appropriate section titles.

Finally, if appropriate, the extended abstract may have a references section that appears at the end of the document. The references section is not numbered. The references section is included in the two page limit for the extended abstract. Due to space limitations, extended abstracts will not include author biographies.

\section{FORMAT OF EXTENDED ABSTRACTS}

The general format of the extended abstracts will follow the same formatting requirements as WSC proceedings papers for all of the required elements (title, author information, abstract, section titles, paragraphs, equations, figures, tables, references, etc.) For specific formatting instructions for each of these items, please refer to the appropriate MS Word or Latex instructions/sample papers available from the WSC Author Kit on the WSC website \url{http://www.wintersim.org}~\cite{WSC}.

\section{GETTING HELP}
If you need help in preparing your paper, contact the proceedings editors. You can reach the entire team by writing to our unified point of contact at \href{mailto://wsc15proceedings@gmail.com}{wsc15proceedings@gmail.com}.

You may also reach us individually using the contact information below.

\vspace{6pt}

\noindent Levent Yilmaz\\
Auburn University\\
Email: \href{mailto://wsc15yilmaz@gmail.com}{wsc15yilmaz@gmail.com}\\
\\
Wai Kin (Victor) Chan\\
Rensselaer Polytechnic Institute\\
Email: \href{mailto://wsc15chan@gmail.com}{wsc15chan@gmail.com}\\
\\
II-Chul Moon\\
KAIST\\
Email: \href{mailto://wsc15moon@gmail.com}{wsc15moon@gmail.com}\\
\\
Theresa M. K. Roeder\\
San Francisco State University\\
Email: \href{mailto://wsc15roeder@gmail.com}{wsc15roeder@gmail.com}\\
\\
% Please don't exchange the bibliographystyle style
\bibliographystyle{wsc}
% AUTHOR: Include your bib file here
\bibliography{demobib}

\end{document}

### 2015-04-17 paper/paper_version2.tex
04/17/15

@@
 \]
-and the resulting expresion is
+and the resulting expression is
 
@@
 where g is the selection decision from applying the BIZ procedure
-in continuous time; and (3) the BIZ procedure satsifies the IZ guarantee
+in continuous time; and (3) the BIZ procedure satisfies the IZ guarantee
 when applied in continuous time.

### 2015-05-04 paper/wish/wsc15paper.tex
conference

--- 2015-04-17 paper/paper_version2.tex
@@
-%% LyX 2.1.2.1 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass[11pt,english]{article}
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
-\usepackage{geometry}
-\geometry{verbose,tmargin=1.5cm,bmargin=1.5cm,lmargin=1.5cm,rmargin=1.5cm}
-\usepackage{color}
+%**************************************************************************
+%*
+%*  Paper: ``INSTRUCTIONS FOR AUTHORS OF LATEX DOCUMENTS''
+%*
+%*  Publication: 2015 Winter Simulation Conference Author Kit
+%*
+%*  Filename: wsc15paper.tex
+%*
+%*  Date: January 31, 2001   Time:  9:45 PM
+%*      BASE of current version: Feb 01, 2010 (primary WSC'10 LaTeX file)
+%*
+%*  Word Processing System: TeXnicCenter and MiKTeX
+%*
+%*
+%*  All files need the following
+\input{wsc15style.tex}     % download from author kit.  Style files for wsc formatting. Don't remove this line - required for generating the final paper!
+
+\documentclass{wscpaperproc}
+\usepackage{latexsym}
+\usepackage{caption}
+\usepackage{graphicx}
+\usepackage{mathptmx}
+
+%
+%****************************************************************************
+% AUTHOR: You may want to use some of these packages. (Optional)
+\usepackage{subcaption}
 \usepackage{amsmath}
+\usepackage{amsfonts}
 \usepackage{amssymb}
-\usepackage{setspace}
-\onehalfspacing
-
-\makeatletter
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-%\documentclass[opre,blindrev]{informs3} % current default for manuscript submission
-
-% current default line spacing
-%%\OneAndAHalfSpacedXII 
-%%\DoubleSpacedXII
-%%\DoubleSpacedXI
-
-% If hyperref is used, dvi-to-ps driver of choice must be declared as
-%   an additional option to the \documentclass. For example
-%\documentclass[dvips,opre]{informs3}      % if dvips is used 
-%\documentclass[dvipsone,opre]{informs3}   % if dvipsone is used, etc.
-
-%%% OPRE uses endnotes
-\usepackage{endnotes}
-\let\footnote=\endnote
-\let\enotesize=\normalsize
-\def\notesname{Endnotes}%
-\def\makeenmark{\hbox to1.275em{\theenmark.\enskip\hss}}
-\def\enoteformat{\rightskip0pt\leftskip0pt\parindent=1.275em
-  \leavevmode\llap{\makeenmark}}
-
-\date{}
+\usepackage{amsbsy}
+\usepackage{amsthm}
+\usepackage{algorithm}
+\usepackage{algorithmic}
+%****************************************************************************
+
+%
+%****************************************************************************
+% AUTHOR: If you do not wish to use hyperlinks, then just comment
+% out the hyperref usepackage commands below.
+
+%% This version of the command is used if you use pdflatex. In this case you
+%% cannot use ps or eps files for graphics, but pdf, jpeg, png etc are fine.
+
+\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,anchorcolor=black,linkcolor=black]{hyperref}
+
+%% The next versions of the hyperref command are used if you adopt the
+%% outdated latex-dvips-ps2pdf route in generating your pdf file. In
+%% this case you can use ps or eps files for graphics, but not pdf, jpeg, png etc.
+%% However, the final pdf file should embed all fonts required which means that you have to use file
+%% formats which can embed fonts. Please note that the final PDF file will not be generated on your computer!
+%% If you are using WinEdt or PCTeX, then use the following. If you are using
+%% Y&Y TeX then replace "dvips" with "dvipsone"
+
+%%\usepackage[dvips,colorlinks=true,urlcolor=blue,citecolor=black,%
+%% anchorcolor=black,linkcolor=black]{hyperref}
+%****************************************************************************
+
+%
+%****************************************************************************
+%*
+%* AUTHOR: YOUR CALL!  Document-specific macros can come here.
+%*
+%****************************************************************************
 
@@
 
-\usepackage{algorithm,algorithmic,enumerate}
-
-%% Setup of theorem styles. Outcomment only one. 
-%% Preferred default is the first option.
-  % Preferred (Theorem 1, Lemma 1, Theorem 2)
-%\TheoremsNumberedByChapter  % (Theorem 1.1, Lema 1.1, Theorem 1.2)
-
-\makeatother
-
-\usepackage{babel}
+% If you use theoremes
+\newtheoremstyle{wsc}% hnamei
+{3pt}% hSpace abovei
+{3pt}% hSpace belowi
+{}% hBody fonti
+{}% hIndent amounti1
+{\bf}% hTheorem head fontbf
+{}% hPunctuation after theorem headi
+{.5em}% hSpace after theorem headi2
+{}% hTheorem head spec (can be left empty, meaning `normal')i
+
+\theoremstyle{wsc}
+\newtheorem{theorem}{Theorem}
+\renewcommand{\thetheorem}{ \arabic{theorem}}
+\newtheorem{corollary}{Corollary}
+\renewcommand{\thecorollary}{\arabic{corollary}}
+\newtheorem{definition}{Definition}
+\renewcommand{\thedefinition}{\arabic{definition}}
+\newtheorem{lemma}{Lemma}
+\renewcommand{\thelemma}{\arabic{lemma}}
+
+%#########################################################
+%*
+%*  The Document.
+%*
 \begin{document}
 
-\title{Asymptotic Validity of a Fully Sequential Elimination Procedure for
-Indifference-Zone Ranking and Selection with Tight Bounds on Probability
-of Correct Selection}
-
-\author{Saul Toscano\\
-{\small{}School of Operations Research and Information Engineering,
-Cornell University}\\
-Peter I. Frazier\\
-{\small{}School of Operations Research and Information Engineering,
-Cornell University}}
+%***************************************************************************
+% AUTHOR: AUTHOR NAMES GO HERE
+% FORMAT AUTHORS NAMES Like: Author1, Author2 and Author3 (last names)
+%
+%		You need to change the author listing below!
+%               Please list ALL authors using last name only, separate by a comma except
+%               for the last author, separate with "and"
+%
+\WSCpagesetup{Toscano-Palmerin, Frazier}
+
+% AUTHOR: Enter the title, all letters in upper case
+\title{ASYMPTOTIC VALIDITY OF A FULLY SEQUENTIAL ELIMINATION PROCEDURE FOR INDIFFERENCE-ZONE RANKING AND SELECTION WITH TIGHT BOUNDS ON PROBABILITY OF CORRECT SELECTION}
 
 \maketitle
+
+\begin{figure*}[htb]
+{
+\centering
+Saul Toscano-Palmerin \\
+Peter I. Frazier \\
+\vspace{12pt}
+Cornell University \\
+257 Rhodes Hall \\
+206 Rhodes Hall \\
+Ithaca, NY 14853, USA\\
+}
+\end{figure*}
+
+\section*{ABSTRACT}
 We consider the indifference-zone (IZ) formulation of the ranking
-and selection problem. Conservatism leads classical IZ procedures
+and selection problem in which the goal is to choose with high probability 
+an alternative with similar mean than the one with largest mean. 
+Conservatism leads classical IZ procedures
 to take too many samples in problems with many alternatives. The Bayes-inspired
-Indifference Zone (BIZ) procedure, proposed in Frazier (2014), is
+Indifference Zone (BIZ) procedure, proposed in \citeN{Frazier:BIZ}, is
 less conservative than previous procedures, but its proof of validity
-requires strong assumptions. In this paper, we present a new proof
-of asymptotic validity that relaxes these assumptions.
-
-\section{Introduction}
-
-One common problem in simulation is that of choosing the best among
-several simulated systems. The problem of deciding how many samples
-to use from each alternative to support our selection as the best
-is the ranking and selection problem. An efficient solution to this
-problem has to balance between the time spent simulating and the quality
-of the selection.
-
-This paper will consider the indifference-zone (IZ) formulation of
-the ranking and selection problem, in which we choose the best system
-with probability larger than a pre-specified threshold, whenever the
-distance between the best system and the others is sufficiently large.
-We say that a sampling procedure having this property satisfies the
-IZ guarantee and the set of system configurations under which the
-best alternative is better than the second best by at least some given
-$\delta>0$ is called the preference zone (PZ). The seminal work dates
-back to Bechhofer (1954), with early work compiled in the monograph
-Bechhofer et al. (1968). The progress in the area has been summarized
-in Bechhofer et al. (1995), Swisher et al. (2003), Kim and Nelson
-(2006, 2007) and Frazier (2014).
-
-The goal of an IZ algorithm is to take as few samples as possible
-while the IZ guarantee is satisfied. The first IZ procedures presented
-in Bechhofer (1954), Paulson (1964), Fabian (1974), Rinott (1978),
-Hartmann (1988, 1991), Paulson (1994) satisfy the IZ guarantee, but
-they usually take too many samples when there are many alternatives,
+requires strong assumptions, specifically it assumes that the variances are known 
+and have an integer multiple structure. In this paper, we consider a slightly
+modification of the original BIZ procedure in order to simplify the analysis, and we
+present a new proof of its asymptotic validity that relaxes these assumptions.
+Specifically, we prove the validity of the algorithm when the variances are known
+and the difference between the best alternative and the second best goes to zero.
+
+\section{INTRODUCTION}
+\label{sec:intro}
+
+There are many applications where we have to choose the best alternative
+among a finite number of simulated alternatives.
+For example, in inventory problems, we may want to choose the best inventory policy $(s,S)$ for a finite number of values of $s$ and $S$.
+The ranking and selection problem has to decide how many samples are needed to find the alternative with the largest mean.
+A good solution to the problem is efficient and accurate, i.e.
+the procedure proposed for the problem must balance between the number of samples required and quality of the selection.
+
+This paper considers the indifference-zone (IZ) formulation of
+the ranking and selection problem, in which the distance between the best system and
+the other systems is sufficiently large and the best system is chosen with probability larger
+than some threshold given by the user. This property is called the IZ guarantee, and the preference zone (PZ)
+is defined as the set of system configurations under which the difference between the best system and the others is
+at least some given  $\delta>0$. The paper \citeN{Bechhofer:1954} is considered the seminal work, and early work is 
+presented in the monograph \citeN{Bechhofer:1968}. Some compilations of the theory developed in the area can be found
+in \citeN{Bechhofer:1995}, \citeN{swisher:survey}, \citeN{kim:20062} and \citeN{kim:2007}. Beyond these classical approaches, 
+there are the Bayesian approach \cite{Frazier:Tutorial} and the optimal computing budget allocation approach \cite{chen:ocva}.
+
+A good IZ procedure satisfies the IZ guarantee and requires as few samples as possible.
+The first IZ procedures presented in \citeN{Bechhofer:1954}, \citeN{Paulson:01}, \citeN{Fabian}, \citeN{Rinott},
+\citeN{Harmann:1988}, \citeN{hartmann:sequential}, \citeN{Paulson:1994} 
+satisfy the IZ guarantee, but they usually take too many samples when there are many alternatives,
 in part because their probability of correct selection (PCS) is much
-larger than the probability specified by the user. A reason of this
-is the use of the Bonferroni's inequality which leads to sample more
-than necessary. More recent algorithms in Kim and Nelson (2001), Goldsman
-et al. (2002), Hong (2006) improve the performance but they still
+larger than the probability specified by the user \cite{kim:Conserv}. One reason for this
+is that these procedures use Bonferroni's inequality, which leads then to sample more
+than necessary. More recently, new algorithms were developed in \citeN{Kim:2001}, \citeN{Goldsman:2002}, 
+\citeN{Hong}, and they improve the performance but they still
 use the Bonferroni's inequality, and so the methods are inefficient
-when there are several systems. Procedures in Kim and Dieker (2011),
-Dieker and Kim (2012) do not use the Bonferroni's inequality only
-when compare groups of three alternatives.
-
-Since the classic IZ procedures take too many samples with many alternatives,
-these methods are unpopular when there are more than a few hundred
-alternatives. However, Frazier (2014) presented a new sequential elimination
+when there are many alternatives. Procedures in \citeN{kim:2011},
+\citeN{dieker:2012} do not use the Bonferroni's inequality 
+when there are only three alternatives, but when they compare more than three
+alternatives, they do use the Bonferroni's inequality.
+
+Conservative algorithms lead to take more samples than needed, and consequently conservative procedures are unpopular 
+when there are more than a few hundred of alternatives. Three common sources of conservativeness are
+ the Bonferroni's inequality, the change from discrete process to continuous process, and bound the worst case which is not a common case.
+  \citeN{Frazier:BIZ} eliminates one source of conservativeness: the Bonferroni's inequality. He presented  a new sequential elimination
 IZ procedure, called BIZ (Bayes-inspired Indifference Zone), whose
@@
 discrete time. In numerical experiments, the number of samples required
-by BIZ is significantly smaller than that of the most popular IZ procedures,
+by BIZ is significantly smaller than that of procedures like the KN procedure of \citeN{Kim:2001} and
+the $\mathcal{P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968}, 
 especially on problems with many alternatives. Unfortunately, the
@@
 case assumes that variances are known and have an integer multiple
-structure which is not very realistic. In practice, variances are
-unknown. However, asymptotically we can use a central limit theorem
-that allows us to prove the asymptotic validity of the BIZ procedure
-for the discrete-time case. Moreover, we only need to assume that
-the systems are independent, identically distributed and have finite
-variance.
-
-Kim et al. (2006) also proves the asymptotical validity of a IZ procedure.
-Our proof is larger because the BIZ procedure is more sophisticated
-and the bound for the PCS is tighter. To prove the case when the variances
-are known, we use a theorem for Ergodic processes that shows how to
-standardize the output data to make them behave like Brownian motion
-processes in the limit. We also use an extension of the Continuous
-Mapping Theorem (Theorem 5.5 of Billingsley 1968) to see that the
-algorithm behaves like a sequential elimination IZ procedure with
-a Brownian motion process instead of the standardized sum of the output
-data in the limit, and then we use the results of the paper of Frazier
-\cite{key-5} to prove the validity of this algorithm in the limit.
-Finally, we use a random change of time argument to prove the case
-when the variances are unknown.
-
-This paper is organized as follows: In $\text{§}2$, we recall the
-indifference-zone ranking and selection problem. In $\text{§}3$,
-we recall the Bayes-inspired IZ (BIZ) procedure. In $\text{§}4$,
+structure which is not very realistic.
+
+The contribution of this work is that we prove the asymptotic validity of the 
+BIZ procedure for the discrete-time case when the variances are known and $\delta$ goes to zero. 
+In order to simplify analysis, we consider a slightly modification of this procedure.
+Although we only proved it in the known variance setting, it is still a significantly
+generalization over the assumption that the variances are known and have an integer multiple
+structure. Furthermore, we do not need to assume that the alternatives follow a normal distribution. 
+The only assumptios are that the alternatives are independent, identically distributed and have
+finite variance. We conjecture that these techniques can be used to show the validity of this procedure when
+the variances are unknown, and we present numerical experiments that support this belief. 
+\citeN{kim:asympt} also proves the asymptotical validity of a IZ procedure in the same limit.
+Our proof shares some similarities since we both use a central limit theorem.
+
+This paper is organized as follows: In $\text{ß}2$, we recall the
+indifference-zone ranking and selection problem. In $\text{ß}3$,
+we recall the Bayes-inspired IZ (BIZ) procedure from \citeN{Frazier:BIZ}. In $\text{ß}4$,
 we present the proof of the validity of the algorithm when the variances
-are known. In $\text{§}5$, we prove the case when the variances are
-unknown. In $\text{§}6$, we present some simulations showing the
-effectiveness of the algorithm. In $\text{§}7$, we conclude.
-
-\section{Indifference-Zone Ranking and Selection }
-
-Ranking and Selection is a procedure for selecting the best system
+are known. In $\text{ß}5$, we present some numerical experiments. 
+In $\text{ß}6$, we conclude.
+
+\section{INDIFFERENCE-ZONE RANKING AND SELECTION}
+
+Ranking and Selection is a problem where we have to select the best system
 among a finite set of alternatives, i.e. the system with the largest
 mean. The method selects a system as the best based on the samples
-that are observed sequentially over the time. If the best system is
-selected, we say that the procedure has made the \emph{correct selection}
+that are observed sequentially over time. We suppose that samples
+are identically distributed and independent, over time and across alternatives, and
+each alernative $x$ has mean $\mu_{x}$. We define $\mu=(\mu_{1},\ldots,\mu_{k})$.
+
+If the best system is selected, we say that the procedure has made the \emph{correct selection}
 (CS). We define the \emph{probability of correct selection} as 
 \[
-\mbox{PCS}\left(\mu,\lambda\right)=\mathbb{P}_{\mu,\lambda}\left(\hat{x}\in\mbox{arg max}_{x}\mu_{x}\right)
-\]
-where $\hat{x}$ is the alternative chosen by the procedure and $\mathbb{P}_{\mu,\lambda}$
+\mbox{PCS}\left(\mu\right)=\mathbb{P}_{\mu}\left(\hat{x}\in\mbox{arg max}_{x}\mu_{x}\right)
+\]
+where $\hat{x}$ is the alternative chosen by the procedure and $\mathbb{P}_{\mu}$
 is the probability measure under which samples from system $x$ have
@@
 \[
-\mbox{PCS}\left(\mu,\lambda\right)\geq P^{*}\mbox{ for all }\mu\in\mbox{PZ}\left(\delta\right).
+\mbox{PCS}\left(\mu\right)\geq P^{*}\mbox{ for all }\mu\in\mbox{PZ}\left(\delta\right).
 \]
@@
 
-\section{The Bayes-inspired IZ (BIZ) Procedure}
+\section{THE BAYES-INSPIRED IZ (BIZ) PROCEDURE}
 
 BIZ is an elimination procedure. This procedure maintains a set of
-alternatives that are in contention, and it takes samples from each
+alternatives that are candidates for the best system, and it takes samples from each
 alternative in this set at each point in time. At beginning, all alternatives
-are in contention, and over the time alternatives are eliminated.
+are possible candidates for the best system, and over the time alternatives are eliminated.
 The procedure ends when there is only one alternative in the contention
@@
 
-Frazier (2014) showed that the BIZ procedure with known common variance
+Frazier \cite{Frazier:BIZ} showed that the BIZ procedure with known common variance
 satisfies the IZ guarantee when the systems follow the normal distribution
@@
 The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
-variances is given in Alg. 2. It takes a variable number of samples
+variances is given below.  It takes a variable number of samples
 from each alternative, and $n_{tx}$ is this number. This algorithm
@@
 $B_{x}$ controls the number of samples taken from system $x$ in
-each stage.
+each stage. The procedure presented is a slightly modification of the original BIZ 
+procedure where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead 
+of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.
 
@@
 from alternative $x$ thus far and $Z_{tx}=Y_{n_{tx},x}$.
+
+\vspace{5mm}
 
@@
 In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$.
-The algorithm 2 can be generalized to the continuous case (See appendix B and Frazier (2014)).
-This procedure is a slightly modification of the original BIZ procedure where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.
-
-\section{Asymptotic Validity when the Variances are Known}
-
-In this section we prove that the BIZ procedure satisfies the IZ guarantee
-when the variances are known and $\delta\rightarrow0$, where the
-vector of the true means $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
-is equal to $\delta a$ for some $a\in\mathbb{R}^{k}$ and $\delta>0$.
-Without loss of generality suppose that the true means satisfy that
-$\mu_{k}>\mu_{k-1}\geq\cdots\geq\mu_{1}$. We suppose that samples
-from system $x\in\left\{ 1\ldots,k\right\} $ are identically distributed
+The algorithm 2 can be generalized to the continuous case (See  \citeN{Frazier:BIZ}).
+
+\section{ASYMPTOTIC VALIDITY WHEN THE VARIANCES ARE KNOWN}
+
+In this section we prove that the BIZ procedure satisfies asymptotically the IZ guarantee
+when the variances are known. This means that we consider a collection of
+ranking and selection problems parametrized by $\delta>0$.  
+For the problem given $\delta$, we suppose that the vector of the true means
+$\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$ is equal to $\delta a$ for some fixed $a\in\mathbb{R}^{k}$ that
+does not depend on $\delta$ and $a_{k}>a_{k-1}\geq \cdots \geq a_{1}$, $a_{k}-a_{k-1}>1$.
+Moreover, the variances of the alternatives are finite, strictly greater than zero and do not depend on $\delta$.
+We also suppose that samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically distributed
 and independent, over time and across alternatives. We also define
-$\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$
-and we suppose that $\mbox{min}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}>0$
-and $\mbox{max}{}_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}<\infty$.
+$\lambda_{z}^{2}:=\max_{i\in\left\{ 1\ldots,k\right\} }\lambda_{i}^{2}$.
 
@@
 topology. The definition and the properties of this topology may be
-found in Chapter 3 of Billingsley 1999 and the appendix.
+found in Chapter 3 of \citeN{billingsley:convergnce2}.
 
@@
 motion in the sense of $D_{\infty}$. 
-
-\paragraph*{Lemma 1.}
-
+\\
+\begin{lemma}
 For each $x\in\left\{ 1\ldots,k\right\} $, we define
@@
 
-\paragraph*{Proof.}
-
-By Theorem 19.1 of Billingsley 1999,
+\end{lemma}
+
+\begin{proof}
+By Theorem 19.1 of  \citeN{billingsley:convergnce2},
 
@@
 
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
+\end{proof}
 
@@
 if and only if $Z_{n}^{i}\rightarrow Z_{0}^{i}$ for all $i\in\left\{ 1,\ldots,k\right\} $.
-See the Miscellany of Billingsley 1968. The following corollary follows
+See the Miscellany of  \citeN{billingsley:convergence}. The following corollary follows
 from the previous result and independence.
 
-\paragraph*{Corollary 1.}
-
+\vspace{5mm}
+
+\begin{corollary}
 We have that
@@
 \]
-as $\delta\rightarrow0$ in the sense of $D_{\infty}^{k}$.\\
+as $\delta\rightarrow0$ in the sense of $D_{\infty}^{k}$.
+\end{corollary}
+
+\vspace{5mm}
 
@@
 
-In order to prove this, we first prove a continuity property in Lemma
-2, which will allow us to use Theorem 5.5 of Billingsley 1968, which
-implies the desired result.
-
-\paragraph*{Lemma 2.}
-
-Let $\left\{ \delta_{n}\right\} \subset\left(0,\infty\right)$ such
-that $\delta_{n}\rightarrow0$. If $D_{s}\equiv\{Z\in D\left[0,\infty\right)^{k}:\mbox{ if }\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}\mbox{ and }$
-$\mbox{lim}{}_{n}d_{\infty}\left(Z_{n},Z\right)=0$ , then the sequence
-$\left\{ f\left(Z_{n},\delta_{n}\right)\right\} $ converges to $\left\{ g\left(Z\right)\right\} $$\left.\right\} $$ $,
-then $ $$\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\right)=1$.\\
-
-First, we are going to prove the following five results.\\
-
-\paragraph*{Proposition 1.}
-
-Suppose $\left\{ f_{n}\right\} $ and $\left\{ g_{n}\right\} $ are
-two sequences of functions on $D_{\infty}$ such that $f_{n}\rightarrow f$
-and $g_{n}\rightarrow g$ in $D_{\infty}$. If $f$ and $g$ are continuous,
-then
-\[
-\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)
-\]
-in $D_{\infty}$.
-
-\paragraph*{Proof.}
-
-Let $t^{*}>0$. We will prove that $\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)$
-in $D_{t^{*}}$ and the theorem will follow from Theorem 16.2 of Billingsley
-1999.
-
-Since $f$ and $g$ are uniformly continuous in $\left[0,t^{*}\right]$
-and $f_{n}\rightarrow f$ and $g_{n}\rightarrow g$ in $\left[0,t^{*}\right]$,
-then $ $ $f_{n}$ and $g_{n}$ converge uniformly to $f$ and $g$,
-respectively. Consequently, $\left(f_{n},g_{n}\right)\rightarrow\left(f,g\right)$
-uniformly in $\left[0,t^{*}\right]$. Let $a_{f}^{+}=\mbox{max}_{t\in\left[0,t^{*}\right]}\left|f(t)\right|$,
-$a_{f}^{-}=-a_{f}^{+}$, $a_{g}^{+}=\mbox{max}_{t\in\left[0,t^{*}\right]}\left|g(t)\right|$
-and $a_{g}^{-}=-a_{g}^{+}$. Let $N$ such that if $n\geq N$, implies
-$\left|f_{n}\left(t\right)-f\left(t\right)\right|<1$ and $\left|g_{n}\left(t\right)-g\left(t\right)\right|<1$
-for all $t\in\left[0,t^{*}\right]$. Consequently, if $n\geq N$,$ $
-$f_{n}\left(t\right)\in\left[a_{f}^{-}-1,a_{f}^{+}+1\right]$ and
-$g_{n}\left(t\right)\in\left[a_{g}^{-}-1,a_{g}^{+}+1\right]$ for
-all $t$ in $\left[0,t^{*}\right]$. Since $\mbox{min}\left(x,y\right)$
-is continuous, then it is uniformly continuous in $A=\left[a_{f}^{-}-1,a_{f}^{+}+1\right]\times\left[a_{g}^{-}-1,a_{g}^{+}+1\right]$.
-
-Let $\epsilon>0$, then there exists $\delta>0$ such that if $\left\Vert \left(u,v\right)\right\Vert _{2}<\delta$
-and $ $$\left(u:=\left(u_{1},u_{2}\right),v:=\left(v_{1},v_{2}\right)\right)\in A$,
-then 
-\begin{equation}
-\left|\mbox{min}\left(u_{1},u_{2}\right)-\mbox{min}\left(v_{1},v_{2}\right)\right|<\epsilon.\label{eq:1.10}
-\end{equation}
-Let $M>N$ such that if $n>M$, then
-\[
-\left\Vert \left(f_{n}\left(t\right),g_{n}\left(t\right)\right)-\left(f\left(t\right),g\left(t\right)\right)\right\Vert _{2}<\delta
-\]
-for all $t\in\left[0,t^{*}\right]$. Consequently, if $n>M$, by (\ref{eq:1.10}),
-\[
-\left|\mbox{min}\left(f_{n}\left(t\right),g_{n}\left(t\right)\right)-\mbox{min}\left(f\left(t\right),g\left(t\right)\right)\right|<\epsilon
-\]
-for all $t\in\left[0,t^{*}\right]$. Since uniform convergence implies
-Skorohod convergence, then $\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)$
-in $D_{t^{*}}$, and the result follows.
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-\paragraph*{Proposition 2.}
-
-Suppose $\left\{ f_{n}\right\} $ is a sequence of functions in $D_{\infty}$
-such that $f_{n}\rightarrow f$ in $D_{\infty}$ , $f$ is continuous,
-and $\left\{ T_{n}\right\} \subset\left[0,\infty\right)$ is a sequence
-such that $T_{n}\rightarrow T$. We define $T\left(a\right):=\mbox{inf}\left\{ t\geq T:f\left(t\right)\geq a\right\} $
-for each $a\in\mathbb{R}$. Suppose $T\left(0\right)\in\mathbb{R}$.
-Furthermore, we suppose that there exists $\left\{ \epsilon_{n}\right\} \subset\left(0,\infty\right)$
-such that $\epsilon_{n}\rightarrow0$ , $\epsilon_{n}\geq\epsilon_{n+1}$,
-and$ $
-\begin{equation}
-\left\Vert f_{n}\left(t\right)-f\left(t\right)\right\Vert _{2}<\epsilon_{n}\label{eq:2.11}
-\end{equation}
-for all $t\in\left[0,T\left(0\right)\right]$. We also suppose that
-$\mbox{lim sup}_{n}T\left(\epsilon_{n}\right)\leq T\left(0\right)$.
-Thus we have that
-
-\[
-\mbox{inf}\left\{ t\geq T_{n}:f_{n}\left(t\right)\geq0\right\} \rightarrow\mbox{inf}\left\{ t\geq T:f\left(t\right)\geq0\right\} 
-\]
-if $T\left(0\right)>T$ or $T_{n}=T$.
-
-\paragraph*{Proof.}
-
-We are going to suppose $T\left(0\right)>T$, and the case $T_{n}=T$
-can be proved using almost the same ideas. We introduce the notation
-$T_{n}\left(a\right):\mbox{inf}\left\{ t\geq T_{n}:f_{n}\left(t\right)\geq a\right\} $
-for $a\in\mathbb{R}$. Since $T\left(0\right)>T$, we can take $N$
-such that if $n>N$, then $T_{n}<T+T\left(0\right)-T=T\left(0\right)$
-and $\epsilon>\epsilon_{n}$ where $\epsilon:=sup_{n}\epsilon_{n}$.
-Let $n>N$. Note that $T_{n}\left(0\right)\leq T_{n}\left(\epsilon_{n}\right)$.
-
-We also have that
-\begin{eqnarray}
-T\left(0\right) & \leq & \mbox{lim inf}_{n}T\left(\epsilon_{n}\right)\nonumber \\
- & \leq & \mbox{lim sup}_{n}T\left(\epsilon_{n}\right)\label{eq:2.3}
-\end{eqnarray}
-Now, since $\mbox{lim sup}_{n}T\left(\epsilon_{n}\right)\leq T\left(0\right)$,
-\begin{eqnarray*}
-T\left(0\right) & \geq & \mbox{lim sup}_{n}T\left(\epsilon_{n}\right)\\
- & \geq & \mbox{lim inf}_{n}T\left(\epsilon_{n}\right)\\
- & \geq & T\left(0\right)
-\end{eqnarray*}
-and so 
-\[
-\mbox{lim inf}_{n}T_{n}\left(0\right)\leq\mbox{lim sup}_{n}T_{n}\left(0\right)\leq\mbox{lim sup}_{n}T_{n}\left(\epsilon_{n}\right)=\mbox{lim}_{n}T\left(\epsilon_{n}\right)=T\left(0\right)
-\]
-
-Now, let's prove that $\mbox{lim inf}_{n}T_{n}\left(0\right)\geq T\left(0\right)$.
-Since $T\left(0\right)>T$, there exists $M$ such that $T\left(0\right)-\frac{1}{m}\geq T$
-if $m>M$, and let $t_{m}=T\left(0\right)-\frac{1}{m}$ and $\alpha_{m}=\mbox{max}\left\{ f\left(t\right):t\in\left[T,t_{m}\right]\right\} $.
-Note that $\alpha_{m}<0$ because $t_{m}<T\left(0\right)$. Since
-$\epsilon_{n}\rightarrow0$, there exists $N$ such that if $n>N$,
-then
-\[
-\epsilon_{n}\leq-\alpha_{m}
-\]
-Thus, since $\left\Vert f_{n}\left(t\right)-f\left(t\right)\right\Vert _{2}<\epsilon_{n}$
-if $t\in\left[T,t_{m}\right]$, then
-\begin{equation}
-f_{n}\left(t\right)<f\left(t\right)+\epsilon_{n}\leq f\left(t\right)-\alpha_{m}\leq0\label{eq:20.1}
-\end{equation}
-
-If $T\leq T_{n}\left(0\right)$ for all $n>N$, then $T_{n}\left(0\right)\geq t_{m}$
-by (\ref{eq:20.1}) and so $\mbox{lim inf}_{n}T_{n}\left(0\right)\geq t_{m}$.
-Taking the limit $m\rightarrow\infty$, we conclude that $\mbox{lim inf}_{n}T_{n}\left(0\right)\geq T\left(0\right)$.
-
-So, we only need to prove that $T\leq T_{n}\left(0\right)$ for $n$
-large. We proceed by contradiction. Let $s>0$ be any number. Take
-$N$ such that if $n>N$, then $\epsilon_{n}<s$. Since we are supposing
-that for all $N'$ there exists $n>N'$ such that $T>T_{n}\left(0\right)$,
-and $T_{n}\left(0\right)\geq T_{n}$, $T_{n}\rightarrow T$, then
-we have that for every $\epsilon>0$ there exists $n$ large such
-that $T-\epsilon<T_{n}\left(0\right)<T$ . By (\ref{eq:2.11}), 
-\begin{eqnarray*}
-f\left(T_{n}\left(0\right)\right) & \geq & f_{n}\left(T_{n}\left(0\right)\right)-\epsilon_{n}\\
- & \geq & -\epsilon_{n}>-s
-\end{eqnarray*}
-Let $a>0$, since $f$ is continuous there exists $\epsilon>0$ such
-that $f\left(x\right)<f\left(T\right)+a$ if $\left|x-T\right|<\epsilon$.
-Thus, there exists $n>N$ such that $T-\epsilon<T_{n}\left(0\right)<T$
-and so 
-\[
--s<f\left(T_{n}\left(0\right)\right)<f\left(T\right)+a
-\]
-
-Since $s$ and $a$ are arbitrary, 
-\[
-f\left(T\right)\geq0
-\]
-which is a contradiction because $T\left(0\right)>T$. Consequently,
-$T\leq T_{n}\left(0\right)$ and so
-\[
-\mbox{lim}_{n}T_{n}\left(0\right)=T\left(0\right).
-\]
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-\paragraph*{Proposition 3.}
-
-Let $\mathcal{S}$ be the event such that $W$ is continuous and $\mathbb{P}\left[\mathcal{S}\right]=1$.
-Fix $\omega\in\mathcal{S}$ and let $\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}$
-be a sequence of functions such that $Z_{n}\rightarrow W$ in $D^{k}\left[0,\infty\right)$,
-then 
-\begin{eqnarray*}
-f_{Z_{n}}\left(\cdot\right): & = & \mbox{max}\left\{ c-\mbox{min}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right),\mbox{max}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)-P\right\} \\
- & \rightarrow & f_{W}\left(\cdot\right):=\mbox{max}\left\{ c-\mbox{min}_{x\in A}q_{\cdot x}^{W}\left(A\right),\mbox{max}_{x\in A}q_{\cdot x}^{W}\left(A\right)-P\right\} 
-\end{eqnarray*}
-
-in $D\left[0,\infty\right)$ for any $P\in\left(0,1\right)$ and $ $$A\subset\left\{ 1,\ldots,k\right\} $.
-Furthermore, if $m\in\mathbb{N}$, there exists a sequence $\left\{ \epsilon_{k}\right\} $
-such that $\epsilon_{k}\downarrow0$ and 
-\[
-\left|f_{Z_{k}}\left(t\right)-f_{W}\left(t\right)\right|<\epsilon_{k}
-\]
-for all $t\in\left[0,m\right]$.
-
-\paragraph*{Proof.}
-
-\paragraph*{\textmd{Since $Z_{n}\rightarrow W$ in $D\left[0,\infty\right)$,
-by Theorem 16.2 of Billingsley 1999, for each $s\geq0$ there exist
-functions $\lambda_{s}^{n}$ in $\Lambda_{s}$ such that 
-\[
-\mbox{lim}_{n}Z_{n}\left(\lambda_{s}^{n}t\right)=W\left(t\right)
-\]
-uniformly in $t$ and
-\[
-\mbox{lim}_{n}\lambda_{s}^{n}t=t
-\]
-uniformly in $t$. Then
-\[
-\mbox{lim}_{n}\frac{\lambda_{x}^{2}\beta_{\delta}\left(\lambda_{s}^{n}t\right)}{\lambda_{z}\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{\lambda_{s}^{n}\left(t\right)}{\delta^{2}}\right)\right)}Z_{n}^{x}\left(\lambda_{s}^{n}t\right)+\delta_{n}^{2}\lambda_{x}^{2}\frac{\left(n_{0}+\lambda_{s}^{n}\left(t\right)\frac{1}{\delta_{n}^{2}}\right)\beta_{\delta}\left(\lambda_{s}^{n}\left(t\right)\right)}{\lambda_{z}^{2}\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{\lambda_{s}^{n}\left(t\right)}{\delta^{2}}\right)\right)}a_{x}=W_{x}\left(t\right)\frac{1}{\lambda_{z}}+\frac{t}{\lambda_{z}^{2}}a_{x}
-\]
-uniformly in $t$, and so
-\[
-\mbox{lim}_{n}\mbox{exp}\left(\frac{\lambda_{x}^{2}\beta_{\delta}\left(\lambda_{s}^{n}t\right)}{\lambda_{z}\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{\lambda_{s}^{n}\left(t\right)}{\delta^{2}}\right)\right)}Z_{n}^{x}\left(\lambda_{s}^{n}t\right)+\delta_{n}^{2}\lambda_{x}^{2}\frac{\left(n_{0}+\lambda_{s}^{n}\left(t\right)\frac{1}{\delta_{n}^{2}}\right)\beta_{\delta}\left(\lambda_{s}^{n}\left(t\right)\right)}{\lambda_{z}^{2}\mbox{ceil}\left(\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{\lambda_{s}^{n}\left(t\right)}{\delta^{2}}\right)\right)}\right)=\mbox{exp}\left(W_{x}\left(t\right)\frac{1}{\lambda_{z}}+\frac{t}{\lambda_{z}^{2}}a_{x}\right)
-\]
-uniformly in $t$ since $\mbox{exp}$ is uniformly continuous in $\left[0,s\right]$.
-Consequently,
-\[
-q_{\lambda_{s}^{n}\left(t\right)x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{tx}^{W}\left(A\right)
-\]
-uniformly in $t\in\left[0,s\right]$. Thus, $q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{\cdot x}^{W}\left(A\right)$
-in $D\left[0,s\right]$ for any set $A\subset\left\{ 1,\ldots,k\right\} $
-and $s\geq0$. Consequently, $q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow q_{\cdot x}^{W}\left(A\right)$
-in $D\left[0,\infty\right)$ by Theorem 16.2 of Billingsley 1999.
-By Proposition 1, $\mbox{min}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow\mbox{min}_{x\in A}q_{\cdot x}^{W}\left(A\right)$
-and $\mbox{max}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)\rightarrow\mbox{max}_{x\in A}q_{\cdot x}^{W}\left(A\right)$
-in $D\left[0,\infty\right)$, and so by Proposition 1,
-\[
-f_{Z_{n}}:=\mbox{max}\left\{ c-\mbox{min}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right),\mbox{max}_{x\in A}q_{\cdot x}^{Z_{n},\delta_{n}}\left(A\right)-P\right\} \rightarrow f_{W}:=\mbox{max}\left\{ c-\mbox{min}_{x\in A}q_{\cdot x}^{W}\left(A\right),\mbox{max}_{x\in A}q_{\cdot x}^{W}\left(A\right)-P\right\}
-\]
-in $D\left[0,\infty\right)$ for any $P\in\left(0,1\right)$.}}
-
-Now, let's prove the second part. Fix $m\in\mathbb{N}$. By the definition
-of $d_{m}\left(f_{Z_{n}},f_{W}\right)$, we have that there exists
-$\lambda_{n}\in\Lambda_{\infty}$ such that 
-\begin{eqnarray*}
-\mbox{sup}_{t\leq m}\left\Vert \lambda_{n}\left(t\right)-t\right\Vert _{2} & \leq & d_{m}\left(f_{Z_{n}},f_{W}\right)+\frac{1}{n}\\
-\mbox{sup}_{t\leq m}\left\Vert f_{Z_{n}}\left(t\right)-f_{W}\left(\lambda_{n}t\right)\right\Vert _{2} & \leq & d_{m}\left(f_{Z_{n}},f_{W}\right)+\frac{1}{n}
-\end{eqnarray*}
-for all $n$. Taking $g_{n}\equiv\mbox{sup}_{t\leq m}\left\Vert f_{W}\left(t\right)-f_{W}\left(\lambda_{n}t\right)\right\Vert _{2}$,
-we see from the uniform continuity of $f_{W}$ on $\left[0,m\right]$
-($f_{W}$ is uniformly continuous because it's continuos in a compact
-set) and the definition of $g_{n}$ that $\mbox{lim}_{n\rightarrow\infty}g_{n}=0.$
-Moreover, if we take $\epsilon_{n}=2n^{-1}+2\mbox{sup}\left\{ d_{m}\left(f_{Z_{l}},f_{W}\right)+g_{l}:l=n,n+1,\ldots\right\} $,
-then $\left\{ \epsilon_{n}\right\} $ is a monotonically decreasing
-sequence of positive numbers with limit zero by the previous result.
-
-From the definition of $\epsilon_{n}$ we have that $d_{m}\left(f_{Z_{n}},f_{W}\right)<\epsilon_{n}/2-\frac{1}{n}$
-and $g_{n}<\epsilon_{n}/2$ for $n=1,2,\ldots$ Consequently, we have
-\begin{eqnarray*}
-\left\Vert f_{Z_{n}}\left(t\right)-f_{W}\left(t\right)\right\Vert  & \leq & \left\Vert f_{Z_{n}}\left(t\right)-f_{W}\left(\lambda_{n}t\right)\right\Vert +\left\Vert f_{W}\left(\lambda_{n}t\right)-f_{W}\left(t\right)\right\Vert \\
- & < & d_{m}\left(f_{Z_{n}},f_{W}\right)+\frac{1}{n}+g_{n}\\
- & < & \epsilon_{n}
-\end{eqnarray*}
-for all $t\in\left[0,m\right]$.
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-\paragraph*{Proposition 4.}
-
-Let $W=\left(W_{1},\ldots,W_{k}\right)$ be a $k-$dimensional independent
-standard Brownian motion.
-Let $q_{tx}^{W}\left(A\right):=\mbox{exp}\left(\frac{1}{\lambda_{z}^{2}}\left(\lambda_{z}W_{x}\left(t\right)+ta_{x}\right)\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{1}{\lambda_{z}^{2}}\left(\lambda_{z}W_{x^{'}}\left(t\right)+ta_{x^{'}}\right)\right)$
-for all $x\in A$ and $A\subset\left\{ 1,\ldots,k\right\} $. Fix
-$m\in\left\{ 1,\ldots,k-1\right\} $. We have that for all $N\in\mathbb{N}$,
-there exists $t$ such that $\tau_{m}+\frac{1}{N}\geq t>\tau_{m}$
-and $q_{tx}^{W}\left(A_{m-1}\right)>P_{m-1}$ for some $x\in A_{m-1}$
-almost surely given that $M=m$. (See the definitions in p. 4).
-
-\paragraph*{Proof.}
-
-The proof has the same spirit than the proof of Lemma 4 of Frazier
-\cite{key-5}, there Frazier proved that $\tau_{m}<\infty$ almost
-surely. Furthermore, $M\leq k-1$ almost surely. We should note that
-the Lemma 4 supposes that all systems have the same variance which
-is the case here because $\mbox{Var}\left(\lambda_{z}W_{x}\left(t\right)+ta_{x}\right)=\lambda_{z}^{2}t$.
-We condition on the event $\mathcal{S}$ such that the previous properties
-hold and has probability $1$.
-
-Define $a=\lambda_{z}\mbox{log}\left(\frac{P_{m-1}\left(k-1\right)}{1-P_{m-1}}\right)$.
-If $m=1$, then $P_{m-1}=P^{*}\in\left(0,1\right)$, and so $a$ is
-finite. If $m>1$, then 
-\[
-P^{*}\leq P_{m-1}\leq P^{*}/\left(1-c\right)^{m-1}\leq P^{*}/\left(1-c\right)^{k-2}\leq P^{*}/\left(P^{*}\right)^{k-2/k-1}<1
-\]
-and so $P_{m-1}\in\left(0,1\right)$ and $a$ is finite.
-
-We define $T^{*}=\mbox{inf}\left\{ t\geq\tau_{m}:q_{t,x}^{W}\left(A_{m-1}\right)>P_{m-1}\mbox{ for some }x\in A_{m-1}\right\} $.
-Fix $n\in\mathbb{N}$, $n>2$, and define $\tau=\tau_{m}+\frac{t^{*}}{nN}$
-for a deterministic $t^{*}\in\left\{ 1,\ldots,n-1\right\} $. Let
-$x$ be any $\mathcal{F}_{\tau_{m}}$-measurable random variable that
-is almost surely in $A_{m-1}$ and we define $\Gamma_{t,x}=W_{x}\left(t\right)+t\frac{a_{x}}{\lambda_{z}}$.
-Consider the event $ $$a<\Gamma_{\tau+\frac{1}{nN},x}-\Gamma_{\tau+\frac{1}{nN},y}$
-for each $y\in A_{m-1}-\left\{ x\right\} $.
-On this event, $q_{\tau+\frac{1}{mN},y}^{W}\left(A_{m-1}\right)/q_{\tau+\frac{1}{mN},x}^{W}\left(A_{m-1}\right)=\mbox{exp}\left(\frac{1}{\lambda_{z}}\left(\Gamma_{\tau+\frac{1}{nN},y}-\Gamma_{\tau+\frac{1}{nN},x}\right)\right)<\mbox{exp}\left(-a/\lambda_{z}\right)$
-for $ $ $y\in A_{m-1}-\left\{ x\right\} $ and
-\[
-q_{\tau+\frac{1}{nN},x}\left(A_{m-1}\right)=\left[1+\sum_{y\in A_{m-1}-\left\{ x\right\} }q_{\tau+\frac{1}{nN},y}\left(A_{m-1}\right)/q_{\tau+\frac{1}{nN},x}\left(A_{m-1}\right)\right]^{-1}>\left[1+\left(k-1\right)\mbox{exp}\left(-a/\lambda_{z}\right)\right]^{-1}=P_{m-1}.
-\]
-Thus, on the event considered, $T^{*}\leq\tau+\frac{1}{nN}$.
-
-We now define $\tilde{x}\in\mbox{arg max}_{x\in A_{m-1}}\mbox{ }\Gamma_{\tau,x}$,
-which is $\mathcal{F}_{\tau}$-measurable and is almost surely in
-$A_{m-1}$. Then we have that
-\begin{eqnarray*}
-\mathbb{P}\left\{ T^{*}\leq\tau+\frac{1}{nN}\mid\mathcal{F}_{\tau},T^{*}>\tau\right\}  & \geq & \mathbb{P}\left\{ a<\Gamma_{\tau+\frac{1}{nN},\tilde{x}}-\Gamma_{\tau+\frac{1}{nN},x}\mbox{ \mbox{}}\forall x\in A_{m-1}-\left\{ \tilde{x}\right\} \mid\mathcal{F}_{\tau},T^{*}>\tau\right\} \\
- & \geq & \mathbb{P}\left\{ \Gamma_{\tau+\frac{1}{nN},\tilde{x}}\geq\Gamma_{\tau,\tilde{x}},\Gamma_{\tau,\tilde{x}}-\Gamma_{\tau+\frac{1}{nN},x}>a\mbox{ \mbox{}}\forall x\in A_{m-1}-\left\{ \tilde{x}\right\} \mid\mathcal{F}_{\tau},T^{*}>\tau\right\} \\
- & \geq & \mathbb{P}\left\{ \Gamma_{\tau+\frac{1}{nN},\tilde{x}}\geq\Gamma_{\tau,\tilde{x}},\Gamma_{\tau,x}-\Gamma_{\tau+\frac{1}{nN},x}>a\mbox{ \mbox{}}\forall x\in A_{m-1}-\left\{ \tilde{x}\right\} \mid\mathcal{F}_{\tau},T^{*}>\tau\right\} \\
- & = & \mathbb{P}\left\{ \Gamma_{\tau+\frac{1}{nN},\tilde{x}}\geq\Gamma_{\tau_{m},\tilde{x}}\mid\mathcal{F}_{\tau}\right\} \prod_{x\in A_{m-1}\setminus\left\{ \tilde{x}\right\} }\mathbb{P}\left\{ \Gamma_{\tau,x}-\Gamma_{\tau+\frac{1}{nN},x}>a\mid\mathcal{F}_{\tau}\right\} .
-\end{eqnarray*}
-Note that $\Gamma_{t,x}$ is a Brownian motion, and so $\mathbb{P}\left\{ \Gamma_{\tau+\frac{1}{nN},\tilde{x}}\geq\Gamma_{\tau_{m},\tilde{x}}\mid\mathcal{F}_{\tau_{m}}\right\} $
-is the probability of a conditionally $N\left(\frac{a_{\tilde{x}}}{nN}\frac{1}{\lambda_{z}},1\right)$
-random variable $\Gamma_{\tau+\frac{1}{nN},\tilde{x}}-\Gamma_{\tau,\tilde{x}}$,
-exceeding $0$. This probability is $\Phi\left(\frac{a_{\tilde{x}}}{nN}\frac{1}{\lambda_{z}}\right)$,
-which is bounded below by $ $$\Phi\left(\frac{\mbox{min}_{x}a_{x}}{N}\frac{x_{0}}{\lambda_{z}}\right)$
-where $x_{0}=0$ if $\mbox{min}_{x}a_{x}\geq0$, and $x_{0}=\frac{1}{3}$
-otherwise. Here, $\Phi$ is the normal cumulative distribution function.
-Similarly, the probability $\mathbb{P}\left\{ \Gamma_{\tau,x}-\Gamma_{\tau+\frac{1}{nN},x}>a\mid\mathcal{F}_{\tau_{m}}\right\} $
-is the probability of a conditionally $N\left(-a-\frac{a_{x}}{nN}\frac{1}{\lambda_{z}},1\right)$
-random variable, $\Gamma_{\tau,x}-\Gamma_{\tau+\frac{1}{nN},x}-a$,
-exceeding $0$. This probability is $\Phi\left(-a-\frac{a_{x}}{nN}\frac{1}{\lambda_{z}}\right)$,
-and is bounded below by $\Phi\left(-a-\frac{\mbox{max}_{x}a_{x}}{N}\frac{x_{0}^{+}}{\lambda_{z}}\right)$
-where $x_{0}^{+}=0$ if $\mbox{max}_{x}a_{x}\leq0$ and $x_{0}^{+}=\frac{1}{3}$
-otherwise.
-
-Thus, replacing $\tau$ with $\tau_{m}+\frac{t^{*}}{nN}$,
-\[
-\mathbb{P}\left\{ T^{*}\leq\tau_{m}+\frac{t^{*}}{nN}+\frac{1}{nN}\mid\mathcal{F}_{\tau_{m}+\frac{t^{*}}{nN}},T^{*}>\tau_{m}+\frac{t^{*}}{nN}\right\} \geq\Phi\left(\frac{\mbox{min}_{x}a_{x}}{N}\frac{x_{0}}{\lambda_{z}}\right)\Phi\left(-a-\frac{\mbox{max}_{x}a_{x}}{N}\frac{x_{0}^{+}}{\lambda_{z}}\right)^{k-1}
-\]
-Let $\epsilon$ be the quantity on the right-hand side of this inequality,
-then $\epsilon<1$ and it does not depend on $t^{*}$ and $n$.
-
-By repeated application of this inequality, we have that $\mathbb{P}\left\{ T^{*}>T_{W}^{1}\left(P\right)+\frac{1}{N}\mid\mathcal{F}_{\tau_{m}}\right\} \leq\left(1-\epsilon\right)^{n}$
-for all $n>2$. This is true because
-\begin{eqnarray*}
-\mathbb{P}\left\{ T^{*}>T_{W}^{1}\left(P\right)+\frac{1}{N}\mid\mathcal{F}_{\tau_{m}+\frac{n-1}{nN}},T^{*}>\tau_{m}+\frac{n-1}{nN}\right\}  & < & \left(1-\epsilon\right)\\
-\Rightarrow\mathbb{P}\left\{ T^{*}>\tau_{m}+\frac{1}{N}\mid\mathcal{F}_{T_{W}^{1}\left(P\right)+\frac{n-2}{nN}},T^{*}>\tau_{m}+\frac{n-2}{nN}\right\}  & < & \left(1-\epsilon\right)\mathbb{P}\left\{ T^{*}>\tau_{m}+\frac{n-1}{nN}\mid\mathcal{F}_{\tau_{m}++\frac{n-2}{nN}},T^{*}>\tau_{m}+\frac{n-2}{nN}\right\} \\
- & \leq & \left(1-\epsilon\right)^{2}\\
- & \vdots\\
-\Rightarrow\mathbb{P}\left\{ T^{*}>\tau_{m}+\frac{1}{N}\mid\mathcal{F}_{T_{W}^{1}\left(P\right)}\right\}  & \leq & \left(1-\epsilon\right)^{n}
-\end{eqnarray*}
-and $\left(1-\epsilon\right)^{n}$ vanishes in the limit as $n\rightarrow\infty$.
-Then, $\mathbb{P}\left\{ T^{*}>\tau_{m}+\frac{1}{N}\mid\mathcal{F}_{T_{W}^{1}\left(P\right)}\right\} =0$
-and then 
-\[
-\mathbb{P}\left\{ \tau_{m}\leq T^{*}\leq\tau_{m}+\frac{1}{N}\mid\mathcal{F}_{T_{W}^{1}\left(P\right)}\right\} =1
-\]
- for all $N$.
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-The following proposition can be proved using a similar argument.
-
-\paragraph*{Proposition 5.}
-
-Let $W=\left(W_{1},\ldots,W_{k}\right)$ be a $k-$dimensional independent
-standard Brownian motion.
-Let $q_{tx}^{W}\left(A\right):=\mbox{exp}\left(\frac{1}{\lambda_{z}^{2}}\left(\lambda_{z}W_{x}\left(t\right)+ta_{x}\right)\right)/\sum_{x^{'}\in A}\mbox{exp}\left(\frac{1}{\lambda_{z}^{2}}\left(\lambda_{z}W_{x^{'}}\left(t\right)+ta_{x^{'}}\right)\right)$
-for all $x\in A$ and $A\subset\left\{ 1,\ldots,k\right\} $. Fix
-$m\in\left\{ 1,\ldots,k-1\right\} $. We have that for all $N\in\mathbb{N}$,
-there exists $t$ such that $\tau_{m}-\frac{1}{N}\leq t<\tau_{m}$
-and $q_{tx}^{W}\left(A_{m-1}\right)<c$ for some $x\in A_{m-1}$ almost
-surely given that $M=m$. \\
-
-We are now ready to prove the lemma 2.
-
-\paragraph*{Lemma 2.}
+In order to prove this, we first proved a continuity property in Lemma
+2, which allows us to use Theorem 5.5 of \citeN{billingsley:convergence}, which
+implies the desired result. A proof of Lemma 2 may be found in a full version which will be
+submitted soon to arXiv. 
+\\
+\begin{lemma}
 
@@
 
-\paragraph*{Proof of Lemma 2.}
-
-By Lemma 4 and 6 of Frazier, $\tau_{n}<\infty$ for $n=0,1,\ldots,k-1$,
-$M\leq k-1$,$\tau_{n}=\tau_{M}$ for all $n\geq M$, $\hat{x}\in\mbox{arg max}_{x\in A_{m-1}}\left(\lambda_{z}W_{x}\left(\tau_{M}\right)+a_{x}\tau_{M}\right)$
-and $\tau_{M-1}<\tau_{M}$ with probability 1. Then there exists a
-measurable set $\mathcal{L}$ such that $\mathbb{P}\left[\mathcal{L}\right]=1$
-and the previous properties are true, $W$ is continuous and Proposition
-4 and 5 hold. We will show that $\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\mid M_{W}=i,\mathcal{L}\right)=1$
-for $i\in\left\{ 1,\ldots,k-1\right\} $ so that the desired conclusion
-follows. It will be useful to use the same notation than in Proposition
-2: 
-\begin{eqnarray*}
-T_{W}^{m}\left(a\right) & = & \begin{cases}
-\mbox{inf}\left\{ t\geq\tau_{m-1}:\mbox{max}_{x\in A_{m-1}}q_{tx}^{W}\left(A_{m-1}\right)\geq a\right\}  & \mbox{if }m\geq M_{W}\\
-\mbox{inf}\left\{ t\geq\tau_{m-1}:\mbox{min}_{x\in A_{m-1}}q_{tx}^{W}\left(A_{m-1}\right)\leq a\right\}  & \mbox{if }m<M_{W}
-\end{cases}
-\end{eqnarray*}
- and 
-\[
-T_{n}^{m}\left(a\right):=\mbox{inf}\left\{ t\geq\tau_{m-1}:\mbox{max}_{x\in A_{m-1}}q_{tx}^{Z_{n},\delta_{n}}\left(A_{m-1}\right)\geq a\mbox{ or }\mbox{min}_{x\in A_{m-1}}q_{tx}^{Z_{n},\delta_{n}}\left(A_{m-1}\right)\leq c\right\}
-\]
- for any $a\in\mathbb{R}$ and $1\leq m\leq k-1$.
-
-\subparagraph*{Case I.}
-
-First, we fix $\omega\in\mathcal{L}\bigcap\left\{ M_{W}=1\right\} $.
-Let $\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}$ such
-that $Z_{n}\rightarrow W$. We want to prove that $f\left(Z_{n},\delta_{n}\right)\rightarrow g\left(W\right)$.
-Let's prove that $\tau_{1}^{Z_{n},\delta_{n}}\rightarrow\tau_{1}^{W}$
-as $n\rightarrow\infty$.
-
-First, we are going to prove that $ $$T_{W}^{1}\left(P_{0}\right)=\mbox{lim}_{n}T_{W}^{1}\left(P_{0}+\epsilon_{n}\right)$.
-Note that $ $ $\mbox{lim}_{n}T_{W}^{1}\left(P_{0}+\epsilon_{n}\right)=\mbox{inf}_{n}T_{W}^{1}\left(P_{0}+\epsilon_{n}\right)$
-and so we have to prove that for all $M>0$ there exists $n$ such
-that $T_{W}^{1}\left(P_{0}+\epsilon_{n}\right)<T_{W}^{1}\left(P_{0}\right)+M.$
-Equivalently, we should prove that for all $N\in\mathbb{N}$ there
-exists $t\in\left(T_{W}^{1}\left(P_{0}\right),T_{W}^{1}\left(P_{0}\right)+\frac{1}{N}\right]$
-such that for some $x\in A_{0}$, $q_{t,x}^{W}\left(A_{0}\right)>P_{0}$.
-However, this is true by proposition 4.
-
-By Proposition 2 and 3,
-\begin{equation}
-T_{W}^{1}\left(P_{0}\right)=\mbox{lim}_{n}T_{n}^{1}\left(P_{0}\right).\label{eq:10.1}
-\end{equation}
-
-By Proposition 3, we have that $f_{Z_{n}}\left(\cdot\right)\rightarrow f_{W}\left(\cdot\right)$
-uniformly in $\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$ and so
-it should be the case that $\mbox{max}_{x\in A_{0}}q_{T_{n}^{1}\left(P_{0}\right)x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\geq P_{0}$
-for $n$ large.
-
-Recall that $\hat{x}\in\gamma:=\mbox{arg max}_{x\in A_{0}}\left(\lambda_{z}W_{x}\left(T_{W}^{1}\left(P_{0}\right)\right)+a_{x}T_{W}^{1}\left(P_{0}\right)\right)$.
-
-Let $\epsilon=\left(q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-\mbox{arg max}_{x\in A_{0}-\gamma}q_{T_{W}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)\right)/4$.
-Since the function $q_{\cdot,x}^{W}\left(A_{0}\right)$ is uniformly
-continuous in $\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$ for
-all $x\in A_{0}$, then there exists $\delta>0$ such that if $\left|t-s\right|<\delta$
-and $t,s\in\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$, then 
-\[
-\left|q_{t,x}^{W}\left(A_{0}\right)-q_{s,x}^{W}\left(A_{0}\right)\right|<\frac{\epsilon}{2}
-\]
-for all $x\in A_{0}$. By the proof of Proposition 3, $q_{\cdot,x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\rightarrow q_{\cdot,x}^{W}\left(A_{0}\right)$
-in $\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$ with the Skorohod
-topology, and then $q_{\cdot,x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\rightarrow q_{\cdot,x}^{W}\left(A_{0}\right)$
-uniformly in $\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$ because
-$q_{\cdot,x}^{W}\left(A_{0}\right)$ is uniformly continuous in $\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$
-for all $x\in A_{0}$. Consequently, there exists $N_{1}$ such that
-if $n>N_{1}$, then $\left|q_{t,x}^{W}\left(A_{0}\right)-q_{t,x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right|<\frac{\epsilon}{2}$
-for all $t\in\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$ and all
-$x\in A_{0}$. By (\ref{eq:10.1}), there exists $N_{2}$ such that
-if $n>N_{2}$, then $\left|T_{W}^{1}\left(P_{0}\right)-T_{n}^{1}\left(P_{0}\right)\right|<\delta$
-and $T_{n}^{1}\left(P_{0}\right)\in\left[0,T_{W}^{1}\left(P_{0}\right)+1\right]$.
-So if $n>\mbox{max}\left\{ N_{1},N_{2}\right\} $, we have that
-
-\begin{eqnarray*}
-\left|q_{T_{W}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)-q_{T_{n}^{1}\left(P_{0}\right),x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right| & = & \left|q_{T_{W}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)-q_{T_{n}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)\right|+\left|q_{T_{n}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)-q_{T_{n}^{1}\left(P_{0}\right),x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right|\\
- & < & \frac{\epsilon}{2}+\frac{\epsilon}{2}=\epsilon
-\end{eqnarray*}
-
-for all $x\in A_{0}$.
-
-By Proposition 3, there exists a sequence $\left\{ \epsilon_{n}\right\} _{n>N^{*}}$
-decreasing to zero for some $N^{*}$ such that if $n>N^{*}$ .
-\[
-\left|q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-\mbox{max}_{x\in A_{0}}q_{T_{n}^{1}\left(P_{0}\right),x}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right|<\epsilon_{n}.
-\]
-
-Let $y_{n}\in\mbox{arg max}q_{T_{n}^{1}\left(P_{0}\right),y}^{Z_{n},\delta_{n}}\left(A_{0}\right)$.
-Thus if $n>\mbox{max}\left\{ N^{*},N_{1},N_{2}\right\} $, then
-\begin{eqnarray*}
-\left|q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-q_{T_{W}^{1}\left(P_{0}\right),y_{n}}^{W}\left(A_{0}\right)\right| & \leq & \left|q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-q_{T_{n}^{1}\left(P_{0}\right),y_{n}}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right|+\left|-q_{T_{W}^{1}\left(P_{0}\right),y_{n}}^{W}\left(A_{0}\right)+q_{T_{n}^{1}\left(P_{0}\right),y_{n}}^{Z_{n},\delta_{n}}\left(A_{0}\right)\right|\\
- & < & \epsilon_{n}+\epsilon
-\end{eqnarray*}
-
-Take $N_{3}$ such that if $n>N_{3}$, then $\epsilon_{n}<\epsilon$.
-Consequently, if $n>\mbox{max}\left\{ N_{3},N_{1},N_{2},N^{*}\right\} $,
-we have that
-\begin{eqnarray*}
-\left|q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-q_{T_{W}^{1}\left(P_{0}\right),y_{n}}^{W}\left(A_{0}\right)\right| & < & \frac{q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-\mbox{arg max}_{x\in A_{0}-\gamma}q_{T_{W}^{1}\left(P_{0}\right),x}^{W}\left(A_{0}\right)}{2}
-\end{eqnarray*}
-if $y_{n}\neq\hat{x}$, then
-\[
-\left|q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-q_{T_{W}^{1}\left(P_{0}\right),y_{n}}^{W}\left(A_{0}\right)\right|<\frac{q_{T_{W}^{1}\left(P_{0}\right),\hat{x}}^{W}\left(A_{0}\right)-q_{T_{W}^{1}\left(P_{0}\right),y_{n}}^{W}\left(A_{0}\right)}{2}
-\]
-which is a contradiction. Consequently, $y_{n}=\hat{x}$ for $n$
-large. Consequently, $f\left(Z_{n},\delta_{n}\right)$ converges to
-$g\left(W\right)$.
-
-\subparagraph*{Case II.}
-
-Now, we fix we fix $\omega\in\mathcal{L}\bigcap\left\{ M_{W}=2\right\} $.
-Similarly, we take $\left\{ Z_{n}\right\} \subset D\left[0,\infty\right)^{k}$
-such that $Z_{n}\rightarrow W$. Let's prove that $\tau_{1}^{Z_{n},\delta_{n}}\rightarrow\tau_{1}^{W}$.
-First, we are going to prove that $ $$T_{W}^{1}\left(c\right)=\mbox{lim}_{n}T_{W}^{1}\left(c-\epsilon_{n}\right)$.
-Note that $ $ $\mbox{lim}_{n}T_{W}^{1}\left(c-\epsilon_{n}\right)=\mbox{inf}_{n}T_{W}^{1}\left(c-\epsilon_{n}\right)$
-and so we have to prove that for all $M>0$ there exists $n$ such
-that $T_{W}^{1}\left(c-\epsilon_{n}\right)<T_{W}^{1}\left(c\right)+M.$
-Equivalently, we should prove that for all $N\in\mathbb{N}$ there
-exists $t\in\left(T_{W}^{1}\left(c\right),T_{W}^{1}\left(c\right)+\frac{1}{N}\right]$
-such that for some $x\in A_{0}$, $q_{t,x}^{W}\left(A_{0}\right)<c$.
-However, this is true by proposition 5. By Proposition 2 and 3, $T_{W}^{1}\left(c\right)=\mbox{lim}_{n}T_{n}^{1}\left(P_{0}\right).$
-Using similar arguments than the given in Case I, we can conclude
-that $f\left(Z_{n},\delta_{n}\right)$ converges to $g\left(W\right)$.\\
-
-The cases $M_{W}=i$ for $k-1\geq i\geq3$ can be proved in a similar
-way. Then we conclude that $\mathbb{P}\left(W\in D_{s}\right)=1.$
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-\[
-\]
-
-By the extension of the CMT (Theorem 5.5 of Billingsley 1968), we
+\end{lemma}
+\vspace{5mm}
+By the extension of the CMT \cite{billingsley:convergence}, we
 have the following corollary.
-
-\paragraph*{Corollary 2.}
+\vspace{5mm}
+
+\begin{corollary}
 
@@
 \]
-
-\paragraph*{Theorem 1.}
-
+\end{corollary}
+\vspace{1mm}
+
+\begin{theorem}
 If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
@@
 provided $\mu_{k}=a_{k}\delta,\mu_{k-1}=a_{k-1}\delta,\ldots,\mu_{1}=a_{1}\delta$,
-and $\mu_{k}>\mu_{k-1}>\cdots>\mu_{1}$.
+$a_{k}>a_{k-1}\geq \cdots \geq a_{1}$, $a_{k}-a_{k-1}>1$, and the variances are finite and
+do not depend on $\delta$.
 
@@
 \]
-where $PZ\left(1\right)=\left\{ a\in\mathbb{R}^{k}:a_{k}-a_{k-1}\geq1\right\} $.
-
-\paragraph*{Proof.}
+where $PZ\left(1\right)=\left\{ a\in\mathbb{R}^{k}:a_{k}-a_{k-1}>1, a_{k}>a_{k-1}\geq \cdots \geq a_{1} \right\} $.
+
+\end{theorem}
+
+\begin{proof}
 
@@
 We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
-which are defined as $\tau_{n+1}=\mbox{inf}\left\{ t\geq\tilde{\tau}_{n}:\mbox{ min}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\geq P_{n}\right\} $.
+which are defined as
+
+\[
+\tau_{n+1}=\mbox{inf}\left\{ t\geq\tau_{n}:\mbox{ min}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\geq P_{n}\right\} .
+\]
 
@@
 \end{eqnarray*}
-where the last inequality follows from the Theorem 2 of Frazier \cite{key-5}.
+where the last inequality follows from the Theorem 2 of \citeN{Frazier:BIZ}.
 
@@
 
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}\;\;\;\;}$
-
-\section{Asymptotic Validity when the Variances are Unknown}
-
-We use a random change of time to prove that the new $\hat{\mathcal{C}}_{x}$
-defined using the sample variances also converges to a Brownian motion
-in the sense of $D_{\infty}$.
-
-\paragraph*{Lemma 3.}
-
-We have that
-\[
-\hat{\mathcal{C}}_{x}\left(\delta,\cdot\right):=\frac{Y_{\mbox{ceil}\left(\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\right),x}-\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\mu_{x}}{\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}}\frac{1}{\delta}}\Rightarrow W_{x}\left(\cdot\right)
-\]
-
-in the sense of $D_{\infty}$ for each $x\in A$, where $\hat{\lambda}_{t/\delta^{2},x}^{2}=\frac{1}{n_{t/\delta^{2},x}-1}\sum_{i=1}^{n_{t/\delta^{2},x}}\left(X_{xi}-Y_{n_{t/\delta^{2},x}}\right)^{2}$.
-
-\paragraph*{Proof. }
-
-Fix $x\in A$. Define $\Psi_{\delta}:\left[0,\infty\right)\rightarrow\left[0,\infty\right)$
-by $\Psi_{\delta}\left(t\right)=-n_{0}\delta^{2}+\frac{\lambda_{z}^{2}}{\lambda_{x}^{2}}\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}^{2}}\left(t+\delta^{2}n_{0}\right)$,
-then $\Psi_{\delta}\in D_{\infty}$. Now define $\varphi:D_{\infty}\times D_{\infty}\rightarrow D_{\infty}$
-by
-\[
-\varphi\left(\mathcal{X},\mathcal{Y}\right)=\mathcal{X}\circ\mathcal{Y}
-\]
-
-Using Lemma 1, we have that $\left(\mathcal{C}_{x}\left(\delta,\cdot\right),\Psi_{\delta}\left(\cdot\right)\right)\Rightarrow\left(W_{x}\left(\cdot\right),I\left(\cdot\right)\right)$
-as $\delta\rightarrow0$ in the sense of $D_{\infty}$. We can prove
-that $\varphi$ is measurable, and since $W_{x}$ is continuous almost
-surely, we can use a generalization of the Lemma from the chapter
-Random Change of Time of Billingsley (1999) to conclude that $\varphi\left(\mathcal{C}_{x}\left(\delta,\cdot\right),\Psi_{\delta}\left(\cdot\right)\right)\Rightarrow\varphi\left(W_{x}\left(\cdot\right),I\left(\cdot\right)\right)=W_{x}\left(\cdot\right)$
-in the sense of $D_{\infty}$ as we wanted to prove.
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}\;\;\;\;}$\\
-
-In the previous proof, we only have to replace $\lambda_{x}^{2}$
-by its estimators and we get the same result. We should note that
-\[
-\mbox{ceil}\left(\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}^{2}}\left(n_{0}+\cdot\frac{1}{\delta^{2}}\right)\right)-n_{t/\delta^{2},x}\rightarrow0
-\]
-for any $x$. Consequently, we will have that
-\[
-\frac{Y_{n_{t/\delta^{2},x},x}-n_{t/\delta^{2},x}\mu_{x}}{\frac{\hat{\lambda}_{t/\delta^{2},x}^{2}}{\hat{\lambda}_{t/\delta^{2},z}}\frac{1}{\delta}}\Rightarrow W_{x}\left(\cdot\right)
-\]
-
-So, we have the following theorem.
-
-\paragraph*{Theorem 2.}
-
-If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
-distributed and independent, over time and across alternatives, then
-$\mbox{lim}_{\delta\rightarrow0}Pr\left\{ \mbox{BIZ selects }k\right\} \geq P*$
-provided $\mu_{k}=a_{k}\delta,\mu_{k-1}=a_{k-1}\delta,\ldots,\mu_{1}=a_{1}\delta$,
-and $\mu_{k}>\mu_{k-1}>\cdots>\mu_{1}$.
-
-Furthermore,
-\[
-\mbox{inf}_{a\in PZ\left(1\right)}\mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right)=P^{*}
-\]
-where $PZ\left(1\right)=\left\{ a\in\mathbb{R}^{k}:a_{k}-a_{k-1}\geq1\right\} $.
-
-\section{Probability of Good Selection}
-
-Ideally, we would like that the difference between the chosen system
-and the best system is practically insignificant. We thus define the
-probability of good selection as
-\[
-\mbox{PGS}\left(\mu\right)=\mathbb{P}\left(\mu_{k}-\mu_{\hat{x}}\leq\delta\right).
-\]
-
-We would like to prove the PGS guarantee:
-\[
-\forall\mu,\mbox{ PGS}\left(\mu\right)\geq P^{*}.
-\]
-First, observe that if $\mu_{k}-\mu_{k-1}>\delta$, then $\mbox{PGS}\left(\mu\right)=\mbox{PCS}\left(\mu\right)$
-and so $\mbox{PGS}\left(\mu\right)\geq P^{*}$. Consequently, we only
-need to prove that if $\mu_{k}-\mu_{k-1}\leq\delta$, then we have
-that $\mbox{PGS}\left(\mu\right)\geq P^{*}$.
-
-Inspired on Frazier (2014), we first construct a probability measure
-$Q$ as follows. Let $X^{*}$ be chosen uniformly at random from among
-$1,\ldots,k$ and let $\theta_{X^{*}}=\delta$ and $\theta_{x}=0$
-if $x\neq X^{*}$. We then define a family of probability measures
-$Q_{u}$ that i
-
-\section{Simulations}
-
-\section{Conclusion}
+\end{proof}
+
+\section{NUMERICAL EXPERIMENTS}
+
+We show the performance of the BIZ procedure in discrete time with maximum elimination
+($c=1-(P^*)^\frac{1}{k-1}$)when $\delta$ goes to zero. We plot both the PCS and the expected total number 
+of samples simulated divided by the number of systems, denoted by $E[N]/k$. We consider this quotient 
+to normalize the number of samples used by the algorithm.
+
+First, we consider the known variance case. Specifically, we consider a slippage configuration 
+with $100$ systems normally distributed, where $\mu_{k}=\delta,\mu_{k-1}=0,\dots,\mu_{1}=0$, $\delta$ is 
+within the interval $[0.1,10]$, and $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5$. Here, $P^*=0.9$ and $n_{0}=0$.
+Figure ~\ref{fig: tahi3} shows that in this case the IZ guarantee is always satisfied, and the bound on probability of correct selection is tight when $\delta$ goes to zero.
+When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the
+BIZ procedure.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{plot5}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{plot6}
+    \end{subfigure}
+    \caption{Known variances and $P^*=0.9$. $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5,n_{0}=0$.
+    In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero.
+    \label{fig: tahi3}}
+\end{figure}
+
+We now consider the unknown variance case. Specifically, we consider a slippage configuration 
+with $100$ systems normally distributed, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is 
+within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. Here, $P^*=0.9$ and $n_{0}=15$.
+Figure ~\ref{fig: tahi2} gives us evidence that our theorem should also be true when the variances are unknown. We should note that
+this is a difficult example, and still we have a good performance in most of the cases. However, if we want to always satisfy the IZ guarantee, 
+we can just increment the parameter $n_{0}$.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{plot3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{plot4}
+    \end{subfigure}
+    \caption{Unknown variances and $P^*=0.9$. $\lambda_{100}=10\sqrt(2),\lambda_{99}=10+\frac{(10)(98)}{99}(\sqrt(2)-1),\cdots,\lambda_{1}=10,n_{0}=15$.
+    In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero. If we want that the IZ guarantee be 
+    satisfied in all the cases, we can just increment $n_{0}$.
+    \label{fig: tahi2}}
+\end{figure}
+
+ Now, we consider a pathological case when the variances are known. Specifically, we consider a slippage configuration 
+with $100$ systems normally distributed, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is 
+within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. Here, $P^*=0.9$ and $n_{0}=0$.
+This configurations was specially chosen to ilustrate our theorem, and so it is harder than typical configurations.
+In fact, in most of the configurations the algorithm always satisfies the IZ guarantee. Furthermore, in practice, we would
+have run the algorithm with $n_{0}>0$, and the BIZ algorithm would have worked well even in this pathological example. 
+Figure ~\ref{fig: tahi} shows that PCS converges to $0.9$ as $\delta$ goes to zero. Specifically, PCS is equal to $0.904$ when $\delta=0.1$.
+This figure also shows that the bound is tight  on probability of correct selection. We should also note that the number of samples required increases very fast. 
+Here, the points plotted have central confidence intervals of length at most $0.014$.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{plot1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{plot2}
+    \end{subfigure}
+    \caption{Known variances, $P^*=0.9$, $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1,n_{0}=0$. This was a hard example to find
+    and it was specially chosen to ilustrate our theorem. In practice, we would choose $n_{0}>0$ and the IZ guarantee will be satisfied. \label{fig: tahi}}
+\end{figure}
+
+\section{CONCLUSION}
 
 We have proved the asymptotic validity of the Bayes-inspired Zone
-procedure (Frazier 2014) when the variances are known, which is a
+procedure \cite{Frazier:BIZ} when the variances are known, which is a
 new sequential elimination procedure. This algorithm is relevant because
@@
 
-\section*{Appendix A: Skorohod topology}
-
-We are going to define the Skorohod topology on $D[0,\infty)$ by
-defining a metric on the space. The Skorohod metric $d_{t}$ on $D\left[0,t\right]$
-for each $t\geq0$ is:
-\[
-d_{t}\left(\mathcal{X},\mathcal{Y}\right)=\mbox{inf}_{\lambda\in\Lambda_{t}}\left\{ \left\Vert \lambda-I\right\Vert \vee\left\Vert \mathcal{X}-\mathcal{Y}\circ\lambda\right\Vert \right\} 
-\]
-where $\Lambda_{t}$ is the set of strictly increasing, continuous
-mappings of $\left[0,t\right]$ onto itself, and $\left\Vert \cdot\right\Vert $
-is the uniform norm, and $I$ is the identity map. Note that uniform
-convergence on $\left[0,t\right]$ implies Skorohod convergence.
-
-We define the Skorohod topology on $D\left[0,\infty\right)$. For
-$\mathcal{X}\in D\left[0,\text{\ensuremath{\infty}}\right)$, let
-$\mathcal{X}^{m}$ be the element of $D_{\infty}:=D[0,\infty)$ defined
-by
-\[
-\mathcal{X}^{m}\left(t\right)=g_{m}\left(t\right)\mathcal{X}\left(t\right)
-\]
-where 
-\[
-g_{m}\left(t\right)=\begin{cases}
-1 & \mbox{if }t\leq m-1,\\
-m-t & \mbox{if }m-1\leq t\leq m,\\
-0 & \mbox{if }t\geq m.
-\end{cases}
-\]
-And now take
-\[
-d_{\infty}\left(\mathcal{X},\mathcal{Y}\right)=\sum_{m=1}^{\infty}2^{-m}\left(1\wedge d_{m}\left(\mathcal{X}^{m},\mathcal{Y}^{m}\right)\right)
-\]
-which is the Skorohod metric on $D\left[0,\infty\right)$. By Theorem
-16.2 of Billingsley1999, there is convergence $d_{\infty}\left(x_{n},x\right)\rightarrow0$
-in $D_{\infty}$ if and only if $d_{t}\left(x_{n},x\right)\rightarrow0$
-for each continuity point $t$ of $x$.
-
-We can also define
-
-\[
-d_{\infty}^{\circ}\left(\mathcal{X},Y\right)=\sum_{m=1}^{\infty}2^{-m}\left(1\wedge d_{m}^{\circ}\left(\mathcal{X}^{m},\mathcal{Y}^{m}\right)\right)
-\]
-where $d_{m}^{\circ}\left(\mathcal{X}^{m},\mathcal{Y}^{m}\right)=\mbox{inf}_{\lambda\in\Lambda_{m}}\left\{ \mbox{sup}_{s<t}\left|\mbox{log}\frac{\lambda t-\lambda s}{t-s}\right|\vee\left\Vert \mathcal{X}-\mathcal{Y}\circ\lambda\right\Vert \right\} $.
-This is also a metric and the proof is in Bilingsley 1999 and these
-two metrics are equivalent.
-
-\subparagraph*{Theorem A.1}
-
-We have that $d_{\infty}\left(\mathcal{X}_{n},\mathcal{Y}_{n}\right)\rightarrow0$
-if and only if $d_{\infty}^{\circ}\left(\mathcal{X}_{n},\mathcal{Y}_{n}\right)\rightarrow0$
-and $d_{t}\left(\mathcal{X}_{n},\mathcal{Y}_{n}\right)\rightarrow0$
-if and only if $d_{t}^{\circ}\left(\mathcal{X}_{n},\mathcal{Y}_{n}\right)\rightarrow0$
-for all $t\geq0$.
-
-\subparagraph*{Theorem A.2}
-
-Suppose we have two sequences of random paths $\left\{ \mathcal{X}_{n}=\left(X_{n}\left(t\right):0\leq t<\infty\right)\right\} _{n\geq0}^{\infty}$,$\left\{ \mathcal{Y}_{n}=\left(Y_{n}\left(t\right):0\leq t<\infty\right)\right\} _{n\geq1}^{\infty}$
-such that $\mathcal{X}_{n},\mathcal{Y}_{n}:\mathcal{F}\rightarrow D_{\infty}$
-for all $n\geq0$ where $\left(\Omega,\mathcal{F},\mathbb{P}\right)$
-is our space of probability. Suppose that $\mathcal{X}_{n}\Rightarrow\mathcal{X}_{0}$
-in the sense of $D\left[0,\infty\right)$ and $\mathcal{X}_{n}-\mathcal{Y}_{n}\rightarrow0$
-uniformly in $\left[0,m\right]$ for all $m\in\mathbb{N}$ with probability
-1, then $\mathcal{Y}_{n}\Rightarrow\mathcal{X}_{0}$.
-
-\subparagraph*{Proof.}
-
-We only need to prove that $d_{\infty}\left(\mathcal{X}_{n},\mathcal{Y}_{n}\right)\rightarrow0$
-almost surely and the result will follow by Theorem 3.1 of Billingsley
-1999. Then we only need to prove that $d_{m}\left(\mathcal{Y}_{n}^{m},\mathcal{X}_{n}^{m}\right)\rightarrow0$
-almost surely for all $m\in\mathbb{N}$. Fix $\omega\in\Omega$ and
-$m\in\mathbb{N}$ such that $\mathcal{X}_{n}-\mathcal{Y}_{n}\rightarrow0$
-uniformly in $\left[0,m\right]$. Observe that 
-\begin{eqnarray*}
-d_{m}\left(\mathcal{Y}_{n}^{m},\mathcal{X}_{n}^{m}\right) & = & \mbox{inf}_{\lambda\in\Lambda_{m}}\left\{ \left\Vert \lambda-I\right\Vert \vee\left\Vert \mathcal{Y}_{n}^{m}-\mathcal{X}_{n}^{m}\circ\lambda\right\Vert \right\} \\
- & \leq & \left\Vert \mathcal{Y}_{n}^{m}-\mathcal{X}_{n}^{m}\right\Vert \\
- & = & \left\Vert g_{m}\mathcal{Y}_{n}-g_{m}\mathcal{X}_{n}\right\Vert \\
- & = & \mbox{sup}_{t\leq m-1}\left\Vert Y_{n}\left(t\right)-X_{n}\left(t\right)\right\Vert \lor\mbox{sup}_{t>m-1}\left\Vert Y_{n}\left(t\right)-X_{n}\left(t\right)\right\Vert \left(m-t\right)\\
- & \leq & \mbox{sup}_{t\leq m}\left\Vert Y_{n}\left(t\right)-X_{n}\left(t\right)\right\Vert \\
- & \rightarrow & 0
-\end{eqnarray*}
-as we wanted to prove.
-
-$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-${\color{white}sssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssssss}$$\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\text{\ensuremath{\blacksquare}}$
-
-\section*{Appendix B: The BIZ Procedure}
-
-\subsection*{B.1 The BIZ Procedure with Known Common Variance}
-
-We first define the Bayes-inspired indifference zone (BIZ) procedure
-for the case of known common variance, when $\lambda_{x}^{2}=\sigma^{2}<\infty$
-for all $x$. Frazier (2014) showed that this procedure satisfies
-the IZ guarantee when the systems follow the normal distribution,
-with tight bounds on worst-case preference-zone in continuous time.
-
-BIZ depends on $P^{*}\in\left(1/k,1\right)$ and $\delta>0$ for which
-we desire an IZ guarantee, and a parameter $c$ such that
-\begin{eqnarray*}
-c & \in & \left[0,1-\left(P^{*}\right)^{\frac{1}{k-1}}\right]\mbox{ if }k>2\\
-c & = & 0\mbox{ if }k=2
-\end{eqnarray*}
-The parameter $c$controls how aggressively the alternatives are eliminated.
-It is recommended to choose $c$ equal to $1-\left(P^{*}\right)^{\frac{1}{k-1}}$.
-
-For each $t$, $x\in\left\{ 1,\ldots,k\right\} $, and subset $A\subset\left\{ 1,\ldots,k\right\} $,
-we define a function
-\[
-\hat{q}_{tx}\left(A\right)=\mbox{exp}\left(\frac{\delta}{\sigma^{2}}Y_{tx}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\frac{\delta}{\sigma^{2}}Y_{tx'}\right)\right.
-\]
-where $Y_{tx}$ is the sum of the samples observed from alternative
-$x$ by time $t$.
-
-Then, the BIZ procedure for known common variance is defined by Alg.
-1.
-
-\paragraph{Algorithm 1: BIZ for known common sampling variance, in discrete time.}    
-\begin{algorithmic}[1]   
-\label{alg:hetero-BIZ}   
-\REQUIRE $c \in [0,\cmax]$, $\delta>0$, $P^*\in(1/k,1)$, common sampling variance $\sigma^2>0$.     
-\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$, $Y_{0x} \leftarrow 0$ for each $x$.
-\WHILE{$\mbox{max}_{x\in A} \hat{q}_{tx}\left(A\right)<P$}
-\WHILE{$\mbox{min}_{x\in A} \hat{q}_{tx}\left(A\right) \le c$}
- \STATE Let $x\in\mbox{arg min}_{x\in A} \hat{q}_{tx}\left(A\right)$.
-    \STATE Let $\upthresh \leftarrow \upthresh/(1-\hat{q}_{tx}\left(A\right))$.     
-\STATE Remove $x$ from $A$.
-\ENDWHILE
-  \STATE Sample from each $x \in A$ and add this sample to $Y_{tx}$ to obtain $Y_{t+1,x}$. Then increment $t$.        
- \ENDWHILE
-  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} Y_{tx}$ as our estimate of the best.
-
-\end{algorithmic}
-
-\subsection*{B.2 The BIZ Procedure with Heterogeneous and Unknown Sampling Variances}
-
-Frazier (2014) showed that this procedure retains the IZ guarantee
-when the systems follow the normal distribution, and the variances
-are known and are integer multiples of a common value. The continuous
-time version of this procedure also satisfies the IZ guarantee, with
-a tight worst-case preference-zone PCS bound.
-
-The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
-variances is given in Alg. 2. It takes a variable number of samples
-from each alternative, and $n_{tx}$ is this number. This algorithm
-depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
-and $n_{0}$. $n_{0}$ is the number of samples to use in the first
-stage of samples, and $100$ is the recommended value for $n_{0}$.
-$B_{x}$ controls the number of samples taken from system $x$ in
-each stage.
-
-For each $t$, $x\in\left\{ 1,\ldots,k\right\} $, and subset $A\subset\left\{ 1,\ldots,k\right\} $,
-we define a function
-\[
-q_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right),\right.\mbox{ }\beta_{t}=\frac{\sum_{x'\in A}n_{tx'}}{\sum_{x'\in A}\hat{\lambda}_{tx'}^{2}}
-\]
-where $\hat{\lambda}_{tx'}^{2}$ is the sample variance of all samples
-from alternative $x$ thus far and $Z_{tx}=Y_{n_{tx},x}$.
-
-\paragraph{Algorithm 2: Discrete-time implementation of BIZ, for unknown and/or heterogeneous variances.}    
-\begin{algorithmic}[1]   
-\label{alg:hetero-BIZ}   
-\REQUIRE $c \in [0,\cmax]$, $\delta>0$, $P^*\in(1/k,1)$, $n_0\ge0$ an integer, $B_1,\ldots,B_k$ strictly positive integers.
-Recommended choices are $c=\cmax$, $B_1=\cdots=B_k=1$ and $n_0$ between $10$ and $30$.
-If the sampling variances $\lambda^2_x$ are known, replace the estimators
-$\lambdahat^2_{tx}$ with the true values $\lambda^2_x$, and set $n_0=0$.
-
-\STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
-Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.     
-\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
-\WHILE{$x\in\mbox{max}_{x\in A} q_{tx}\left(A\right)<P$}
-\WHILE{$\mbox{min}_{x\in A} q_{tx}\left(A\right) \le c$}
- \STATE Let $x\in\mbox{arg min}_{x\in A} q_{tx}\left(A\right)$.
-    \STATE Let $\upthresh \leftarrow \upthresh/(1-q_{tx}\left(A\right))$.     
-\STATE Remove $x$ from $A$.
-\ENDWHILE
-  \STATE Let $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.     
-\STATE For each $x\in A$, let      $n_{t+1,x} = \ceil\left( \lambdahat^2_{tx} (n_{tz} + B_z) / \lambdahat^2_{tz} \right)$.
-\STATE For each $x\in A$, if $n_{t+1,x}>n_{tx}$, take $n_{t+1,x}-n_{tx}$ additional samples from alternative $x$.
-Let $W_{t+1,x}$ and $\lambdahat^2_{t+1,x}$ be the sample mean and sample variance respectively of all samples from alternative $x$ thus far.
-\STATE Increment $t$.
- \ENDWHILE
-  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} W_{tx} / n_{tx}$ as our estimate of the best.
-
-\end{algorithmic}
-
-\subsection*{B.3 Generalization to Continuous Time}
-
-We let $\left(Y_{tx}:t\in\mathbb{R}_{+}\right)$ be a Brownian motion
-under $\mathbb{P}_{\mu,\lambda}$ starting from $0$, with drift $\mu_{x}$,
-volatility $\lambda_{x}$ and independence across $x$.
-
-\subsubsection*{B.3.1 Generalization to Continuous Time: The BIZ Procedure with Common
-Variance}
-
-In this section, we assume $\lambda_{x}^{2}=\sigma^{2}$ for all $x$,
-with $\sigma^{2}$ known. To define this procedure, we recursively
-define the stopping times $0=\tau_{1}\leq\tau_{2}\leq\cdots\leq\tau_{k-1}\leq\infty$,
-random variables $Z_{1},\ldots,Z_{k-1}$, and $P_{0},\ldots,P_{k-1}$,
-and random sets $A_{0},A_{1},\ldots,A_{k-1}$. We first define $\tau_{0},A_{0}$
-and $P_{0}$ as 
-\[
-\tau_{0}=0,\mbox{ }A_{0}=\left\{ 1,\ldots,k\right\} ,\mbox{ },P_{0}=P^{*}.
-\]
-Then, for each $n=0,1,\ldots,k-2$, we define
-\begin{eqnarray*}
-\tau_{n+1} & = & \mbox{inf }\left\{ t\in\mathbb{R}_{+}\bigcap\left[\tau_{n},\infty\right):\mbox{min}_{x\in A_{n}}\hat{q}_{tx}\left(A_{n}\right)\leq c\mbox{ or}\mbox{max}_{x\in A_{n}}\hat{q}_{tx}\left(A_{n}\right)\geq P\right\} \\
-Z_{n+1} & \in & \mbox{arg min}_{x\in A_{n}}\hat{q}_{\tau_{n+1},x}\left(A_{n}\right)\\
-A_{n+1} & = & A_{n}\left\backslash \left\{ Z_{n+1}\right\} \right.\\
-P_{n+1} & = & P_{n}\left/\left(1-\mbox{min}_{x\in A_{n}}\hat{q}_{\tau_{n+1},x}\left(A_{n}\right)\right)\right.
-\end{eqnarray*}
-Finally, $\hat{x}$ is the single alternative in $A_{k-1}$.
-
-We also define
-\[
-M=\mbox{inf}\left\{ n=1,\ldots,k-1:\mbox{max}_{x\in A_{n-1}}\hat{q}_{\tau_{n},x}\left(A_{n-1}\right)\geq P_{n-1}\right\} .
-\]
-
-Frazier (2014) showed that $\tau_{M}=\tau_{M+1}=\cdots=\tau_{k-1}$,
-and that the one alternative remaining in $A_{k-1}$ is the one whose
-$\hat{q}_{tx}\left(A_{n}\right)$ satisfied $\hat{q}_{tx}\left(A_{n}\right)\geq P_{n}$
-at time $\tau_{M}$. He also showed that $\tau_{M}<\infty$ almost
-surely under any $\mathbb{P}_{\mu,\sigma}$.
-
-\subsubsection*{B.3.2 Generalization to Continuous Time: The BIZ Procedure for the
-Heterogeneous Variance Setting}
-
-This procedure is similar than the one given in 3.4. For each $x$
-let $n_{x}\left(t\right)=\gamma\lambda_{x}^{2}t$. Now, we define
-a stochastic process $\left(Y'_{tx}:t\geq0\right)$ as $Y'_{tx}=Y_{n_{x}\left(t\right),x}/\gamma\lambda_{x}^{2}$.
-We have that $\left(Y'_{tx}:t\geq0\right)$ is a Brownian motion with
-drift $\mu_{x}$ and volatility $1/\gamma$.
-
-The procedure is defined by first defining $\tau_{0},A_{0}$ and $P_{0}$
-as 
-\[
-\tau_{0}=0,\mbox{ }A_{0}=\left\{ 1,\ldots,k\right\} ,\mbox{ },P_{0}=P^{*},
-\]
-then defining recursively, for $n=0,1,\ldots,k-2$,
-
-\begin{eqnarray*}
-\tau_{n+1} & = & \mbox{inf }\left\{ t\in\mathbb{R}_{+}\bigcap\left[\tau_{n},\infty\right):\mbox{min}_{x\in A_{n}}q'_{tx}\left(A_{n}\right)\leq c\mbox{ or}\mbox{max}_{x\in A_{n}}q'_{tx}\left(A_{n}\right)\geq P\right\} \\
-Z_{n+1} & \in & \mbox{arg min}_{x\in A_{n}}q'_{\tau_{n+1},x}\left(A_{n}\right)\\
-A_{n+1} & = & A_{n}\left\backslash \left\{ Z_{n+1}\right\} \right.\\
-P_{n+1} & = & P_{n}\left/\left(1-\mbox{min}_{x\in A_{n}}q'_{\tau_{n+1},x}\left(A_{n}\right)\right)\right.
-\end{eqnarray*}
-where $q'_{tx}\left(A\right)$ is defined by
-\[
-q'_{tx}\left(A\right)=\mbox{exp}\left(\gamma\delta Y'_{tx}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\gamma\delta Y'_{tx'}\right)\right.=\mbox{exp}\left(\frac{\delta}{\lambda_{x}^{2}}Y_{n_{x}\left(t\right),x}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\frac{\delta}{\lambda_{x'}^{2}}Y_{n_{x'}\left(t\right),x'}\right)\right..
-\]
-Frazier (2014) showed that this procedure satisfies the IZ guarantee,
-and and its worst-case preference-zone PCS bound is tight in continuous
-time.
-
-\[
-\]
-
-\begin{thebibliography}{References}
-\bibitem{key-3}Billingsley, P. 1968. \textit{Convergence of Probability
-Measures. }John Wiley and Sons. New York.
-
-\bibitem{key-8}Billingsley, P. 1999. \textit{Convergence of Probability
-Measures, }second edition. .John Wiley and Sons. New York.
-
-\bibitem{key-5}Frazier, P. I. A Fully Sequential Elimination Procedure
-for Indifference-Zone Ranking and Selection with Tight Bounds on Probability
-of Correct Selection. \textit{Operations Research,} to appear.
-
-\bibitem{key-9}Karatzas, I., Shreve, S. E. 1991. \textit{Brownian
-Motion and Stochastic Calculus}, second edition. Springer. New York.
-
-\end{thebibliography}
-\[
-\]
-\[
-\]
+\section*{ACKNOWLEDGMENTS}
+Peter Frazier and Saul Toscano-Palmerin were partially supported by NSF CAREER CMMI-1254298, AFOSR FA9550-12-1-0200, and AFOSR FA9550-15-1-0038.
+Peter Frazier was also partially supported by NSF IIS-1247696 and the Atkinson Center for a Sustainable Future Academic Venture Fund.
+Saul Toscano-Palmerin was also partially supported by the Mexican Secretariat of Public Education (SEP).
+
+% Please don't exchange the bibliographystyle style
+\bibliographystyle{wsc}
+% AUTHOR: Include your bib file here
+\bibliography{wsc15paper}
+
+\section*{AUTHOR BIOGRAPHIES}
+
+\noindent {\bf SAUL TOSCANO-PALMERIN} is a Ph.D.
+student of the School of Operations Research and Information Engineering at Cornell University, Ithaca, NY.
+His research interest is in simulation optimization, machine learning and sequential decision-making under uncertainty.
+His email address is \email{st684@cornell.edu}.
+\\
+
+\noindent {\bf PETER I.
+FRAZIER} is an Assistant Professor of the School of Operations Research and Information Engineering at Cornell University, Ithaca, NY.
+He holds a Ph.D.
+in operations research and financial engineering industrial engineering from Princeton University.
+His research interests include optimal learning, sequential decision-making under uncertainty, and machine learning, focusing on applications in simulation optimization, design of experiments, materials science, e-commerce and medicine.
+He is a member of INFORMS, and SIAM.
+His e-mail address is \email{pf98@cornell.edu}.\\
 

### 2015-05-04 paper/wish/wsc15paper.tex
edits during meeting

@@
 paths of the $k$-dimensional discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
-onto selection decisions. The BIZ procedure's mapping from paths onto
-selections decisions can be understood as the composition of three
+onto selection decisions. 
+Our proof uses this viewpoint, noting that 
+the BIZ procedure's mapping from paths onto
+selections decisions is the composition of three
 simpler maps.
@@
 \[
-q'_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\right.:=q'\left(\left(Z_{tx},t:x\in A\right),\delta,t\right)
+q'_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\right.:=q'\left(\left(Z_{tx}:x\in A\right),\delta,t\right)
 \]
@@
 The third maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
-onto selection decisions. Specifically, this mapping finds the first
-time that $\mbox{max}_{x\in A}q_{tx}\left(A\right)$ is larger than
-some threshold $P$, and then it chooses the system with the largest
-empirical mean $Z_{tx}/n_{tx}$.
+onto selection decisions. Specifically, this mapping begins with $A_0 = \{1,\ldots,k\}$,
+$P_0=P^*$, 
+and finds the first time $\tau_1$ that $q'_{tx}(A_0)$ falls above the threshold $P_0$,
+or below the threshold $c$.
+If the first case occurs, the alternative with the largest $q'_{\tau_1,x}(A_0)$ is selected as the best.
+If the second case occurs, the alternative with the smallest
+$q'_{\tau_1,x}(A_0)$ is eliminated, resulting in a new set $A_1$, a new selection threshold 
+$P_1$ is calculated from $P_0$ and the eliminated alternative's value of $q'_{\tau_1,x}(A_0)$, and the process continues.
+This process is repeated until an alternative is selected as the best.
+Call this mapping $h$, so that the BIZ selection decision is
+$h\left(\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)\right)$.
 
-Later, we can approximate the previous process by the continuous time
-process
-\begin{eqnarray}
-q_{tx}\left(A\right) & = & q\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)\label{eq:0.001-1}
-\end{eqnarray}
-where $t\geq0$ . Then we will show the difference in selection decisions
-vanishes as $\delta\rightarrow0$.
+\subsection{Proof Outline}
+Based on this view of the BIZ procedure as a composition of three maps, we outline the main ideas of our proof here.
 
-After that, we would like to use a kind of central limit theorem for
-$Z_{\frac{t}{\delta^{2}}x}$ when $\delta$ goes to zero to work with
-a Brownian motion instead. In order to do this, we are going to rewrite
-equation (1) in terms of a centralized version of $Z$:
+Our proof first notes that the same selection decision is obtained if we apply
+the BIZ selection map $h$ to a time-changed version of 
+$\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$, specifically to 
+\begin{equation*}
+\left(q_{tx}\left(A\right):t\in\delta^2 \mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right),
+\end{equation*}
+where
+$q_{tx}\left(A\right) := q'\left(\left(Z_{\frac{t}{\delta^{2}}x}:x\in A\right),\delta,t \right)$.
 
+This discrete-time process is interpolated by the continuous-time process 
+\begin{equation}
+\left(q_{tx}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right).
+\label{eq:q-continuous}
+\end{equation}
+If we apply the BIZ selection map $h$ to this continuous-time process, the selection decision will differ from BIZ's selection decision for $\delta>0$, but we show that this difference vanishes as $\delta\to0$.
+Thus, our proof focuses on showing that, as $\delta\to0$, applying the third map to \eqref{eq:q-continuous} produces a selection decision that satisfies the indifference-zone guarantee.
+
+To accomplish this, we use a functional central limit theorem for
+$Z_{\frac{t}{\delta^{2}}x}$, which shows that a centralized
+version of $Z_{\frac{t}{\delta^{2}}x}$ converges to a Brownian motion as $\delta$ goes to $0$.
+This centralized version of $Z_{\frac{t}{\delta^{2}}x}$ is 
 \[
-\mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
+\mathcal{C}_{x}\left(\delta,t\right):=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}.
 \]
-and the resulting expression is
+Rewriting $Z_{\frac{t}{\delta^{2}}x}$ in terms of $\mathcal{C}_{x}\left(\delta,t\right)$ and substituting into the definition of $q_{tx}(A)$ provides the expression
+\begin{equation}
+    q_{tx}\left(A\right)=q\left(\left(\mathcal{C}_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x}:x\in A\right),\delta,t \right).
+    \label{eq:q}
+\end{equation}
 
-\[
-q_{tx}\left(A\right)=q\left(\left(C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
-\]
-
-Thus, we can see the selection decision resulting from the BIZ algorithm
-as the result of applying some mapping $f\left(\cdot,\delta\right)$
+We will construct a mapping $f\left(\cdot,\delta\right)$ that takes as input the process
+$\left(\mathcal{C}_{x}\left(\delta,t\right) : x\in \{1,\ldots,k\}, t\in\mathbb{R}\right)$,
+calculates 
+\eqref{eq:q-continuous}
+% \left(q_{tx}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right).
+from it,
+applies the BIZ selection map $h$ to \eqref{eq:q-continuous}, 
+and then returns $1$ if the correct selection was made,
+and $0$ otherwise.
+Thus, the correct selection event that results from applying
+the BIZ selection map $h$ to \eqref{eq:q-continuous} is the result
+of applying the mapping $f\left(\cdot,\delta\right)$
 to the paths $t\mapsto\mathcal{C}_{x}\left(\delta,t\right)$ .
 
-The last part of our proof is to observe that (1) $\mathcal{C}\left(\delta,\cdot\right)$
+% Thus, we can see the selection decision resulting from BIZ as being closely app
+
+With these pieces in place, the last part of our proof is to observe that (1) $\mathcal{C}\left(\delta,\cdot\right)$
 converges to a multivariate Brownian motion $W$ as $\delta$ goes
@@
 in continuous time; and (3) the BIZ procedure satisfies the IZ guarantee
-when applied in continuous time.
+when applied in continuous time (Theorem~1 in \cite{Frazier:BIZ}), and so $E[g(W)] \ge P^*$ with equality for the worst configurations in the preference zone.
 
-First, we are going to see that the the standardized sum of the output
-data converges to a Brownian motion in the sense of $D_{\infty}:=D[0,\infty)$,
+\subsection{Preliminary Results}
+
+First, we are going to see that the centralized sum of the output
+data $\mathcal{C}_x(\delta,t)$ converges to a Brownian motion in the sense of $D_{\infty}:=D[0,\infty)$,
 which is the set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$
@@
 
-The following lemma shows that the standardized sum of the output
+The following lemma shows that the centralized sum of the output
 data with $t$ changed by $t/\delta^{2}$ converges to a Brownian
@@
 \begin{lemma}
-For each $x\in\left\{ 1\ldots,k\right\} $, we define
-\[
-\mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
-\]
-where $Y_{n,x}$ is the sum of the first $n$ samples from alternative
-$x$. Let $x\in\left\{ 1\ldots,k\right\} $, then
+% For each $x\in\left\{ 1\ldots,k\right\} $, we define
+% \[
+% % \mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
+% \]
+% where $Y_{n,x}$ is the sum of the first $n$ samples from alternative
+$x$. 
+Let $x\in\left\{ 1\ldots,k\right\} $, then
 \[
@@
 is a standard Brownian motion.
-
 \end{lemma}
@@
 
-Observe that $\mathcal{C}\left(\delta,\cdot\right)\in D\left[0,\infty\right)^{k}$
-and the convergence of Lemma 1 is in $D\left[0,\infty\right)^{k}$,
-consequently the following natural step is to generalize the continuous-time
-procedure for the heterogeneous variance setting, see Appendix B,
-to the space $D\left[0,\infty\right)^{k}$. Specifically, for each
-$F\in D\left[0,\infty\right)^{k}$, we define $q_{tx}^{F,\delta}\left(A\right)$
-as
+Now that we have obtained this functional central limit theorem for 
+$\mathcal{C}\left(\delta,\cdot\right)$, we now continue along the proof outline and define the function $f(\cdot,\delta)$ that was sketched there.
+This function has three parts: first, computing a ``non-centralized'' path from an arbitrary input ``centralized'' path in $D\left[0,\infty\right)^{k}$; and second, applying the BIZ selection map $h$ to this non-centralized path; and third, reporting when selection was correct or not.
+
+% Observe that $\mathcal{C}\left(\delta,\cdot\right)\in D\left[0,\infty\right)^{k}$ and the convergence of Lemma 1 is in $D\left[0,\infty\right)^{k}$, consequently the following natural step is to generalize the continuous-time procedure for the heterogeneous variance setting, see Appendix B, to the space $D\left[0,\infty\right)^{k}$.
+To accomplish the first part, for each $F\in D\left[0,\infty\right)^{k}$, 
+we define $q_{tx}^{F,\delta}\left(A\right)$ as
 \[
@@
 \]
+Note that if we replace $F$ by $\mathcal{C}\left(\delta,t\right)$,
+we get $q_{tx}\left(A\right)$ in \eqref{eq:q}.   
+% In this sense, 
+% we consider to be $q_{tx}^{F,\delta}\left(A\right)$ a ``non-centralized'' version of $F$.
 
-Note that if we replace $F$ by $\mathcal{C}\left(\delta,t\right)$,
-we get $q{}_{tx}\left(A\right)$ in the previous equation. Using the
-continuous-time procedure for the heterogeneous variance setting with
-the paths $\left(q_{tx}^{F,\delta}\left(A\right):t\geq0\right)$,
-we see that there exists a selection decision for each $F\in D\left[0,\infty\right)^{k}$.
-Since we are interested in the right selection, ( i.e. in choosing
-$k$) for each $F\in D\left[0,\infty\right)^{k}$, we define the following
-function 
+To accomplish the second and third parts, we define
+$f\left(F,\delta\right)$ to be obtained by applying the BIZ selection map $h$ to the process
+$\left(q_{tx}^{F,\delta}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$, and then reporting whether the selection was correct.
+More precisely, $f(F,\delta)$ is defined to be
+% Using the
+% continuous-time procedure for the heterogeneous variance setting with
+% the paths $\left(q_{tx}^{F,\delta}\left(A\right):t\geq0\right)$,
+% we see that there exists a selection decision for each $F\in D\left[0,\infty\right)^{k}$.
+% Since we are interested in the right selection, ( i.e. in choosing
+% $k$) for each $F\in D\left[0,\infty\right)^{k}$, we define the following
+% function 
 \begin{eqnarray*}
 f\left(F,\delta\right) & = & \begin{cases}
-1 & \mbox{if }k\mbox{ is chosen}\mbox{ }\\
-0 & \mbox{otherwise}
+    1 & \text{if $h\left(\left(q_{tx}^{F,\delta}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)\right) = k$,}\\
+0 & \text{otherwise.}
 \end{cases}
 \end{eqnarray*}
- Observe that $f$ is a function that depends in the path $\left\{ q_{tx}^{F,\delta}\left(A\right):t\geq0\right\} $.
+ % Observe that $f$ is a function that depends in the path $\left\{ q_{tx}^{F,\delta}\left(A\right):t\geq0\right\} $.
+
+{\it PF: I stopped here.}
 We are doing all this because we want to see that $f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)$

### 2015-05-06 paper/wish/wsc15paper.tex
5-5-155-5-155-5-155-5-155-5-15

@@
 {\it PF: I stopped here.}
-We are doing all this because we want to see that $f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)$
-looks like the right or wrong selection decision of an algorithm that
-depends on a standard Brownian motion instead of $\mathcal{C}\left(\delta,\cdot\right)$,
-and this will give us the proof because we will be able to use the
-theory developed by Frazier (2014) to prove the theorem. Thus, the
-following step is to find the limit of $q_{tx}^{F,\delta}\left(A\right)$
+%We are doing all this because we want to see that $f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)$
+%looks like the right or wrong selection decision of an algorithm that
+%depends on a standard Brownian motion instead of $\mathcal{C}\left(\delta,\cdot\right)$,
+%and this will give us the proof because we will be able to use the
+%theory developed by Frazier (2014) to prove the theorem. Thus, the
+The following step is to find the limit of $q_{tx}^{F,\delta}\left(A\right)$
 when $\delta$ goes to zero, which is called $q_{tx}^{F}\left(A\right)$
@@
 
+\subsection{The Main Result}
+
 \begin{theorem}
@@
 By the comments given at the beginning of this section, we know that
-we can work with the algorithm defined by
+we can work with the algorithm, which we call the discrete-time BIZ algorithm, defined by
 
@@
 \end{eqnarray*}
-We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
+The corresponding BIZ algorithm is called the continuous-time BIZ algorithm. We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
 which are defined as
@@
 Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
-we can prove that $\hat{\tau}_{n}\left(\delta\right)-\tau_{n}\left(\delta\right)\rightarrow0$
-with probability $1$ as $\delta\rightarrow0$, and so we can use
-$\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
-of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$
-in the limit.
+we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero.
+Then we can use the continuous-time BIZ algorithm in the limit, i.e.
+we can use $\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
+of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. (The details may be found in a full version which will be submitted soon to arXiv).
 
@@
 
-\begin{figure}
+\begin{figure}[h]
   \centering
@@
       \centering
-        \includegraphics[width=\textwidth]{plot5}
+       \includegraphics[width=0.7\textwidth]{plot5}
+    \caption{Known variances and $P^*=0.9$. In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero.
+    \label{fig: tahi3}}
    \end{subfigure}
@@
         \centering
-        \includegraphics[width=\textwidth]{plot6}
+         \includegraphics[width=0.7\textwidth]{plot3}
+             \caption{Unknown variances and $P^*=0.9$.
+In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero.
+If we want that the IZ guarantee be
+    satisfied in all the cases, we can just increment $n_{0}$.
+    \label{fig: tahi2}}
     \end{subfigure}
-    \caption{Known variances and $P^*=0.9$. $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5,n_{0}=0$.
-    In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero.
-    \label{fig: tahi3}}
+        \hfill
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+         \includegraphics[width=0.7\textwidth]{plot1}
+    \caption{Known variances, $P^*=0.9$ This was a hard example to find and it was specially chosen to ilustrate our theorem.
+In practice, we would choose $n_{0}>0$ and the IZ guarantee will be satisfied.
+\label{fig: tahi}}
+    \end{subfigure}
+    \caption{PCS for different numerical experiments
+\label{fig:tahi10}}
+
 \end{figure}
@@
 we can just increment the parameter $n_{0}$.
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{plot3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{plot4}
-    \end{subfigure}
-    \caption{Unknown variances and $P^*=0.9$. $\lambda_{100}=10\sqrt(2),\lambda_{99}=10+\frac{(10)(98)}{99}(\sqrt(2)-1),\cdots,\lambda_{1}=10,n_{0}=15$.
-    In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero. If we want that the IZ guarantee be 
-    satisfied in all the cases, we can just increment $n_{0}$.
-    \label{fig: tahi2}}
-\end{figure}
 
@@
 Here, the points plotted have central confidence intervals of length at most $0.014$.
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{plot1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{plot2}
-    \end{subfigure}
-    \caption{Known variances, $P^*=0.9$, $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1,n_{0}=0$. This was a hard example to find
-    and it was specially chosen to ilustrate our theorem. In practice, we would choose $n_{0}>0$ and the IZ guarantee will be satisfied. \label{fig: tahi}}
-\end{figure}
 

### 2015-05-06 paper/wish/wsc15paper.tex
edits to proof section during meeting.

@@
 If we apply the BIZ selection map $h$ to this continuous-time process, the selection decision will differ from BIZ's selection decision for $\delta>0$, but we show that this difference vanishes as $\delta\to0$.
-Thus, our proof focuses on showing that, as $\delta\to0$, applying the third map to \eqref{eq:q-continuous} produces a selection decision that satisfies the indifference-zone guarantee.
+Thus, our proof focuses on showing that, as $\delta\to0$, applying the BIZ selection map $h$ to \eqref{eq:q-continuous} produces a selection decision that satisfies the indifference-zone guarantee.
 
@@
 
-\subsection{Preliminary Results}
+\subsection{Preliminaries for the Proof of the Main Theorem}
+
+In this section, we present preliminary results and definitions used in the proof of the main theorem: first, a central limit theorem Corollary~\ref{cor:CLT}; second, definitions of the functions $f(\cdot,\delta)$ and $g(\cdot)$; and third, a continuity result Lemma~\ref{l:continuity}.
 
@@
 \begin{corollary}
+    \label{cor:CLT}
 We have that
@@
 $\mathcal{C}\left(\delta,\cdot\right)$, we now continue along the proof outline and define the function $f(\cdot,\delta)$ that was sketched there.
-This function has three parts: first, computing a ``non-centralized'' path from an arbitrary input ``centralized'' path in $D\left[0,\infty\right)^{k}$; and second, applying the BIZ selection map $h$ to this non-centralized path; and third, reporting when selection was correct or not.
+This function has three parts: first, computing a ``non-centralized'' path from an arbitrary input ``centralized'' path in $D\left[0,\infty\right)^{k}$; second, applying the BIZ selection map $h$ to this non-centralized path; and third, reporting whether selection was correct or not.
 
@@
 \[
-q_{tx}^{F,\delta}\left(A\right)=q'\left(\left(F_{x}\left(t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
+q_{tx}^{F,\delta}\left(A\right)=q'\left(\left(F_{x}\left(t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
 \]
@@
 
-{\it PF: I stopped here.}
 %We are doing all this because we want to see that $f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)$
@@
 %theory developed by Frazier (2014) to prove the theorem. Thus, the
-The following step is to find the limit of $q_{tx}^{F,\delta}\left(A\right)$
-when $\delta$ goes to zero, which is called $q_{tx}^{F}\left(A\right)$
-and equal to
+We now construct a function $g(\cdot)$ that, when applied to the path of a $k$-dimensional standard Brownian motion, will be equal in distribution to the indicator of the correct selection event from the continuous-time BIZ procedure from \cite{Frazier:BIZ}
+% to a problem with indifference-zone parameter equal to 1, where each alternative's observation process has volatility $\lambda_z$ and drift $a_x$.
+to a transformed problem that does not depend on $\delta$.
 
+We construct $g$ analogously to $f(\cdot,\delta)$, but we replace the path $q_{tx}^{F,\delta}$ used in the construction of $f(\cdot,\delta)$ by a new path $q_{tx}^{F}$ that doesn't depend on $\delta$, and is obtained by taking the limit as $\delta\to0$.
+This path is
+% Going back to the proof outline, 
+% the next step is to find the limit of $q_{tx}^{F,\delta}\left(A\right)$
+% when $\delta$ goes to zero, which we denote $q_{tx}^{F}\left(A\right)$, 
+% and is equal to
 \[
@@
 \]
- Using the same previous idea, for each $F\in D\left[0,\infty\right)^{k}$,
-we define the new functions
-\[
-\]
+Then, $g$ is defined to be
+ %Using the same previous idea, for each $F\in D\left[0,\infty\right)^{k}$,
+%we define the new functions
 \begin{eqnarray*}
 g\left(F\right) & = & \begin{cases}
-1 & \mbox{if }k\mbox{ is chosen}\mbox{ }\\
-0 & \mbox{otherwise}
-\end{cases}.
+    1 & \text{if $h\left(\left(q_{tx}^{F}\left(A\right):t\in\mathbb{R},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)\right) = k$,}\\
+0 & \text{otherwise.}
+\end{cases}
 \end{eqnarray*}
 
-So, we want to prove that 
+In the proof of the main theorem, we will show that 
 \[
@@
 \]
-as $\delta\rightarrow0$ in distribution.
-
-In order to prove this, we first proved a continuity property in Lemma
-2, which allows us to use Theorem 5.5 of \citeN{billingsley:convergence}, which
-implies the desired result. A proof of Lemma 2 may be found in a full version which will be
-submitted soon to arXiv. 
+as $\delta\rightarrow0$ in distribution. We will use the following lemma, which shows a continuity property.
+A proof of Lemma~\ref{l:continuity} may be found in a full version of this paper \cite{fullpaper},
+which will be submitted soon to arXiv. 
 \\
 \begin{lemma}
-
 Let $\left\{ \delta_{n}\right\} \subset\left(0,\infty\right)$ such
@@
 then $ $$\mathbb{P}\left(W\text{\ensuremath{\in}}D_{s}\right)=1$.
-
+\label{l:continuity}
 \end{lemma}
 \vspace{5mm}
-By the extension of the CMT \cite{billingsley:convergence}, we
-have the following corollary.
-\vspace{5mm}
-
-\begin{corollary}
-
-We have that
-
-\[
-f\left(C\left(\delta,t\right),\delta\right)\Rightarrow g\left(W\left(t\right)\right)
-\]
-in distribution as $\delta\rightarrow0$.
-
-\[
-\]
-\end{corollary}
-\vspace{1mm}
 
@@
 provided $\mu_{k}=a_{k}\delta,\mu_{k-1}=a_{k-1}\delta,\ldots,\mu_{1}=a_{1}\delta$,
-$a_{k}>a_{k-1}\geq \cdots \geq a_{1}$, $a_{k}-a_{k-1}>1$, and the variances are finite and
+$a_{k}>a_{k-1}\geq \cdots \geq a_{1}$, $a_{k}-a_{k-1}\ge1$, and the variances are finite and
 do not depend on $\delta$.
@@
 \[
-\mbox{inf}_{a\in PZ\left(1\right)}\mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right)=P^{*}
+\inf_{a\in PZ\left(1\right)}\mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right)=P^{*}
 \]
@@
 
-\begin{proof}
+%By the comments given at the beginning of this section, we know that
+%we can work with the algorithm, which we call the discrete-time BIZ algorithm, defined by
 
-By the comments given at the beginning of this section, we know that
-we can work with the algorithm, which we call the discrete-time BIZ algorithm, defined by
+%\[
+%q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
+%\]
+%where $t\in\delta^{2}\mathbb{N}$, instead of the algorithm defined
+%by
+%\[
+%q'_{tx}\left(A\right)=q'\left(\left(Z_{tx},t:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
+%\]
+%where $t\in\mathbb{N}$.
+%
+%Now, we define
+%\begin{eqnarray*}
+%%\hat{\tau}_{n+1}\left(\delta\right) & = & \mbox{inf}\left\{ t\in\left\{ \tau_{n}\delta^{2},\left(\tau_{n}+1\right)\delta^{2},\ldots\right\} :\mbox{ min}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\geq P_{n}\right\}
+%\end{eqnarray*}
+% The corresponding BIZ algorithm is called the continuous-time BIZ algorithm. We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
+% which are defined as
 
+% Maybe some of this goes into the proof of the new lemma
 \[
-q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
-\]
-where $t\in\delta^{2}\mathbb{N}$, instead of the algorithm defined
-by
-\[
-q'_{tx}\left(A\right)=q'\left(\left(Z_{tx},t:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
-\]
-where $t\in\mathbb{N}$.
-
-Now, we define
-\begin{eqnarray*}
-\hat{\tau}_{n+1}\left(\delta\right) & = & \mbox{inf}\left\{ t\in\left\{ \tau_{n}\delta^{2},\left(\tau_{n}+1\right)\delta^{2},\ldots\right\} :\mbox{ min}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\geq P_{n}\right\}
-\end{eqnarray*}
-The corresponding BIZ algorithm is called the continuous-time BIZ algorithm. We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
-which are defined as
-
-\[
-\tau_{n+1}=\mbox{inf}\left\{ t\geq\tau_{n}:\mbox{ min}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\geq P_{n}\right\} .
+% \tau_{n+1}=\mbox{inf}\left\{ t\geq\tau_{n}:\mbox{ min}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\geq P_{n}\right\} .
 \]
 
-Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
-we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero.
+% Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
+% we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero.
 Then we can use the continuous-time BIZ algorithm in the limit, i.e.
 we can use $\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
-of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. (The details may be found in a full version which will be submitted soon to arXiv).
+% of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. The details may be found in the full version of this paper \cite{fullpaper}.
 
-Let $CS_{\delta}$ be the event of doing a correct selection given
-the configuration $\mu_{k}=a_{k}\delta,\mu_{k-1}=a_{k-1}\delta,\ldots,\mu_{1}=a_{1}\delta$
-$ $. Then by the previous argument and the Corollary 2, 
-\begin{eqnarray*}
-\mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right) & = & \mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(f\left(\mathcal{C}\left(\delta,t\right),\delta\right)=1\right)\\
- & = & \mathbb{P}\left(g\left(W\right)=1\right)\\
- & \geq & P^{*}
-\end{eqnarray*}
-where the last inequality follows from the Theorem 2 of \citeN{Frazier:BIZ}.
+% and allows us to use Theorem~5.5 of \citeN{billingsley:convergence}.
 
-Furthermore, by the same theorem 2,
-\[
+\begin{proof}
+Using the definitions given at the beginning of this section,
+the selection decision of the discrete-time BIZ procedure for a particular $\delta>0$ when $\mu_{k}=a_{k}\delta,\mu_{k-1}=a_{k-1}\delta,\ldots,\mu_{1}=a_{1}\delta$ is given by
+\begin{equation*}
+h\left(\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)\right)
+\end{equation*}
+and the probability of correct selection $\mbox{PCS}(\delta)$ is
+\begin{equation*}
+    \mbox{PCS}(\delta) = P\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right).
+\end{equation*}
+By Lemma~\ref{l:new}, as $\delta\to0$, we have that 
+\begin{equation}
+\lim_{\delta\to0}
+\mbox{PCS}(\delta)
+% P\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right)
+ = \lim_{\delta\rightarrow0}
+ \mathbb{P}\left(
+ f\left(\mathcal{C}\left(\delta,t\right),\delta\right)=1
+ \right)
+ \label{eq:convergence1}
+\end{equation}
+
+We also have, by Lemma~\ref{l:continuity} and an extension of the continuous mapping theorem (Theorem~5.5 of \citeN{billingsley:convergence}), 
+\begin{equation*}
+    f\left(\mathcal{C}\left(\delta,t\right),\delta\right)\Rightarrow g\left(W\left(t\right)\right)
+%\label{eq:convergence}
+\end{equation*}
+in distribution as $\delta\rightarrow0$.
+This implies that
+\begin{equation}
+\lim_{\delta\rightarrow0}\mathbb{P}\left(f\left(\mathcal{C}\left(\delta,t\right),\delta\right)=1\right)
+ = \mathbb{P}\left(g\left(W\right)=1\right)
+ \label{eq:convergence2}
+\end{equation}
+
+The random variable $g(W)$ is equal in distribution to the indicator of the event of correct selection that results from applying the continuous-time BIZ procedure from \cite{Frazier:BIZ} in a problem with indifference-zone parameter equal to 1, where each alternative's observation process has volatility $\lambda_z$ and drift $a_x$.
+This can be seen by noting that the path $(q^{W}_{tx}(A) : t\ge0)$ defined above is equal in distribution to the path $(q_{tx}(A) : t\ge0)$ defined in equation (2) of \citeN{Frazier:BIZ}, and that the selection decision of the continuous-time algorithm in \citeN{Frazier:BIZ} is obtained by applying $h$ to this path.
+
+Theorem 1 in \citeN{Frazier:BIZ} states that 
+\begin{equation}
+\mathbb{P}\left(g\left(W\right)=1\right)\ge P^{*}.
+\label{eq:correct}
+\end{equation}
+
+Combining 
+\eqref{eq:convergence1}, 
+\eqref{eq:convergence2}, and
+\eqref{eq:correct}, we have
+\begin{equation*}
+    \lim_{\delta\to0} \mbox{PCS}(\delta) \ge P^*.
+\end{equation*}
+
+Furthermore, Theorem~1 in \citeN{Frazier:BIZ} shows that 
+\begin{equation}
 \mbox{inf}_{a\in PZ\left(1\right)}\mathbb{P}\left(g\left(W\right)=1\right)=P^{*}
-\]
+\label{eq:tight}
+\end{equation}
+where $PZ\left(1\right)=\left\{ a\in\mathbb{R}^{k}:a_{k}-a_{k-1}\geq1\right\} $.
 
-where $PZ\left(1\right)=\left\{ a\in\mathbb{R}^{k}:a_{k}-a_{k-1}\geq1\right\} $.
+Combining 
+\eqref{eq:convergence1}, 
+\eqref{eq:convergence2}, and
+\eqref{eq:tight}, shows
+\begin{equation*}
+\inf_{a\in PZ\left(1\right)}\lim_{\delta\rightarrow0}\mbox{PCS}(\delta)=P^{*}.
+\end{equation*}
 

### 2015-05-06 paper/wish/wsc15paper.tex
edits to abstract.

@@
 % AUTHOR: Enter the title, all letters in upper case
-\title{ASYMPTOTIC VALIDITY OF A FULLY SEQUENTIAL ELIMINATION PROCEDURE FOR INDIFFERENCE-ZONE RANKING AND SELECTION WITH TIGHT BOUNDS ON PROBABILITY OF CORRECT SELECTION}
+\title{ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE: 
+%THE NON-NORMAL KNOWN VARIANCE CASE}
+THE GENERAL DISTRIBUTION  KNOWN VARIANCE CASE}
 
@@
 \section*{ABSTRACT}
-We consider the indifference-zone (IZ) formulation of the ranking
-and selection problem in which the goal is to choose with high probability 
-an alternative with similar mean than the one with largest mean. 
-Conservatism leads classical IZ procedures
-to take too many samples in problems with many alternatives. The Bayes-inspired
+We consider the indifference-zone (IZ) formulation of the ranking and selection problem in which the goal is to choose an alternative with the largest mean with guaranteed probability, as long as the difference between this mean and the second largest exceeds a threshold.
+Conservatism leads classical IZ procedures to take too many samples in problems with many alternatives. The Bayes-inspired
 Indifference Zone (BIZ) procedure, proposed in \citeN{Frazier:BIZ}, is
 less conservative than previous procedures, but its proof of validity
-requires strong assumptions, specifically it assumes that the variances are known 
-and have an integer multiple structure. In this paper, we consider a slightly
-modification of the original BIZ procedure in order to simplify the analysis, and we
-present a new proof of its asymptotic validity that relaxes these assumptions.
-Specifically, we prove the validity of the algorithm when the variances are known
-and the difference between the best alternative and the second best goes to zero.
+requires strong assumptions, specifically that samples are normal, and variances are known 
+with an integer multiple structure. In this paper, 
+we show asymptotic validity of a slight modification of the original BIZ procedure 
+as the difference between the best alternative and the second best goes to zero,
+when the variances are known and finite, and samples are independent and identically distributed, but not necessarily normal.
 

### 2015-05-06 paper/wish/wsc15paper.tex
edits to introduction

@@
 There are many applications where we have to choose the best alternative
-among a finite number of simulated alternatives.
-For example, in inventory problems, we may want to choose the best inventory policy $(s,S)$ for a finite number of values of $s$ and $S$.
-The ranking and selection problem has to decide how many samples are needed to find the alternative with the largest mean.
-A good solution to the problem is efficient and accurate, i.e.
-the procedure proposed for the problem must balance between the number of samples required and quality of the selection.
+among a finite number of simulated alternatives. For example, in inventory problems, we may want to choose the best inventory policy $(s,S)$ for a finite number of values of $s$ and $S$. 
+This is called the ranking and selection problem.
+% In such ranking and selection problems, we must decide how many samples we need to accurately find the alternative with the largest mean. 
+A good procedure for addressing this problem should be both efficient and accurate, i.e. it should balance the number of samples it takes with the quality of its selection.
 
-This paper considers the indifference-zone (IZ) formulation of
-the ranking and selection problem, in which the distance between the best system and
-the other systems is sufficiently large and the best system is chosen with probability larger
-than some threshold given by the user. This property is called the IZ guarantee, and the preference zone (PZ)
-is defined as the set of system configurations under which the difference between the best system and the others is
-at least some given  $\delta>0$. The paper \citeN{Bechhofer:1954} is considered the seminal work, and early work is 
+This paper considers the indifference-zone (IZ) formulation of the ranking and selection problem, in which we require that a procedure satisfy the IZ guarantee, i.e., that the best system be chosen with probability larger than some threshold $P^*$ given by the user, when the distance between the best system and the others is larger than some other user-specified threshold $\delta>0$.
+The set of problem configurations satisfying this constraint on the difference in means is called the preference zone.
+The paper \citeN{Bechhofer:1954} is considered the seminal work, and early work is 
 presented in the monograph \citeN{Bechhofer:1968}. Some compilations of the theory developed in the area can be found
-in \citeN{Bechhofer:1995}, \citeN{swisher:survey}, \citeN{kim:20062} and \citeN{kim:2007}. Beyond these classical approaches, 
-there are the Bayesian approach \cite{Frazier:Tutorial} and the optimal computing budget allocation approach \cite{chen:ocva}.
+in \citeN{Bechhofer:1995}, \citeN{swisher:survey}, \citeN{kim:20062} and \citeN{kim:2007}.
+Other approaches, beyond the indifference-zone approach, include the Bayesian approach \cite{Frazier:Tutorial}, the optimal computing budget allocation approach \cite{chen:ocva}, and the large deviations approach \cite{glynn2004large}.
 
@@
 satisfy the IZ guarantee, but they usually take too many samples when there are many alternatives,
-in part because their probability of correct selection (PCS) is much
+in part because they are conservative: their probability of correct selection (PCS) is much
 larger than the probability specified by the user \cite{kim:Conserv}. One reason for this
 is that these procedures use Bonferroni's inequality, which leads then to sample more
-than necessary. More recently, new algorithms were developed in \citeN{Kim:2001}, \citeN{Goldsman:2002}, 
-\citeN{Hong}, and they improve the performance but they still
-use the Bonferroni's inequality, and so the methods are inefficient
+than necessary. The Bonferonni-based bounds underlying these procedures become looser, and the tendency to take more samples than necessary increases, as the number of alternatives grow.
+More recently, new algorithms were developed in \citeN{Kim:2001}, \citeN{Goldsman:2002}, 
+\citeN{Hong}, and they improve performance but they still
+use Bonferroni's inequality, and so the methods are inefficient
 when there are many alternatives. Procedures in \citeN{kim:2011},
-\citeN{dieker:2012} do not use the Bonferroni's inequality 
-when there are only three alternatives, but when they compare more than three
-alternatives, they do use the Bonferroni's inequality.
+\citeN{dieker:2012} do not use Bonferroni's inequality 
+when there are only three alternatives, but again use Bonferroni's inequality when 
+comparing more than three alternatives.
 
-Conservative algorithms lead to take more samples than needed, and consequently conservative procedures are unpopular 
-when there are more than a few hundred of alternatives. Three common sources of conservativeness are
- the Bonferroni's inequality, the change from discrete process to continuous process, and bound the worst case which is not a common case.
-  \citeN{Frazier:BIZ} eliminates one source of conservativeness: the Bonferroni's inequality. He presented  a new sequential elimination
+\citeN{Frazier:BIZ} eliminates the use of Bonferroni's inequality, reducing conservatism. This paper presents a new sequential elimination
 IZ procedure, called BIZ (Bayes-inspired Indifference Zone), whose
@@
 Our proof shares some similarities since we both use a central limit theorem.
+
+Two other common sources of conservatism are the change from discrete-time processes to continuous-time processes used to show IZ guarantees, and the fact that typically, the configuration under consideration is not a worst-case configuration \cite{kim:20062}.
+This last source tends to be the largest in terms of its contribution to conservatism, and the first tends to be the smallest, with the contribution from Bonferonni inequality's lying between \cite{kim:20062}.
+Although the BIZ procedure avoids the Bonferonni inequality, it does not avoid these other two sources of conservatism.
+Indeed, all indifference zone procedures must meet the PCS guarantee for all configurations in the preference zone, including worst-case configurations.
+In this sense, this last source of conservatism arises from the indifference zone guarantee itself, rather than the from a design of a particular procedure.
 

### 2015-05-07 paper/wish/wsc15paper.tex
5-7-15

@@
 %
-\WSCpagesetup{Toscano-Palmerin, Frazier}
+\WSCpagesetup{Toscano-Palmerin, and Frazier}
 
@@
 
-\maketitle
-
-\begin{figure*}[htb]
-{
-\centering
-Saul Toscano-Palmerin \\
-Peter I. Frazier \\
-\vspace{12pt}
+\author{
+	Saul Toscano-Palmerin\\ 
+    	Peter I. Frazier\\[12pt]
 	Cornell University \\
@@
 }
-\end{figure*}
+
+\maketitle
 
@@
 in part because they are conservative: their probability of correct selection (PCS) is much
-larger than the probability specified by the user \cite{kim:Conserv}. One reason for this
+larger than the probability specified by the user \cite{Kim:Conserv}. One reason for this
 is that these procedures use Bonferroni's inequality, which leads then to sample more
@@
 
-Two other common sources of conservatism are the change from discrete-time processes to continuous-time processes used to show IZ guarantees, and the fact that typically, the configuration under consideration is not a worst-case configuration \cite{kim:20062}.
-This last source tends to be the largest in terms of its contribution to conservatism, and the first tends to be the smallest, with the contribution from Bonferonni inequality's lying between \cite{kim:20062}.
+Two other common sources of conservatism are the change from discrete-time processes to continuous-time processes used to show IZ guarantees, and the fact that typically, the configuration under consideration is not a worst-case configuration \cite{Kim:Conserv}.
+This last source tends to be the largest in terms of its contribution to conservatism, and the first tends to be the smallest, with the contribution from Bonferonni inequality's lying between \cite{Kim:Conserv}.
 Although the BIZ procedure avoids the Bonferonni inequality, it does not avoid these other two sources of conservatism.
@@
 
-\vspace{5mm}
-
 \paragraph{Algorithm: Discrete-time implementation of BIZ, for unknown and/or heterogeneous variances.}    
@@
 \end{algorithmic} 
+\hspace{5 mm}
 
-\vspace{10mm}
 This algorithm generalizes the BIZ procedure with known common variance.
@@
 
-In this section, we present preliminary results and definitions used in the proof of the main theorem: first, a central limit theorem Corollary~\ref{cor:CLT}; second, definitions of the functions $f(\cdot,\delta)$ and $g(\cdot)$; and third, a continuity result Lemma~\ref{l:continuity}.
+In this section, we present preliminary results and definitions used in the proof of the main theorem: first, a central limit theorem Corollary~\ref{cor:CLT}; second, definitions of the functions $f(\cdot,\delta)$ and $g(\cdot)$; third, a continuity result Lemma~\ref{l:continuity}; and fourth, a result Lemma~\ref{l:interpolation} that allows us to change from discrete-time processes to continuous-time processes.
 
@@
 motion in the sense of $D_{\infty}$.
-\\
+
 \begin{lemma}
@@
 
-\vspace{5mm}
-
 \begin{corollary}
@@
 \end{corollary}
-
-\vspace{5mm}
 
@@
 which will be submitted soon to arXiv.
-\\
+
 \begin{lemma}
@@
 \end{lemma}
-\vspace{5mm}
+
+% Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
+% we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero.
+Then we can use the continuous-time BIZ algorithm in the limit, i.e.
+we can use $\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
+% of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. The details may be found in the full version of this paper \cite{fullpaper}. 
+The following lemma allows us to use the continuous-time BIZ algorithm in the limit. A proof Lemma~\ref{l:interpolation} may be found in a full version of this paper \cite{fullpaper}.
+
+\begin{lemma}
+If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
+distributed with finite variance and independent, over time and across alternatives, then
+\begin{equation*}
+    \lim_{\delta\rightarrow0} \mathbb{P}\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right) = \lim_{\delta\rightarrow0}
+ \mathbb{P}\left(
+ f\left(\mathcal{C}\left(\delta,t\right),\delta\right)=1
+ \right).
+\end{equation*}
+
+\label{l:interpolation}
+\end{lemma}
 
@@
 distributed and independent, over time and across alternatives, then
-$\mbox{lim}_{\delta\rightarrow0}Pr\left\{ \mbox{BIZ selects }k\right\} \geq P*$
+$\mbox{lim}_{\delta\rightarrow0}\mbox{PCS}(\delta) \geq P*$
 provided $\mu_{k}=a_{k}\delta,\mu_{k-1}=a_{k-1}\delta,\ldots,\mu_{1}=a_{1}\delta$,
@@
 \[
-\inf_{a\in PZ\left(1\right)}\mbox{lim}_{\delta\rightarrow0}\mathbb{P}\left(CS_{\delta}\right)=P^{*}
+\inf_{a\in PZ\left(1\right)}\mbox{lim}_{\delta\rightarrow0}\mbox{PCS}(\delta)=P^{*}
 \]
@@
 \begin{equation*}
-    \mbox{PCS}(\delta) = P\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right).
+    \mbox{PCS}(\delta) =  \mathbb{P}\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right).
 \end{equation*}
-By Lemma~\ref{l:new}, as $\delta\to0$, we have that 
+By Lemma~\ref{l:interpolation}, as $\delta\to0$, we have that 
 \begin{equation}
@@
 We show the performance of the BIZ procedure in discrete time with maximum elimination
-($c=1-(P^*)^\frac{1}{k-1}$)when $\delta$ goes to zero. We plot both the PCS and the expected total number 
-of samples simulated divided by the number of systems, denoted by $E[N]/k$. We consider this quotient 
-to normalize the number of samples used by the algorithm.
+($c=1-(P^*)^\frac{1}{k-1}$) when $\delta$ goes to zero. We plot the PCS of three different examples.
 
@@
 When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the
-BIZ procedure.
+BIZ procedure. Here, the points plotted have central confidence intervals of length at most $0.014$.
 
@@
   \centering
-   \begin{subfigure}[b]{0.4\textwidth}
+   \begin{subfigure}[b]{0.3\textwidth}
       \centering
        \includegraphics[width=0.7\textwidth]{plot5}
-    \caption{Known variances and $P^*=0.9$. In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero.
+    \caption{
     \label{fig: tahi3}}
@@
     \hfill
-    \begin{subfigure}[b]{0.4\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
         \centering
          \includegraphics[width=0.7\textwidth]{plot3}
-             \caption{Unknown variances and $P^*=0.9$.
-In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero.
-If we want that the IZ guarantee be
-    satisfied in all the cases, we can just increment $n_{0}$.
+             \caption{
     \label{fig: tahi2}}
@@
         \hfill
-    \begin{subfigure}[b]{0.4\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
         \centering
          \includegraphics[width=0.7\textwidth]{plot1}
-    \caption{Known variances, $P^*=0.9$ This was a hard example to find and it was specially chosen to ilustrate our theorem.
+    \caption{ \label{fig: tahi}}
+    \end{subfigure}
+    \caption{(a)  Known variances and $P^*=0.9$.
+In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero.
+(b) Unknown variances and $P^*=0.9$.
+In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero.
+If we want that the IZ guarantee be satisfied in all the cases, we can just increment $n_{0}$.
+(c) Known variances, $P^*=0.9$ This was a hard example to find and it was specially chosen to illustrate our theorem.
 In practice, we would choose $n_{0}>0$ and the IZ guarantee will be satisfied.
-\label{fig: tahi}}
-    \end{subfigure}
-    \caption{PCS for different numerical experiments
 \label{fig:tahi10}}
@@
 this is a difficult example, and still we have a good performance in most of the cases. However, if we want to always satisfy the IZ guarantee, 
-we can just increment the parameter $n_{0}$.
+we can just increment the parameter $n_{0}$. Here, the points plotted have central confidence intervals of length at most $0.014$.
 
@@
 within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. Here, $P^*=0.9$ and $n_{0}=0$.
-This configurations was specially chosen to ilustrate our theorem, and so it is harder than typical configurations.
+This configurations was specially chosen to illustrate our theorem, and so it is harder than typical configurations.
 In fact, in most of the configurations the algorithm always satisfies the IZ guarantee. Furthermore, in practice, we would
@@
 Figure ~\ref{fig: tahi} shows that PCS converges to $0.9$ as $\delta$ goes to zero. Specifically, PCS is equal to $0.904$ when $\delta=0.1$.
-This figure also shows that the bound is tight  on probability of correct selection. We should also note that the number of samples required increases very fast. 
+This figure also shows that the bound is tight  on probability of correct selection.
+We should also note that the number of samples required increases very fast.
 Here, the points plotted have central confidence intervals of length at most $0.014$.

### 2015-05-07 paper/wish/wsc15paper.tex
meeting
changes to text during meeting

@@
 Conservatism leads classical IZ procedures to take too many samples in problems with many alternatives. The Bayes-inspired
-Indifference Zone (BIZ) procedure, proposed in \citeN{Frazier:BIZ}, is
+Indifference Zone (BIZ) procedure, proposed in Frazier (2014), is
 less conservative than previous procedures, but its proof of validity
@@
 
-\citeN{Frazier:BIZ} eliminates the use of Bonferroni's inequality, reducing conservatism. This paper presents a new sequential elimination
-IZ procedure, called BIZ (Bayes-inspired Indifference Zone), whose
-lower bound on worst-case probability of correct selection in the
+In addition to Bonferroni's inequality, two other common sources of conservatism in indifference-zone ranking and selection procedures are the change from discrete time to continuous time often used to show IZ guarantees, and the fact that typically, the configuration under consideration is not a worst-case configuration \cite{Kim:Conserv}.
+The difference between worst and typical cases tends to contribute the most to conservatism, with Bonferonni's inequality contributing second-most, and the continuous/discrete time difference contributing the least \cite{Kim:Conserv}.
+Although the difference between the worst and typical cases is the largest contributor to conservatism, all indifference zone procedures must meet the PCS guarantee for all configurations in the preference zone, including worst-case configurations, and so this source of conservatism is fundamental to the indifference-zone formulation.
+Thus, eliminating the use of Bonferroni's inequality remains an important route for reducing conservatism while still retaining the indifference-zone guarantee.
+
+\citeN{Frazier:BIZ} presents a new sequential elimination
+IZ procedure, called BIZ (Bayes-inspired Indifference Zone), 
+that eliminates the use of Bonferroni's inequality, reducing conservatism. 
+This procedure's lower bound on worst-case probability of correct selection in the
 preference zone is tight in continuous time, and almost tight in the
@@
 especially on problems with many alternatives. Unfortunately, the
-proof that the BIZ procedure satisfies the IZ guarantee for the discrete-time
-case assumes that variances are known and have an integer multiple
-structure which is not very realistic.
+proof from \cite{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
+(2) variances are known;
+and (3) the variances are either common across alternatives, or have an unrealistic integer multiple structure.
 
-The contribution of this work is that we prove the asymptotic validity of the 
-BIZ procedure for the discrete-time case when the variances are known and $\delta$ goes to zero. 
-In order to simplify analysis, we consider a slightly modification of this procedure.
-Although we only proved it in the known variance setting, it is still a significantly
-generalization over the assumption that the variances are known and have an integer multiple
-structure. Furthermore, we do not need to assume that the alternatives follow a normal distribution. 
-The only assumptios are that the alternatives are independent, identically distributed and have
-finite variance. We conjecture that these techniques can be used to show the validity of this procedure when
+The contribution of this work is to prove the asymptotic validity of the BIZ procedure as $\delta$ goes to zero, retaining the assumption of known variances, but replacing assumptions (1) and (3) by the much weaker assumption of independent and identically distributed finite variance samples.
+Thus, our proof allows a much broader set of sampling distributions than that allowed by \cite{Frazier:BIZ}, including non-normal samples and general heterogeneous variances.
+We also show that this bound on worst-case PCS is asymptotically tight as $\delta$ goes to zero, 
+showing that the BIZ procedure successfully eliminates conservatism due to Bonferonni's inequality in this more general setting, just as was demonstrated by \citeN{Frazier:BIZ} for more restricted settings.
+
+To simplify our analysis, we analyze a slight modification of the version of the BIZ procedure presented in \cite{Frazier:BIZ}, which keeps a certain parameter $\lambda^2_z$ fixed rather than letting it vary as did \cite{Frazier:BIZ}.
+Numerical experiments on typical cases show little difference in performance between the version of BIZ we analyze and the version in \cite{Frazier:BIZ}.
+We conjecture that a proof technique similar to the one presented here can be used to show asymptotic validity of the BIZ procedure when
 the variances are unknown, and we present numerical experiments that support this belief. 
-\citeN{kim:asympt} also proves the asymptotical validity of a IZ procedure in the same limit.
-Our proof shares some similarities since we both use a central limit theorem.
-
-Two other common sources of conservatism are the change from discrete-time processes to continuous-time processes used to show IZ guarantees, and the fact that typically, the configuration under consideration is not a worst-case configuration \cite{Kim:Conserv}.
-This last source tends to be the largest in terms of its contribution to conservatism, and the first tends to be the smallest, with the contribution from Bonferonni inequality's lying between \cite{Kim:Conserv}.
-Although the BIZ procedure avoids the Bonferonni inequality, it does not avoid these other two sources of conservatism.
-Indeed, all indifference zone procedures must meet the PCS guarantee for all configurations in the preference zone, including worst-case configurations.
-In this sense, this last source of conservatism arises from the indifference zone guarantee itself, rather than the from a design of a particular procedure.
+% \citeN{kim:asympt} also proves the asymptotical validity of a IZ procedure in the same limit.
+% Our proof shares some similarities since we both use a central limit theorem.
 
@@
 \section{THE BAYES-INSPIRED IZ (BIZ) PROCEDURE}
+\label{sec:BIZ}
 
@@
 % of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. The details may be found in the full version of this paper \cite{fullpaper}. 
-The following lemma allows us to use the continuous-time BIZ algorithm in the limit. A proof Lemma~\ref{l:interpolation} may be found in a full version of this paper \cite{fullpaper}.
+The following lemma shows that the difference in the correct selection events obtained from applying the BIZ selection map $h$ to the discrete-time and continuous-time versions of $q_{tx}(A)$ vanish as $\delta$ goes to $0$.
+A proof of Lemma~\ref{l:interpolation} may be found in a full version of this paper \cite{fullpaper}.
 
 \begin{lemma}
-If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
-distributed with finite variance and independent, over time and across alternatives, then
-\begin{equation*}
-    \lim_{\delta\rightarrow0} \mathbb{P}\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right) = \lim_{\delta\rightarrow0}
+% If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
+% distributed with finite variance and independent, over time and across alternatives, then
+    $\lim_{\delta\rightarrow0} \mathbb{P}\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right) = \lim_{\delta\rightarrow0}
  \mathbb{P}\left(
  f\left(\mathcal{C}\left(\delta,t\right),\delta\right)=1
- \right).
-\end{equation*}
+ \right)$.
 
@@
 \begin{theorem}
+\label{t:main}
 If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
@@
 \end{equation*}
-By Lemma~\ref{l:interpolation}, as $\delta\to0$, we have that 
+By Lemma~\ref{l:interpolation}, we have that 
 \begin{equation}
@@
  f\left(\mathcal{C}\left(\delta,t\right),\delta\right)=1
- \right)
+ \right).
  \label{eq:convergence1}
@@
 \lim_{\delta\rightarrow0}\mathbb{P}\left(f\left(\mathcal{C}\left(\delta,t\right),\delta\right)=1\right)
- = \mathbb{P}\left(g\left(W\right)=1\right)
+ = \mathbb{P}\left(g\left(W\right)=1\right).
  \label{eq:convergence2}
@@
 
-We show the performance of the BIZ procedure in discrete time with maximum elimination
-($c=1-(P^*)^\frac{1}{k-1}$) when $\delta$ goes to zero. We plot the PCS of three different examples.
+We now use simulation experiments to illustrate and further investigate the phenomenon characterized by Theorem~\ref{t:main}.
+Using the version of BIZ described in Section~\ref{sec:BIZ} with maximum elimination ($c=1-(P^*)^\frac{1}{k-1}$), we estimate and then plot the PCS as a function of $\delta$ using 10,000 independent replications.
+We consider three different examples, setting $P^*=0.9$ in all three.
 
-First, we consider the known variance case. Specifically, we consider a slippage configuration 
-with $100$ systems normally distributed, where $\mu_{k}=\delta,\mu_{k-1}=0,\dots,\mu_{1}=0$, $\delta$ is 
-within the interval $[0.1,10]$, and $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5$. Here, $P^*=0.9$ and $n_{0}=0$.
-Figure ~\ref{fig: tahi3} shows that in this case the IZ guarantee is always satisfied, and the bound on probability of correct selection is tight when $\delta$ goes to zero.
-When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the
-BIZ procedure. Here, the points plotted have central confidence intervals of length at most $0.014$.
+Our first example, illustrated in Figure~\ref{fig: tahi3}, is a known variance slippage configuration.
+Specifically, we consider $100$ systems with independent normally distributed samples, where $\mu_{k}=\delta,\mu_{k-1}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5$.
+Here, $n_{0}=0$.
+Figure ~\ref{fig: tahi3} shows that in this example the IZ guarantee is always satisfied, and the PCS approaches $P^*$ as $\delta$ goes to zero.
+When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the BIZ procedure.
+Here, the points plotted have central confidence intervals of length at most $0.014$.
 
@@
       \centering
-       \includegraphics[width=0.7\textwidth]{plot5}
+       \includegraphics[width=\textwidth]{plot5}
     \caption{
@@
         \centering
-         \includegraphics[width=0.7\textwidth]{plot3}
+         \includegraphics[width=\textwidth]{plot3}
              \caption{
@@
         \centering
-         \includegraphics[width=0.7\textwidth]{plot1}
+         \includegraphics[width=\textwidth]{plot1}
     \caption{ \label{fig: tahi}}
@@
 \label{fig:tahi10}}
-
 \end{figure}
 
-We now consider the unknown variance case. Specifically, we consider a slippage configuration 
-with $100$ systems normally distributed, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is 
-within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. Here, $P^*=0.9$ and $n_{0}=15$.
-Figure ~\ref{fig: tahi2} gives us evidence that our theorem should also be true when the variances are unknown. We should note that
+Our second example, illustrated in Figure~\ref{fig: tahi2}, is an unknown variance slippage configuration.
+Although Theorem~\ref{t:main} applies only to the known-variance version of BIZ, we conjecture that the unknown-variance version of BIZ should exhibit similar behavior.
+In this example, we consider $100$ systems with independent normally distributed samples, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$.
+We set $n_{0}=15$.
+In this example, we have intentionally chosen $n_0$ to be small, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
+
+We should note that
 this is a difficult example, and still we have a good performance in most of the cases. However, if we want to always satisfy the IZ guarantee, 
@@
 His research interests include optimal learning, sequential decision-making under uncertainty, and machine learning, focusing on applications in simulation optimization, design of experiments, materials science, e-commerce and medicine.
-He is a member of INFORMS, and SIAM.
+He is the secretary of the INFORMS Simulation Society.
 His e-mail address is \email{pf98@cornell.edu}.\\

### 2015-05-07 paper/wish/wsc15paper.tex
Finishing compilation after getting all images.

@@
 We now use simulation experiments to illustrate and further investigate the phenomenon characterized by Theorem~\ref{t:main}.
-Using the version of BIZ described in Section~\ref{sec:BIZ} with maximum elimination ($c=1-(P^*)^\frac{1}{k-1}$), we estimate and then plot the PCS as a function of $\delta$ using 10,000 independent replications.
-We consider three different examples, setting $P^*=0.9$ in all three.
+Using the version of BIZ described in Section~\ref{sec:BIZ} with maximum elimination ($c=1-(P^*)^\frac{1}{k-1}$), we estimate and then plot the PCS as a function of $\delta$.
+In all examples, $P^*=0.9$, PCS was estimated using 10,000 independent replications, and confidence intervals have length at most $0.014$.
 
@@
 When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the BIZ procedure.
-Here, the points plotted have central confidence intervals of length at most $0.014$.
 
@@
       \centering
-       \includegraphics[width=\textwidth]{plot5}
+       \includegraphics[width=\textwidth]{plot5.pdf}
     \caption{
@@
         \centering
-         \includegraphics[width=\textwidth]{plot3}
+         \includegraphics[width=\textwidth]{unknown.pdf}
              \caption{
@@
         \centering
-         \includegraphics[width=\textwidth]{plot1}
+         \includegraphics[width=\textwidth]{plot3.pdf}
     \caption{ \label{fig: tahi}}
@@
 this is a difficult example, and still we have a good performance in most of the cases. However, if we want to always satisfy the IZ guarantee, 
-we can just increment the parameter $n_{0}$. Here, the points plotted have central confidence intervals of length at most $0.014$.
+we can just increment the parameter $n_{0}$.
 
@@
 Figure ~\ref{fig: tahi} shows that PCS converges to $0.9$ as $\delta$ goes to zero. Specifically, PCS is equal to $0.904$ when $\delta=0.1$.
-This figure also shows that the bound is tight  on probability of correct selection.
-We should also note that the number of samples required increases very fast.
-Here, the points plotted have central confidence intervals of length at most $0.014$.
+This figure also shows that the bound is tight  on probability of correct selection. We should also note that the number of samples required increases very fast.
 

### 2015-05-08 paper/wish/wsc15paper.tex
5-8-15

@@
 %THE NON-NORMAL KNOWN VARIANCE CASE}
-THE GENERAL DISTRIBUTION  KNOWN VARIANCE CASE}
+THE NON-NORMAL KNOWN VARIANCE CASE}
 
@@
 This is called the ranking and selection problem.
-% In such ranking and selection problems, we must decide how many samples we need to accurately find the alternative with the largest mean. 
 A good procedure for addressing this problem should be both efficient and accurate, i.e. it should balance the number of samples it takes with the quality of its selection.
@@
 than necessary. The Bonferonni-based bounds underlying these procedures become looser, and the tendency to take more samples than necessary increases, as the number of alternatives grow.
-More recently, new algorithms were developed in \citeN{Kim:2001}, \citeN{Goldsman:2002}, 
+More recently, new algorithms were developed in \citeN{Kim:2001}, \shortciteN{Goldsman:2002}, 
 \citeN{Hong}, and they improve performance but they still
@@
 the variances are unknown, and we present numerical experiments that support this belief.
-% \citeN{kim:asympt} also proves the asymptotical validity of a IZ procedure in the same limit.
-% Our proof shares some similarities since we both use a central limit theorem.
 
@@
 are identically distributed and independent, over time and across alternatives, and
-each alernative $x$ has mean $\mu_{x}$. We define $\mu=(\mu_{1},\ldots,\mu_{k})$.
+each alternative $x$ has mean $\mu_{x}$. We define $\mu=(\mu_{1},\ldots,\mu_{k})$.
 
@@
 $B_{x}$ controls the number of samples taken from system $x$ in
-each stage. The procedure presented is a slightly modification of the original BIZ 
-procedure where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead 
-of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.
+each stage. To simplify our analysis, the procedure presented is a slight modification of the original BIZ 
+procedure \cite{Frazier:BIZ} where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead 
+of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$. Numerical experiments on 
+common cases show little difference in the PCS between the version of BIZ
+we analyze and the version in \cite{Frazier:BIZ}.
 
@@
 In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$.
-The algorithm 2 can be generalized to the continuous case (See  \citeN{Frazier:BIZ}).
+The algorithm can be generalized to the continuous case (see  \citeN{Frazier:BIZ}).
 
@@
 
-% Thus, we can see the selection decision resulting from BIZ as being closely app
-
 With these pieces in place, the last part of our proof is to observe that (1) $\mathcal{C}\left(\delta,\cdot\right)$
@@
 \begin{lemma}
-% For each $x\in\left\{ 1\ldots,k\right\} $, we define
-% \[
-% % \mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
-% \]
-% where $Y_{n,x}$ is the sum of the first $n$ samples from alternative
-$x$. 
 Let $x\in\left\{ 1\ldots,k\right\} $, then
@@
 
-% Observe that $\mathcal{C}\left(\delta,\cdot\right)\in D\left[0,\infty\right)^{k}$ and the convergence of Lemma 1 is in $D\left[0,\infty\right)^{k}$, consequently the following natural step is to generalize the continuous-time procedure for the heterogeneous variance setting, see Appendix B, to the space $D\left[0,\infty\right)^{k}$.
 To accomplish the first part, for each $F\in D\left[0,\infty\right)^{k}$, 
@@
 we get $q_{tx}\left(A\right)$ in \eqref{eq:q}.
-% In this sense, 
-% we consider to be $q_{tx}^{F,\delta}\left(A\right)$ a ``non-centralized'' version of $F$.
 
@@
 More precisely, $f(F,\delta)$ is defined to be
-% Using the
-% continuous-time procedure for the heterogeneous variance setting with
-% the paths $\left(q_{tx}^{F,\delta}\left(A\right):t\geq0\right)$,
-% we see that there exists a selection decision for each $F\in D\left[0,\infty\right)^{k}$.
-% Since we are interested in the right selection, ( i.e. in choosing
-% $k$) for each $F\in D\left[0,\infty\right)^{k}$, we define the following
-% function 
 \begin{eqnarray*}
@@
 \end{eqnarray*}
- % Observe that $f$ is a function that depends in the path $\left\{ q_{tx}^{F,\delta}\left(A\right):t\geq0\right\} $.
 
-%We are doing all this because we want to see that $f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)$
-%looks like the right or wrong selection decision of an algorithm that
-%depends on a standard Brownian motion instead of $\mathcal{C}\left(\delta,\cdot\right)$,
-%and this will give us the proof because we will be able to use the
-%theory developed by Frazier (2014) to prove the theorem. Thus, the
 We now construct a function $g(\cdot)$ that, when applied to the path of a $k$-dimensional standard Brownian motion, will be equal in distribution to the indicator of the correct selection event from the continuous-time BIZ procedure from \cite{Frazier:BIZ}
-% to a problem with indifference-zone parameter equal to 1, where each alternative's observation process has volatility $\lambda_z$ and drift $a_x$.
 to a transformed problem that does not depend on $\delta$.
@@
 This path is
-% Going back to the proof outline, 
-% the next step is to find the limit of $q_{tx}^{F,\delta}\left(A\right)$
-% when $\delta$ goes to zero, which we denote $q_{tx}^{F}\left(A\right)$, 
-% and is equal to
 \[
@@
 Then, $g$ is defined to be
- %Using the same previous idea, for each $F\in D\left[0,\infty\right)^{k}$,
-%we define the new functions
 \begin{eqnarray*}
@@
 
-% Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
-% we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero.
-Then we can use the continuous-time BIZ algorithm in the limit, i.e.
-we can use $\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
-% of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. The details may be found in the full version of this paper \cite{fullpaper}. 
 The following lemma shows that the difference in the correct selection events obtained from applying the BIZ selection map $h$ to the discrete-time and continuous-time versions of $q_{tx}(A)$ vanish as $\delta$ goes to $0$.
@@
 \begin{lemma}
-% If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
-% distributed with finite variance and independent, over time and across alternatives, then
     $\lim_{\delta\rightarrow0} \mathbb{P}\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right) = \lim_{\delta\rightarrow0}
@@
 \end{theorem}
-
-%By the comments given at the beginning of this section, we know that
-%we can work with the algorithm, which we call the discrete-time BIZ algorithm, defined by
-
-%\[
-%q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
-%\]
-%where $t\in\delta^{2}\mathbb{N}$, instead of the algorithm defined
-%by
-%\[
-%q'_{tx}\left(A\right)=q'\left(\left(Z_{tx},t:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
-%\]
-%where $t\in\mathbb{N}$.
-%
-%Now, we define
-%\begin{eqnarray*}
-%%\hat{\tau}_{n+1}\left(\delta\right) & = & \mbox{inf}\left\{ t\in\left\{ \tau_{n}\delta^{2},\left(\tau_{n}+1\right)\delta^{2},\ldots\right\} :\mbox{ min}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\geq P_{n}\right\}
-%\end{eqnarray*}
-% The corresponding BIZ algorithm is called the continuous-time BIZ algorithm. We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
-% which are defined as
-
-% Maybe some of this goes into the proof of the new lemma
-\[
-% \tau_{n+1}=\mbox{inf}\left\{ t\geq\tau_{n}:\mbox{ min}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\geq P_{n}\right\} .
-\]
-
-% Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
-% we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero.
-Then we can use the continuous-time BIZ algorithm in the limit, i.e.
-we can use $\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
-% of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. The details may be found in the full version of this paper \cite{fullpaper}.
-
-% and allows us to use Theorem~5.5 of \citeN{billingsley:convergence}.
 
@@
 
-Our first example, illustrated in Figure~\ref{fig: tahi3}, is a known variance slippage configuration.
-Specifically, we consider $100$ systems with independent normally distributed samples, where $\mu_{k}=\delta,\mu_{k-1}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5$.
-Here, $n_{0}=0$.
-Figure ~\ref{fig: tahi3} shows that in this example the IZ guarantee is always satisfied, and the PCS approaches $P^*$ as $\delta$ goes to zero.
-When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the BIZ procedure.
-
 \begin{figure}[h]
@@
        \includegraphics[width=\textwidth]{plot5.pdf}
-    \caption{
+    \caption{Known heterogeneous variances, 
+        $\lambda^2_k = 0.25$, $\lambda_{1}^2 = 1$, $n_0=0$.
     \label{fig: tahi3}}
@@
              \caption{
+    Unknown highly heterogeneous variances, 
+    $\lambda^2_{k} = 100$, $\lambda_{1}^2 = 1$, $n_0=15$.
     \label{fig: tahi2}}
@@
          \includegraphics[width=\textwidth]{plot3.pdf}
-    \caption{ \label{fig: tahi}}
+    \caption{ 
+    Known highly heterogeneous variances, 
+    $\lambda^2_{k} = 100$, $\lambda_{1}^2 = 1$, $n_0=0$.
+        \label{fig: tahi}}
     \end{subfigure}
-    \caption{(a)  Known variances and $P^*=0.9$.
-In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero.
-(b) Unknown variances and $P^*=0.9$.
-In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero.
-If we want that the IZ guarantee be satisfied in all the cases, we can just increment $n_{0}$.
-(c) Known variances, $P^*=0.9$ This was a hard example to find and it was specially chosen to illustrate our theorem.
-In practice, we would choose $n_{0}>0$ and the IZ guarantee will be satisfied.
+\caption{
+    The PCS of the BIZ procedure versus $\delta$ for three different slippage configurations with 100 alternatives and $P^*=0.9$.
+    We observe in all three examples that the PCS converges to $P^*$ as $\delta$ goes to $0$.
+    The first example (a) shows typical behavior, where the PCS is above $P^*$ for all values of $\delta$.
+    The second (b) and third (c) examples are atypical, and were chosen specially to illustrate that BIZ can underdeliver on PCS in slippage configurations when $n_0$ is small and the variance of the best alternative is much larger than the variance of the other alternatives.
 \label{fig:tahi10}}
@@
 
-Our second example, illustrated in Figure~\ref{fig: tahi2}, is an unknown variance slippage configuration.
+Our first example, illustrated in Figure~\ref{fig: tahi3}, is a known variance slippage configuration where the variance of the best alternative is 1/4 of the variance of the worst alternative.
+Specifically, we consider $100$ systems with independent normally distributed samples, where $\mu_{k}=\delta,\mu_{k-1}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5$.
+Here, $n_{0}=0$.
+Figure~\ref{fig: tahi3} shows that in this example the IZ guarantee is always satisfied.
+Moreover, the PCS approaches $P^*$ as $\delta$ goes to zero, as predicted by Theorem~\ref{t:main}.
+When $\delta$ is big enough, the PCS is almost one because the difference between the best system and the others is large enough to be easily identifiable by the BIZ procedure.
+
+Our second example, illustrated in Figure~\ref{fig: tahi2}, is an unknown variance slippage configuration where the variance of the best alternative is 100 times larger than the variance of the other alternatives.
 Although Theorem~\ref{t:main} applies only to the known-variance version of BIZ, we conjecture that the unknown-variance version of BIZ should exhibit similar behavior.
@@
 We set $n_{0}=15$.
+As $\delta$ goes to $0$, we observe that the PCS converges to $P^*$, as it did in the known-variance slippage configuration example.
 In this example, we have intentionally chosen $n_0$ to be small, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
+Increasing the parameter $n_0$ typically causes BIZ to meet the IZ guarantee for all $\delta$, and we recommend a larger value of $n_0$ in practice.
 
-We should note that
-this is a difficult example, and still we have a good performance in most of the cases. However, if we want to always satisfy the IZ guarantee, 
-we can just increment the parameter $n_{0}$.
-
-Now, we consider a pathological case when the variances are known. Specifically, we consider a slippage configuration 
-with $100$ systems normally distributed, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is 
-within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. Here, $P^*=0.9$ and $n_{0}=0$.
-This configurations was specially chosen to illustrate our theorem, and so it is harder than typical configurations.
-In fact, in most of the configurations the algorithm always satisfies the IZ guarantee. Furthermore, in practice, we would
-have run the algorithm with $n_{0}>0$, and the BIZ algorithm would have worked well even in this pathological example. 
-Figure ~\ref{fig: tahi} shows that PCS converges to $0.9$ as $\delta$ goes to zero. Specifically, PCS is equal to $0.904$ when $\delta=0.1$.
-This figure also shows that the bound is tight  on probability of correct selection. We should also note that the number of samples required increases very fast.
+Our third example, illustrated in Figure~\ref{fig: tahi}, uses the same sampling distributions as the second example, but assumes the variances are known, and sets $n_0=0$.
+The effect of this change, and especially of setting $n_0$ to $0$, is to cause significant underdelivery on PCS for large values of $\delta$.  
+As remarked above, this example was chosen specially to illustrate that BIZ can underdeliver on PCS in slippage configurations when $n_0$ is small, and the variance of the best alternative is much larger than the variance of the worst alternative.
+However, as predicted by Theorem~\ref{t:main}, the PCS converges to $P^*$ as $\delta$ grows small, even in this pathological case.
 
@@
 We have proved the asymptotic validity of the Bayes-inspired Zone
-procedure \cite{Frazier:BIZ} when the variances are known, which is a
-new sequential elimination procedure. This algorithm is relevant because
-it takes fewer samples than other IZ procedures, especially for problems
-with large numbers of alternatives. Even though this proof does not
-guarantee that the algorithm will work for any sample, we know that
-it will work if the alternatives are not very different, which are
-the most difficult cases.
+procedure \cite{Frazier:BIZ} when the variances are known.
+This algorithm takes fewer samples than other IZ procedures, especially for
+problems with large numbers of alternatives, and so characterizing when it
+satisfies the indifference-zone guarantee is important for understanding when
+it should be used in practice.
 

### 2015-05-08 paper/wish/wsc15paper.tex
last version

@@
 To simplify our analysis, we analyze a slight modification of the version of the BIZ procedure presented in \cite{Frazier:BIZ}, which keeps a certain parameter $\lambda^2_z$ fixed rather than letting it vary as did \cite{Frazier:BIZ}.
-Numerical experiments on typical cases show little difference in performance between the version of BIZ we analyze and the version in \cite{Frazier:BIZ}.
+Numerical experiments on typical cases show little difference in performance between the version of BIZ we analyze and the version in \citeN{Frazier:BIZ}.
 We conjecture that a proof technique similar to the one presented here can be used to show asymptotic validity of the BIZ procedure when
@@
 
-Frazier \cite{Frazier:BIZ} showed that the BIZ procedure with known common variance
-satisfies the IZ guarantee when the systems follow the normal distribution
-, with tight bounds on worst-case preference-zone in continuous time.
-He also proved that this procedure retains the IZ guarantee when the
-systems follow the normal distribution, and the variances are known
-and are integer multiples of a common value. The continuous time version
-of this procedure also satisfies the IZ guarantee, with a tight worst-case
+\citeN{Frazier:BIZ} shows that the BIZ procedure satisfies the IZ guarantee 
+under the assumptions that samples are normally distributed, variances are known, and
+the variances are either common across alternatives, or have an integer multiple structure.
+The continuous time version of this procedure also satisfies the IZ guarantee, with a tight worst-case
 preference-zone PCS bound.
 
-The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
+A slight modification of the discrete-time BIZ procedure for unknown and/or heterogeneous sampling
 variances is given below.  It takes a variable number of samples
@@
 depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
-and $n_{0}$. $n_{0}$ is the number of samples to use in the first
-stage of samples, and $100$ is the recommended value for $n_{0}$.
+and $n_{0}$. Here, $n_{0}$ is the number of samples to use in the first
+stage of samples, and $100$ is the recommended value for $n_{0}$. The paramater
 $B_{x}$ controls the number of samples taken from system $x$ in
 each stage. To simplify our analysis, the procedure presented is a slight modification of the original BIZ 
-procedure \cite{Frazier:BIZ} where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead 
-of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$. Numerical experiments on 
-common cases show little difference in the PCS between the version of BIZ
-we analyze and the version in \cite{Frazier:BIZ}.
+procedure \cite{Frazier:BIZ} where $z \in \mbox{arg max}_{x\in A} \lambda^2_{x}$, instead 
+of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambda^2_{x}$. According to numerical experiments on common cases, there is little difference in the PCS between the version of BIZ
+we analyze and the version in \citeN{Frazier:BIZ}.
 
@@
 \STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
-Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.Let $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$.     
+Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.
+Let $t\leftarrow 0$.
+Let $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{x}$, where $\lambdahat^2_{x}$ is the empirical estimator of the variance $\lambda^2_x$ using $n_0$ samples if $x\in A$.
 \STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.

### 2015-06-09 montreal/presentation.tex
montreal

%% LyX 2.1.2.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{beamer}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{subcaption}
\captionsetup{compatibility=false}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
 % this default might be overridden by plain title style
 \newcommand\makebeamertitle{\frame{\maketitle}}%
 % (ERT) argument for the TOC
 \AtBeginDocument{%
   \let\origtableofcontents=\tableofcontents
   \def\tableofcontents{\@ifnextchar[{\origtableofcontents}{\gobbletableofcontents}}
   \def\gobbletableofcontents#1{\origtableofcontents}
 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\beamertemplateshadingbackground{red!5}{structure!5}

\usepackage{beamerthemeshadow}
\usepackage{pgfnodes,pgfarrows,pgfheaps}

\beamertemplatetransparentcovereddynamicmedium

\newcommand{\Class}[1]{\operatorname{\mathchoice
  {\text{\small #1}}
  {\text{\small #1}}
  {\text{#1}}
  {\text{#1}}}}

\newcommand{\Lang}[1]{\operatorname{\text{\textsc{#1}}}}

\newcommand{\tape}[3]{%
  \color{structure!30!bg}
  \pgfmoveto{\pgfxy(-0.5,0)}
  \pgflineto{\pgfxy(-0.6,0.1)}
  \pgflineto{\pgfxy(-0.4,0.2)}
  \pgflineto{\pgfxy(-0.6,0.3)}
  \pgflineto{\pgfxy(-0.4,0.4)}
  \pgflineto{\pgfxy(-0.5,0.5)}
  \pgflineto{\pgfxy(4,0.5)}
  \pgflineto{\pgfxy(4.1,0.4)}
  \pgflineto{\pgfxy(3.9,0.3)}
  \pgflineto{\pgfxy(4.1,0.2)}
  \pgflineto{\pgfxy(3.9,0.1)}
  \pgflineto{\pgfxy(4,0)}
  \pgfclosepath
  \pgffill

  \color{structure}  
  \pgfputat{\pgfxy(0,0.7)}{\pgfbox[left,base]{#1}}
  \pgfputat{\pgfxy(0,-0.1)}{\pgfbox[left,top]{#2}}

  \color{black}
  \pgfputat{\pgfxy(-.1,0.25)}{\pgfbox[left,center]{\texttt{#3}}}%
}

\newcommand{\shorttape}[3]{%
  \color{structure!30!bg}
  \pgfmoveto{\pgfxy(-0.5,0)}
  \pgflineto{\pgfxy(-0.6,0.1)}
  \pgflineto{\pgfxy(-0.4,0.2)}
  \pgflineto{\pgfxy(-0.6,0.3)}
  \pgflineto{\pgfxy(-0.4,0.4)}
  \pgflineto{\pgfxy(-0.5,0.5)}
  \pgflineto{\pgfxy(1,0.5)}
  \pgflineto{\pgfxy(1.1,0.4)}
  \pgflineto{\pgfxy(0.9,0.3)}
  \pgflineto{\pgfxy(1.1,0.2)}
  \pgflineto{\pgfxy(0.9,0.1)}
  \pgflineto{\pgfxy(1,0)}
  \pgfclosepath
  \pgffill

  \color{structure}  
  \pgfputat{\pgfxy(0.25,0.7)}{\pgfbox[center,base]{#1}}
  \pgfputat{\pgfxy(0.25,-0.1)}{\pgfbox[center,top]{#2}}

  \color{black}
  \pgfputat{\pgfxy(-.1,0.25)}{\pgfbox[left,center]{\texttt{#3}}}%
}

\pgfdeclareverticalshading{heap1}{\the\paperwidth}%
  {color(0pt)=(black); color(1cm)=(structure!65!white)}
\pgfdeclareverticalshading{heap2}{\the\paperwidth}%
  {color(0pt)=(black); color(1cm)=(structure!55!white)}
\pgfdeclareverticalshading{heap3}{\the\paperwidth}%
  {color(0pt)=(black); color(1cm)=(structure!45!white)}
\pgfdeclareverticalshading{heap4}{\the\paperwidth}%
  {color(0pt)=(black); color(1cm)=(structure!35!white)}
\pgfdeclareverticalshading{heap5}{\the\paperwidth}%
  {color(0pt)=(black); color(1cm)=(structure!25!white)}
\pgfdeclareverticalshading{heap6}{\the\paperwidth}%
  {color(0pt)=(black); color(1cm)=(red!35!white)}

\newcommand{\heap}[5]{%
  \begin{pgfscope}
    \color{#4}
    \pgfheappath{\pgfxy(0,#1)}{\pgfxy(-#2,0)}{\pgfxy(#2,0)}
    \pgfclip
    \begin{pgfmagnify}{1}{#1}
      \pgfputat{\pgfpoint{-.5\paperwidth}{0pt}}{\pgfbox[left,base]{\pgfuseshading{heap#5}}}
    \end{pgfmagnify}
  \end{pgfscope}
  %\pgffill

  \color{#4}
  \pgfheappath{\pgfxy(0,#1)}{\pgfxy(-#2,0)}{\pgfxy(#2,0)}
  \pgfstroke

  \color{white}
  \pgfheaplabel{\pgfxy(0,#1)}{#3}%
}

\newcommand{\langat}[2]{%
  \color{black!30!beamerexample}
  \pgfsetlinewidth{0.6pt}
  \pgfsetendarrow{\pgfarrowdot}
  \pgfline{\pgfxy(-3.5,#1)}{\pgfxy(0.05,#1)}
  \color{beamerexample}
  \pgfputat{\pgfxy(-3.6,#1)}{\pgfbox[right,center]{#2}}%
}

\newcommand{\langatother}[2]{%
  \color{black!30!beamerexample}
  \pgfsetlinewidth{0.6pt}
  \pgfsetendarrow{\pgfarrowdot}
  \pgfline{\pgfxy(3.5,#1)}{\pgfxy(-0.05,#1)}
  \color{beamerexample}
  \pgfputat{\pgfxy(3.6,#1)}{\pgfbox[left,center]{#2}}%
}

\pgfdeclaremask{knight1-mask}{beamer-knight1-mask} \pgfdeclareimage[height=2cm,mask=knight1-mask]{knight1}{beamer-knight1} \pgfdeclaremask{knight2-mask}{beamer-knight2-mask} \pgfdeclareimage[height=2cm,mask=knight2-mask]{knight2}{beamer-knight2} \pgfdeclaremask{knight3-mask}{beamer-knight3-mask} \pgfdeclareimage[height=2cm,mask=knight3-mask,interpolate=true]{knight3}{beamer-knight3} \pgfdeclaremask{knight4-mask}{beamer-knight4-mask} \pgfdeclareimage[height=2cm,mask=knight4-mask,interpolate=true]{knight4}{beamer-knight4}

\pgfdeclareradialshading{graphnode}
  {\pgfpoint{-3pt}{3.6pt}}%
  {color(0cm)=(beamerexample!15);
    color(2.63pt)=(beamerexample!75);
    color(5.26pt)=(beamerexample!70!black);
    color(7.6pt)=(beamerexample!50!black);
    color(8pt)=(beamerexample!10!bg)}

\newcommand{\graphnode}[2]{
  \pgfnodecircle{#1}[virtual]{#2}{8pt}
  \pgfputat{#2}{\pgfbox[center,center]{\pgfuseshading{graphnode}}}
}

\makeatother

\usepackage{babel}
\begin{document}

\title{Asymptotic Validity of the Bayes-Inspired Indifference Zone Procedure:
the Non-Normal Known Variance Case}

\author{Saul Toscano-Palmerin\\
Peter Frazier}

\institute{School of Operations Research and Information Engineering, Cornell
University\\
}

\date{June 14, 2015\\
}
\makebeamertitle
\begin{frame}{Indifference-Zone Ranking and Selection}

\begin{block}{}

\begin{itemize}
\item Ranking and Selection is a problem where we have to select the best
alternative among $\left\{ \mu_{1},\mu_{2},\ldots,\mu_{k}\right\} $
based on iid samples. \\
\textrm{}\\
\item If a procedure chooses $\hat{x}$, the probability of correct selection
is \[
\mbox{PCS}\left(\mu\right)=\mathbb{P}_{\mu}\left(\hat{x}\in\mbox{arg max}_{x}\mu_{x}\right).
\]\textrm{}\\
\item The preference zone is $\mbox{PZ}\left(\delta\right)=\left\{ \mu\in\mathbb{R}^{k}:\mu_{\left[k\right]}-\mu_{\left[k-1\right]}\geq\delta\right\} $.
\\
\textrm{}\\
\item A procedure meets the IZ guarantee at $P^{*}\in\left(1/k,1\right)$
and $\delta>0$ if 
\[
\mbox{PCS}\left(\mu\right)\geq P^{*}\mbox{ for all }\mu\in\mbox{PZ}\left(\delta\right).
\]
\\
\textrm{}\\
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{The Bayes-Inspired IZ (BIZ) Procedure}

\begin{block}{}

\begin{itemize}
\item BIZ is an elimination procedure that does not use Bonferroni's inequality.
\\
\textrm{}\\
\item Its lower bound on worst-case probability of correct selection in
the preference zone is tight in continuous time, and almost tight
in the discrete time.\\
\textrm{}\\
\item The number of samples required by BIZ is significantly smaller than
the KN procedure and the $\mathscr{P}_{B}^{*}$ procedure.\\
\textrm{}\\
\item It satisfies the IZ guarantee under the follwing assumptions:

\begin{itemize}
\item Normal samples.\\

\item Known variances.\\

\item Variances are either common across alternatives, or have an integer
multiple structure. 
\end{itemize}
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Asymptotic Validity}

\begin{block}{Theorem}
 If samples are iid and the variances are finite and do not depend
on $\delta$, then

\[
\mbox{inf }_{a\in\mbox{PZ}\left(1\right)}\mbox{lim}_{\delta\rightarrow0^{+}}\mbox{PCS}\left(\delta\right)=P^{*}
\]
where $\mu_{k}=a_{k}\delta,\ldots,\mu_{1}=a_{1}\delta.$ 
\end{block}
\end{frame}

\begin{frame}{The Bayes-Inspired IZ (BIZ) Procedure}

\begin{block}{}

The BIZ procedure can be viewed as the composition of three maps:\\
\textrm{}\\

\end{block}
\begin{itemize}
\item The mapping from $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$,
where $Y_{tx}$ is the sum of the first $t$ samples from alternative
$x$, onto $\left(Z_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
where $Z_{tx}=Y_{n_{tx},t}$ is the sum of samples from alternative
$x$observed by stage $t$.\\
\textrm{}\\
\item The second maps the previous time-changed random walk through a non-linear
mapping for each $t,x$ and subset $A\subset\left\{ 1,\ldots,k\right\} $,
to $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$,
where
\[
q_{tx}^{'}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right)\right.
\]

\end{itemize}
\end{frame}

\begin{frame}{The Bayes-Inspired IZ (BIZ) Procedure}

\begin{itemize}
\item The third map, $h$, maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
onto selection decisions.

\begin{itemize}
\item Finds first time $\tau_{1}$ that $q_{tx}^{'}\left(A_{0}\right)\geq P_{0}$
or $q_{tx}^{'}\left(A_{0}\right)\leq c$. In the first case, $x_{0}\in\mbox{arg max}_{x}q_{tx}^{'}\left(A_{0}\right)$
is selected as the best. In the second case, $x_{0}\in\mbox{arg min}_{x}q_{tx}^{'}\left(A_{0}\right)$
is eliminated from $A_{0}$, resulting in new parameters $A_{1}$
and $P_{1}$.\\
\textrm{}\\
\item This process is repeated until an alternative is selected as the best.\\
\textrm{}\\
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Proof Outline}

\begin{block}{}

\begin{itemize}
\item The same selection decision is obtained if we apply the map $h$ to
$\left(q_{tx}\left(A\right):t\in\delta^{2}\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
\inputencoding{latin1}{where $q_{tx}\left(A\right):=q^{'}\left(\left(Z_{\frac{t}{\delta^{2}}x}:x\in A\right),\delta,t\right)$.}\\
\inputencoding{latin9}\textrm{}\\
\item The discrete-time process is interpolated by the continuous-time process
$\left(q_{tx}\left(A\right):t\geq0,A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$.\\
\textrm{}\\
\item The selection decision between the continuous-time process and the
discrete-time process goes to zero as $\delta\rightarrow0$.\\
\textrm{}\\
\item Applying the BIZ selection map $h$ to the previous process, produces
a selection decision that satisfies the indifference-zone guarantee
as $\delta\rightarrow0$.
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Proof Outline}

\begin{block}{}

\begin{itemize}
\item \inputencoding{latin1}The following centralized version of $Z_{\frac{t}{\delta^{2}}x}$
\[
\mathscr{C}_{x}\left(\delta,t\right):=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}}\delta}
\]
converges to a Brownian motion as $\delta\rightarrow0$.\\
\inputencoding{latin9}\foreignlanguage{english}{\textrm{}\\}
\selectlanguage{english}%
\item We construct $f\left(\cdot,\delta\right)$ that takes as input the
process $\left(\mathscr{C}_{x}\left(\delta,t\right):x\in\left\{ 1,\ldots,k\right\} ,t\in\mathbb{R}\right)$,
and returns $1$ if the correction selection was made, and $0$ otherwise.\\
\textrm{}\\
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Proof Outline}

\begin{block}{}

\begin{itemize}
\item $f$ has a continuity property that causes $f\left(\mathscr{C}\left(\delta,\cdot\right),\delta\right)\Rightarrow g\left(W\right)$
where $g$ is the selection decision from applying the BIZ procedure
in continuous time.\inputencoding{latin1}{}\\
\inputencoding{latin9}\textrm{}\\
\item \inputencoding{latin1}The BIZ procedure satisfies the IZ guarantee
when applied in continuous time, and so $\mathbb{E}\left[g\left(W\right)\right]\geq P^{*}$
with equality for the worst configuration in the preference zone.\\
\inputencoding{latin9}\foreignlanguage{english}{\textrm{}\\}
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Numerical Experiments}
\begin{figure}[ht]
\includegraphics[width=\textwidth,height=0.7\textheight,keepaspectratio]{plot5.pdf}
\caption{
    Known variance case. 100 alternatives and $P^*=0.9$. PCS converges to $P^*$ as $\delta$ goes to $0$.
    Typical behavior, where the PCS is above $P^*$ for all values of $\delta$.}
\end{figure}
\end{frame}

\begin{frame}{Numerical Experiments}
\begin{figure}[ht]
\includegraphics[width=\textwidth,height=0.7\textheight,keepaspectratio]{unknown.pdf}
\caption{
    Unknown variance case. 100 alternatives and $P^*=0.9$. PCS converges to $P^*$ as $\delta$ goes to $0$. 
    Atypical behavior, $n_0$ is small and the variance of the best alternative is much larger than the other variances.}
\end{figure}
\end{frame}

\begin{frame}{Numerical Experiments}
\begin{figure}[ht]
\includegraphics[width=\textwidth,height=0.7\textheight,keepaspectratio]{plot3.pdf}
\caption{
    Known variance case. 100 alternatives and $P^*=0.9$. PCS converges to $P^*$ as $\delta$ goes to $0$. 
    Atypical behavior, $n_0$ is small and the variance of the best alternative is much larger than the other variances.}
\end{figure}
\end{frame}

\begin{frame}{}

{\Huge{}Thank you!!}\end{frame}

\end{document}

### 2015-06-09 paper/wish/wsc15paper.tex
last
montreal

@@
 	257 Rhodes Hall \\
-	206 Rhodes Hall \\
+	232 Rhodes Hall \\
 	Ithaca, NY 14853, USA\\
@@
 This algorithm generalizes the BIZ procedure with known common variance.
-In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$.
+In that case, we have that $B_1=\cdots=B_k=1$ and $n_{tx}=t$.
 The algorithm can be generalized to the continuous case (see  \citeN{Frazier:BIZ}).

### 2015-06-10 montreal/presentation.tex
presentation

@@
 
+\begin{frame}{Conservatism Causes the Number of Samples Taken to Be Larger than
+Necessary }
+
+\begin{block}{}
+
+\begin{itemize}
+\item A user wants to meet the IZ guarantee and have $\mathbb{E}\left[\mbox{\# of samples}\right]$
+as small as possible.\\
+\textrm{}\\
+\item The conservatism can be defined as $\mbox{PCS}\left(\mu\right)-P^{*}$.
+If this number is large, then $\mathbb{E}\left[\mbox{sample size}\right]$
+may be large. 
+\end{itemize}
+\end{block}
+\end{frame}
+
+\begin{frame}{Sources of Conservatism}
+
+\begin{block}{}
+
+\begin{itemize}
+\item The change from discrete time to continuous time often used to show
+IZ guarantees.\\
+\textrm{}\\
+\item The configuration under consideration is not a worst-case configuration.
+\\
+\textrm{}\\
+\item Bonferroni\textquoteright s inequality.
+\end{itemize}
+\end{block}
+\end{frame}
+
 \begin{frame}{The Bayes-Inspired IZ (BIZ) Procedure}
@@
 \begin{itemize}
-\item BIZ is an elimination procedure that does not use Bonferroni's inequality.
-\\
+\item BIZ is an elimination procedure that eliminates the use of Bonferroni\textquoteright s
+inequality, reducing conservatism. \\
 \textrm{}\\
@@
 \textrm{}\\
-\item It satisfies the IZ guarantee under the follwing assumptions:
+
+\end{itemize}
+\end{block}
+\end{frame}
+
+\begin{frame}{BIZ Requires Fewer Samples}
+\begin{figure}[ht]
+\includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio]{BIZ.png}
+\end{figure}
+\end{frame}
+
+\begin{frame}{The Bayes-Inspired IZ (BIZ) Procedure}
+
+\begin{block}{}
+
+\begin{itemize}
+\item It satisfies the IZ guarantee under the following assumptions:
 
@@
 \item Variances are either common across alternatives, or have an integer
-multiple structure. 
+multiple structure.\\
+\textrm{}\\
 \end{itemize}
+\item Based on empirical evidence, the BIZ procedure satisfies the IZ guarantee
+almost always even when the last two assumptions are not true.\\
+\textrm{}\\
+\item Our contribution is to theoretically explain why it works. Specifically,
+we show asymptotic validity of the BIZ procedure. 
 \end{itemize}
@@
 
+\begin{frame}{Conclusion}
+
+\begin{block}{}
+
+\begin{itemize}
+\item BIZ is a fully sequential IZ procedure with elimination that eliminates
+one common source of conservatism: Bonferroni's inequality.\\
+\textrm{}\\
+\item We have proved the asymptotic validity of the Bayes-inspired Zone
+procedure when the variances are known. This implies that BIZ procedure
+satisfies the IZ guarantee when the means of the systems are very
+similar. \\
+\textrm{}\\
+\item Theoretical results require unrealistic assumptions on the sampling
+variances, but empirical results suggest that behavior is robust to
+violations of these assumptions in the problem regimes tested.\\
+\textrm{}\\
+\end{itemize}
+\end{block}
+
+\end{frame}
+
+\begin{frame}{Future Work}
+
+\begin{block}{}
+
+\begin{itemize}
+\item Asymptotic validity when the variances are unknown.\\
+\textrm{}\\
+\item Probability of good selection guarantee: 
+\begin{eqnarray*}
+\forall\mu,\mbox{ PGS}\left(\mu\right):=\mathbb{P}\left(\mu_{k}-\mu_{\hat{x}}\leq\delta\right) & \geq & P^{*}
+\end{eqnarray*}
+ \\
+\textrm{}\\
+\end{itemize}
+\end{block}
+\end{frame}
+
 \begin{frame}{}

### 2015-06-13 montreal/presentation.tex
modifications

@@
 $x$, onto $\left(Z_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
-where $Z_{tx}=Y_{n_{tx},t}$ is the sum of samples from alternative
-$x$observed by stage $t$.\\
+where $Z_{tx}=Y_{n_{tx},x}$ is the sum of samples from alternative
+$x$ observed by stage $t$.\\
 \textrm{}\\

### 2015-06-16 2013-afosr-presentation/2013.04.AFOSR.without_animation.tex
adding my 2013 afosr presentation for saul to use.

\documentclass[13pt]{beamer}
%\documentclass[handout]{beamer}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{color}
\usepackage{amsmath,amsthm,amssymb,amsfonts,amsxtra,amstext}
\usepackage{pgf,pgfarrows,pgfnodes,pgfautomata,pgfheaps}
\usepackage[english]{babel}
\usepackage{mathptmx}
\usepackage{multimedia}
\usepackage{cancel}
\usepackage{hyperref}
\newcommand{\figdir}{../../fig}
\newcommand{\zap}[1]{ }
\newcommand{\xhat}{\hat{x}}
\newcommand{\sgn}{\mathrm{sgn}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\T}{\mathbb{T}} % Time index set.
\newcommand{\IZ}{\mathrm{IZ}}
\newcommand{\CS}{\mathrm{CS}}
\newcommand{\PZ}{\mathrm{PZ}}
\newcommand{\PCS}{\mathrm{PCS}}
% \newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Ybar}{\overline{Y}}
  \newcommand{\BIZ}{\mathrm{BIZ}}
  \newcommand{\sigmahat}{\widehat{\sigma}}
  \newcommand{\qhat}{\hat{q}}
\newcommand{\ceil}{\mathrm{ceil}}
\newcommand{\PstarB}{\mathcal{P}^*_B}
\newcommand{\upthresh}{P}

% Run with this to make it compile faster by leaving out the images
%\usepackage[draft]{graphics}

\input{../../evan_commands.tex}
\input{../../pete_commands.tex}

%\usetheme{Rochester}
%\usetheme{Antibes}
%\usetheme{Warsaw}
%\usetheme{Boadilla}
%\usetheme{Montpellier}
%\usetheme{Luebeck}
%\usetheme{Copenhagen}
%\usetheme{Malmoe}
%\usetheme{Pittsburgh}
%\usetheme{CambridgeUS}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Marburg}
%\usetheme{Darmstadt}
%\usetheme{Berlin}
%\usetheme{PaloAlto}
%\usetheme{Dresden}
%\usetheme{Singapore}
%\usetheme{AnnArbor}
%\usetheme{Szeged}
%\usetheme{Berkeley}
%\usetheme{Bergen}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
\usetheme{Madrid}
%\usetheme{Frankfurt}

%\usecolortheme{rose}
\usecolortheme{seahorse}
%\usecolortheme{sidebartab}
%\usecolortheme{IAS}
%\usecolortheme{crane}

%% If you have a file called "university-logo-filename.xxx", where xxx
%% is a graphic format that can be processed by latex or pdflatex,
%% resp., then you can add a logo as follows:
%
 %\pgfdeclareimage[height=0.5cm]{university-logo}{\figdir/cornell-logo.pdf}
 %\logo{\pgfuseimage{university-logo}}

\title{Optimal Learning:\\ Bayesian Methods for Simulation Optimization}
\author[Frazier]{Peter I. Frazier}
\institute[Cornell University]{Operations Research \& Information Engineering, Cornell University}
\date[talk]
{Thursday April 18, 2013\\ 
AFOSR Program Review\\
Optimization \& Discrete Mathematics\\
Arlington, VA\\
\vspace{0.2in}
AFOSR YIP FA9550-11-1-0083\\(Optimization \& Discrete Mathematics)\\
AFOSR BRI FA9550-12-1-0200, with Warren Powell\\(Natural Materials, Systems \& Extremophiles)
}

\AtBeginSection[]
{
   \begin{frame}
       \frametitle{Outline}
       \tableofcontents[currentsection]
   \end{frame}
}

\begin{document}

\setbeamertemplate{navigation symbols}{} %gets rid of navigation symbols
\setbeamertemplate{footline}{} % gets rid of footline

\frame{ \titlepage } % Make the title page

\zap{
\begin{frame} \frametitle{Overview}
  \begin{itemize}
    \item We use Bayesian statistics to design optimization algorithms for problems with expensive or time-consuming function evaluations.
    \item Objective functions are expensive or time-consuming to evaluate when they require running:
      \begin{itemize}
	\item a complex computer simulator; or
	\item a physical laboratory experiment.
      \end{itemize}
    \item We discuss two kinds of optimization algorithms:
      \begin{itemize}
	\item Methods with worst-case non-Bayesian guarantees on solution quality, where Bayesian analysis plays a role in the theory. 
	\item Methods with good (or even optimal) average-case (Bayesian) performance under the prior.
      \end{itemize}
  \end{itemize}
\end{frame}
}

\section{Part I: Worst-case Performance Guarantees}
\subsection{Ranking and Selection with Tight Bounds on Solution Quality}

% What is the problem?
\begin{frame} \frametitle{Ranking \& Selection (R\&S) is a basic problem in simulation optimization}
\begin{itemize}
  \item We have $k$ alternative choices that can be simulated.
  \item When we simulate alternative $x$, we observe random payoff $Z(x)$.
  \item We wish to know which $x$ has the largest $E[Z(x)]$.
  \item Sampling is the only way to estimate $E[Z(x)]$ because the simulator is too complex for direct theoretical analysis.  
    \begin{itemize}
      \item e.g., a large-scale discrete-event simulation of a supply chain; or a whole-theater combat simulator.
    \end{itemize}
  \item We make no a priori assumptions about the relationships between alternatives.
\end{itemize}
\end{frame}

\begin{frame} \frametitle{We Assume Independent Normal Samples}
  \begin{itemize}
  \item The R\&S literature often assumes that Z(x) is normally distributed: 
    \begin{equation*}
      Z(x) \sim \mathrm{Normal}(\theta_x, \sigma^2_x) \qquad \text{(independent across $x$ and time)}
    \end{equation*}
  \item $\theta_x$ is unknown but fixed (non-Bayesian). 
  \item For simplicity in this talk, we assume $\sigma^2_x$ is known, but the procedure presented can also be used in the unknown variance setting.
  \item Approximate normality of $Z(x)$ can be checked empirically, and if it is not met, samples can be batched together.
\end{itemize}
\end{frame}

\begin{frame} \frametitle{A Typical Ranking \& Selection Procedure}
  \begin{figure}
    \center \includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0238.pdf}
  \end{figure}
\end{frame}

\zap{
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0001.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0002.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0003.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0004.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0005.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0006.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0007.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0008.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0009.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0010.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0011.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0012.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0013.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0014.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0015.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0016.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0017.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0018.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0019.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0020.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0021.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0022.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0023.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0024.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0025.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0026.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0027.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0028.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0029.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0030.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0031.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0032.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0033.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0034.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0035.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0036.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0037.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0038.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0039.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0040.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0041.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0042.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0043.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0044.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0045.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0046.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0047.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0048.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0049.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0050.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0051.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0052.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0053.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0054.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0055.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0056.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0057.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0058.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0059.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0060.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0061.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0062.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0063.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0064.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0065.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0066.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0067.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0068.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0069.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0070.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0071.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0072.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0073.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0074.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0075.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0076.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0077.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0078.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0079.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0080.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0081.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0082.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0083.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0084.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0085.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0086.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0087.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0088.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0089.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0090.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0091.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0092.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0093.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0094.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0095.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0096.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0097.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0098.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0099.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0101.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0102.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0103.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0104.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0105.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0106.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0107.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0108.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0109.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0110.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0111.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0112.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0113.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0114.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0115.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0116.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0117.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0118.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0119.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0120.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0121.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0122.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0123.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0124.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0125.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0126.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0127.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0128.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0129.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0130.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0131.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0132.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0133.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0134.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0135.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0136.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0137.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0138.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0139.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0140.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0141.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0142.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0143.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0144.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0145.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0146.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0147.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0148.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0149.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0150.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0151.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0152.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0153.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0154.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0155.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0156.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0157.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0158.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0159.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0160.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0161.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0162.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0163.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0164.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0165.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0166.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0167.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0168.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0169.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0170.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0171.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0172.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0173.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0174.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0175.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0176.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0177.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0178.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0179.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0180.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0181.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0182.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0183.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0184.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0185.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0186.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0187.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0188.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0189.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0190.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0191.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0192.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0193.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0194.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0195.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0196.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0197.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0198.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0199.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0201.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0202.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0203.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0204.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0205.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0206.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0207.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0208.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0209.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0210.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0211.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0212.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0213.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0214.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0215.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0216.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0217.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0218.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0219.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0220.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0221.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0222.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0223.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0224.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0225.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0226.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0227.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0228.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0229.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0230.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0231.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0232.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0233.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0234.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0235.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0236.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0237.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{A Typical Ranking \& Selection Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf2/animation_0238.pdf}\end{figure}\end{frame}
}

\begin{frame}\frametitle{We focus on ranking \& selection procedures with statistical guarantees on solution quality}
  \begin{itemize}
    \item We consider one type of ranking \& selection procedures: {\bf indifference zone} ranking and selection procedures.
    \item These procedures provide solutions that have an associated statistical guarantee.
    \item This statistical guarantee is a lower bound on probaility of correct selection, over problem instances in a certain to-be-described set.
  \end{itemize}
\end{frame}

\begin{frame} \frametitle{Studying ranking \& selection is useful for three reasons}
\begin{enumerate}
  \item R\&S procedures can be used directly to solve smaller problems ($k<1000$).
    \begin{itemize}
      \item Pro: statistical guarantee on solution quality; 
      \item Pro: no assumptions required on the relationships between alternatives
      \item Con: lack of assumptions makes sample sizes big when $k$ is big.
    \end{itemize}
  \item R\&S procedures are used as subroutines by algorithms for bigger problems ($k>1000$ or $k=\infty$):
%  R&S procedures are used to solve sub-problems in algorithms for big sim-opt problems 
    \begin{itemize}
      \item Cleaning up after optimization \cite{Boesel2003}.
      \item Finding a direction of local increase \cite{HongNelson2006,XuNelsonHong2010}.
	% Note that statistical guarantees on the R\&S sub-problem are required to prove convergence of the larger algorithm.
    \end{itemize}
  \item R\&S is a core problem in sim-opt problem: Understanding it supports understanding of other problems.
\end{enumerate}
\end{frame}

\begin{frame}\frametitle{Ranking \& Selection is a well-studied problem}
  \begin{itemize}
    \item Indifference-zone Ranking and Selection: \cite{Bec54,Pa64,BeKiSo68,Fabian1974,DuDa75,Ri78,BeGo87,Ha88,Ha91,Pa94,BeSaGo95,KiNe01,NeSwGoSo01,Malone2005,Ho06,Dieker2011,Wang2011b,Dieker2012} 
    % \item Other formulations (Bayesian, OCBA): 
      % \cite{FuHuChXi04,ChHeFu06,ChenLee2010}
    % \item Novel problem formulations (constraints, steady state simulation):
      % \cite{GoKiMaNe02,AndradottirGoldsmanKim2005,KiNe06,AndradottirKim2010}
    \item This does not include all the work on other problem formulations (Bayesian, large devations, OCBA).
    \item There is also a recent interest body of work in theoretical computer science, under the name ``pure exploration multi-armed bandit'' \cite{madani2004budgeted,Bubeck2009,audibert2010best,bubeck2011pure}
  \end{itemize}
\end{frame}

\begin{frame}\frametitle{Existing procedures have loose bounds, which lead them to sample more than necessary}
  \begin{columns}[t]
    \begin{column}{0.6\textwidth}
      \begin{itemize}
	\item {\bf Problem 1:} Existing procedures have loose theoretical bounds on solution quality, when $k>2$.  
	\item {\bf Problem 2:} This leads them to sample more than necessary, to guarantee minimum solution quality. 
	\item {\bf Our Contribution:} We construct a procedure (BIZ, or {\bf B}ayes-inspired {\bf I}ndifference {\bf Z}one) with tight bounds on solution quality.  BIZ guarantees minimum solution quality while sampling less than existing procedures.
      \end{itemize}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{figure}
	\center
	\includegraphics[width=\textwidth]{\figdir/biz/AFOSR2013/AFOSR2013-SC-KN-PCS.pdf}
      \end{figure}
      \medskip
      \begin{figure}
	\center
	\includegraphics[width=\textwidth]{\figdir/biz/AFOSR2013/AFOSR2013-SC-BIZ-PCS.pdf}
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame} \frametitle{Notation \& Terminology}
  \begin{itemize}
    % \item A {\bf procedure} (or ``policy'', or ``algorithm'') is a (possibly adaptive) rule for deciding how many samples to take from each alternative, and for selecting an estimate of $\argmax_x \theta_x$ based on these samples.
    \item Let $\PCS(\theta)$ be the {\bf Probability of Correct Selection}, where $\theta=(\theta_1,\ldots,\theta_k)$ is the vector of sampling means. 
      This is the probability that the sampling procedure selects an alternative in $\argmax_x \theta_x$.\\
    (The dependence on $\sigma^2_x$ is suppressed in the notation.)
    \item Let $\delta > 0$ represent the smallest meaningful difference in performance.
    \item Let $P^*$ be a pre-specified lower bound with which we would like to select the best. 
  \end{itemize}
\end{frame}

\begin{frame} \frametitle{We consider the following form of statistical guarantee}
\begin{itemize}
  \item Define the {\bf preference zone} as the set of $\theta$ where the best is better than the second best by at least $\delta$:
\begin{equation*}
  \PZ(\delta) = \left\{ \theta\in \R^k : \theta_{[1]} - \theta_{[2]} \ge \delta\right\},
\end{equation*}
where $\theta_{[1]} \ge \theta_{[2]} \ge \ldots \ge \theta_{[k]}$ are the order statistics of $\theta$.
\item The {\bf indifference zone (IZ)} is the preference zone's complement.
\item A procedure has an {\bf IZ guarantee} with parameters $\delta$ and $P^*$ if 
\begin{equation*}
  \PCS(\theta) \ge P^*
  \quad \text{for all $\theta\in \PZ(\delta)$}.
\end{equation*}
\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{We construct our procedure with Bayesian ideas}
  \begin{itemize}
  \item Let $Y_{tx}$ be the sum of all observations from alternative $x$ by time $t$.
  \item We use a prior distribution that is concentrated on slippage configurations.
  \item The posterior probability that an alternative $x$ is the best, given that the best is in a specified set $A$, is 
    \begin{equation*}
      q_{tx}(A) = \exp\left(\frac{\delta}{\sigma^2} Y_{tx}\right) \bigg/ \sum_{x'\in A} \exp\left(\frac{\delta}{\sigma^2} Y_{tx'}\right).
    \end{equation*}
  \item We watch $q_{tx}(A)$, where $A$ is the set of alternatives in contention.  An alternative is eliminated if it hits a lower threshold, and selected as best if it hits an upper threshold.
  \item The upper threshold increases with each elimination, to compensate for the possibility that we may mistakenly eliminate the best.
    % \begin{itemize}
      % \item BIZ eliminates an alternative when its $q_{tx}(A_t)$ falls below a lower threshold;
      % \item BIZ selects an alternative as the best when its $q_{tx}(A_t)$ exceeds an upper threshold;
      % \item The set $A_t$ is the set of alternatives is still in content.
    % \end{itemize}
  % \item 
    % Under a Bayesian prior distribution that is concentrated on slippage configurations, 
    % $q_{tx}(A)$ is the posterior probability that $x=X^*$, given that $X^* \in
    % A$.  Here, $X^*$ is the alternative with the largest sampling mean.
  % \item Although we construct BIZ with Bayesian ideas, and manipulate Bayesian PCS in its analysis, it is a non-Bayesian method: You do not need to have a prior to use BIZ, and its IZ guarantee is non-Bayesian.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The Bayes-inspired Indifference Zone (BIZ) Procedure}
  \begin{figure}
    \center
  \includegraphics[height=.9\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0238.pdf}
  \end{figure}
\end{frame}

\zap{
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0001.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0002.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0003.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0004.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0005.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0006.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0007.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0008.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0009.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0010.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0011.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0012.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0013.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0014.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0015.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0016.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0017.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0018.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0019.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0020.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0021.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0022.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0023.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0024.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0025.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0026.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0027.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0028.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0029.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0030.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0031.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0032.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0033.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0034.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0035.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0036.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0037.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0038.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0039.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0040.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0041.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0042.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0043.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0044.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0045.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0046.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0047.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0048.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0049.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0050.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0051.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0052.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0053.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0054.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0055.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0056.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0057.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0058.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0059.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0060.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0061.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0062.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0063.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0064.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0065.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0066.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0067.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0068.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0069.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0070.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0071.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0072.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0073.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0074.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0075.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0076.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0077.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0078.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0079.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0080.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0081.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0082.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0083.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0084.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0085.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0086.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0087.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0088.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0089.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0090.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0091.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0092.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0093.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0094.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0095.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0096.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0097.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0098.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0099.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0101.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0102.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0103.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0104.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0105.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0106.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0107.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0108.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0109.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0110.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0111.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0112.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0113.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0114.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0115.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0116.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0117.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0118.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0119.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0120.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0121.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0122.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0123.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0124.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0125.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0126.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0127.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0128.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0129.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0130.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0131.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0132.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0133.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0134.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0135.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0136.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0137.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0138.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0139.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0140.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0141.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0142.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0143.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0144.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0145.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0146.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0147.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0148.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0149.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0150.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0151.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0152.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0153.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0154.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0155.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0156.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0157.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0158.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0159.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0160.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0161.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0162.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0163.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0164.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0165.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0166.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0167.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0168.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0169.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0170.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0171.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0172.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0173.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0174.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0175.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0176.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0177.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0178.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0179.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0180.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0181.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0182.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0183.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0184.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0185.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0186.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0187.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0188.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0189.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0190.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0191.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0192.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0193.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0194.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0195.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0196.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0197.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0198.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0199.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0201.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0202.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0203.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0204.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0205.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0206.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0207.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0208.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0209.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0210.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0211.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0212.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0213.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0214.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0215.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0216.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0217.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0218.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0219.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0220.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0221.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0222.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0223.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0224.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0225.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0226.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0227.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0228.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0229.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0230.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0231.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0232.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0233.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0234.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0235.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0236.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0237.pdf}\end{figure}\end{frame}
\begin{frame}\frametitle{The BIZ Procedure}\begin{figure}\includegraphics[height=\textheight]{\figdir/biz/AFOSR2013/animation/pdf1/animation_0238.pdf}\end{figure}\end{frame}
}

\begin{frame}
  \frametitle{The BIZ Procedure}
  Fix parameters $c \le 1-(P^*)^{1/(k-1)}$, $\delta>0$, $P^*>1/k$.
  \begin{itemize}
    \item[1.] Let $A \leftarrow \{ 1,\ldots, k\}$, $t\leftarrow 0$, $\upthresh \leftarrow P^*$.
    \item[2.] While $\max_{x\in A} q_{tx}(A) < \upthresh$
    \begin{itemize}
      \item[2a.] While $\min_{x\in A} q_{tx}(A) \le c$
      \begin{itemize}
	\item Let $x \in \argmin_x q_{tx}(A)$.
	\item Let $\upthresh \leftarrow \upthresh/(1-q_{tx}(A))$.
	\item Remove $x$ from $A$.
      \end{itemize}
    \item[2b.] Sample from each $x\in A$ to obtain $Y_{t+1,x}$.  Then increment $t$.
    \end{itemize}
  \item[3.] Select $\xhat \in \argmax_{x\in A} Y_{tx}$ as our estimate of the best.
  \end{itemize}
  \bigskip
  Recall:
\begin{equation*}
  q_{tx}(A) = \exp\left(\frac{\delta}{\sigma^2} Y_{tx}\right) \bigg/ \sum_{x'\in A} \exp\left(\frac{\delta}{\sigma^2} Y_{tx'}\right).
\end{equation*}
\end{frame}

\begin{frame}
  \frametitle{BIZ has Tight PCS Bounds}
  \begin{theorem}
  Assume that $\sigma^2_x = \sigma^2$ is known.
  Fix any $\delta>0$, $P^* \in (1/k,1)$, $c \le 1-(P^*)^{1/(k-1)}$, $\T \in \{\R_+,\Z_+\}$, 
  and let sampling occur under BIZ.
  Then,
    \begin{equation*}
      \PCS(\theta) \ge P^*\quad \forall \theta\in\PZ(\delta)
    \end{equation*}
    Moreover, for a generalization of BIZ to continuous time,
    \begin{equation*}
      \inf_{\theta\in\PZ(\delta)} \PCS(\theta) = P^*
    \end{equation*}
  \end{theorem}

This is the first sequential elimination indifference-zone procedure with tight bounds for $k>2$.
\end{frame}

\zap{
\begin{frame}
  \frametitle{Contribution: Tight PCS Bounds}
We construct a fully sequential elimination procedure, called the {\bf Bayes-Inspired IZ (BIZ)} procedure, which has two properties:
      \begin{enumerate}
	\item $\BIZ$ satisfies the IZ guarantee:
	  \begin{equation*}
	    \PCS(\theta)  \ge P^*, \quad\text{for all $\theta\in\PZ(\delta)$}.
	  \end{equation*}
	\item In continuous time, the lower bound $P^*$ on PCS is tight:
	  \begin{equation*}
	\inf_{\theta\in\PZ(\delta)} \PCS(\theta)  = P^*
	  \end{equation*}
      \end{enumerate}
      Caveat: Theoretical results require strong assumptions on the variances.
      % that they are known, and are either common across alternatives, or are rational multiples of a common value. 
      Empirical results suggest performance is robust to violations of these assumptions.
\end{frame}
}

\zap{
\begin{frame}
  \begin{figure}
    \centering
    \includegraphics[width=4.2in]{\figdir/BayesIZ/ALL_01_2013c.pdf} 
  \end{figure}
\end{frame}
\begin{frame}
  \begin{figure}
    \centering
    \includegraphics[width=4.2in]{\figdir/BayesIZ/ALL_01_2013b.pdf} 
  \end{figure}
\end{frame}
\begin{frame}
  \begin{figure}
    \centering
    \includegraphics[width=4.2in]{\figdir/BayesIZ/ALL_01_2013a.pdf} 
  \end{figure}
\end{frame}
}

\begin{frame}
  \frametitle{Tight bounds allow taking fewer samples}
  \begin{figure}[tb]
    \center
    \includegraphics[width=3.5in]{\figdir/BayesIZ/FINAL-Common-Known-ImprovementFactor.pdf}
  \end{figure}
  \begin{itemize}
    \item On many of the largest problems considered in our numerical experiments, BIZ requires between 1/3 and 1/2 as many samples as KN \cite{KiNe01}, the $\mathcal{P}$ procedure of \cite{Wang2011b}, and Paulson's procedure \cite{Pa64}.  
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{BIZ can be generalized to Heterogeneous and Unknown Sampling Variance}

  \begin{itemize}
    \item In practice, sampling variances are unknown and heterogeneous.
    \item The BIZ procedure has been generalized to this more general setting.
    \item Theoretical results can also be generalized, but require restrictive assumptions unlikely to be met in practice, e.g., a continuous-time observation process.
    \item Empirical results, however, in the heterogeneous unknown variance case are similar to what is predicted by the continuous-time theory.
  \end{itemize}
  \begin{figure}
    \center
    % \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SC-PCS}\\
    %\includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCINC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCINC-PCS}\\
    %\includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCDEC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCDEC-PCS}\\
    %\includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMINC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMINC-PCS}\\
    %\includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMDEC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMDEC-PCS}\\
    % \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-RPI-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-RPI-PCS}\\
    \includegraphics[width=2.5in]{\figdir/BayesIZ/FINAL-UNK-RPIHET-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-RPIHET-PCS}
  \end{figure}
\end{frame}

% \begin{frame}
  % \frametitle{For the largest problems, BIZ requires 3 to 4 times fewer samples than KN.}
  % \begin{figure}[tb]
    % \center
    % \includegraphics[width=4in]{\figdir/BayesIZ/FINAL-ImprovementFactor}
  % \end{figure}
% \end{frame}

\begin{frame}
\frametitle{Part I Conclusion}
\begin{itemize}
  \item BIZ is a fully sequential IZ procedure with elimination that delivers {\bf exactly} $P^*$ (in continuous time, and under the worst $\theta$ in the preference zone).
  \item To my knowledge, this is the {\bf first fully sequential elimination IZ procedure with this property} for $k>2$.
  \item Theoretical results require unrealistic assumptions on the sampling variances, but empirical results suggest that behavior is robust to violations of these assumptions in the problem regimes tested.
\end{itemize}
\end{frame}

\section{Part II: Average-case Performance}
\begin{frame}
  \frametitle{Bayesian methods are useful for designing methods with good average-case performance}
  \begin{itemize}
    \item The previous part of the talk used Bayesian methods as a theoretical tool for designing a procedure with a {\bf worst-case} performance guarantee.
    \item Bayesian methods are also extremely useful for designing methods with {\bf good average-case} performance. 
  \end{itemize}
\end{frame}

\begin{frame}\frametitle{Current Applications of Optimal Learning}
  \begin{itemize}
    \item Design of cardiovascular bypass grafts (Alison Marsden, UCSD)
    \item Large-scale simulation optimization with common random numbers (Steve Chick, INSEAD)
    \item Materials Science: finding minimal peptide-based substrates (Nathan Giannesci, UCSD)
    \item {\bf Materials Science: finding peptides with specific nanoparticle binding properties} (Paras Prasad, Buffalo)
    \item Materials Science: optimization of continuous parameters (several groups, at Princeton, Cornell and AFRL)
  \end{itemize}
  The materials science collaborations are funded by AFOSR BRI FA9550-12-1-0200, from Natural Materials, Systems \& Extremophiles, with Warren Powell as PI.
\end{frame}

\subsection{Materials Science: Finding peptides with specific nanoparticle binding properties}

\begin{frame}\frametitle{Finding peptides with specific nanoparticle binding properties}
  Our {\bf collaborators}: Paras Prasad (PI, Buffalo); Tiff Walsh (Deakin); Marc Knecht (Miami); Aidong Zhang (Buffalo); Mark Swihart (Buffalo).
  \begin{figure}\includegraphics[width=4.8in]{\figdir/Prasad/Collaborators.pdf}\end{figure}
  {\bf Project Goal}: create novel nano-materials with useful photonic, electronic, and plasmonic properties, by creating peptide links between various nano-size metals and oxides.
\end{frame}

\begin{frame}\frametitle{Background: What's a Peptide?  What's an Amino Acid?} 
\begin{figure}\includegraphics[height=\textheight]{\figdir/Prasad/Amino-Acid-Chart5.jpg}\end{figure}
\end{frame}

\begin{frame}\frametitle{Challenge}
  \begin{itemize}
    \item Given two materials, e.g., gold and iron oxide, find a
      peptide that binds strongly to the first material (e.g., gold), and
      weakly to the second (e.g., iron oxide).
    \item The role of mathematics is to suggest which experiments to perform. 
  \end{itemize}
  \begin{figure}\includegraphics[width=4.8in]{\figdir/Prasad/PARE_Prasad2.pdf}\end{figure}
\end{frame}

\begin{frame}\frametitle{There are two kinds of experiments we can run} 
  \begin{itemize}
    \item {\bf Physical (lab) experiments}: Given a peptide, measure the Gibbs free energy of binding (a measure of binding strength). 
    \item {\bf Computer experiments}: Given a peptide, use a physics-based simulation to calculate to calculate, for each amino acid, the percentage of time it is in contact with the target material.
  \end{itemize}
  Each experiment (lab or computer) takes $\approx 1$ week.
\begin{figure}\includegraphics[height=2.5in]{\figdir/Prasad/ReplicaExchange2.png}\end{figure}
\end{frame}

\begin{frame}\frametitle{Our preliminary dataset required $\approx$ 2.5 months of lab effort, and $\approx$ 2.5 months of computer time}
\begin{figure}\includegraphics[height=\textheight]{\figdir/Prasad/AuData.png}\end{figure}
\end{frame}

\begin{frame}\frametitle{We build a Bayesian model that takes advantage of {\bf all} of our data: domain knowledge, computer experiments, lab experiments}
\begin{figure}\includegraphics[width=.9\textwidth]{\figdir/Prasad/StatisticalModel.pdf}\end{figure}
\end{frame}

\begin{frame}\frametitle{Part II: Conclusion}
  \begin{itemize}
    \item This statistical model takes advantage of all of the data available: domain knowledge, computer experiments, and lab experiments.
    \item This allows us to make reasonable predictions, despite having very little experimental data (only 12 datapoints).
    \item A KG method is then defined by this statistical model, and will suggest which experiment (computer or lab, and which peptide) we should perform next.
    \item Next steps: 
      \begin{itemize}
	\item We are validating the statistical model.
	\item We are developing methods for computing the KG method efficiently.
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
\frametitle{Thank You!}
\end{frame}

\begin{frame}[allowframebreaks]
\frametitle{References}
\tiny{
% \bibliography{../../../bib/pfrazier,../../../bib/pub,extra_cites}
\bibliography{MyCollection,../../../bib/pub}
\bibliographystyle{apalike}
}
\end{frame}

\end{document}

### 2015-06-16 2013-afosr-presentation/backup.tex
adding my 2013 afosr presentation for saul to use.

\zap{
\begin{frame}
% \frametitle{The BIZ Procedure: Heterogeneous and Unknown Sampling Variance}
  Fix $c \le 1-(P^*)^{1/(k-1)}$, $\delta>0$, $P^*>1/k$, $B_1,\ldots,B_k>0$, $n_0$ and let
\begin{equation*}
  \label{eq:qhat}
  \qhat_{tx}(A) = 
  \exp\left(\delta\frac{\sum_{x''\in A} \,n_{tx''}}{\sum_{x''\in A}\sigmahat^2_{tx''}} \,\frac{Y_{n_{tx},x}}{n_{tx}}\right) \bigg/
  \sum_{x' \in A}
  \exp\left(\delta\,\frac{\sum_{x''\in A} n_{tx''}}{\sum_{x''\in A}\sigmahat^2_{tx''}}\, \frac{Y_{n_{tx'},x'}}{n_{tx'}}\right).
\end{equation*}

\bit
\item[1.] Sample each alternative $n_0$ times.  For each $x$, let $n_{0x} \leftarrow n_0$, and let $Y_{0x}$ and $\sigmahat^2_{0x}$ be the sample mean and sample variance respectively.
Also let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$, $t \leftarrow 1$.
\item[2.] While $\max_{x\in A} \qhat_{tx}(A) < P$
  \bit
\item[2a.] While $\min_{x\in A} \qhat_{tx}(A) \le c$
  \bit
	\item Let $x \in \argmin_{x\in A} \qhat_{tx}(A)$.
	\item Let $\upthresh \leftarrow \upthresh/(1-\qhat_{tx}(A))$.
	\item Remove $x$ from $A$.
   \eit
 \item[2b.] Let $z \in \argmin_{x\in A} n_{tx} / \sigmahat^2_{tx}$.
 \item[2c.] For each $x\in A$, let 
    $n_{t+1,x} = \ceil\left( \sigmahat^2_{tx} (n_{tz} + B_z) / \sigmahat^2_{tz} \right)$.
  \item[2d.] For each $x\in A$, if $n_{t+1,x}>n_{tx}$, take $n_{t+1,x}-n_{tx}$ additional samples from alternative $x$.  Let $Y_{t+1,x}$ and $\sigmahat^2_{t+1,x}$ be the sample mean and sample variance respectively of all samples from alternative $x$ thus far.  Then increment $t$.
\eit
\item[3.] Select $\xhat \in \argmax_{x\in A} Y_{tx} / n_{tx}$ as our estimate of the best.
\eit
\end{frame}

\begin{frame}
  \frametitle{Continuation Region}
  \begin{itemize}
    \item Images show continuation region for $k=3$, \\ in linear coordinates (left) and exponential coordinates (right).  
    \item BKS (BIZ with $c=0$) stops when $Y_t$ exits the continuation region.
  \end{itemize}
  \begin{figure}
  \center{
  \includegraphics[width=2in]{\figdir/BayesIZ/ContinuationRegion.pdf}
  \quad
  \includegraphics[width=2in]{\figdir/BayesIZ/ContinuationRegionGBM.pdf}
  }
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Proof Sketch}
  Let $\CS$ be the event of correct selection. \\
  For $\theta\in\R^d$, let $Q_\theta$ be a prior that is uniform on the permutations $\theta$.
  In particular, $Q = Q_{[\delta,0,\ldots,0]}$.

  \begin{lemma}[Symmetry]
    %$\PCS(\pi,\theta) = Q_\theta\left\{ \text{correct selection under $\pi$} \right\}$ \\
    $\PCS(\pi,\theta)$ is invariant to permutations of $\theta$.  \\ Moreover, $\PCS(\pi,\theta) = Q^\pi_\theta\left\{ \CS \right\}$.
  \end{lemma}
  % \begin{proof}
    % Proof uses a symmetry or ``equalizing'' argument.
  % \end{proof}

  % The first, Lemma~\ref{l:correspondence}, shows that the non-Bayesian
  % probability of correct selection $\PCS(\pi,u)$ is identical to the probability
  % of correct selection under the Bayesian prior $Q_u$.  The proof follows a
  % symmetry or ``equalizing'' argument.

  \begin{lemma}[Monotonicity]
    For $\theta\in\PZ(\delta)$, 
    $Q^\pi_\theta\{CS\} \ge Q^\pi_{[\delta,0,\ldots,0]}\{CS\}$.
  \end{lemma}
   % monotonicity argument dealing directly with the form of the posterior probabilities.

   \begin{lemma}[Bayes PCS of Least-favorable Configuration]
    $Q^\pi_{[\delta,0,\ldots,0]}\{CS\} \ge P^*$, with equality if $\T=\R_+$.
   \end{lemma}
\end{frame}

\begin{frame}
  \frametitle{Generalization of BIZ, which allows sampling in discrete or continuous time} 
  \begin{itemize}
    \item {\bf Parameters}: $\T \in \{\R_+,\Z_+\}$, $c \le 1 - (P^*)^{1/(k-1)}$, $\delta>0$, $P^*>1/k$.
    \item {\bf Initalization}: $\tau_0 = 0$, $A_0=\{1,\ldots,k\}$, $\upthresh_0 = P^*$.
\item {\bf Elimination Time}: 
  \begin{multline*}
  \tau_{n+1} = \inf\left\{ t \in \T \cap [\tau_n,\infty) : 
  \min_{x\in A_n} q_{tx}(A_n) \le c 
  %\right. \\ \left. 
  \text{ or } 
  \max_{x\in A_n} q_{tx}(A_n) \ge \upthresh_n \right\}.
  \end{multline*}
\item {\bf Eliminated Alternative and Contention Set}:
  \begin{equation*}
    Z_{n+1} = \argmin_{x\in A_n} q_{\tau_{n+1}}(A_n), \qquad
    A_{n+1} = A_n \setminus Z_{n+1}
  \end{equation*}
\item {\bf Stopping Boundary}: 
  \begin{equation*}
    \upthresh_{n+1} = \upthresh_n \bigg/ \left(1 - \min_{x\in A_n} q_{\tau_{n+1}}(A_n)\right).
  \end{equation*}
\item The {\bf selected alternative} is the single alternative in $A_{k-1}$.
\end{itemize}
\end{frame}

\zap{
\begin{frame}
  \frametitle{We construct BIZ with Bayesian ideas \ldots \\ 
  \ldots but BIZ is a non-Bayesian Method}
    \begin{itemize}
      \item BIZ is motived using Bayesian ideas, and manipulation of Bayesian PCS is critical in proofs of theoretical results.
      \item However, BIZ is a non-Bayesian method.
      \item You do not need to have a prior to use BIZ, and its IZ guarantee is non-Bayesian.
  \end{itemize}
\end{frame}
}

\begin{frame}
\frametitle{Heterogeneous Sampling Variance: Continuous Time}
\begin{itemize}
  \item In general, sampling variances $\sigma_x^2$ are heterogeneous and unknown.
  \item In continuous time, this problem is easily addressed:
    \begin{enumerate}
  \item The sampling variance $\sigma^2_x$ can be estimated perfectly given $(Y_{tx} : 0\le t \le \epsilon)$ for any $\epsilon > 0$. 
  \item Replace $Y_{t,x} \sim \Ncal(\theta_x,t\sigma^2_x)$ with $Y_{\sigma_x^2 t,x} / \sigma_x^2 \sim \Ncal(\theta_x,t)$ and we obtain a ranking and selection problem with common sampling variance $1$.
  \item Use BIZ for common sampling variance $1$ on the transformed $Y$ values.
\end{enumerate}
  \item The IZ guarantee and the tightness of the PCS bound still hold.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Heterogeneous and Unknown Sampling Variance: \\ Discrete Time}
\begin{itemize}
  \item In discrete time, the problem is harder:
  \item Idea: use a discrete-time approximation to $Y_{\sigma_x^2 t,x} / \sigma_x^2$ in our calculation of $q_{tx}(A)$, based on the sample variances $\sigmahat^2_x$.
  \item When this discrete-time approximation is exact, we retain the IZ guarantee.
  \item When it does not hold, the IZ guarantee no longer holds, and the procedure is a heuristic.
  \item Ongoing work: Does the IZ guarantee hold in a limiting sense?
  %\item Let $n_{tx}$ be the number of samples taken from alternative $x$ by time $t$. 
  %\item Keep $n_{tx}$ proportional to $\sigmahat^2_x$ (as much as allowed by discrete time).
  %\item Most obvious approach:  Then, use $Y_{n_{tx},x} / \sigmahat^2_x$ as our approximation to 
%$Y_{\sigma_x^2 t,x} / \sigma_x^2$
  %\item A better approach: use
    %\begin{equation*}
    %\frac{\sum_{x'\in A} \,n_{tx'}}{\sum_{x'\in A}\sigmahat^2_{tx'}} \,\frac{Y_{n_{tx},x}}{n_{tx}}
    %\end{equation*}
  %\item When $n_{tx}$ is exactly proportional to $\sigma^2_x$ and $\sigmahat^2_x = \sigma^2_x$, this reduces to what we had in continuous time, and the IZ guarantee still holds.
  %\item Otherwise, the IZ guarantee does not hold, and the procedure is a heuristic.
  %\item Ongoing work: Does the IZ guarantee hold in a limiting sense?
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Heterogeneous and Unknown Sampling Variance: \\ Discrete Time}
\begin{itemize}
  \item Let $n_{tx}$ be the number of samples taken from alternative $x$ by time $t$. 
  \item We sample so as to keep $n_{tx}$ proportional to $\sigmahat^2_x$ (as much as allowed by discrete time).
  \item Most obvious approach:  Approximate $Y_{\sigma_x^2 t,x} / \sigma_x^2$
    with $Y_{n_{tx},x} / \sigmahat^2_x$.
  \item A better approach: approximate it with
    \begin{equation*}
      \frac{\sum_{x'\in A} \,n_{tx'}}{\sum_{x'\in A}\sigmahat^2_{tx'}} \,\frac{Y_{n_{tx},x}}{n_{tx}}
    \end{equation*}
  This allows the alternative with the highest $q_{tx}(A)$ to also be the one with the highest sample mean, $Y_{n_{tx},x}/n_{tx}$.
  \item When $n_{tx}$ is exactly proportional to $\sigma^2_x$ and $\sigmahat^2_x = \sigma^2_x$, this reduces to what we had in continuous time, and the IZ guarantee still holds.
  % \item Otherwise, the IZ guarantee does not hold, and the procedure is a heuristic.
  % \item Ongoing work: Does the IZ guarantee hold in a limiting sense?
\end{itemize}
\end{frame}

  % \REQUIRE $c \in [0,\cmax]$, $\delta>0$, $P^*\in(1/k,1)$, $n_0\ge0$ an integer, $B_1,\ldots,B_k$ strictly positive integers.  Recommended choices are $c=\cmax$, $B_1=\cdots=B_k=1$ and $n_0 = 100$.
    % $\sigmahat^2_{tx}$ with the true values $\lambda^2_x$, and set $n_0=0$.
    % To compute $\qhat_{tx}(A)$, use \eqref{eq:qhat}.

\begin{frame}
  \frametitle{Unknown Heterogeneous Variance}
  Slippage configuration.\\
  Top row: increasing variance.  Bottom row: decreasing variance.\\
  Left column: $E[N]/k$.  Right column: PCS.\\
  \begin{figure}
    \center
    % \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SC-PCS}\\
    \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCINC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCINC-PCS}\\
    \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCDEC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCDEC-PCS}\\
    % {\bf MDM-INC} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMINC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMINC-PCS}\\
    % {\bf MDM-DEC} \includegraphics[width=2.7in]{\figdir/BayesIZ/FINAL-UNK-MDMDEC-Nk} \includegraphics[width=2.7in]{\figdir/BayesIZ/FINAL-UNK-MDMDEC-PCS}\\
    % {\bf RPI-HET} \includegraphics[width=2.7in]{\figdir/BayesIZ/FINAL-UNK-RPIHET-Nk} \includegraphics[width=2.7in]{\figdir/BayesIZ/FINAL-UNK-RPIHET-PCS}\\
  \end{figure}

    %Row shows PCS and $E[N]/k$ as a function of the number of alternatives $k$ under the following configurations:
    %SC-INC (row 1); SC-DEC (row 2); MDM-INC (row 3); MDM-DEC (row 4); and RPI-HET (row 5).
    %In all configurations, $P^*=0.8$, $\sigma=10$, $\delta=0.5$, and the sampling variances are unknown.
\end{frame}

\begin{frame}
  \frametitle{Unknown Heterogeneous Variance}
  Monotone Decreasing Means configuration.\\
  Top row: increasing variance.  Bottom row: decreasing variance.\\
  Left column: $E[N]/k$.  Right column: PCS.\\
  \begin{figure}
    \center
    % \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SC-PCS}\\
    %\includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCINC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCINC-PCS}\\
    %\includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCDEC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCDEC-PCS}\\
    \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMINC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMINC-PCS}\\
    \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMDEC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMDEC-PCS}\\
    % {\bf RPI-HET} \includegraphics[width=2.7in]{\figdir/BayesIZ/FINAL-UNK-RPIHET-Nk} \includegraphics[width=2.7in]{\figdir/BayesIZ/FINAL-UNK-RPIHET-PCS}\\
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Unknown Heterogeneous Variance}
  Random Problem Instances.  \\
  Top row: common variance.  Bottom row: heterogeneous variance.\\
  Left column: $E[N]/k$.  Right column: PCS.\\
  \begin{figure}
    \center
    % \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SC-PCS}\\
    %\includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCINC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCINC-PCS}\\
    %\includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCDEC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-SCDEC-PCS}\\
    %\includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMINC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMINC-PCS}\\
    %\includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMDEC-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-MDMDEC-PCS}\\
    \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-RPI-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-RPI-PCS}\\
    \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-RPIHET-Nk} \includegraphics[width=2in]{\figdir/BayesIZ/FINAL-UNK-RPIHET-PCS}\\
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Tight PCS Bounds}
  \begin{theorem}
  Assume that $\sigma^2_x = \sigma^2$ is known.
  Fix any $\delta>0$, $P^* \in (1/k,1)$, $c \le 1-(P^*)^{1/(k-1)}$, $\T \in \{\R_+,\Z_+\}$, 
  and let sampling occur under BIZ.
  Then,
    \begin{equation*}
      \PCS(\theta) \ge P^*\quad \forall \theta\in\PZ(\delta)
    \end{equation*}
    Moreover, for a continuous-time generalization of BIZ,
    \begin{equation*}
      \inf_{\theta\in\PZ(\delta)} \PCS(\theta) = P^*
    \end{equation*}
  \end{theorem}
\end{frame}

\begin{frame}
  \begin{figure}
    \centering
    \includegraphics[width=4.2in]{\figdir/BayesIZ/ALL_01_2013a.pdf} 
  \end{figure}
\end{frame}

}

\zap{
\begin{frame}\frametitle{Loose PCS bounds cause the
the number of samples taken to be larger than necessary}
\begin{columns}[l]
\column{1.5in}
	\begin{figure}
	\center
	\includegraphics[width=2in]{\figdir/BayesIZ/ICS2013_overdelivery2.pdf}
	\end{figure}
\column{3in}
\begin{itemize}
  \item Consider a sampling procedure with a tunable parameter $h$, that controls how much sampling is done.
  \item If we increase $h$, then $\pi(h)$ takes more samples, and provides a bigger PCS.
  \item Let $\alpha(h) = \inf_{\theta \in \PZ(\delta)} \PCS(\pi(h),\theta)$ be the actual worst-case preference-zone PCS.  (solid line, from exhaustive simulation)
  \item Let $\beta(h) \le \alpha(h)$ be the best bound on $\alpha(h)$ that we can prove.  (dashed line)
  \item We choose $h$ so that $\beta(h) = P^*$.
  \item Had we known $\alpha$, we could have instead chosen a smaller $h$ with $\alpha(h) = P^*$, and taken fewer samples. 
  % \item Loose bounds cause the number of samples taken to be larger than necessary.
\end{itemize}
\end{columns}
\end{frame}
}

\zap{
\begin{frame}
\frametitle{Loose PCS Bounds Lead To Oversampling}
\center
\includegraphics[width=3.5in]{\figdir/BayesIZ/ICS2013_overdelivery.pdf} \\
\bit
\item The procedure we would use is the one where the horizontal line at $0.85$ crosses the dashed line, expected sample size 575.
\item Had our bounds been perfect, we would have used the one where the horizontal line crosses the solid line, expected sample size 450.
% \item (results from KN, $k=32$ alternatives)
\eit
\end{frame}
}

\zap{
\begin{frame}
  \frametitle{Loose PCS Bounds Lead To Oversampling}
% A common criticism of policies with IZ guarantees is that they are
% ``difficult to control'' and take too many samples for the desired level of PCS.
\begin{itemize}
  \item Let $\pi$ be a procedure with an IZ guarantee for a fixed $P^*$ and $\delta$.
  \item $P^*$ is the PCS that $\pi$ guarantees it will deliver.
  \item For any $\theta\in\PZ(\delta)$, 
	\begin{equation*}
	\PCS(\pi,\theta) - P^* 
	\end{equation*}
	is the {\bf overdelivery} on PCS.
      % \item For existing policies, there are configurations $\theta$ for which this overdelivery is {\bf significantly} greater than $0$. % large.
      \item Overdelivery on PCS is inefficient: we could have taken fewer samples and achieved the guaranteed PCS faster.
      \item For existing policies and large $k$, this overdelivery causes the number of
	samples to be {\bf significantly} larger than needed.
	% while having a larger PCS is nice, it comes at a cost of having taken more samples.
	% \item Goal: keep $\PCS(\pi,\theta)-P^*$ non-negative and close to $0$.
      \end{itemize}
\end{frame}
}

\zap{
\begin{frame}
  \frametitle{Example}
  \begin{itemize}
  \item In most fully sequential techniques, bounds become very loose as $k$ grows large.
  \begin{itemize}
    \item Example:
      KN (citation)
      $k=10$
      $\delta = 1$
      $\theta = [1,0,\ldots,0]$,
      $P^* = 0.90$.
    \item $\PCS(KN,\theta) \approx 0.98$, Expected number of samples taken is $\approx 5000$
    \item It seems that we could take fewer samples while still meeting $PCS(\pi,\theta)\ge 0.90$.
  \end{itemize}
\item This seems to be due to incidental overdelivery caused by inequalities, e.g., Bonferonni's inequality, used when
  proving the IZ guarantee for particular policies.
  \end{itemize}
\end{frame}
}

\zap{
\begin{frame}
  \frametitle{Example: Too Many Samples}
  % In most (all?) existing R\&S techniques, bounds become very loose as $k$ grows large.
  \center{
  \includegraphics[width=2in]{\figdir/BayesIZ/APS-MDMplotN-KN.pdf} \quad
  \includegraphics[width=2in]{\figdir/BayesIZ/APS-MDMplotPCS-KN.pdf}
  }
  \begin{itemize}
    \item This is the {\bf monotone-decreasing-means configuration}, $\theta=[-\delta,-2\delta,\ldots,-k\delta]$.
    \item Parameters are: $\delta=1$, $\sigma_x=10$, $P^*=0.9$.
    \item The procedure is the KN procedure of \cite{KiNe01}, which is state-of-the-art for problems with not much
      variation in $\sigma^2_x$.  It has been modified to use a known sampling variance.
  \end{itemize}
\end{frame}
}

\zap{
\begin{frame}
  \frametitle{Example}
  \begin{itemize}
  \item In most fully sequential techniques, bounds become very loose as $k$ grows large.
  \begin{itemize}
    \item Example:
      KN (citation)
      $k=10$
      $\delta = 1$
      $\theta = [1,0,\ldots,0]$,
      $P^* = 0.90$.
    \item $\PCS(KN,\theta) \approx 0.98$, Expected number of samples taken is $\approx 5000$
    \item It seems that we could take fewer samples while still meeting $PCS(\pi,\theta)\ge 0.90$.
  \end{itemize}
\item This seems to be due to incidental overdelivery caused by inequalities, e.g., Bonferonni's inequality, used when
  proving the IZ guarantee for particular policies.
  \end{itemize}
\end{frame}
}

\begin{frame}
  \frametitle{Bayesian global optimization}
  \begin{itemize}
    \item We wish to solve an optimization problem
      \begin{equation*}
	\max_{x\in[0,1]^d} f(x).
      \end{equation*}
    \item We begin with a Bayesian prior distribution on $f$.
    \item We have the ability to adaptively choose a sequence of points $x_1,x_2,\ldots$ adaptively, observing
      \begin{equation*}
	y_n = f(x_n) + \epsilon_n,
      \end{equation*}
      where $\epsilon_n$ is typically mean-0 Gaussian noise.
    \item Once our budget of $N$ function evaluations is exhausted, we choose one final point, $\xhat$, and we receive a reward $f(\xhat)$.
    \item Our goal in Bayesian global optimization is to find an algorithm for choosing $x_1,x_2,\ldots,x_N$ and $\xhat$ that maximizes $E[f(\xhat)]$ under the prior.
    \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Example strategies for solving the Bayesian global optimization problem}
  \begin{itemize}
    \item The Bayes-optimal algorithm is the solution to a (very difficult-to-solve) dynamic programming.
    \item In lieu of the Bayes-optimal algorithm, a number of one-step and two-step approximations have been developed:
      \begin{itemize}
	\item Expected improvement methods,
	\item Knowledge-gradient methods,
	\item Stepwise Entropy-reduction methods.
      \end{itemize}
  \end{itemize}
\end{frame}

\newcommand{\KG}{\mathrm{KG}}
\begin{frame}
  \frametitle{The Knowledge-gradient Method}
  Given data $x_1,\ldots,x_n$, $y_1,\ldots,y_n$, the Knowledge-Gradient (KG) method calculates the next measurement $x_{n+1}$ to perform via:
  \begin{itemize}
    \item $\mu_n^* = \max_{\xhat} E_n\left[ G(\xhat,\theta) \right]$ is the best we can do if we stop now, at time $n$, and choose $\xhat$.
    \item $\mu_{n+1}^* = \max_{\xhat} E_{n+1}\left[ G(\xhat,\theta) \right]$ is the best we could do with just 1 additional measurement.  It is random, as it depends on $y_{n+1}$, and its distribution depends on $x_{n+1}$.
    \item $\KG_n(x_{n+1}) = E_n\left[ \mu_{n+1}^* - \mu_n^* \right]$ is the expected value of sample information, or KG factor, and it depends on what we choose to measure, $x_{n+1}$.
    \item The KG policy recommends that our next measurement should be 
      $\argmax_{x_{n+1}} \KG_n(x_{n+1})$. 
  \end{itemize}
\end{frame}

\zap{
\begin{frame}
  \frametitle{Optimal Learning}
  This problem is really a special case of a broader mathematical problem of sequential experimental design:
  \begin{itemize}
    \item There is some unknown quantity $\theta$.
    \item We operate in a Bayesian framework, in which we have a prior on $\theta$.
    \item If we choose to make an observation of type $x_n$ at time $n$, we observe an independent sample $y_n$ from a probability distribution $F(x,\theta)$.
    \item We will adaptive choose a sequence of observation types $x_1,x_2,\ldots,x_N$, after which we will make an implementation decision $\xhat$, and receive a reward $G(\xhat,\theta)$.  ($x_n$ and $\xhat$ may live in completely different spaces, and $F$ and $G$ may be completely different functions).
    \item Our goal is to find an algorithm for choosing $x_1,x_2,\ldots,x_N$ and $\xhat$ that maximize $E[G(\xhat,\theta)]$ under the prior.
  \end{itemize}
\end{frame}
}

\zap{
\begin{frame}\frametitle{Step 1: We Build a Statistical Model that Relates the Peptide to Computer Experiment Output}
  \begin{itemize}
    \item Input: a sequence of letters (amino acids).  
    \item Output: for each letter, a number between 0 and 1 (percent of time in contact); change in configurational entropy due to the target material's presence.
    \item Method: We use Bayesian linear regression, using features based on domain knowledge about how amino acid properties (size, charge, hydrophobicity, binding strength) affects binding.
    \item Prior: We use empirical Bayes, with training data from previous computer experiments.
\end{itemize}
Put model output
  \begin{figure}\includegraphics[width=2in]{\figdir/Prasad/PARE_Prasad2.pdf}\end{figure}
\end{frame}

\begin{frame}\frametitle{Step 2: We Build a Statistical Model that Relates Computer Experiment Output to Physical Experiment Output}
  \begin{itemize}
    \item Input: for each amino acid in the peptide, a number between 0 and 1 (percent of time in contact); change in configurational entropy due to the target material's presence.
    \item Output: 
    \item Method: We use Bayesian linear regression, and domain knowledge about (1) the binding strength of an individual amino acid when it is in contact, and (2) statistical mechanics.
    \item Prior: We use empirical Bayes, with training data from previous computer and lab experiments.
\end{itemize}
  \begin{figure}\includegraphics[width=2in]{\figdir/Prasad/PARE_Prasad2.pdf}\end{figure}
\end{frame}

\begin{frame}\frametitle{Step 3: We Use the Knowledge-Gradient Method}
  \begin{itemize}
    \item

  \end{itemize}
\end{frame}
}

\begin{frame}
  \frametitle{Optimal Learning includes ``learn-then-do'' problems}
  % This problem is really a special case of a broader mathematical problem of sequential experimental design:
  \begin{itemize}
    \item There is some unknown quantity $\theta$.
    \item We operate in a Bayesian framework, in which we have a prior on $\theta$.
    \item If we make an observation of type $x_n$ at time $n$, we observe a sample whose distribution depends on $x_n$ and $\theta$.
    \item We adaptively choose a sequence of observation types $x_1,x_2,\ldots,x_N$, after which we will make an implementation decision $\xhat$, and receive a reward whose value depends on $\xhat$ and $\theta$
    \item Our goal is to find an algorithm for choosing $x_1,x_2,\ldots,x_N$ and $\xhat$ that maximizes the expected reward received under the prior.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Policies for solving optimal learning problems}
  \begin{itemize}
    \item The Bayes-optimal algorithm is the solution to a dynamic program.
      \begin{itemize}
	\item This DP is usually intractable.
	\item In a few special cases, we can solve it, using special structure (last year's talk).
      \end{itemize}
    \item When the Bayes-optimal algorithm cannot be computed, we can instead try:
      \begin{itemize}
	\item Expected improvement methods.
	\item Knowledge-gradient methods.
	\item Stepwise entropy-reduction methods.
      \end{itemize}
  \end{itemize}
\end{frame}

### 2015-06-18 paper/wish/wsc15paper.tex
new changes

@@
 that eliminates the use of Bonferroni's inequality, reducing conservatism. 
-This procedure's lower bound on worst-case probability of correct selection in the
-preference zone is tight in continuous time, and almost tight in the
-discrete time. In numerical experiments, the number of samples required
-by BIZ is significantly smaller than that of procedures like the KN procedure of \citeN{Kim:2001} and
-the $\mathcal{P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968}, 
-especially on problems with many alternatives. Unfortunately, the
+This procedure's lower bound on the worst-case probability of correct selection in the
+preference zone is tight in continuous time, and almost tight in discrete time. In numerical experiments, the number of samples required
+by BIZ is significantly smaller than that of procedures like the $\mathcal{P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968} and the KN procedure of \citeN{Kim:2001}, especially on problems with many alternatives.
+Unfortunately, the
 proof from \cite{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
@@
 in the selection of a system whenever the means of the populations
-are nearly the same. Formally, let $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
+are nearly the same. Formally, let $\mu=\left[\mu_{1},\ldots,\mu_{k}\right]$
 be the vector of the true means, the \emph{indifference zone} is defined
@@
 We assume $P^{*}>1/k$ because IZ guarantees can be meet by choosing
-$\hat{x}$ uniformly at random from among $\left\{ 1,\ldots,k\right\} $.
+$\hat{x}$ uniformly at random from $\left\{ 1,\ldots,k\right\} $.
 
@@
 The procedure ends when there is only one alternative in the contention
-set and this remain alternative is chosen as the best.
+set and this remaining alternative is chosen as the best.
 
@@
 A slight modification of the discrete-time BIZ procedure for unknown and/or heterogeneous sampling
-variances is given below.  It takes a variable number of samples
-from each alternative, and $n_{tx}$ is this number. This algorithm
-depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
+variances is given below.  This algorithm takes a variable number of samples
+from alternative $x$ at time $t$, and $n_{tx}$ is this number (its definition may found in the algorithm given below). 
+This algorithm depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
 and $n_{0}$. Here, $n_{0}$ is the number of samples to use in the first
-stage of samples, and $100$ is the recommended value for $n_{0}$. The paramater
+stage of samples, and $100$ is the recommended value for $n_{0}$ when the variances are unknown. The paramater
 $B_{x}$ controls the number of samples taken from system $x$ in
@@
 where $\hat{\lambda}_{tx'}^{2}$ is the sample variance of all samples
-from alternative $x$ thus far and $Z_{tx}=Y_{n_{tx},x}$.
+from alternative $x$ thus far, and $Z_{tx}=Y_{n_{tx},x}$ is the sum of
+the samples from alternative $x$ observed by stage $t$.
 
@@
 For the problem given $\delta$, we suppose that the vector of the true means
-$\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$ is equal to $\delta a$ for some fixed $a\in\mathbb{R}^{k}$ that
+$\mu=\left[\mu_{1},\ldots,\mu_{k}\right]$ is equal to $\delta a$ for some fixed $a\in\mathbb{R}^{k}$ that
 does not depend on $\delta$ and $a_{k}>a_{k-1}\geq \cdots \geq a_{1}$, $a_{k}-a_{k-1}>1$.
@@
 
-The first is the mapping from the raw discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
+The first mapping is from the raw discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
 onto a time changed version of this random walk, written as $\left(Z_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$,
-where we recall $Z_{tx}=Y_{n_{x}\left(t\right),t}$ is the sum of
+where we recall $Z_{tx}=Y_{n_{tx},x}$ is the sum of
 the samples from alternative $x$ observed by stage $t$.
 
-The second maps this time-changed random walk through a non-linear
+The second one maps this time-changed random walk through a non-linear
 mapping for each $t,x$ and subset $A\subset\left\{ 1,\ldots,k\right\} $,
@@
 
-We have proved the asymptotic validity of the Bayes-inspired Zone
+We have proved the asymptotic validity of the Bayes-inspired Indifference Zone
 procedure \cite{Frazier:BIZ} when the variances are known.

### 2015-06-22 paper/wish/wsc15paper.tex
corrections

@@
 Unfortunately, the
-proof from \cite{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
+proof from \citeN{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
 (2) variances are known;
@@
 The contribution of this work is to prove the asymptotic validity of the BIZ procedure as $\delta$ goes to zero, retaining the assumption of known variances, but replacing assumptions (1) and (3) by the much weaker assumption of independent and identically distributed finite variance samples.
-Thus, our proof allows a much broader set of sampling distributions than that allowed by \cite{Frazier:BIZ}, including non-normal samples and general heterogeneous variances.
+Thus, our proof allows a much broader set of sampling distributions than that allowed by \citeN{Frazier:BIZ}, including non-normal samples and general heterogeneous variances.
 We also show that this bound on worst-case PCS is asymptotically tight as $\delta$ goes to zero, 
@@
 
-To simplify our analysis, we analyze a slight modification of the version of the BIZ procedure presented in \cite{Frazier:BIZ}, which keeps a certain parameter $\lambda^2_z$ fixed rather than letting it vary as did \cite{Frazier:BIZ}.
+To simplify our analysis, we analyze a slight modification of the version of the BIZ procedure presented in \citeN{Frazier:BIZ}, which keeps a certain parameter $\lambda^2_z$ fixed rather than letting it vary as did \citeN{Frazier:BIZ}.
 Numerical experiments on typical cases show little difference in performance between the version of BIZ we analyze and the version in \citeN{Frazier:BIZ}.
@@
 
-This paper is organized as follows: In $\text{ß}2$, we recall the
-indifference-zone ranking and selection problem. In $\text{ß}3$,
-we recall the Bayes-inspired IZ (BIZ) procedure from \citeN{Frazier:BIZ}. In $\text{ß}4$,
+This paper is organized as follows: In $\mathsection$\ref{IZR}, we recall the
+indifference-zone ranking and selection problem. In $\mathsection$\ref{sec:BIZ},
+we recall the Bayes-inspired IZ (BIZ) procedure from \citeN{Frazier:BIZ}. In $\mathsection$\ref{proof},
 we present the proof of the validity of the algorithm when the variances
-are known. In $\text{ß}5$, we present some numerical experiments. 
-In $\text{ß}6$, we conclude.
+are known. In $\mathsection$\ref{numericalExperiments}, we present some numerical experiments. 
+In $\mathsection$\ref{conclusion}, we conclude.
 
 \section{INDIFFERENCE-ZONE RANKING AND SELECTION}
+\label{IZR}
 
@@
 The procedure ends when there is only one alternative in the contention
-set and this remaining alternative is chosen as the best.
+set and this remaining alternative is chosen as the best. It is shown in \citeN{Frazier:BIZ} that the
+algorithm ends in a finite number of steps with probability one.
 
@@
 \section{ASYMPTOTIC VALIDITY WHEN THE VARIANCES ARE KNOWN}
+\label{proof}
 
@@
 in continuous time; and (3) the BIZ procedure satisfies the IZ guarantee
-when applied in continuous time (Theorem~1 in \cite{Frazier:BIZ}), and so $E[g(W)] \ge P^*$ with equality for the worst configurations in the preference zone.
+when applied in continuous time (Theorem~1 in \citeN{Frazier:BIZ}), and so $E[g(W)] \ge P^*$ with equality for the worst configurations in the preference zone.
 
@@
 
-We now construct a function $g(\cdot)$ that, when applied to the path of a $k$-dimensional standard Brownian motion, will be equal in distribution to the indicator of the correct selection event from the continuous-time BIZ procedure from \cite{Frazier:BIZ}
+We now construct a function $g(\cdot)$ that, when applied to the path of a $k$-dimensional standard Brownian motion, will be equal in distribution to the indicator of the correct selection event from the continuous-time BIZ procedure from \citeN{Frazier:BIZ}
 to a transformed problem that does not depend on $\delta$.
@@
 
-The random variable $g(W)$ is equal in distribution to the indicator of the event of correct selection that results from applying the continuous-time BIZ procedure from \cite{Frazier:BIZ} in a problem with indifference-zone parameter equal to 1, where each alternative's observation process has volatility $\lambda_z$ and drift $a_x$.
+The random variable $g(W)$ is equal in distribution to the indicator of the event of correct selection that results from applying the continuous-time BIZ procedure from \citeN{Frazier:BIZ} in a problem with indifference-zone parameter equal to 1, where each alternative's observation process has volatility $\lambda_z$ and drift $a_x$.
 This can be seen by noting that the path $(q^{W}_{tx}(A) : t\ge0)$ defined above is equal in distribution to the path $(q_{tx}(A) : t\ge0)$ defined in equation (2) of \citeN{Frazier:BIZ}, and that the selection decision of the continuous-time algorithm in \citeN{Frazier:BIZ} is obtained by applying $h$ to this path.
@@
 \section{NUMERICAL EXPERIMENTS}
+\label{numericalExperiments}
 
@@
 \section{CONCLUSION}
+\label{conclusion}
 

### 2015-07-02 paper/wish/wsc15paper.tex
corrections

@@
 
-The third maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
+The third one maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
 onto selection decisions. Specifically, this mapping begins with $A_0 = \{1,\ldots,k\}$,

### 2015-07-02 paper/wish/wsc15paper.tex
small changes to paper before final version is ready

--- 2015-06-22 paper/wish/wsc15paper.tex
@@
 As $\delta$ goes to $0$, we observe that the PCS converges to $P^*$, as it did in the known-variance slippage configuration example.
-In this example, we have intentionally chosen $n_0$ to be small, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
+In this example, we have intentionally chosen $n_0$ to be smaller than the recommended value of 100, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
 Increasing the parameter $n_0$ typically causes BIZ to meet the IZ guarantee for all $\delta$, and we recommend a larger value of $n_0$ in practice.
@@
 \noindent {\bf PETER I.
-FRAZIER} is an Assistant Professor of the School of Operations Research and Information Engineering at Cornell University, Ithaca, NY.
+FRAZIER} is an Associate Professor of the School of Operations Research and Information Engineering at Cornell University, Ithaca, NY.
 He holds a Ph.D.

### 2015-07-02 paper/wish/correctionsWSC.tex

%% LyX 2.1.2.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=1.5cm,bmargin=1.5cm,lmargin=1.5cm,rmargin=1.5cm}
\usepackage{mathrsfs}
\usepackage{babel}
\begin{document}

\title{Changes to the WSC paper}
\maketitle
\begin{enumerate}
\item Frazier 2014 is now correctly cited in the paper.
\item Page, 3rd paragraph: line 3, lower bound on {*}the{*} worst-case probability;
line 4, in the discrete time -> in discrete time; Line 5, order for
references to KN and $\mathscr{P}_{B}^{*}$ has been switched.
\item Page 2, Last paragraph, - it's now Section 2, 3, 4 instead of 2,3,4. 
\item Page 3, 3rd paragraph, and page 4 - vector mu is now indexed from
1 to k. 
\item Page 3, 4th paragraph, - the word among before \{1, ..., k\} was removed.
\item Page 3, 1st paragraph in Section 3, remain -> remaining 
\item 3rd paragraph in Section 3 -Before: It takes a variable number of
samples from each alternative, and ntx is this number. Now: This algorithm
takes a variable number of samples from alternative $x$ at time $t$,
and $n_{tx}$ is this number (its definition may found in the algorithm
given below). 
\item End of page 3, Before: $Z_{tx}=Y_{n_{tx},x}$ . Now: and $Z_{tx}=Y_{n_{tx},x}$
is the sum of the samples from alternative $x$ observed by stage
$t$.
\item Section 4, 3rd paragraph, Before: The first is the mapping; The second
maps; The third maps. Now: The first mapping is ; The second one maps;
The third one maps
\item Section 6, Zone -> Indifference Zone 
\item References: before: \textquotedblleft automatic control\textquotedblright ;
S.-H. Kim. Now: \textquotedblleft Automatic Control\textquotedblright ;
S. Kim\end{enumerate}

\end{document}

### 2015-07-02 paper/wish/corrections.tex
corrections.txt

%% LyX 2.1.2.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,english]{article}
\usepackage[LGR,T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=1.5cm,bmargin=1.5cm,lmargin=1.5cm,rmargin=1.5cm}
\usepackage{textcomp}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\DeclareRobustCommand{\greektext}{%
  \fontencoding{LGR}\selectfont\def\encodingdefault{LGR}}
\DeclareRobustCommand{\textgreek}[1]{\leavevmode{\greektext #1}}
\DeclareFontEncoding{LGR}{}{}
\DeclareTextSymbol{\~}{LGR}{126}

\makeatother

\usepackage{babel}
\begin{document}

\title{WSC15 paper}

\maketitle

\section*{Reviewer 1.}
\begin{enumerate}
\item \textit{Frazier 2014 was cite lots of times, modify the cite commands
accordingly to make sure the correct format. }Now, it should be fine.
\item \textit{Second corrections. }They're now correct.
\item \textit{Use Section 2, 3, 4 instead just 2,3,4 when referring to those
sections.} I changed this part, but I'm not sure if we have to write
the word section before the number.
\item Page 3, 3rd paragraph. Now it is correct.
\item Page 3, 4th paragraph. Now it is correct.
\item Page 3, 1st paragraph in Section 3. Now it is correct.
\item 3rd paragraph in Section 3. I think that now it is clear. \textit{Says
100 is the recommended value for n\_0, but later in the algorithm
and experiments used something else. }I added that this value is recommended
when the variances are unknown.
\item End of page 3. Now it should be clear.
\item Section 4, 3rd paragraph. Now it is correct.
\item Section 6. Now it is correct.
\end{enumerate}

\section*{Reviewer 2.}
\begin{enumerate}
\item \textit{It seems that the choice of n0 is relatively arbitrary. In
practice, can problem properties be used to obtain some understanding
of how large/small n0 should be? }I don't now if we should say something
in section 3 about this because it is difficult to say something if
we don't now the variances of the alternatives.
\item \textit{It does seem to me that we choose a far too stringent threshold,
the resulting problem may be rendered infeasible since \textmu {[}k
are exogenously specified and presumably unavailable a prior and \textgreek{d}
is a user-specified parameter. In re-reading the paper, it seems that
the alternatives may have nearly the same means, in which case, the
likelihood of infeasibility may be modest. }Should we say that if
the configuration is not in the preference zone, then we can't say
anything about the alternative selected?
\item \textit{While the BIZ procedure is asymptotically valid, naturally
in practice, the schemes have to be terminated after a finite number
of samples. Are there error bounds available, even in a restricted
regime, that can govern the choice of when the procedure may be terminated.
}I said in section 3 that the algorithm will end in a finite number
of steps. However, I think there are no error bounds available if
we just stop the algorithm before time. What should we say about this?
\item \textit{In the numerical experiments, the choice of \textmu \textquoteright s
and \textgreek{d} ensures feasibility. Suppose \textmu 100 is set
to \textgreek{d} + 1, then unless I have misunderstood how the scheme
works, the threshold constraint would render the problem infeasible.
In this case, how would the scheme respond? }This can't happen because
we are supposing that $\mu=a\delta$. Should we say something else?
\item \textit{It might be useful to see how the BIZ procedure is indeed
less conservative in practice compared to its counterparts in the
R\&S literature. The authors claim that the proposed procedure requires
less samples \textendash{} presumably this is only an empirical observation.
If so, please emphasize that this is the case; else it might be worth
pointing to the formal statement that guarantees this claim. }This
observation is based on empirical observations and that the BIZ procedure
is less conservative. Should we say something else in the introduction
to make this more clear?
\item \textit{Finally, some quick observations regarding the references.
}I think that now they are fine. I had to cite the two editions of
Billingsley's book because I used the two editions. \end{enumerate}

\end{document}

### 2015-07-02 paper/wish/wsc15paper.tex
good selectiongood selection

@@
 in \citeN{Bechhofer:1995}, \citeN{swisher:survey}, \citeN{kim:20062} and \citeN{kim:2007}.
-Other approaches, beyond the indifference-zone approach, include the Bayesian approach \cite{Frazier:Tutorial}, the optimal computing budget allocation approach \cite{chen:ocva}, and the large deviations approach \cite{glynn2004large}.
+Other approaches, beyond the indifference-zone approach, include the Bayesian approach \cite{Frazier:Tutorial}, the optimal computing budget allocation approach \cite{chen:ocva}, the large deviations approach \cite{glynn2004large}, and the probability of good selection guarantee \cite{nelson2001selecting}.
+The last approach is similar to the indifference-zone formulation, but provides a more robust guarantee.
 
@@
 IZ procedure, called BIZ (Bayes-inspired Indifference Zone), 
-that eliminates the use of Bonferroni's inequality, reducing conservatism. 
+that eliminates the use of Bonferroni's inequality, reducing conservatism. \mathcal
 This procedure's lower bound on the worst-case probability of correct selection in the
 preference zone is tight in continuous time, and almost tight in discrete time. In numerical experiments, the number of samples required
-by BIZ is significantly smaller than that of procedures like the $\mathcal{P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968} and the KN procedure of \citeN{Kim:2001}, especially on problems with many alternatives.
+by BIZ is significantly smaller than that of procedures like the ${P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968} and the KN procedure of \citeN{Kim:2001}, especially on problems with many alternatives.
 Unfortunately, the

### 2015-07-02 paper/wish/wsc15paper.tex
changes

@@
 IZ procedure, called BIZ (Bayes-inspired Indifference Zone), 
-that eliminates the use of Bonferroni's inequality, reducing conservatism. \mathcal
+that eliminates the use of Bonferroni's inequality, reducing conservatism. 
 This procedure's lower bound on the worst-case probability of correct selection in the

### 2015-07-02 paper/wish/wsc15paper.tex
edits to paper to address reviewer 2

--- 2015-07-02 paper/wish/wsc15paper.tex
@@
 Increasing the parameter $n_0$ typically causes BIZ to meet the IZ guarantee for all $\delta$, and we recommend a larger value of $n_0$ in practice.
+The choice of $n_0$, and its impact on PCS, merits further study.
 
@@
 procedure \cite{Frazier:BIZ} when the variances are known.
-This algorithm takes fewer samples than other IZ procedures, especially for
+This algorithm has been observed empirically to take fewer samples than other IZ procedures, especially for
 problems with large numbers of alternatives, and so characterizing when it

### 2015-07-02 paper/wish/corrections.tex
new corrections file.  also checking in second review.

@@
 \item \textit{Frazier 2014 was cite lots of times, modify the cite commands
-accordingly to make sure the correct format. }Now, it should be fine.
-\item \textit{Second corrections. }They're now correct.
+accordingly to make sure the correct format. }
+We have corrected this.
+
+\item \textit{Second corrections. }
+We have corrected this.
+
 \item \textit{Use Section 2, 3, 4 instead just 2,3,4 when referring to those
-sections.} I changed this part, but I'm not sure if we have to write
-the word section before the number.
-\item Page 3, 3rd paragraph. Now it is correct.
-\item Page 3, 4th paragraph. Now it is correct.
-\item Page 3, 1st paragraph in Section 3. Now it is correct.
-\item 3rd paragraph in Section 3. I think that now it is clear. \textit{Says
-100 is the recommended value for n\_0, but later in the algorithm
-and experiments used something else. }I added that this value is recommended
-when the variances are unknown.
-\item End of page 3. Now it should be clear.
-\item Section 4, 3rd paragraph. Now it is correct.
-\item Section 6. Now it is correct.
+sections.} 
+We have corrected this.  To preserve space, we have used the section symbol, rather than the word ``Section''.
+\item {\it Page 3, 3rd paragraph}. Now it is correct.
+\item {\it Page 3, 4th paragraph}. Now it is correct.
+\item {\it Page 3, 1st paragraph in Section 3}. Now it is correct.
+\item {\it 3rd paragraph in Section 3}.\\
+{\it -- It's not clear what n\_tx is, especially the range for t and x.}\\
+{\it -- Says 100 is the recommended value for n\_0, but later in the algorithm and experiments used something else.}
+
+We have clarified the description of $n_{tx}$.
+
+Regarding $n_0$, we do indeed recommend the value of 100, but only when variances are unknown.
+We have clarified this in the text in the noted place in Section 3.
+Additionally, in the unknown variance example in the numerical experiments, we use a value lower than the recommended value to make correct selection more difficult, and to observe the full range of behavior from the algorithm.
+When the recommended value is used, the algorithm provides performance similar to that shown in Figure 1(a).
+We have clarified this in the text discussing the second example in Section 5.
+
+\item {\it End of page 3.} We have clarified the definition of $Y_{n_{tx},x}$.
+\item {\it Section 4, 3rd paragraph.} Now it is correct.
+\item {\it Section 6.} Now it is correct.
 \end{enumerate}
@@
 practice, can problem properties be used to obtain some understanding
-of how large/small n0 should be? }I don't now if we should say something
-in section 3 about this because it is difficult to say something if
-we don't now the variances of the alternatives.
+of how large/small n0 should be? }
+
+Our experience is that when n0 is chosen reasonably large ($\ge 100$), then the performance of BIZ is robust, in terms of providing a PCS that is consistently above $P^*$.
+When n0 is smaller than this, we observe, as we did in the numerical experiments, that PCS may fall below $P^*$.
+However, we have not yet done enough experiments to say anything beyond the statements in the current paper recommending a value of 100 for n0.
+
+In Section 5, we previously stated,
+
+``In this example, we have intentionally chosen $n_0$ to be small, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta > 0$.
+Increasing the parameter $n_0$ typically causes BIZ to meet the IZ guarantee for all $\delta$, and we recommend a larger value of $n_0$ in practice.''
+
+We have added to this the sentence, ``The choice of $n_0$, and its impact on PCS, merits further study.''
+
 \item \textit{It does seem to me that we choose a far too stringent threshold,
@@
 the alternatives may have nearly the same means, in which case, the
-likelihood of infeasibility may be modest. }Should we say that if
-the configuration is not in the preference zone, then we can't say
-anything about the alternative selected?
+likelihood of infeasibility may be modest. }
+
+Actually, in the problem that we study, there cannot be infeasibility.
+We believe that the reviewer is referring to the fact that the configuration may not be in the preference zone.
+In this case, the indifference zone guarantee does not guarantee a probability of correct selection, but the problem is not infeasible.
+This is a property of the indifference-zone formulation of ranking and selection, and is not specific to the current paper.
+
+In practice, most procedures that satisfy the indifference-zone guarantee also satisfy what is called a ``probability of good selection'' guarantee, which is defined by Nelson and Banerjee (2001).
+This guarantee does apply to configurations inside of the preference-zone --- it says that with probability $P^*$, the procedure selects an alternative within $\delta$ of the best.
+We have added a brief discussion of this point, and the reference to Nelson and Banerjee (2001), to the paper.
+Extending our results to a probability of good selection guarantee is worthwhile, and we hope to pursue it in future work.
+
+% We could add a discussion of this in the paper if we wanted.
+
 \item \textit{While the BIZ procedure is asymptotically valid, naturally
@@
 regime, that can govern the choice of when the procedure may be terminated.
-}I said in section 3 that the algorithm will end in a finite number
-of steps. However, I think there are no error bounds available if
-we just stop the algorithm before time. What should we say about this?
-\item \textit{In the numerical experiments, the choice of \textmu \textquoteright s
-and \textgreek{d} ensures feasibility. Suppose \textmu 100 is set
-to \textgreek{d} + 1, then unless I have misunderstood how the scheme
-works, the threshold constraint would render the problem infeasible.
-In this case, how would the scheme respond? }This can't happen because
-we are supposing that $\mu=a\delta$. Should we say something else?
-\item \textit{It might be useful to see how the BIZ procedure is indeed
-less conservative in practice compared to its counterparts in the
-R\&S literature. The authors claim that the proposed procedure requires
-less samples \textendash{} presumably this is only an empirical observation.
-If so, please emphasize that this is the case; else it might be worth
-pointing to the formal statement that guarantees this claim. }This
-observation is based on empirical observations and that the BIZ procedure
-is less conservative. Should we say something else in the introduction
-to make this more clear?
-\item \textit{Finally, some quick observations regarding the references.
-}I think that now they are fine. I had to cite the two editions of
-Billingsley's book because I used the two editions. \end{enumerate}
+}
+
+The BIZ procedure terminates on its own, in a finite number of samples.
+The user does not need to make this decision.
+The asymptotic aspect of the analysis refers to $\delta$ becoming small.
+When the procedure terminates, in the cases considered in Frazier (2014) (which includes common known variance with normal samples), the procedure satisfies the IZ guarantee, which is an error bound, even which $\delta>0$.
+
+We clarified this point in section 3 by stating that the algorithm ends in a finite number of steps.
+
+\item \textit{In the numerical experiments, the choice of $\mu$ 
+and $\delta$ ensures feasibility. Suppose $\mu_{100}$ is set
+to $\delta + 1$, then unless I have misunderstood how the scheme
+works, the threshold constraint would render the problem infeasible. In this case, how would the scheme respond? }
+
+As discussed above, the problem would not become infeasible.
+Instead, a problem configuration might not be in the preference zone.
+For problem configurations outside of the preference zone, the indifference-zone guarantee does not provide any guarantee on PCS.
+
+\item \textit{It might be useful to see how the BIZ procedure is indeed less conservative in practice compared to its counterparts in the R\&S literature.
+The authors claim that the proposed procedure requires less samples \textendash{} presumably this is only an empirical observation.
+If so, please emphasize that this is the case; else it might be worth pointing to the formal statement that guarantees this claim.
+}
+
+This statement is based on extensive numerical experiments in Frazier (2014).
+
+We state in the introduction, when the BIZ procedure is first mentioned, that
+
+``In numerical experiments, the number of samples required by BIZ
+is significantly smaller than that of procedures like the $P^*_\mathcal{B}$ procedure of Bechhofer, Kiefer, and Sobel (1968) and the KN  procedure of Kim and Nelson (2001), especially on problems with many alternatives.''
+
+This sentence states that the observation is empirical, as it is based on numerical experiments.
+
+We have modified the conclusion to also point out the empirical nature of this statement:
+
+``[BIZ] has been observed empirically to take fewer samples than other IZ procedures, especially for problems with large numbers of alternatives\ldots''
+
+\item \textit{Finally, some quick observations regarding the references.}
+
+We have corrected these issues.  We reference Billingsley twice because we use results from two different editions of the book (1968 and 1999). 
+\end{enumerate}
 

### 2015-07-02 paper/wish/first_submission.tex
combining corrections and diff together into response

--- 2015-07-02 paper/wish/wsc15paper.tex
@@
 	257 Rhodes Hall \\
-	232 Rhodes Hall \\
+	206 Rhodes Hall \\
 	Ithaca, NY 14853, USA\\
@@
 This is called the ranking and selection problem.
+% In such ranking and selection problems, we must decide how many samples we need to accurately find the alternative with the largest mean. 
 A good procedure for addressing this problem should be both efficient and accurate, i.e. it should balance the number of samples it takes with the quality of its selection.
@@
 than necessary. The Bonferonni-based bounds underlying these procedures become looser, and the tendency to take more samples than necessary increases, as the number of alternatives grow.
-More recently, new algorithms were developed in \citeN{Kim:2001}, \shortciteN{Goldsman:2002}, 
+More recently, new algorithms were developed in \citeN{Kim:2001}, \citeN{Goldsman:2002}, 
 \citeN{Hong}, and they improve performance but they still
@@
 that eliminates the use of Bonferroni's inequality, reducing conservatism. 
-This procedure's lower bound on the worst-case probability of correct selection in the
-preference zone is tight in continuous time, and almost tight in discrete time. In numerical experiments, the number of samples required
-by BIZ is significantly smaller than that of procedures like the $\mathcal{P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968} and the KN procedure of \citeN{Kim:2001}, especially on problems with many alternatives.
-Unfortunately, the
-proof from \citeN{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
+This procedure's lower bound on worst-case probability of correct selection in the
+preference zone is tight in continuous time, and almost tight in the
+discrete time. In numerical experiments, the number of samples required
+by BIZ is significantly smaller than that of procedures like the KN procedure of \citeN{Kim:2001} and
+the $\mathcal{P}_{B}^{*}$ procedure of \citeN{Bechhofer:1968}, 
+especially on problems with many alternatives. Unfortunately, the
+proof from \cite{Frazier:BIZ} that the BIZ procedure satisfies the IZ guarantee for the discrete-time case assumes that (1) samples are normally distributed; 
 (2) variances are known;
@@
 The contribution of this work is to prove the asymptotic validity of the BIZ procedure as $\delta$ goes to zero, retaining the assumption of known variances, but replacing assumptions (1) and (3) by the much weaker assumption of independent and identically distributed finite variance samples.
-Thus, our proof allows a much broader set of sampling distributions than that allowed by \citeN{Frazier:BIZ}, including non-normal samples and general heterogeneous variances.
+Thus, our proof allows a much broader set of sampling distributions than that allowed by \cite{Frazier:BIZ}, including non-normal samples and general heterogeneous variances.
 We also show that this bound on worst-case PCS is asymptotically tight as $\delta$ goes to zero, 
@@
 
-To simplify our analysis, we analyze a slight modification of the version of the BIZ procedure presented in \citeN{Frazier:BIZ}, which keeps a certain parameter $\lambda^2_z$ fixed rather than letting it vary as did \citeN{Frazier:BIZ}.
-Numerical experiments on typical cases show little difference in performance between the version of BIZ we analyze and the version in \citeN{Frazier:BIZ}.
+To simplify our analysis, we analyze a slight modification of the version of the BIZ procedure presented in \cite{Frazier:BIZ}, which keeps a certain parameter $\lambda^2_z$ fixed rather than letting it vary as did \cite{Frazier:BIZ}.
+Numerical experiments on typical cases show little difference in performance between the version of BIZ we analyze and the version in \cite{Frazier:BIZ}.
 We conjecture that a proof technique similar to the one presented here can be used to show asymptotic validity of the BIZ procedure when
 the variances are unknown, and we present numerical experiments that support this belief. 
+% \citeN{kim:asympt} also proves the asymptotical validity of a IZ procedure in the same limit.
+% Our proof shares some similarities since we both use a central limit theorem.
 
-This paper is organized as follows: In $\mathsection$\ref{IZR}, we recall the
-indifference-zone ranking and selection problem. In $\mathsection$\ref{sec:BIZ},
-we recall the Bayes-inspired IZ (BIZ) procedure from \citeN{Frazier:BIZ}. In $\mathsection$\ref{proof},
+This paper is organized as follows: In $\text{ß}2$, we recall the
+indifference-zone ranking and selection problem. In $\text{ß}3$,
+we recall the Bayes-inspired IZ (BIZ) procedure from \citeN{Frazier:BIZ}. In $\text{ß}4$,
 we present the proof of the validity of the algorithm when the variances
-are known. In $\mathsection$\ref{numericalExperiments}, we present some numerical experiments. 
-In $\mathsection$\ref{conclusion}, we conclude.
+are known. In $\text{ß}5$, we present some numerical experiments. 
+In $\text{ß}6$, we conclude.
 
 \section{INDIFFERENCE-ZONE RANKING AND SELECTION}
-\label{IZR}
 
@@
 are identically distributed and independent, over time and across alternatives, and
-each alternative $x$ has mean $\mu_{x}$. We define $\mu=(\mu_{1},\ldots,\mu_{k})$.
+each alernative $x$ has mean $\mu_{x}$. We define $\mu=(\mu_{1},\ldots,\mu_{k})$.
 
@@
 in the selection of a system whenever the means of the populations
-are nearly the same. Formally, let $\mu=\left[\mu_{1},\ldots,\mu_{k}\right]$
+are nearly the same. Formally, let $\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$
 be the vector of the true means, the \emph{indifference zone} is defined
@@
 We assume $P^{*}>1/k$ because IZ guarantees can be meet by choosing
-$\hat{x}$ uniformly at random from $\left\{ 1,\ldots,k\right\} $.
+$\hat{x}$ uniformly at random from among $\left\{ 1,\ldots,k\right\} $.
 
@@
 The procedure ends when there is only one alternative in the contention
-set and this remaining alternative is chosen as the best. It is shown in \citeN{Frazier:BIZ} that the
-algorithm ends in a finite number of steps with probability one.
+set and this remain alternative is chosen as the best.
 
-\citeN{Frazier:BIZ} shows that the BIZ procedure satisfies the IZ guarantee 
-under the assumptions that samples are normally distributed, variances are known, and
-the variances are either common across alternatives, or have an integer multiple structure.
-The continuous time version of this procedure also satisfies the IZ guarantee, with a tight worst-case
+Frazier \cite{Frazier:BIZ} showed that the BIZ procedure with known common variance
+satisfies the IZ guarantee when the systems follow the normal distribution
+, with tight bounds on worst-case preference-zone in continuous time.
+He also proved that this procedure retains the IZ guarantee when the
+systems follow the normal distribution, and the variances are known
+and are integer multiples of a common value. The continuous time version
+of this procedure also satisfies the IZ guarantee, with a tight worst-case
 preference-zone PCS bound.
 
-A slight modification of the discrete-time BIZ procedure for unknown and/or heterogeneous sampling
-variances is given below.  This algorithm takes a variable number of samples
-from alternative $x$ at time $t$, and $n_{tx}$ is this number (its definition may found in the algorithm given below). 
-This algorithm depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
-and $n_{0}$. Here, $n_{0}$ is the number of samples to use in the first
-stage of samples, and $100$ is the recommended value for $n_{0}$ when the variances are unknown. The paramater
+The discrete-time BIZ procedure for unknown and/or heterogeneous sampling
+variances is given below.  It takes a variable number of samples
+from each alternative, and $n_{tx}$ is this number. This algorithm
+depends on a collection of integers $B_{1},\ldots,B_{k}$, $P^{*},c,\delta$
+and $n_{0}$. $n_{0}$ is the number of samples to use in the first
+stage of samples, and $100$ is the recommended value for $n_{0}$.
 $B_{x}$ controls the number of samples taken from system $x$ in
-each stage. To simplify our analysis, the procedure presented is a slight modification of the original BIZ 
-procedure \cite{Frazier:BIZ} where $z \in \mbox{arg max}_{x\in A} \lambda^2_{x}$, instead 
-of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambda^2_{x}$. According to numerical experiments on common cases, there is little difference in the PCS between the version of BIZ
-we analyze and the version in \citeN{Frazier:BIZ}.
+each stage. The procedure presented is a slightly modification of the original BIZ 
+procedure where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead 
+of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.
 
@@
 where $\hat{\lambda}_{tx'}^{2}$ is the sample variance of all samples
-from alternative $x$ thus far, and $Z_{tx}=Y_{n_{tx},x}$ is the sum of
-the samples from alternative $x$ observed by stage $t$.
+from alternative $x$ thus far and $Z_{tx}=Y_{n_{tx},x}$.
 
@@
 \STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
-Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.
-Let $t\leftarrow 0$.
-Let $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{x}$, where $\lambdahat^2_{x}$ is the empirical estimator of the variance $\lambda^2_x$ using $n_0$ samples if $x\in A$.
+Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.Let $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$.     
 \STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
@@
 This algorithm generalizes the BIZ procedure with known common variance.
-In that case, we have that $B_1=\cdots=B_k=1$ and $n_{tx}=t$.
-The algorithm can be generalized to the continuous case (see  \citeN{Frazier:BIZ}).
+In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$.
+The algorithm 2 can be generalized to the continuous case (See  \citeN{Frazier:BIZ}).
 
 \section{ASYMPTOTIC VALIDITY WHEN THE VARIANCES ARE KNOWN}
-\label{proof}
 
@@
 For the problem given $\delta$, we suppose that the vector of the true means
-$\mu=\left[\mu_{1},\ldots,\mu_{k}\right]$ is equal to $\delta a$ for some fixed $a\in\mathbb{R}^{k}$ that
+$\mu=\left[\mu_{k},\ldots,\mu_{1}\right]$ is equal to $\delta a$ for some fixed $a\in\mathbb{R}^{k}$ that
 does not depend on $\delta$ and $a_{k}>a_{k-1}\geq \cdots \geq a_{1}$, $a_{k}-a_{k-1}>1$.
@@
 
-The first mapping is from the raw discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
+The first is the mapping from the raw discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
 onto a time changed version of this random walk, written as $\left(Z_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$,
-where we recall $Z_{tx}=Y_{n_{tx},x}$ is the sum of
+where we recall $Z_{tx}=Y_{n_{x}\left(t\right),t}$ is the sum of
 the samples from alternative $x$ observed by stage $t$.
 
-The second one maps this time-changed random walk through a non-linear
+The second maps this time-changed random walk through a non-linear
 mapping for each $t,x$ and subset $A\subset\left\{ 1,\ldots,k\right\} $,
@@
 
-The third one maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
+The third maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
 onto selection decisions. Specifically, this mapping begins with $A_0 = \{1,\ldots,k\}$,
@@
 
+% Thus, we can see the selection decision resulting from BIZ as being closely app
+
 With these pieces in place, the last part of our proof is to observe that (1) $\mathcal{C}\left(\delta,\cdot\right)$
@@
 in continuous time; and (3) the BIZ procedure satisfies the IZ guarantee
-when applied in continuous time (Theorem~1 in \citeN{Frazier:BIZ}), and so $E[g(W)] \ge P^*$ with equality for the worst configurations in the preference zone.
+when applied in continuous time (Theorem~1 in \cite{Frazier:BIZ}), and so $E[g(W)] \ge P^*$ with equality for the worst configurations in the preference zone.
 
@@
 \begin{lemma}
+% For each $x\in\left\{ 1\ldots,k\right\} $, we define
+% \[
+% % \mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
+% \]
+% where $Y_{n,x}$ is the sum of the first $n$ samples from alternative
+$x$. 
 Let $x\in\left\{ 1\ldots,k\right\} $, then
@@
 
+% Observe that $\mathcal{C}\left(\delta,\cdot\right)\in D\left[0,\infty\right)^{k}$ and the convergence of Lemma 1 is in $D\left[0,\infty\right)^{k}$, consequently the following natural step is to generalize the continuous-time procedure for the heterogeneous variance setting, see Appendix B, to the space $D\left[0,\infty\right)^{k}$.
 To accomplish the first part, for each $F\in D\left[0,\infty\right)^{k}$, 
@@
 we get $q_{tx}\left(A\right)$ in \eqref{eq:q}.   
+% In this sense, 
+% we consider to be $q_{tx}^{F,\delta}\left(A\right)$ a ``non-centralized'' version of $F$.
 
@@
 More precisely, $f(F,\delta)$ is defined to be
+% Using the
+% continuous-time procedure for the heterogeneous variance setting with
+% the paths $\left(q_{tx}^{F,\delta}\left(A\right):t\geq0\right)$,
+% we see that there exists a selection decision for each $F\in D\left[0,\infty\right)^{k}$.
+% Since we are interested in the right selection, ( i.e. in choosing
+% $k$) for each $F\in D\left[0,\infty\right)^{k}$, we define the following
+% function 
 \begin{eqnarray*}
@@
 \end{eqnarray*}
+ % Observe that $f$ is a function that depends in the path $\left\{ q_{tx}^{F,\delta}\left(A\right):t\geq0\right\} $.
 
-We now construct a function $g(\cdot)$ that, when applied to the path of a $k$-dimensional standard Brownian motion, will be equal in distribution to the indicator of the correct selection event from the continuous-time BIZ procedure from \citeN{Frazier:BIZ}
+%We are doing all this because we want to see that $f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)$
+%looks like the right or wrong selection decision of an algorithm that
+%depends on a standard Brownian motion instead of $\mathcal{C}\left(\delta,\cdot\right)$,
+%and this will give us the proof because we will be able to use the
+%theory developed by Frazier (2014) to prove the theorem. Thus, the
+We now construct a function $g(\cdot)$ that, when applied to the path of a $k$-dimensional standard Brownian motion, will be equal in distribution to the indicator of the correct selection event from the continuous-time BIZ procedure from \cite{Frazier:BIZ}
+% to a problem with indifference-zone parameter equal to 1, where each alternative's observation process has volatility $\lambda_z$ and drift $a_x$.
 to a transformed problem that does not depend on $\delta$.
@@
 This path is
+% Going back to the proof outline, 
+% the next step is to find the limit of $q_{tx}^{F,\delta}\left(A\right)$
+% when $\delta$ goes to zero, which we denote $q_{tx}^{F}\left(A\right)$, 
+% and is equal to
 \[
@@
 Then, $g$ is defined to be
+ %Using the same previous idea, for each $F\in D\left[0,\infty\right)^{k}$,
+%we define the new functions
 \begin{eqnarray*}
@@
 
+% Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
+% we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero.
+Then we can use the continuous-time BIZ algorithm in the limit, i.e.
+we can use $\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
+% of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. The details may be found in the full version of this paper \cite{fullpaper}. 
 The following lemma shows that the difference in the correct selection events obtained from applying the BIZ selection map $h$ to the discrete-time and continuous-time versions of $q_{tx}(A)$ vanish as $\delta$ goes to $0$.
@@
 \begin{lemma}
+% If samples from system $x\in\left\{ 1\ldots,k\right\} $ are identically
+% distributed with finite variance and independent, over time and across alternatives, then
     $\lim_{\delta\rightarrow0} \mathbb{P}\left( h\left( \left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right) \right) =k\right) = \lim_{\delta\rightarrow0}
@@
 \end{theorem}
+
+%By the comments given at the beginning of this section, we know that
+%we can work with the algorithm, which we call the discrete-time BIZ algorithm, defined by
+
+%\[
+%q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
+%\]
+%where $t\in\delta^{2}\mathbb{N}$, instead of the algorithm defined
+%by
+%\[
+%q'_{tx}\left(A\right)=q'\left(\left(Z_{tx},t:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)
+%\]
+%where $t\in\mathbb{N}$.
+%
+%Now, we define
+%\begin{eqnarray*}
+%%\hat{\tau}_{n+1}\left(\delta\right) & = & \mbox{inf}\left\{ t\in\left\{ \tau_{n}\delta^{2},\left(\tau_{n}+1\right)\delta^{2},\ldots\right\} :\mbox{ min}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\geq P_{n}\right\}
+%\end{eqnarray*}
+% The corresponding BIZ algorithm is called the continuous-time BIZ algorithm. We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
+% which are defined as
+
+% Maybe some of this goes into the proof of the new lemma
+\[
+% \tau_{n+1}=\mbox{inf}\left\{ t\geq\tau_{n}:\mbox{ min}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{tx}\left(A_{n}\right)\geq P_{n}\right\} .
+\]
+
+% Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
+% we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero.
+Then we can use the continuous-time BIZ algorithm in the limit, i.e.
+we can use $\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
+% of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. The details may be found in the full version of this paper \cite{fullpaper}.
+
+% and allows us to use Theorem~5.5 of \citeN{billingsley:convergence}.
 
@@
 
-The random variable $g(W)$ is equal in distribution to the indicator of the event of correct selection that results from applying the continuous-time BIZ procedure from \citeN{Frazier:BIZ} in a problem with indifference-zone parameter equal to 1, where each alternative's observation process has volatility $\lambda_z$ and drift $a_x$.
+The random variable $g(W)$ is equal in distribution to the indicator of the event of correct selection that results from applying the continuous-time BIZ procedure from \cite{Frazier:BIZ} in a problem with indifference-zone parameter equal to 1, where each alternative's observation process has volatility $\lambda_z$ and drift $a_x$.
 This can be seen by noting that the path $(q^{W}_{tx}(A) : t\ge0)$ defined above is equal in distribution to the path $(q_{tx}(A) : t\ge0)$ defined in equation (2) of \citeN{Frazier:BIZ}, and that the selection decision of the continuous-time algorithm in \citeN{Frazier:BIZ} is obtained by applying $h$ to this path.
@@
 \section{NUMERICAL EXPERIMENTS}
-\label{numericalExperiments}
 
@@
 As $\delta$ goes to $0$, we observe that the PCS converges to $P^*$, as it did in the known-variance slippage configuration example.
-In this example, we have intentionally chosen $n_0$ to be smaller than the recommended value of 100, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
+In this example, we have intentionally chosen $n_0$ to be small, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
 Increasing the parameter $n_0$ typically causes BIZ to meet the IZ guarantee for all $\delta$, and we recommend a larger value of $n_0$ in practice.
-The choice of $n_0$, and its impact on PCS, merits further study.
 
@@
 \section{CONCLUSION}
-\label{conclusion}
 
-We have proved the asymptotic validity of the Bayes-inspired Indifference Zone
+We have proved the asymptotic validity of the Bayes-inspired Zone
 procedure \cite{Frazier:BIZ} when the variances are known.
-This algorithm has been observed empirically to take fewer samples than other IZ procedures, especially for
+This algorithm takes fewer samples than other IZ procedures, especially for
 problems with large numbers of alternatives, and so characterizing when it
@@
 it should be used in practice.
+
+% Even though this proof does not guarantee that the algorithm will satisfy the indifference-zone guarantee for configurations with large $\delta$, the theorem shows that it will work well when the alternatives are not very different, which are the most difficult cases.
 
@@
 \noindent {\bf PETER I.
-FRAZIER} is an Associate Professor of the School of Operations Research and Information Engineering at Cornell University, Ithaca, NY.
+FRAZIER} is an Assistant Professor of the School of Operations Research and Information Engineering at Cornell University, Ithaca, NY.
 He holds a Ph.D.

### 2015-07-07 paper/wish/wsc15paper.tex
final

@@
 
-This paper is organized as follows: In $\mathsection$\ref{IZR}, we recall the
-indifference-zone ranking and selection problem. In $\mathsection$\ref{sec:BIZ},
-we recall the Bayes-inspired IZ (BIZ) procedure from \citeN{Frazier:BIZ}. In $\mathsection$\ref{proof},
+This paper is organized as follows: In section \ref{IZR}, we recall the
+indifference-zone ranking and selection problem. In section \ref{sec:BIZ},
+we recall the Bayes-inspired IZ (BIZ) procedure from \citeN{Frazier:BIZ}. In section \ref{proof},
 we present the proof of the validity of the algorithm when the variances
-are known. In $\mathsection$\ref{numericalExperiments}, we present some numerical experiments. 
-In $\mathsection$\ref{conclusion}, we conclude.
+are known. In section \ref{numericalExperiments}, we present some numerical experiments. 
+In section \ref{conclusion}, we conclude.
 
